### 2023-08-09 oecd_data/weo_oecd_check_cpi.Rmd
oecd consistency checks

---
title: "WEO against OECD - CPI"
author: "Rike"
date: "2023-08-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.dim = c(11, 8))
library(here)
library(ggplot2)
library(data.table)
library(dplyr)
```

## WEO Truth data against OECD

```{r oecd, warning = FALSE}
oecd <- read.csv(here("oecd_data", "oecd_cpi.csv"))

oecd_q <- oecd |> 
  filter(FREQUENCY == "Q",
         SUBJECT == "TOT") |>
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
  rename(country = LOCATION,
         measure = MEASURE,
         yrq = TIME,
         value = Value) |>
  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
  filter(target_year >= 1989,
         quarter == 4,
         measure == "AGRWTH") |>
  select(-c(yrq, quarter)) |>
  rename(q4val = value,
         ccode = country) |>
  select(-measure)

oecd_y <- oecd |> 
  filter(FREQUENCY == "A",
         SUBJECT == "TOT") |>
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA"),
         MEASURE == "AGRWTH") |>
  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
  rename(country = LOCATION,
         measure = MEASURE,
         target_year = TIME,
         value = Value) |>
  mutate(target_year = as.numeric(target_year)) |>
  filter(target_year >= 1990) |>
  group_by(country) |>
  arrange(target_year,  .by_group = TRUE) |>
  rename(yearval = value,
         ccode = country) |>
  select(-measure)

weodat <- fread(here("WEOforecasts_tidy.csv"))

weodat_g7 <- weodat |>
  filter(horizon == 0.5,
         !is.na(tv_1),
         g7 == "G7",
         target == "pcpi_pch") |>
  rename(ccode = ISOAlpha_3Code) |>
  select(ccode, country, target_year, tv_1, tv_2) |>
  distinct() |>
  left_join(oecd_y, by = c("ccode", "target_year")) |>
  left_join(oecd_q, by = c("ccode", "target_year")) |>
  setDT() |>
  melt(id.vars = c("ccode", "country", "target_year"), 
       variable.name = "truth_type", 
       value.name = "truth_value") |>
  filter(truth_type != "q4val") |>
  mutate(truth_type = factor(truth_type, 
                             levels = c("tv_1", "tv_2", "yearval", "q4val"),
                             labels = c("WEO_1yr", "WEO_2yr", "OECD_annual", "OECD_q4q4")))

ltdict <- c("dashed", "solid", "solid", "dashed")
coldict <- RColorBrewer::brewer.pal(3, "Set2")[2:3] |> rep(each = 2)
names(ltdict) <- unique(weodat_g7$truth_type)
names(coldict) <- unique(weodat_g7$truth_type)

ggplot(weodat_g7, aes(x = target_year, y = truth_value)) +
  geom_line(aes(linetype = truth_type, color = truth_type)) +
  scale_color_manual(values = coldict) +
  scale_linetype_manual(values = ltdict) +
  facet_wrap(~country, ncol = 2) +
  theme_minimal() %+replace%
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  ylab("CPI Inflation") +
  xlab("Target Year")
```

### Deviations

Show deviations that are larger than 10% and have absolute deviations of at least 0.3 (to not give "undue attention" to large relative deviations around zero).
```{r pressure, echo=FALSE}
devtab <- weodat_g7 |>
  dcast(ccode + country + target_year ~ truth_type,
        value.var = "truth_value") |>
  select(country, target_year, WEO_2yr, OECD_annual) |>
  mutate(dev = WEO_2yr - OECD_annual,
         dev_pch = 100*(WEO_2yr - OECD_annual)/OECD_annual) |>
    filter(dev_pch > 10 | dev_pch < -10) |>
  filter(dev > 0.3 | dev < -0.3) |>
  mutate(dev = round(dev, 2),
         WEO_2yr = round(WEO_2yr, 2),
         OECD_annual = round(OECD_annual, 2),
         dev_pch = round(dev_pch, 2))
devtab 
```
Some points:

* `r round(100*nrow(devtab)/(nrow(weodat_g7)/4), 2)` % of country-year combinations are affected by 'large' deviations (as defined above) in the two truth data sources
* Deviations clearly affect some countries more than others
  + USA, UK, Canada are not affected at all
  + Germany and the UK are most affected
* Truth data overall seems to be very similar
* annual OECD data more in line with truth values in WEO data than the Q4Q4 OECD data
*

### 2023-08-09 oecd_data/weo_oecd_check_gdp.Rmd
oecd consistency checks

---
title: "WEO against OECD - GDP Growth"
author: "Rike"
date: "2023-08-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.dim = c(11, 8))
library(here)
library(ggplot2)
library(data.table)
library(dplyr)
```

## WEO Truth data against OECD

```{r oecd, warning = FALSE}
oecd <- read.csv(here("oecd_data", "oecd_gdp.csv"))

oecd_q <- oecd |> 
  filter(FREQUENCY == "Q",
         SUBJECT == "TOT") |>
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
  rename(country = LOCATION,
         measure = MEASURE,
         yrq = TIME,
         value = Value) |>
  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
  filter(target_year >= 1989,
         quarter == 4,
         measure == "PC_CHGPY") |> #PC_CHGPP refers to previous period, PC_CHGPY refers to same period previous year
  select(-c(yrq, quarter)) |>
  rename(q4val = value,
         ccode = country) |>
  select(-measure)

oecd_y <- oecd |> 
  filter(FREQUENCY == "A",
         SUBJECT == "TOT") |>
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
  rename(country = LOCATION,
         measure = MEASURE,
         target_year = TIME,
         value = Value) |>
  mutate(target_year = as.numeric(target_year)) |>
  filter(target_year >= 1990) |>
  group_by(country) |>
  arrange(target_year,  .by_group = TRUE) |>
  rename(yearval = value,
         ccode = country) |>
  select(-measure)

weodat <- fread(here("WEOforecasts_tidy.csv"))

weodat_g7 <- weodat |>
  filter(horizon == 0.5, #arbitrary choice, as true values simply duplicate for each horizon
         !is.na(tv_1),
         g7 == "G7",
         target == "ngdp_rpch") |>
  rename(ccode = ISOAlpha_3Code) |>
  select(ccode, country, target_year, tv_1, tv_2) |>
  distinct() |>
  left_join(oecd_y, by = c("ccode", "target_year")) |>
  left_join(oecd_q, by = c("ccode", "target_year")) |>
  setDT() |>
  melt(id.vars = c("ccode", "country", "target_year"), 
       variable.name = "truth_type", 
       value.name = "truth_value") |>
  filter(truth_type != "q4val") |>
  mutate(truth_type = factor(truth_type, 
                             levels = c("tv_1", "tv_2", "yearval", "q4val"),
                             labels = c("WEO_1yr", "WEO_2yr", "OECD_annual", "OECD_q4q4")))

ltdict <- c("dashed", "solid", "solid", "dashed")
coldict <- RColorBrewer::brewer.pal(3, "Set2")[2:3] |> rep(each = 2)
names(ltdict) <- unique(weodat_g7$truth_type)
names(coldict) <- unique(weodat_g7$truth_type)

ggplot(weodat_g7, aes(x = target_year, y = truth_value)) +
  geom_line(aes(linetype = truth_type, color = truth_type)) +
  scale_color_manual(values = coldict) +
  scale_linetype_manual(values = ltdict) +
  facet_wrap(~country, ncol = 2) +
  theme_minimal() %+replace%
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  ylab("CPI Inflation") +
  xlab("Target Year")
```

### Deviations
```{r pressure, echo=FALSE}
absval <- 0.3
devtab <- weodat_g7 |>
  dcast(ccode + country + target_year ~ truth_type,
        value.var = "truth_value") |>
  select(country, target_year, WEO_2yr, OECD_annual) |>
  mutate(dev = WEO_2yr - OECD_annual,
         dev_pch = 100*(WEO_2yr - OECD_annual)/OECD_annual) |>
    filter(dev_pch > 10 | dev_pch < -10) |>
  filter(dev > absval | dev < -absval) |>
  mutate(dev = round(dev, 2),
         WEO_2yr = round(WEO_2yr, 2),
         OECD_annual = round(OECD_annual, 2),
         dev_pch = round(dev_pch, 2))
``` 
Below we list all deviations that are larger than 10% and have absolute deviations of at least 0.3 (to not give "undue attention" to large relative deviations around zero).

Some points:

* `r round(100*nrow(devtab)/(nrow(weodat_g7)/3), 2)` % of country-year combinations are affected by 'large' deviations (as defined above) in the two truth data sources
* Deviations affect all countries similarly
* Truth data seems to be visually similar, but are rarely actually the same

```{r ctdevs, echo=FALSE}
devtab|> print(n = 120)
```

### 2023-08-09 oecd_data/check_gdp.R

@@ -1,0 +1,85 @@
+library(here)
+library(dplyr)
+library(data.table)
+library(ggplot2)
+DT <- `[`
+
+weodat <- data.table::fread(here("WEOforecasts_tidy.csv"))
+cpidat <-
+  data.table::fread(here("oecd_data", "oecd_cpi.csv")) |>
+  filter(FREQUENCY == "A",
+         SUBJECT == "TOT") |>
+ # filter(FREQUENCY == "Q", #quarterly
+#         SUBJECT == "TOT") |> #total CPI (others are e.g. food, engergy)
+  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
+  select(-c("INDICATOR", "SUBJECT", "FREQUENCY", "Flag Codes")) |> #redundant
+  rename(country = LOCATION,
+         measure = MEASURE,
+         target_year = TIME,
+         value = Value) |>
+  mutate(target_year = as.numeric(target_year)) |>
+  filter(target_year >= 1990,
+         measure == "AGRWTH") |>
+  rename(oecdval = value,
+         ccode = country) |>
+  select(-measure)
+
+
+weodat_g7 <- weodat |>
+  filter(horizon == 0.5,
+         !is.na(tv_1),
+         g7 == "G7",
+         target == "pcpi_pch") |>
+  rename(ccode = ISOAlpha_3Code) |>
+  select(ccode, country, target_year, tv_1, tv_2) |>
+  distinct() |>
+  left_join(cpidat, by = c("ccode", "target_year")) |>
+  setDT() |>
+  melt(id.vars = c("ccode", "country", "target_year"),
+       variable.name = "truth_type",
+       value.name = "truth_value") |>
+  mutate(
+    target_year = as.numeric(target_year),
+    truth_type = factor(truth_type,
+                             levels = c("tv_1", "tv_2", "oecdval"),
+                             labels = c("WEO_1yr", "WEO_2yr", "OECD_annual")))
+
+ltdict <- c("solid", "dashed", "solid", "dashed")
+coldict <- RColorBrewer::brewer.pal(3, "Set2")[2:3] |> rep(each = 2)
+names(ltdict) <- unique(weodat_g7$truth_type)
+names(coldict) <- unique(weodat_g7$truth_type)
+
+
+
+
+ggplot(weodat_g7, aes(x = target_year, y = truth_value)) +
[…]

### 2023-08-09 oecd_data/oecd_cpi_clean_quarterly.R

@@ -1,0 +1,26 @@
+library(here)
+library(ggplot2)
+library(data.table)
+library(dplyr)
+
+
+oecd <- read.csv(here("oecd_data", "oecd_cpi.csv"))
+
+oecd_q <- oecd |>
+  filter(FREQUENCY == "Q",
+         SUBJECT == "TOT") |>
+  #filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
+  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
+  rename(country = LOCATION,
+         measure = MEASURE,
+         yrq = TIME,
+         value = Value) |>
+  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
+         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
+  filter(target_year >= 1985,
+         measure == "IDX2015") |>
+  rename(ccode = country) |>
+  select(-c(yrq,measure))
+
+
+data.table::fwrite(oecd_q, here("oecd_data", "oecd_cpi_quarterly.csv"))

### 2023-08-09 oecd_data/oecd_gdp_clean_quarterly.R

@@ -1,0 +1,25 @@
+library(here)
+library(ggplot2)
+library(data.table)
+library(dplyr)
+
+oecd <- read.csv(here("oecd_data", "oecd_gdp.csv"))
+
+oecd_q <- oecd |>
+  filter(FREQUENCY == "Q",
+         SUBJECT == "TOT") |>
+  #filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
+  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
+  rename(country = LOCATION,
+         measure = MEASURE,
+         yrq = TIME,
+         value = Value) |>
+  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
+         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
+  filter(target_year >= 1985,
+         measure == "PC_CHGPP") |> #PC_CHGPP refers to previous period, PC_CHGPY refers to same period previous year
+  rename(ccode = country) |>
+  select(-c(measure, yrq))
+
+
+data.table::fwrite(oecd_q, here("oecd_data", "oecd_gdp_quarterly.csv"))

### 2023-08-22 oecd_data/oecd_cpi_clean_quarterly.R
change data source. extend target_year, keep annual+quarterly, prv_year+ prv_period

@@ -4,38 +4,25 @@ library(data.table)
 library(dplyr)
 
 
-oecd <- read.csv(here("oecd_data", "oecd_cpi.csv"))
-
-oecd_q <- oecd |>
-  filter(FREQUENCY == "Q",
-         SUBJECT == "TOT") |>
-  #filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
-  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
-  rename(country = LOCATION,
+oecd <- read.csv(here("oecd_data", "oecd_cpi_quarter.csv")) |>
+  filter(Subject == "CPI: 01-12 - All items",
+         MEASURE %in% c("GY", "GP")) |>
+  select(-c(Measure, SUBJECT, Subject)) |>
+  select(LOCATION, Country, MEASURE, TIME, Unit, Value) |>
+  rename(ccode = LOCATION,
+         country = Country,
          measure = MEASURE,
          yrq = TIME,
          value = Value) |>
   mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
          quarter = substr(yrq, 7, 7) |> as.numeric()) |>
-  filter(target_year >= 1980) |>
+  mutate(quarter = ifelse(is.na(quarter), "Y", quarter)) |>
   select(-yrq) |>
-  rename(ccode = country)
-
-
-oecd_y <- oecd |>
-  filter(FREQUENCY == "A",
-         SUBJECT == "TOT") |>
-  #filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
-  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
-  rename(country = LOCATION,
-         measure = MEASURE,
-         value = Value,
-         target_year = TIME) |>
-  mutate(quarter = "Y") |>
-  rename(ccode = country)
-
-
-oecd <- rbind(oecd_q, oecd_y)
-
+  mutate(type = ifelse(measure == "GY", "prv_year", "prv_period")) |>
+  mutate(kick = ifelse(type == "prv_year" & quarter == "Y", 1, 0)) |> #redundant
+  filter(kick == 0) |>
+  select(-kick) |>
+  select(-c(Unit, measure)) |> #redundant
+  arrange(ccode)
 
 data.table::fwrite(oecd, here("oecd_data", "oecd_cpi_quarterly_annual.csv"))

### 2023-08-22 oecd_data/oecd_cpi_clean_quarterly_new.R
previous script for new data source

@@ -1,0 +1,28 @@
+library(here)
+library(ggplot2)
+library(data.table)
+library(dplyr)
+
+
+oecd <- read.csv(here("oecd_data", "oecd_cpi_quarter.csv")) |>
+  filter(Subject == "CPI: 01-12 - All items",
+         MEASURE %in% c("GY", "GP")) |>
+  select(-c(Measure, SUBJECT, Subject)) |>
+  select(LOCATION, Country, MEASURE, TIME, Unit, Value) |>
+  rename(ccode = LOCATION,
+         country = Country,
+         measure = MEASURE,
+         yrq = TIME,
+         value = Value) |>
+  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
+         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
+  mutate(quarter = ifelse(is.na(quarter), "Y", quarter)) |>
+  select(-yrq) |>
+  mutate(type = ifelse(measure == "GY", "prv_year", "prv_period")) |>
+  mutate(kick = ifelse(type == "prv_year" & quarter == "Y", 1, 0)) |> #redundant
+  filter(kick == 0) |>
+  select(-kick) |>
+  select(-c(Unit, measure)) |> #redundant
+  arrange(ccode)
+
+data.table::fwrite(oecd, here("oecd_data", "oecd_cpi_quarterly_annual.csv"))

### 2023-08-22 oecd_data/oecd_cpi_clean_quarterly_new.R
remove previous script for new cpi data source

@@ -1,28 +1,0 @@
-library(here)
-library(ggplot2)
-library(data.table)
-library(dplyr)
-
-
-oecd <- read.csv(here("oecd_data", "oecd_cpi_quarter.csv")) |>
-  filter(Subject == "CPI: 01-12 - All items",
-         MEASURE %in% c("GY", "GP")) |>
-  select(-c(Measure, SUBJECT, Subject)) |>
-  select(LOCATION, Country, MEASURE, TIME, Unit, Value) |>
-  rename(ccode = LOCATION,
-         country = Country,
-         measure = MEASURE,
-         yrq = TIME,
-         value = Value) |>
-  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
-         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
-  mutate(quarter = ifelse(is.na(quarter), "Y", quarter)) |>
-  select(-yrq) |>
-  mutate(type = ifelse(measure == "GY", "prv_year", "prv_period")) |>
-  mutate(kick = ifelse(type == "prv_year" & quarter == "Y", 1, 0)) |> #redundant
-  filter(kick == 0) |>
-  select(-kick) |>
-  select(-c(Unit, measure)) |> #redundant
-  arrange(ccode)
-
-data.table::fwrite(oecd, here("oecd_data", "oecd_cpi_quarterly_annual.csv"))

### 2023-08-22 oecd_data/weo_oecd_check_cpi.Rmd
check cpi values after changing data source

@@
 ```{r oecd, warning = FALSE}
-oecd <- read.csv(here("oecd_data", "oecd_cpi.csv"))
+oecd <- read.csv(here("oecd_data", "oecd_cpi_quarter.csv"))
 
-oecd_q <- oecd |> 
-  filter(FREQUENCY == "Q",
-         SUBJECT == "TOT") |>
-  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
-  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
-  rename(country = LOCATION,
+oecd_y <- read.csv(here("oecd_data", "oecd_cpi_quarter.csv")) |>
+  filter(Subject == "CPI: 01-12 - All items",
+         MEASURE %in% c("GP")) |>
+  select(-c(Measure, SUBJECT, Subject)) |>
+  select(LOCATION, MEASURE, TIME, Unit, Value) |>
+  rename(ccode = LOCATION,
          measure = MEASURE,
@@
          quarter = substr(yrq, 7, 7) |> as.numeric()) |>
-  filter(target_year >= 1989,
-         quarter == 4,
-         measure == "AGRWTH") |>
-  select(-c(yrq, quarter)) |>
-  rename(q4val = value,
-         ccode = country) |>
-  select(-measure)
-
-oecd_y <- oecd |> 
-  filter(FREQUENCY == "A",
-         SUBJECT == "TOT") |>
-  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA"),
-         MEASURE == "AGRWTH") |>
-  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
-  rename(country = LOCATION,
-         measure = MEASURE,
-         target_year = TIME,
-         value = Value) |>
-  mutate(target_year = as.numeric(target_year)) |>
-  filter(target_year >= 1990) |>
-  group_by(country) |>
-  arrange(target_year,  .by_group = TRUE) |>
-  rename(yearval = value,
-         ccode = country) |>
-  select(-measure)
+  mutate(quarter = ifelse(is.na(quarter), "Y", quarter)) |>
+  select(-yrq) |>
+  filter(ccode %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
+  filter(quarter == "Y") |>
+  select(-quarter) |>
+  rename(yearval = value)
 
@@
          !is.na(tv_1),
-         g7 == "G7",
+         g7 == 1,
          target == "pcpi_pch") |>
@@
   left_join(oecd_y, by = c("ccode", "target_year")) |>
-  left_join(oecd_q, by = c("ccode", "target_year")) |>
+  #left_join(oecd_q, by = c("ccode", "target_year")) |>
   setDT() |>
+  select(c(ccode, country, target_year, tv_1, tv_2, yearval)) |>
   melt(id.vars = c("ccode", "country", "target_year"), 

### 2023-08-25 benchmarks/ar_forecast.R
benchmark files

@@ -1,0 +1,126 @@
+rm(list = ls())
+setwd("/home/fabian/Schreibtisch/notes_and_ideas/IMF/")
+
+library(dplyr)
+library(zoo)
+library(bvarsv)
+library(tidyr)
+
+# setting 
+g7_oecd <- c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")
+vnms_oecd <- c("cpi", "gdp")
+weights <- c(1:4, 3:1)/4
+yrs_fcst <- 1989:2021
+
+# data frame holding all settings to be run
+all_settings <- data.frame(country = rep(g7_oecd, each = 2), 
+                           season = rep(c("S", "F"), 7))
+
+# get iteration (job id)
+#iter <- as.integer(as.character(Sys.getenv("SLURM_ARRAY_TASK_ID")))
+#iter <- 1
+iter <- 14
+
+cc <- all_settings$country[iter]
+fcst_season <- all_settings$season[iter]
+
+# load cpi data, transform date
+cpi0 <- read.csv("oecd_cpi_quarterly_new.csv") 
+cpi_q <- cpi0 %>%
+  transmute(ccode, y = value, 
+            dt = as.yearqtr(date)) %>%
+  na.omit 
+gdp0 <- read.csv("oecd_gdp_quarterly_annual.csv") 
+gdp_q <- gdp0 %>% 
+  filter(ccode %in% g7_oecd, quarter %in% 1:4, type == "prv_period") %>% 
+  transmute(ccode, dt = as.yearqtr(paste0(target_year, "Q", quarter)), 
+            y = value)
+# Put both into one data frame
+oecd_q <- rbind(data.frame(cpi_q, target = "cpi"), 
+                data.frame(gdp_q, target = "gdp")) %>%
+  pivot_wider(names_from = "target", values_from = "y") %>%
+  na.omit
+
+# initialize data frame
+df_all <- data.frame()
+
+# loop over forecast years
+for (yy in yrs_fcst){
+  
+  # identify latest data
+  if (fcst_season == "S"){
+    last_q <- yy # up until Q1 of forecast year
+  } else {
+    last_q <- yy + .5 # up until Q3 of forecast year
+  }
+  
+  # filter data accordingly
+  dat0 <- oecd_q %>% filter(ccode == cc, dt <= last_q) %>%
+    arrange(dt) %>% select(dt, cpi, gdp) 
+  
+  # data checks
[…]

### 2023-08-25 benchmarks/bvar_forecast_cluster.R

@@ -1,0 +1,121 @@
+rm(list = ls())
+#setwd("/home/fabian/Schreibtisch/notes_and_ideas/IMF/")
+
+library(dplyr)
+library(zoo)
+library(bvarsv)
+library(tidyr)
+
+# setting 
+g7_oecd <- c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")
+vnms_oecd <- c("cpi", "gdp")
+weights <- c(1:4, 3:1)/4
+yrs_fcst <- 1989:2021
+
+# data frame holding all settings to be run
+all_settings <- data.frame(country = rep(g7_oecd, each = 2), 
+                           season = rep(c("S", "F"), 7))
+
+# get iteration (job id)
+iter <- as.integer(as.character(Sys.getenv("SLURM_ARRAY_TASK_ID")))
+iter <- 1
+
+# set random seed
+set.seed(iter)
+
+cc <- all_settings$country[iter]
+fcst_season <- all_settings$season[iter]
+
+# load cpi data, transform date
+cpi0 <- read.csv("oecd_cpi_quarterly_new.csv") 
+cpi_q <- cpi0 %>%
+  transmute(ccode, y = value, 
+            dt = as.yearqtr(date)) %>%
+  na.omit 
+gdp0 <- read.csv("oecd_gdp_quarterly_annual.csv") 
+gdp_q <- gdp0 %>% 
+  filter(ccode %in% g7_oecd, quarter %in% 1:4, type == "prv_period") %>% 
+  transmute(ccode, dt = as.yearqtr(paste0(target_year, "Q", quarter)), 
+            y = value)
+# Put both into one data frame
+oecd_q <- rbind(data.frame(cpi_q, target = "cpi"), 
+                data.frame(gdp_q, target = "gdp")) %>%
+  pivot_wider(names_from = "target", values_from = "y") %>%
+  na.omit %>% filter(dt >= 1962)
+
+# initialize data frame
+df_all <- data.frame()
+
+# loop over forecast years
+for (yy in yrs_fcst){
+  
+  # identify latest data
+  if (fcst_season == "S"){
+    last_q <- yy # up until Q1 of forecast year
+  } else {
+    last_q <- yy + .5 # up until Q3 of forecast year
+  }
+  
+  # filter data accordingly
+  dat0 <- oecd_q %>% filter(ccode == cc, dt <= last_q) %>%
[…]

### 2023-08-25 benchmarks/compare_bvar_imf.R

@@ -1,0 +1,122 @@
+rm(list = ls())
+setwd("/home/fabian/Schreibtisch/notes_and_ideas/IMF/")
+
+library(dplyr)
+library(zoo)
+library(bvarsv)
+library(tidyr)
+library(ggplot2)
+
+# labeling stuff
+g7_oecd <- c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")
+g7_imf <- c("Canada", "France", "Germany", "Italy", "Japan", 
+            "United Kingdom", "United States")
+vnms_oecd <- c("cpi", "gdp")
+vnms_imf <- c("pcpi_pch", "ngdp_rpch")
+
+# collect forecast files (BVAR and AR in separate directories)
+df_all <- data.frame()
+for (gg in c("fcsts", "fcsts_ar")){
+  fc <- list.files(gg)
+  for (ii in fc){
+    tmp <- read.csv(paste0(gg, "/", ii)) %>%
+      mutate(method = gg)
+    df_all <- rbind(df_all, 
+                    data.frame(tmp, 
+                               country = substr(ii, 6, 8), 
+                               season = substr(ii, 10, 10)))
+  }
+}
+
+# compare BVAR and AR to WEO forecasts
+weo0 <- read.csv("WEOforecasts_tidy.csv", sep = ",")
+weo <- weo0 %>%
+  filter(country %in% g7_imf) %>%
+  select(country, target, forecast_year, target_year, 
+         prediction, forecast_season, tv_1) %>%
+  transmute(country = g7_oecd[match(country, g7_imf)], 
+            var = vnms_oecd[match(target, vnms_imf)], 
+            forecast_year, target_year, season = forecast_season, 
+            value_imf = prediction, 
+            truth = tv_1) %>%
+  filter(target_year <= (forecast_year + 1))
+
+# Loop over countries
+for (cc in g7_oecd){
+  # merge time series and imf forecasts
+  tmp1 <- df_all %>% filter(country == cc) %>%
+    pivot_wider(id_cols = c("var", "forecast_year", 
+                            "target_year", "season"), 
+                names_from = "method") %>%
+    rename(value = fcsts, value_ar = fcsts_ar)
+  tmp2 <- weo %>% filter(country == cc)
+  tmp3 <- merge(tmp1, tmp2) %>%
+    mutate(horizon = 2*(target_year - forecast_year) + 
+             as.numeric(season == "S") + 1) %>%
[…]

### 2023-08-25 benchmarks/prepare_CPI.R

@@ -1,0 +1,49 @@
+rm(list = ls())
+
+library(dplyr)
+library(tidyr)
+library(zoo)
+library(ggplot2)
+
+g7_oecd <- c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")
+
+setwd("/home/fabian/Schreibtisch/notes_and_ideas/IMF/")
+
+# rename variables, compute growth rates from CPI level
+dat <- read.csv("DP_LIVE_21082023090139698.csv") %>%
+  filter(LOCATION %in% g7_oecd) %>%
+  transmute(ccode = LOCATION, 
+            date = as.yearqtr(gsub("-", "", TIME)), 
+            value = Value) %>%
+  group_by(ccode) %>% arrange(date) %>%
+  mutate(value = c(NA, 100*diff(log(value)))) %>%
+  na.omit %>% filter(date >= 1960)
+
+# compare to previous download
+comp <- read.csv("oecd_cpi_quarterly_annual.csv") %>%
+  filter(ccode %in% g7_oecd, quarter %in% 1:4, 
+         type == "prv_period") %>%
+  transmute(ccode, value_comp = value, 
+            date = as.yearqtr(paste0(target_year, "Q", quarter)))
+
+both <- full_join(dat, comp) 
+
+# summary stats on discrepancies
+both %>% na.omit %>% group_by(ccode) %>% 
+  summarise(cor = cor(value, value_comp), 
+            mae = mean(abs(value-value_comp))) %>%
+  ungroup
+
+# plot
+both %>% pivot_longer(cols = contains("value")) %>% 
+  filter(ccode == "CAN") %>%
+  ggplot(aes(x = date, y = value, color = name)) + 
+  geom_point() + geom_line() + 
+  theme_minimal() + 
+  theme(legend.position = "top") + 
+  scale_color_discrete(name = "", 
+                       breaks = c("value", "value_comp"), 
+                       labels = c("new", "old"))
+
+# write data
+write.csv(dat, "oecd_cpi_quarterly_new.csv", row.names = FALSE)

### 2023-08-25 manuscript/manuscript.Rmd
manuscript template

---
title: "Compare forecats"
header-includes:
    - \usepackage{lineno}
    - \linenumbers
    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
    toc: false
linestretch: 2 
bibliography:
  - references.bib
csl: vancouver.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-08-25 manuscript/manuscript.tex
manuscript template

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
\linenumbers
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{float}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Compare forecats},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Compare forecats}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\setstretch{2}
\hypertarget{r-markdown}{%
\subsection{R Markdown}\label{r-markdown}}

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see \url{http://rmarkdown.rstudio.com}.

When you click the \textbf{Knit} button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(cars)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      speed           dist       
##  Min.   : 4.0   Min.   :  2.00  
##  1st Qu.:12.0   1st Qu.: 26.00  
##  Median :15.0   Median : 36.00  
##  Mean   :15.4   Mean   : 42.98  
##  3rd Qu.:19.0   3rd Qu.: 56.00  
##  Max.   :25.0   Max.   :120.00
\end{verbatim}

\hypertarget{including-plots}{%
\subsection{Including Plots}\label{including-plots}}

You can also embed plots, for example:

\includegraphics{manuscript_files/figure-latex/pressure-1.pdf}

Note that the \texttt{echo\ =\ FALSE} parameter was added to the code chunk to prevent printing of the R code that generated the plot.

\end{document}

### 2023-09-06 scripts/score-forecasts.R
average scores by country

@@ -73,6 +73,12 @@ weodat_qu <- qufcs |>
 scores <- scoreempQu(weodat_qu, cvg_rg = c(50,80),
                      by = c("model", "error_method", "method", "country", "target", "horizon"))
 
+scores_avgcountry <- scoreempQu(weodat_qu, cvg_rg = c(50,80),
+                     by = c("model", "error_method", "method", "target", "horizon"))
+
+scores_cvgshort <- scoreempQu(weodat_qu, cvg_rg = c(50,80),
+                     by = c("model", "error_method", "method", "target"))
+
 
 weodat_samples <- fcdat |>
   .d(horizon < 2) |>
@@ -108,8 +114,12 @@ all_crps <- lapply(1:nrow(combs_methods), function(idx){
 
   }
 ) |>
-  rbindlist()
+  rbindlist() |>
+  .d(, .(score = mean(score)), by = c("target", "horizon", "method", "error_method", "source"))
 
 
 data.table::fwrite(scores, here("quantile_forecasts", "ci_scores.csv"))
 data.table::fwrite(all_crps, here("quantile_forecasts", "sample_scores.csv"))
+data.table::fwrite(scores_cvgshort, here("quantile_forecasts", "cvg_pooled.csv"))
+data.table::fwrite(scores_avgcountry, here("quantile_forecasts", "ci_scores_avgcnt.csv"))
+

### 2023-09-06 shiny/app.R
change default

@@ -63,7 +63,7 @@ ui <- fluidPage(
 
       radioButtons(inputId = "trueval",
                    choices = c("0.5", "1", "1.5", "2"),
-                   selected = "0.5",
+                   selected = "1",
                    label = "True Value release"),
 
       radioButtons(inputId = "zoomin",

### 2023-09-06 R/uqfc.R
comments

@@ -144,6 +144,10 @@ empFC <- function(weodat,
       .d(, target_year := target_year)
 
     if(error_method == "absolute"){
+      #with absolute errors, the extracted quantile must be transformed:
+      #e.g. when extracting a 50% quantile from the absolute errors, this value
+      #must be added on to the prediction to get the 75% quantile and subtracted
+      #from the prediction to get the 25% quantile
 
       quSet_pos <- quSet |>
         data.table::copy() |>

### 2023-09-06 R/utils.R

@@ -94,7 +94,8 @@ theme_uqimf <- function() {
           axis.ticks = element_line(colour = "grey80"),
           panel.border = element_blank(),
           panel.background = element_blank(),
-          legend.position = "bottom")
+          legend.position = "bottom",
+          legend.title=element_blank())
 }
 
 

### 2023-09-06 manuscript/manuscript.Rmd
visualize scores and coverage

@@
 ---
-title: "Compare forecats"
+title: "IMF and Benchmark Forecasts"
 header-includes:
@@
 ```{r setup, include=FALSE}
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+library(MetBrewer)
+library(purrr)
+library(lattice)
+library(gt)
+library(rlang)
+library(tidyverse)
+devtools::load_all()
 knitr::opts_chunk$set(echo = TRUE)
+.d <- `[`
 ```
 
-## R Markdown
+# A short note on error handling
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+In almost all 72 cases, absolute error handling gives lower scores than directional error handling.
+The only exception is the inflation series for the IMF forecasts and horizon 0, where the expanding window and rolling window method give \textit{slightly} lower scores for the directional methodology.
+We thus decide to focus on the absolute errors in this document.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+# Scores, by estimation method, Horizon and forecast source 
+```{r, echo = FALSE}
+scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
 
-```{r cars}
-summary(cars)
+wis_scores <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  setnames("model", "source")
+
+crps_scores <- fread(here("quantile_forecasts", "sample_scores.csv"))
+
+all_scores <- 
+  crps_scores[wis_scores, on = c("source", "error_method", "method", "target", "horizon")]|>
+  .d(error_method == "absolute") |>
+  .d(, error_method := NULL)
+
+gather_scores <- all_scores |>
+  data.table::copy() |>
+  .d(target == "pcpi_pch") |>
+  .d(,target := NULL) |>
+  .d(, .(horizon, method, source, score, interval_score)) |>
+  setnames("score", "sample_crps") |>
+  melt(id.vars = c("horizon", "method", "source"), variable.name = "score_type", value.name = "score") |>
+  .d(, combms := paste0(method,"_", score_type)) |>
+  .d(, .(horizon, source, combms, score)) |>
+  .d(, horizon := paste0("horizon = ", horizon)) |>
+  .d(, score := round(score, 3)) |>
+  dcast(horizon + combms ~ source, value.var = "score")
+
+gather_scores |>
+  data.table::copy() |>
+  gt(rowname_col = "combms", groupname_col = "horizon") |>
+  cols_label(
+      IMF = "IMF",
+      ar = "ar",
+      bvar = "bvar"
+    )
+
+col_names <- c("IMF", "ar", "bvar")
+
 ```
 
-## Including Plots
+## Inflation
 
-You can also embed plots, for example:
+```{r, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+plots_is <- vector(mode = "list", length = 4)
+plots_cr <- vector(mode = "list", length = 4)
+
+for(i in 1:4){
+
+  hor <- (i-1)*0.5
+
+  mydat <- gather_scores |>
+    .d(horizon == paste0("horizon = ", hor)) |>
+  .d(grep("interval", combms)) |>
+  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score") |>
+  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))
+
+  plots_is[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
+  geom_tile(aes(fill = score)) +
+    guides(fill = FALSE) +
+    ggtitle(paste0("horizon = ", hor, " - Weighted Interval Score"))
+}
+
+for(i in 1:4){
+
+  hor <- (i-1)*0.5
+
+  mydat <- gather_scores |>
+    .d(horizon == paste0("horizon = ", hor)) |>
+  .d(grep("crps", combms)) |>
+  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score")|>
+  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))
+
+  plots_cr[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
+  geom_tile(aes(fill = score))+
+    guides(fill = FALSE)+
+    ggtitle(paste0("horizon = ", hor, " - CRPS by sample"))
+}
+
+ovr_plot <- 
+  (plots_is[[1]] + plots_cr[[1]]) /
+  (plots_is[[2]] + plots_cr[[2]]) /
+  (plots_is[[3]] + plots_cr[[3]]) /
+  (plots_is[[4]] + plots_cr[[4]]) +
+  plot_layout(heights = c(1, 1,1,1)) &
+    plot_annotation(tag_levels = 'I')  &
+    theme(legend.position = 'right', 
+          legend.box="vertical", legend.margin=margin())
+
+ovr_plot
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r cvgdat2, include=FALSE, echo = FALSE}
+
+scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
+scores_cvgshort <- fread(here("quantile_forecasts", "cvg_pooled.csv"))
+
+cvg_rg <- c(50, 80)
+
+cols <- paste0("coverage_", cvg_rg)
+
+large_cvgdat <- scores |>
+  setnames("model", "source") |>
+  .d(, c("country", "horizon", "target", "error_method", "method", "source", cols), with = FALSE) |>
+  melt(id.vars = c("country", "horizon", "target", "error_method", "method", "source"),
+       variable.name = "pilvl",
+       value.name = "coverage") |>
+  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
+  .d(, pilvl := as.numeric(pilvl)/100) |>
+  .d(, idcol := paste0(horizon, country, method)) |>
+  .d(, country := NULL) |>
+  .d(, horizon := NULL)
+
+cvgdat <- scores_cvgshort |>
+  setnames("model", "source") |>
+  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
+  melt(id.vars = c("target", "error_method", "method", "source"),
+       variable.name = "pilvl",
+       value.name = "coverage") |>
+  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
+  .d(, pilvl := as.numeric(pilvl)/100)
+
+cvgdat_cpi <- cvgdat |>
+  .d(target == "pcpi_pch")
+
+cvgdat_gdp <- cvgdat |>
+  .d(target == "ngdp_rpch")
+
+plot_cpi <- ggplot() +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                group = idcol),
+            data = large_cvgdat |> .d(target == "pcpi_pch"),
+            alpha = 0.4,
+            color = "gray") +
+  geom_point(aes(x = pilvl,
+                 y = coverage,
+                 color = method),
+             data = cvgdat_cpi,
+             size = 3) +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                color = method),
+            data = cvgdat_cpi,
+            lwd = 1.25) +
+  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
+               color = "black",
+               linetype = "dashed",
+               data = cvgdat_cpi) +
+  #scale_color_brewer(palette = "Set1") +
+  facet_grid(source ~ error_method)+
+
+  ggtitle("Inflation") +
+
+  scale_color_met_d("Hokusai1") +
+
+  ylab("Empirical Coverage Level (Central PI)") +
+  xlab("Nominal Coverage (Central PI)") +
+  theme_uqimf()
+
+plot_gdp <- ggplot() +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                group = idcol),
+            data = large_cvgdat |> .d(target == "ngdp_rpch"),
+            alpha = 0.4,
+            color = "gray") +
+  geom_point(aes(x = pilvl,
+                 y = coverage,
+                 color = method),
+             data = cvgdat_gdp,
+             size = 3) +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                color = method),
+            data = cvgdat_gdp,
+            lwd = 1.25) +
+  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
+               color = "black",
+               linetype = "dashed",
+               data = cvgdat_gdp) +
+  #scale_color_brewer(palette = "Set1") +
+  facet_grid(source ~ error_method)+
+
+  ggtitle("Real GDP Growth") +
+
+  scale_color_met_d("Hokusai1") +
+
+  ylab("Empirical Coverage Level (Central PI)") +
+  xlab("Nominal Coverage (Central PI)") +
+  theme_uqimf()
+
+```
+
+## GDP
+
+```{r hey3, echo = FALSE}
+scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
+
+wis_scores <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  setnames("model", "source")
+
+crps_scores <- fread(here("quantile_forecasts", "sample_scores.csv"))
+
+all_scores <- 
+  crps_scores[wis_scores, on = c("source", "error_method", "method", "target", "horizon")]|>
+  .d(error_method == "absolute") |>
+  .d(, error_method := NULL)
+
+gather_scores <- all_scores |>
+  data.table::copy() |>
+  .d(target == "ngdp_rpch") |>
+  .d(,target := NULL) |>
+  .d(, .(horizon, method, source, score, interval_score)) |>
+  setnames("score", "sample_crps") |>
+  melt(id.vars = c("horizon", "method", "source"), variable.name = "score_type", value.name = "score") |>
+  .d(, combms := paste0(method,"_", score_type)) |>
+  .d(, .(horizon, source, combms, score)) |>
+  .d(, horizon := paste0("horizon = ", horizon)) |>
+  .d(, score := round(score, 3)) |>
+  dcast(horizon + combms ~ source, value.var = "score")
+
+gather_scores |>
+  data.table::copy() |>
+  gt(rowname_col = "combms", groupname_col = "horizon") |>
+  cols_label(
+      IMF = "IMF",
+      ar = "ar",
+      bvar = "bvar"
+    )
+
+col_names <- c("IMF", "ar", "bvar")
+
+```
+
+```{r, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
+
+plots_is <- vector(mode = "list", length = 4)
+plots_cr <- vector(mode = "list", length = 4)
+
+for(i in 1:4){
+
+  hor <- (i-1)*0.5
+
+  mydat <- gather_scores |>
+    .d(horizon == paste0("horizon = ", hor)) |>
+  .d(grep("interval", combms)) |>
+  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score") |>
+  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))
+
+  plots_is[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
+  geom_tile(aes(fill = score)) +
+    guides(fill = FALSE) +
+    ggtitle(paste0("horizon = ", hor, " - Weighted Interval Score"))
+}
+
+for(i in 1:4){
+
+  hor <- (i-1)*0.5
+
+  mydat <- gather_scores |>
+    .d(horizon == paste0("horizon = ", hor)) |>
+  .d(grep("crps", combms)) |>
+  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score")|>
+  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))
+
+  plots_cr[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
+  geom_tile(aes(fill = score))+
+    guides(fill = FALSE)+
+    ggtitle(paste0("horizon = ", hor, " - CRPS by sample"))
+}
+
+ovr_plot <- 
+  (plots_is[[1]] + plots_cr[[1]]) /
+  (plots_is[[2]] + plots_cr[[2]]) /
+  (plots_is[[3]] + plots_cr[[3]]) /
+  (plots_is[[4]] + plots_cr[[4]]) +
+  plot_layout(heights = c(1, 1,1,1)) &
+    plot_annotation(tag_levels = 'I')  &
+    theme(legend.position = 'right', 
+          legend.box="vertical", legend.margin=margin())
+
+ovr_plot
+
+```
+
+```{r cvgdat, include=FALSE, echo = FALSE}
+
+scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
+scores_cvgshort <- fread(here("quantile_forecasts", "cvg_pooled.csv"))
+
+cvg_rg <- c(50, 80)
+
+cols <- paste0("coverage_", cvg_rg)
+
+large_cvgdat <- scores |>
+  setnames("model", "source") |>
+  .d(, c("country", "horizon", "target", "error_method", "method", "source", cols), with = FALSE) |>
+  melt(id.vars = c("country", "horizon", "target", "error_method", "method", "source"),
+       variable.name = "pilvl",
+       value.name = "coverage") |>
+  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
+  .d(, pilvl := as.numeric(pilvl)/100) |>
+  .d(, idcol := paste0(horizon, country, method)) |>
+  .d(, country := NULL) |>
+  .d(, horizon := NULL)
+
+cvgdat <- scores_cvgshort |>
+  setnames("model", "source") |>
+  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
+  melt(id.vars = c("target", "error_method", "method", "source"),
+       variable.name = "pilvl",
+       value.name = "coverage") |>
+  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
+  .d(, pilvl := as.numeric(pilvl)/100)
+
+cvgdat_cpi <- cvgdat |>
+  .d(target == "pcpi_pch")
+
+cvgdat_gdp <- cvgdat |>
+  .d(target == "ngdp_rpch")
+
+plot_cpi <- ggplot() +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                group = idcol),
+            data = large_cvgdat |> .d(target == "pcpi_pch"),
+            alpha = 0.4,
+            color = "gray") +
+  geom_point(aes(x = pilvl,
+                 y = coverage,
+                 color = method),
+             data = cvgdat_cpi,
+             size = 3) +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                color = method),
+            data = cvgdat_cpi,
+            lwd = 1.25) +
+  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
+               color = "black",
+               linetype = "dashed",
+               data = cvgdat_cpi) +
+  #scale_color_brewer(palette = "Set1") +
+  facet_grid(source ~ error_method)+
+
+  ggtitle("Inflation") +
+
+  scale_color_met_d("Hokusai1") +
+
+  ylab("Empirical Coverage Level (Central PI)") +
+  xlab("Nominal Coverage (Central PI)") +
+  theme_uqimf()
+
+plot_gdp <- ggplot() +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                group = idcol),
+            data = large_cvgdat |> .d(target == "ngdp_rpch"),
+            alpha = 0.4,
+            color = "gray") +
+  geom_point(aes(x = pilvl,
+                 y = coverage,
+                 color = method),
+             data = cvgdat_gdp,
+             size = 3) +
+  geom_line(aes(x = pilvl,
+                y = coverage,
+                color = method),
+            data = cvgdat_gdp,
+            lwd = 1.25) +
+  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
+               color = "black",
+               linetype = "dashed",
+               data = cvgdat_gdp) +
+  #scale_color_brewer(palette = "Set1") +
+  facet_grid(source ~ error_method)+
+
+  ggtitle("Real GDP Growth") +
+
+  scale_color_met_d("Hokusai1") +
+
+  ylab("Empirical Coverage Level (Central PI)") +
+  xlab("Nominal Coverage (Central PI)") +
+  theme_uqimf()
+
+```
+
+# Coverage, by target, methods and source
+
+```{r cvgplot, fig.dim = c(10, 12), echo = FALSE}
+
+ovr_plot <- 
+  (plot_gdp) /
+  (plot_cpi) +
+  plot_layout(guides = "collect", 
+              heights = c(1, 1)) &
+    plot_annotation(tag_levels = 'I')  &
+    theme(legend.position = 'bottom', 
+          legend.box="vertical", legend.margin=margin())
+
+ovr_plot
+
+```
+
+```{r loaddata, include = FALSE, echo = FALSE}
+
+sub_weodat <- 
+   data.table::fread(here("WEOforecasts_tidy.csv")) |>
+      .d(g7 == 1,) |>
+      .d(horizon < 2) |> ######################this shall be extended sometime##############
+      .d(, error := prediction - tv_1) |>
+      .d(target_year < 2015) |>
+      .d(, .(country, prediction, target, error,
+             horizon, target_year, forecast_year,
+             tv_1)
+      )
+
+```
+
+```{r, include = FALSE, echo = FALSE}
+head(sub_weodat)
+```

### 2023-09-06 manuscript/manuscript.tex
visualize scores and coverage

@@
 \usepackage[margin=1in]{geometry}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{longtable,booktabs,array}
@@
 \usepackage{float}
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{longtable}
 \ifLuaTeX
@@
 \hypersetup{
-  pdftitle={Compare forecats},
+  pdftitle={IMF and Benchmark Forecasts},
   hidelinks,
@@
 
-\title{Compare forecats}
+\title{IMF and Benchmark Forecasts}
 \author{}
@@
 \setstretch{2}
-\hypertarget{r-markdown}{%
-\subsection{R Markdown}\label{r-markdown}}
+\hypertarget{a-short-note-on-error-handling}{%
+\section{A short note on error handling}\label{a-short-note-on-error-handling}}
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see \url{http://rmarkdown.rstudio.com}.
+In almost all 72 cases, absolute error handling gives lower scores than directional error handling.
+The only exception is the inflation series for the IMF forecasts and horizon 0, where the expanding window and rolling window method give \textit{slightly} lower scores for the directional methodology.
+We thus decide to focus on the absolute errors in this document.
 
-When you click the \textbf{Knit} button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+\hypertarget{scores-by-estimation-method-horizon-and-forecast-source}{%
+\section{Scores, by estimation method, Horizon and forecast source}\label{scores-by-estimation-method-horizon-and-forecast-source}}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{summary}\NormalTok{(cars)}
-\end{Highlighting}
-\end{Shaded}
+\begin{longtable}{l|rrr}
+\toprule
+\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 0} \\ 
+\midrule
+expanding window\_interval\_score & 0.115 & 0.123 & 0.122 \\ 
+expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
+leave-one-out\_interval\_score & 0.119 & 0.133 & 0.134 \\ 
+leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
+rolling window\_interval\_score & 0.119 & 0.128 & 0.126 \\ 
+rolling window\_sample\_crps & 0.094 & 0.097 & 0.098 \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 0.5} \\ 
+\midrule
+expanding window\_interval\_score & 0.258 & 0.272 & 0.296 \\ 
+expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
+leave-one-out\_interval\_score & 0.261 & 0.313 & 0.317 \\ 
+leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
+rolling window\_interval\_score & 0.261 & 0.266 & 0.288 \\ 
+rolling window\_sample\_crps & 0.191 & 0.201 & 0.235 \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 1} \\ 
+\midrule
+expanding window\_interval\_score & 0.448 & 0.737 & 0.590 \\ 
+expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
+leave-one-out\_interval\_score & 0.427 & 0.726 & 0.600 \\ 
+leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
+rolling window\_interval\_score & 0.451 & 0.739 & 0.591 \\ 
+rolling window\_sample\_crps & 0.333 & 0.514 & 0.434 \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 1.5} \\ 
+\midrule
+expanding window\_interval\_score & 0.495 & 1.044 & 0.800 \\ 
+expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
+leave-one-out\_interval\_score & 0.487 & 1.103 & 0.903 \\ 
+leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
+rolling window\_interval\_score & 0.494 & 1.041 & 0.779 \\ 
+rolling window\_sample\_crps & 0.347 & 0.632 & 0.570 \\ 
+\bottomrule
+\end{longtable}
 
-\begin{verbatim}
-##      speed           dist       
-##  Min.   : 4.0   Min.   :  2.00  
-##  1st Qu.:12.0   1st Qu.: 26.00  
-##  Median :15.0   Median : 36.00  
-##  Mean   :15.4   Mean   : 42.98  
-##  3rd Qu.:19.0   3rd Qu.: 56.00  
-##  Max.   :25.0   Max.   :120.00
-\end{verbatim}
+\hypertarget{inflation}{%
+\subsection{Inflation}\label{inflation}}
 
-\hypertarget{including-plots}{%
-\subsection{Including Plots}\label{including-plots}}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
 
-You can also embed plots, for example:
+\hypertarget{gdp}{%
+\subsection{GDP}\label{gdp}}
 
-\includegraphics{manuscript_files/figure-latex/pressure-1.pdf}
+\begin{longtable}{l|rrr}
+\toprule
+\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 0} \\ 
+\midrule
+expanding window\_interval\_score & 0.241 & 0.301 & 0.298 \\ 
+expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
+leave-one-out\_interval\_score & 0.257 & 0.312 & 0.310 \\ 
+leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
+rolling window\_interval\_score & 0.240 & 0.302 & 0.297 \\ 
+rolling window\_sample\_crps & 0.178 & 0.211 & 0.204 \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 0.5} \\ 
+\midrule
+expanding window\_interval\_score & 0.416 & 0.540 & 0.493 \\ 
+expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
+leave-one-out\_interval\_score & 0.448 & 0.583 & 0.531 \\ 
+leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
+rolling window\_interval\_score & 0.416 & 0.554 & 0.504 \\ 
+rolling window\_sample\_crps & 0.297 & 0.405 & 0.373 \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 1} \\ 
+\midrule
+expanding window\_interval\_score & 0.837 & 1.090 & 0.942 \\ 
+expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
+leave-one-out\_interval\_score & 0.858 & 1.067 & 0.948 \\ 
+leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
+rolling window\_interval\_score & 0.851 & 1.122 & 0.970 \\ 
+rolling window\_sample\_crps & 0.663 & 0.875 & 0.815 \\ 
+\midrule
+\multicolumn{4}{l}{horizon = 1.5} \\ 
+\midrule
+expanding window\_interval\_score & 1.045 & 1.288 & 1.102 \\ 
+expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
+leave-one-out\_interval\_score & 1.034 & 1.278 & 1.107 \\ 
+leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
+rolling window\_interval\_score & 1.056 & 1.312 & 1.143 \\ 
+rolling window\_sample\_crps & 0.831 & 0.985 & 0.949 \\ 
+\bottomrule
+\end{longtable}
 
-Note that the \texttt{echo\ =\ FALSE} parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+
+\hypertarget{coverage-by-target-methods-and-source}{%
+\section{Coverage, by target, methods and source}\label{coverage-by-target-methods-and-source}}
+
+\includegraphics{manuscript_files/figure-latex/cvgplot-1.pdf}
 

### 2023-09-07 manuscript/manuscript.Rmd
current analysis

@@
 
+#############block to merge with cvgdat symmetric
+
+cvgdat_cpin <- data.table::fread(here("quantile_forecasts", "cvg_pooled_directionalsymmetric.csv")) |>
+  setnames("model", "source") |>
+  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
+  melt(id.vars = c("target", "error_method", "method", "source"),
+       variable.name = "pilvl",
+       value.name = "coverage") |>
+  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
+  .d(, pilvl := as.numeric(pilvl)/100) |>
+  .d(target == "pcpi_pch") |>
+  rbind(cvgdat_cpi)
+
+cvgdat_cpi <- cvgdat_cpin
+
+cvgdat_gdpn <- data.table::fread(here("quantile_forecasts", "cvg_pooled_directionalsymmetric.csv")) |>
+  setnames("model", "source") |>
+  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
+  melt(id.vars = c("target", "error_method", "method", "source"),
+       variable.name = "pilvl",
+       value.name = "coverage") |>
+  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
+  .d(, pilvl := as.numeric(pilvl)/100) |>
+  .d(target == "ngdp_rpch") |>
+  rbind(cvgdat_gdp)
+
+cvgdat_gdp <- cvgdat_gdpn
+
 plot_cpi <- ggplot() +

### 2023-09-08 scripts/score-forecasts.R
include point forecasts in scoring

@@ -68,6 +68,7 @@ qufcs <- data.table::fread(here("quantile_forecasts", "quantile_forecasts.csv"))
 combs <- data.table::fread(here("quantile_forecasts", "setting_combinations.csv"))
 
 
+#################score CI's####################################################
 weodat_qu_sameyearset <- qufcs |>
   .d(target_year>=1999) |>
   .d(,.(country, target, horizon, target_year, true_value, prediction, quantile, method, error_method, source)) |>
@@ -93,6 +94,22 @@ scores_cvgshort <- scoreempQu(weodat_qu_sameyearset, cvg_rg = c(50,80),
                      by = c("model", "error_method", "method", "target"))
 
 
+
+################################Score Point Predictions############################
+pp_scores <- fcdat |>
+  .d(target_year>=1999) |>
+  data.table::copy() |>
+  .d(, ae := abs(get(paste0("tv_", tv_release)) - prediction)) |>
+  .d(, sque := (get(paste0("tv_", tv_release)) - prediction)^2) |>
+  .d(, meanae := mean(ae), .(source, target, country, horizon)) |>
+  .d(, meansque := mean(sque), .(source, target, country, horizon)) |>
+  .d(, .(source, target, country, horizon, meanae, meansque)) |>
+  setnames(c("meanae", "meansque"), c("ae", "sque")) |>
+  unique()
+
+
+
+#################################Score by CRPS Sample##############################
 weodat_samples <- fcdat |>
   .d(horizon < 2) |>
   .d(,.(country, source, target, horizon, target_year, tv_1, prediction))
@@ -136,4 +153,5 @@ data.table::fwrite(scores_allyears, here("quantile_forecasts", "ci_scores_allyea
 data.table::fwrite(all_crps, here("quantile_forecasts", "sample_scores.csv"))
 data.table::fwrite(scores_cvgshort, here("quantile_forecasts", "cvg_pooled.csv"))
 data.table::fwrite(scores_avgcountry, here("quantile_forecasts", "ci_scores_avgcnt.csv"))
+data.table::fwrite(pp_scores, here("quantile_forecasts", "pointfc_scores.csv"))
 

### 2023-09-08 manuscript/manuscript.Rmd
update with theory

@@
 
+# Extracting error quantiles
+
+Consider a forecast that stems from a source $s$ for a specific target $k$ in a country $j$, for target year $t$ and with forecast horizon $h$:
+\[
+\hat{y}_{s,k,j,t,h}
+\]
+For example, this could be a forecast stemming from the International Monetary Fund World Economic Outlook ($s = IMF$) for real GDP growth ($k = gdpg$) in Canada ($j = Canada$) for the year $2022$ ($t=2022$).
+$h$ then indexes the forecast horizon, where we code:
+\[
+h = \left\{
+\begin{array}{ll} 
+      0, & \textrm{for forecasts made in October of the same year} \\
+      0.5, & \textrm{for forecasts made in April of the same year} \\
+      1, & \textrm{for forecasts made in October of the previous year} \\
+      1.5, & \textrm{for forecasts made in April of the previous year} \\
+\end{array}\right. 
+\]
+After the target year has completed, we obtain the realized value for the quantity of interest.
+For these, the WEO updates publishes biannual updates for two years, yielding $4$ versions of the realized value.
+In accordance with previous literature (\textit{cite Timmermann 2008}), we use the version that is published in October of the following year and thereby don't index the true value by its publishing date (\textit{rephrase}).
+We thus write the true value as
+\[
+\hat{y}_{k,j,t}
+\]
+Given the forecast and the realized value for the quantity of interest, we can calculate the respective forecast error as
+\[
+e^{d}_{s,k,j,t,h} = y_{k,j,t} - \hat{y}_{s,k,j,t,h}
+\]
+
+for the "directional" error method and as 
+\[
+e^{a}_{s,k,j,t,h} = \left|y_{k,j,t} - \hat{y}_{s,k,j,t,h}\right|
+\]
+for the "absolute" error method.
+
+The objective is to extract quantiles from sets of errors $\mathcal{E}_{s,k,j,t,h}$ constructed of certain years, depending on the estimation method $m$, to be able to quantify the uncertainty inherent in the forecasts via central prediction intervals of level $\alpha = \{0.5, 0.8\}$.
+For the estimation method, we consider a "rolling window" method, an "expanding window" method, and a "leave-one-out" method.
+For the rolling window method ($m = rw$), the errors of the last nine years enter into the estimation.
+For the expanding window method ($m = ew$), all previous years are considered, leaving a nine year window up front for the first estimation.
+For the leave-one-out method, all years except the current target year enter the estimation set.
+The latter is of course equivalent to the expanding window method in a real time setting and is considered in the scope of this analysis as a mere check \textit{rephrase}.
+As an example, the error set for the "directional" error method and the rolling window approach is
+\[
+\mathcal{E}^{d,rw}_{s,k,j,t,h} =  \left\{  e^{d}_{s,k,j,t^*,h} | t-9\leq t^* < t \right\}
+\]
+Insert reasoning to use the past $9$ errors.
+
+To now obtain the lower $l$ and upper $u$ values for a central prediction interval of level $\alpha$, we take quantiles of these sets and add them to the current prediction:
+
+For the directional method:
+\[
+l^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 - \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
+\]
+\[
+u^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 + \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
+\]
+
+And for the absolute method:
+
+\[
+ l^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} -  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
+\]
+\[
+u^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} +  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
+\]
+
+Two different philosophies.
+
+The absolute method will always yield symmetric central prediction intervals around the forecast value, while the directional method will in general yield asymmetric intervals.
+They thus result in different central intervals, unless the errors in $\mathcal{E}$ are perfectly symmetric around zero\footnote{Not totally correct, actually.
+For this to hold exactly, the error set would need to be augmented with one zero value.}.
+In fact, the directional method can yield central prediction intervals that do not even contain the forecast value, in cases where the $(0.5 - \alpha/2)$-quantile is positive or the $(0.5 + \alpha/2)$-quantile is negative.
+
 # A short note on error handling
@@
 
+#join score sets
 all_scores <- 
@@
 
+#bring into long format
 gather_scores <- all_scores |>
@@
   .d(, horizon := paste0("horizon = ", horizon)) |>
-  .d(, score := round(score, 3)) |>
+  .d(, score := round(score, 3)) |> #enough to distinguish
   dcast(horizon + combms ~ source, value.var = "score")
@@
 ```
-
-```{r loaddata, include = FALSE, echo = FALSE}
-
-sub_weodat <- 
-   data.table::fread(here("WEOforecasts_tidy.csv")) |>
-      .d(g7 == 1,) |>
-      .d(horizon < 2) |> ######################this shall be extended sometime##############
-      .d(, error := prediction - tv_1) |>
-      .d(target_year < 2015) |>
-      .d(, .(country, prediction, target, error,
-             horizon, target_year, forecast_year,
-             tv_1)
-      )
-
-```
-
-```{r, include = FALSE, echo = FALSE}
-head(sub_weodat)
-```

### 2023-09-08 manuscript/manuscript.tex
update with theory

@@
 \setstretch{2}
+\hypertarget{extracting-error-quantiles}{%
+\section{Extracting error quantiles}\label{extracting-error-quantiles}}
+
+Consider a forecast that stems from a source \(s\) for a specific target \(k\) in a country \(j\), for target year \(t\) and with forecast horizon \(h\):
+\[
+\hat{y}_{s,k,j,t,h}
+\]
+For example, this could be a forecast stemming from the International Monetary Fund World Economic Outlook (\(s = IMF\)) for real GDP growth (\(k = gdpg\)) in Canada (\(j = Canada\)) for the year \(2022\) (\(t=2022\)).
+\(h\) then indexes the forecast horizon, where we code:
+\[
+h = \left\{
+\begin{array}{ll} 
+      0, & \textrm{for forecasts made in October of the same year} \\
+      0.5, & \textrm{for forecasts made in April of the same year} \\
+      1, & \textrm{for forecasts made in October of the previous year} \\
+      1.5, & \textrm{for forecasts made in April of the previous year} \\
+\end{array}\right. 
+\]
+After the target year has completed, we obtain the realized value for the quantity of interest.
+For these, the WEO updates publishes biannual updates for two years, yielding \(4\) versions of the realized value.
+In accordance with previous literature (\textit{cite Timmermann 2008}), we use the version that is published in October of the following year and thereby don't index the true value by its publishing date (\textit{rephrase}).
+We thus write the true value as
+\[
+\hat{y}_{k,j,t}
+\]
+Given the forecast and the realized value for the quantity of interest, we can calculate the respective forecast error as
+\[
+e^{d}_{s,k,j,t,h} = y_{k,j,t} - \hat{y}_{s,k,j,t,h}
+\]
+
+for the ``directional'' error method and as
+\[
+e^{a}_{s,k,j,t,h} = \left|y_{k,j,t} - \hat{y}_{s,k,j,t,h}\right|
+\]
+for the ``absolute'' error method.
+
+The objective is to extract quantiles from sets of errors \(\mathcal{E}_{s,k,j,t,h}\) constructed of certain years, depending on the estimation method \(m\), to be able to quantify the uncertainty inherent in the forecasts via central prediction intervals of level \(\alpha = \{0.5, 0.8\}\).
+For the estimation method, we consider a ``rolling window'' method, an ``expanding window'' method, and a ``leave-one-out'' method.
+For the rolling window method (\(m = rw\)), the errors of the last nine years enter into the estimation.
+For the expanding window method (\(m = ew\)), all previous years are considered, leaving a nine year window up front for the first estimation.
+For the leave-one-out method, all years except the current target year enter the estimation set.
+The latter is of course equivalent to the expanding window method in a real time setting and is considered in the scope of this analysis as a mere check \textit{rephrase}.
+As an example, the error set for the ``directional'' error method and the rolling window approach is
+\[
+\mathcal{E}^{d,rw}_{s,k,j,t,h} =  \left\{  e^{d}_{s,k,j,t^*,h} | t-9\leq t^* < t \right\}
+\]
+Insert reasoning to use the past \(9\) errors.
+
+To now obtain the lower \(l\) and upper \(u\) values for a central prediction interval of level \(\alpha\), we take quantiles of these sets and add them to the current prediction:
+
+For the directional method:
+\[
+l^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 - \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
+\]
+\[
+u^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 + \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
+\]
+
+And for the absolute method:
+
+\[
+ l^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} -  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
+\]
+\[
+u^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} +  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
+\]
+
+Two different philosophies.
+
+The absolute method will always yield symmetric central prediction intervals around the forecast value, while the directional method will in general yield asymmetric intervals.
+They thus result in different central intervals, unless the errors in \(\mathcal{E}\) are perfectly symmetric around zero\footnote{Not totally correct, actually.
+For this to hold exactly, the error set would need to be augmented with one zero value.}.
+In fact, the directional method can yield central prediction intervals that do not even contain the forecast value, in cases where the \((0.5 - \alpha/2)\)-quantile is positive or the \((0.5 + \alpha/2)\)-quantile is negative.
+
 \hypertarget{a-short-note-on-error-handling}{%
@@
 expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
-leave-one-out\_interval\_score & 0.119 & 0.133 & 0.134 \\ 
+leave-one-out\_interval\_score & 0.114 & 0.122 & 0.122 \\ 
 leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
@@
 expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
-leave-one-out\_interval\_score & 0.261 & 0.313 & 0.317 \\ 
+leave-one-out\_interval\_score & 0.262 & 0.265 & 0.286 \\ 
 leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
@@
 expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
-leave-one-out\_interval\_score & 0.427 & 0.726 & 0.600 \\ 
+leave-one-out\_interval\_score & 0.453 & 0.739 & 0.584 \\ 
 leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
@@
 expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
-leave-one-out\_interval\_score & 0.487 & 1.103 & 0.903 \\ 
+leave-one-out\_interval\_score & 0.486 & 1.025 & 0.760 \\ 
 leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
@@
 expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
-leave-one-out\_interval\_score & 0.257 & 0.312 & 0.310 \\ 
+leave-one-out\_interval\_score & 0.237 & 0.297 & 0.294 \\ 
 leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
@@
 expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
-leave-one-out\_interval\_score & 0.448 & 0.583 & 0.531 \\ 
+leave-one-out\_interval\_score & 0.411 & 0.540 & 0.489 \\ 
 leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
@@
 expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
-leave-one-out\_interval\_score & 0.858 & 1.067 & 0.948 \\ 
+leave-one-out\_interval\_score & 0.831 & 1.086 & 0.943 \\ 
 leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
@@
 expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
-leave-one-out\_interval\_score & 1.034 & 1.278 & 1.107 \\ 
+leave-one-out\_interval\_score & 1.038 & 1.284 & 1.099 \\ 
 leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 

### 2023-09-12 scripts/score-forecasts.R
score bvar quantile forecasts

@@ -63,13 +63,15 @@ fcdat <- hordat[fcdat, on = c("target_year", "forecast_year", "season")] |>
 
 
 
-#######read in quantile forecasts
+####################################read in quantile forecasts########################
 qufcs <- data.table::fread(here("quantile_forecasts", "quantile_forecasts.csv"))
 combs <- data.table::fread(here("quantile_forecasts", "setting_combinations.csv"))
+bvar_qufcs <- data.table::fread(here("benchmarks", "forecast_quantiles.csv"))
 
 
 #################score CI's####################################################
 weodat_qu_sameyearset <- qufcs |>
+  data.table::copy() |>
   .d(target_year>=1999) |>
   .d(,.(country, target, horizon, target_year, true_value, prediction, quantile, method, error_method, source)) |>
   setnames("source", "model") |>
@@ -84,7 +86,7 @@ weodat_qu_allyears <- qufcs |>
 scores <- scoreempQu(weodat_qu_sameyearset, cvg_rg = c(50,80),
                      by = c("model", "error_method", "method", "country", "target", "horizon"))
 
-scores_allyears <- scoreempQu(weodat_qu_sameyearset, cvg_rg = c(50,80),
+scores_allyears <- scoreempQu(weodat_qu_allyears, cvg_rg = c(50,80),
                      by = c("model", "error_method", "method", "country", "target", "horizon"))
 
 scores_avgcountry <- scoreempQu(weodat_qu_sameyearset, cvg_rg = c(50,80),
@@ -148,10 +150,70 @@ all_crps <- lapply(1:nrow(combs_methods), function(idx){
   .d(, .(score = mean(score)), by = c("target", "horizon", "method", "error_method", "source"))
 
 
+
+
+####################################Score BVAR Quantile Forecasts###########################
+idx_bvar <- which(bvar_qufcs$quantile_level == 0.05)[1] #where bvar starts
+
+#remove redundant rows and rename target
+bvar_qus <- hordat[bvar_qufcs[idx_bvar:nrow(bvar_qufcs)], on = c("target_year", "forecast_year", "season")]  |>
+  .d(, target := ifelse(var == "cpi", "pcpi_pch", "ngdp_rpch")) |>
+  .d(, var := NULL)  |>
+  .d(, source := "bvar") |>
+  .d(, method := NULL) |>
+  setnames("value", "prediction") |>
[…]

### 2023-09-12 R/utils.R
plot facet labels

@@ -117,3 +117,26 @@ fperror <- function(type = 0.1){
     return(-2.77e-17)
   }
 }
+
+
+
+plot_horizon_label <- function(length.out = 4){
+
+  phl <- c(`0` = "Fall forecast, same year",
+           `0.5` = "Spring forecast, same year",
+           `1`= "Fall forecast, year ahead",
+           `1.5`= "Spring forecast, year ahead")
+
+  return(phl[1:length.out])
+}
+
+
+plot_horizon_label_short <- function(length.out = 4){
+
+  phl <- c(`0` = "F, same year",
+           `0.5` = "S, same year",
+           `1`= "F, year ahead",
+           `1.5`= "S, year ahead")
+
+  return(phl[1:length.out])
+}

### 2023-09-12 benchmarks/bvar_forecast_cluster_quantiles.R
bvar quantile forecasts and code

@@ -1,0 +1,139 @@
+rm(list = ls())
+setwd("/home/fabian/Schreibtisch/notes_and_ideas/IMF/")
+
+library(dplyr)
+library(zoo)
+library(bvarsv)
+library(tidyr)
+
+# setting 
+g7_oecd <- c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")
+vnms_oecd <- c("cpi", "gdp")
+yrs_fcst <- 1989:2021
+n_draws <- 2e4
+weights <- c(1:4, 3:1)/4
+weights_mat <- matrix(weights, n_draws, 7, byrow = TRUE)
+quantile_grid = seq(from = .05, to = .95, by = .05)
+n_q <- length(quantile_grid)
+
+# data frame holding all settings to be run
+all_settings <- data.frame(country = rep(g7_oecd, each = 2), 
+                           season = rep(c("S", "F"), 7))
+
+# get iteration (job id)
+#iter <- as.integer(as.character(Sys.getenv("SLURM_ARRAY_TASK_ID")))
+iter <- 2
+
+# set random seed
+set.seed(iter)
+
+cc <- all_settings$country[iter]
+fcst_season <- all_settings$season[iter]
+
+# load cpi data, transform date
+cpi0 <- read.csv("oecd_cpi_quarterly_new.csv") 
+cpi_q <- cpi0 %>%
+  transmute(ccode, y = value, 
+            dt = as.yearqtr(date)) %>%
+  na.omit 
+gdp0 <- read.csv("oecd_gdp_quarterly_annual.csv") 
+gdp_q <- gdp0 %>% 
+  filter(ccode %in% g7_oecd, quarter %in% 1:4, type == "prv_period") %>% 
+  transmute(ccode, dt = as.yearqtr(paste0(target_year, "Q", quarter)), 
+            y = value)
+# Put both into one data frame
+oecd_q <- rbind(data.frame(cpi_q, target = "cpi"), 
+                data.frame(gdp_q, target = "gdp")) %>%
+  pivot_wider(names_from = "target", values_from = "y") %>%
+  na.omit %>% filter(dt >= 1962)
+
+# initialize data frame
+df_all <- data.frame()
+
+# loop over forecast years
+for (yy in yrs_fcst){
+  
+  # identify latest data
+  if (fcst_season == "S"){
+    last_q <- yy # up until Q1 of forecast year
+  } else {
+    last_q <- yy + .5 # up until Q3 of forecast year
+  }
+  
+  # filter data accordingly
[…]

### 2023-09-12 manuscript/manuscript.Rmd
manuscript daily update

@@
 linestretch: 2 
+geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
 bibliography:
@@
 
-# Scores, by estimation method, Horizon and forecast source 
-```{r, echo = FALSE}
+```{r loaddata, echo = FALSE}
 scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
@@
 
+```
+
+# Scores, by estimation method, Horizon and forecast source 
+```{r, cpitable = FALSE}
 #bring into long format
-gather_scores <- all_scores |>
-  data.table::copy() |>
-  .d(target == "pcpi_pch") |>
-  .d(,target := NULL) |>
-  .d(, .(horizon, method, source, score, interval_score)) |>
-  setnames("score", "sample_crps") |>
-  melt(id.vars = c("horizon", "method", "source"), variable.name = "score_type", value.name = "score") |>
-  .d(, combms := paste0(method,"_", score_type)) |>
-  .d(, .(horizon, source, combms, score)) |>
-  .d(, horizon := paste0("horizon = ", horizon)) |>
-  .d(, score := round(score, 3)) |> #enough to distinguish
-  dcast(horizon + combms ~ source, value.var = "score")
+long_scores <- gather_scores(all_scores, "pcpi_pch")
 
-gather_scores |>
-  data.table::copy() |>
-  gt(rowname_col = "combms", groupname_col = "horizon") |>
-  cols_label(
-      IMF = "IMF",
-      ar = "ar",
-      bvar = "bvar"
-    )
-
-col_names <- c("IMF", "ar", "bvar")
+scores_to_table(all_scores, "pcpi_pch")
 
@@
 
-```{r, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
+```{r cpitileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
 
@@
 
-for(i in 1:4){
+hor_list <- as.list(1:4)
 
-  hor <- (i-1)*0.5
-
-  mydat <- gather_scores |>
-    .d(horizon == paste0("horizon = ", hor)) |>
-  .d(grep("interval", combms)) |>
-  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score") |>
-  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))
-
-  plots_is[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
-  geom_tile(aes(fill = score)) +
-    guides(fill = FALSE) +
-    ggtitle(paste0("horizon = ", hor, " - Weighted Interval Score"))
-}
-
-for(i in 1:4){
-
-  hor <- (i-1)*0.5
-
-  mydat <- gather_scores |>
-    .d(horizon == paste0("horizon = ", hor)) |>
-  .d(grep("crps", combms)) |>
-  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score")|>
-  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))
-
-  plots_cr[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
-  geom_tile(aes(fill = score))+
-    guides(fill = FALSE)+
-    ggtitle(paste0("horizon = ", hor, " - CRPS by sample"))
-}
+plots_is <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "interval"))
+plots_cr <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "crps"))
 
@@
 
-```{r cvgdat2, include=FALSE, echo = FALSE}
+## GDP
 
-scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
-scores_cvgshort <- fread(here("quantile_forecasts", "cvg_pooled.csv"))
+```{r gdptable, echo = FALSE}
 
-cvg_rg <- c(50, 80)
-
-cols <- paste0("coverage_", cvg_rg)
-
-large_cvgdat <- scores |>
-  setnames("model", "source") |>
-  .d(, c("country", "horizon", "target", "error_method", "method", "source", cols), with = FALSE) |>
-  melt(id.vars = c("country", "horizon", "target", "error_method", "method", "source"),
-       variable.name = "pilvl",
-       value.name = "coverage") |>
-  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
-  .d(, pilvl := as.numeric(pilvl)/100) |>
-  .d(, idcol := paste0(horizon, country, method)) |>
-  .d(, country := NULL) |>
-  .d(, horizon := NULL)
-
-cvgdat <- scores_cvgshort |>
-  setnames("model", "source") |>
-  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
-  melt(id.vars = c("target", "error_method", "method", "source"),
-       variable.name = "pilvl",
-       value.name = "coverage") |>
-  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
-  .d(, pilvl := as.numeric(pilvl)/100)
-
-cvgdat_cpi <- cvgdat |>
-  .d(target == "pcpi_pch")
-
-cvgdat_gdp <- cvgdat |>
-  .d(target == "ngdp_rpch")
-
-plot_cpi <- ggplot() +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                group = idcol),
-            data = large_cvgdat |> .d(target == "pcpi_pch"),
-            alpha = 0.4,
-            color = "gray") +
-  geom_point(aes(x = pilvl,
-                 y = coverage,
-                 color = method),
-             data = cvgdat_cpi,
-             size = 3) +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                color = method),
-            data = cvgdat_cpi,
-            lwd = 1.25) +
-  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
-               color = "black",
-               linetype = "dashed",
-               data = cvgdat_cpi) +
-  #scale_color_brewer(palette = "Set1") +
-  facet_grid(source ~ error_method)+
-
-  ggtitle("Inflation") +
-
-  scale_color_met_d("Hokusai1") +
-
-  ylab("Empirical Coverage Level (Central PI)") +
-  xlab("Nominal Coverage (Central PI)") +
-  theme_uqimf()
-
-plot_gdp <- ggplot() +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                group = idcol),
-            data = large_cvgdat |> .d(target == "ngdp_rpch"),
-            alpha = 0.4,
-            color = "gray") +
-  geom_point(aes(x = pilvl,
-                 y = coverage,
-                 color = method),
-             data = cvgdat_gdp,
-             size = 3) +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                color = method),
-            data = cvgdat_gdp,
-            lwd = 1.25) +
-  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
-               color = "black",
-               linetype = "dashed",
-               data = cvgdat_gdp) +
-  #scale_color_brewer(palette = "Set1") +
-  facet_grid(source ~ error_method)+
-
-  ggtitle("Real GDP Growth") +
-
-  scale_color_met_d("Hokusai1") +
-
-  ylab("Empirical Coverage Level (Central PI)") +
-  xlab("Nominal Coverage (Central PI)") +
-  theme_uqimf()
+long_scores <- gather_scores(all_scores, "ngdp_rpch")
+scores_to_table(all_scores, "ngdp_rpch")
 
@@
 
-## GDP
-
-```{r hey3, echo = FALSE}
-scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
-
-wis_scores <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
-  data.table::copy() |>
-  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
-  setnames("model", "source")
-
-crps_scores <- fread(here("quantile_forecasts", "sample_scores.csv"))
-
-all_scores <- 
-  crps_scores[wis_scores, on = c("source", "error_method", "method", "target", "horizon")]|>
-  .d(error_method == "absolute") |>
-  .d(, error_method := NULL)
-
-gather_scores <- all_scores |>
-  data.table::copy() |>
-  .d(target == "ngdp_rpch") |>
-  .d(,target := NULL) |>
-  .d(, .(horizon, method, source, score, interval_score)) |>
-  setnames("score", "sample_crps") |>
-  melt(id.vars = c("horizon", "method", "source"), variable.name = "score_type", value.name = "score") |>
-  .d(, combms := paste0(method,"_", score_type)) |>
-  .d(, .(horizon, source, combms, score)) |>
-  .d(, horizon := paste0("horizon = ", horizon)) |>
-  .d(, score := round(score, 3)) |>
-  dcast(horizon + combms ~ source, value.var = "score")
-
-gather_scores |>
-  data.table::copy() |>
-  gt(rowname_col = "combms", groupname_col = "horizon") |>
-  cols_label(
-      IMF = "IMF",
-      ar = "ar",
-      bvar = "bvar"
-    )
-
-col_names <- c("IMF", "ar", "bvar")
-
-```
-
-```{r, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
+```{r gdptileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
 
@@
 ovr_plot
+
+```
+
+```{r overall_assessment, fig.dim=c(12,12), echo = FALSE}
+
+scores_cvgshort <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE)
+
+point_scores <- data.table::fread(here("quantile_forecasts", "pointfc_scores.csv"))
+
+ovr_assessment_plot <- function(wis_scoredat, cvg_scoredat, point_scores, crps_scores, trgt){
+
+  cvgscores <- cvg_scoredat |>
+    .d(method == "rolling window") |>
+    .d(target == trgt) |>
+    .d(, target := NULL) |>
+    .d(, method := NULL) #|>
+
+  decomp_data <- wis_scoredat |>
+    .d(method == "rolling window") |>
+    .d(target == trgt) |>
+    .d(, target := NULL) |>
+    .d(, method := NULL) #|>
+
+  point_scores <- point_scores |>
+    .d(target == trgt) |>
+    .d(, target := NULL) |>
+    .d(, meanae := mean(ae), by = c("source", "horizon")) |>
+    .d(, meansque := mean(sque), by = c("source", "horizon")) |>
+    .d(, .(source, country, horizon, meanae, meansque)) |>
+    unique()
+
+  crps_scores_rw <- crps_scores |>
+    .d(method == "rolling window") |>
+    .d(target == trgt) |>
+    .d(, target := NULL)
+
+  crps_scores_loo <- crps_scores |>
+    .d(method == "leave-one-out") |>
+    .d(target == trgt) |>
+    .d(, target := NULL)
+
+  xmax <- max(decomp_data$interval_score)
+
+  decomp_data <- decomp_data |>
+    data.table::melt(id.vars = c("source", "error_method", "horizon"),
+                     value.name = "score",
+                     variable.name = "type") |>
+    .d(type != "interval_score") # filter out total score, only interested in decomposition
+
+  #check arguments of function!
+  wis_plot <- function(decompdat, error_m, maxval){
+
+    if(error_m == "directional"){
+      plot_name <- "Directional Errors"
+    } else {
+      plot_name <- "Absolute Errors"
+    }
+
+    plt <- ggplot(decomp_data |> .d(error_method == error_m),
+                          aes(x = source, 
+                              fill = source,
+                              y = score,
+                              alpha = type)) +
+      geom_bar(position="stack", stat="identity") +
+      facet_wrap(~ horizon,
+                 labeller = as_labeller(plot_horizon_label_short(4)),
+                 nrow = 1) +
+      #geom_hline(yintercept = 1) +
+      scale_alpha_discrete(range = c(0.35,1),
+                           labels = c("Overprediction",
+                                      "Underprediction",
+                                      "Dispersion"),
+                           name = "Components of the WIS") +
+      scale_x_discrete(name = "",
+                       breaks = c("IMF", "bvar", "ar"),
+                       labels = c("IMF", "BVAR", "AR")) +
+      scale_y_continuous(name = "WIS", limits = c(0, maxval)) +
+      scale_fill_brewer(palette = "Set2", 
+                        name = "Model Type")+
+      xlab("") +
+      #labs(fill = "Model Type") +
+      theme_uqimf() %+replace%
+      theme(axis.text.x = element_text(size = 8, angle = 90, hjust = .5, vjust = .5, face = "plain"),
+            strip.text = element_text(size = 8)) +
+      ggtitle(plot_name) +
+      theme(#legend.title=element_blank(),
+            legend.position = "none")
+
+    return(plt)
+
+  }
+
+  horizon_path_plot <- function(score_data,
+                                score_rule,
+                                ylab = score_rule, 
+                                facet = NULL){
+
+    path_plot <- ggplot(score_data, 
+           aes(x = horizon,
+               y = get(score_rule), 
+               color = source)) +
+      scale_color_brewer(palette = "Set2") +
+      geom_line() +
+      geom_point() +
+      ylab(ylab) +
+      xlab("Forecast Horizon") +
+      guides(fill = "none", colour = "none") +
+      theme_uqimf() %+replace%
+      theme(legend.title=element_blank(),
+            legend.position = "none")
+
+    if(!is.null(facet)){
+
+      path_plot <- path_plot +
+      facet_wrap(~ get(facet),
+                 scales = "free") 
+    }
+
+    return(path_plot)
+
+  }
+
+  dir_wis_plot <- wis_plot(decomp_data, "directional", xmax)
+  abs_wis_plot <- wis_plot(decomp_data, "absolute", xmax)
+
+  c50plot <- horizon_path_plot(cvgscores, "coverage_50", "CI Coverage - 50", facet = "error_method") +
+    geom_hline(aes(yintercept = 0.5)) +
+    scale_y_continuous(labels = paste0(seq(0, 100, by = 25), "%"),
+                       breaks = seq(0,1, by = 0.25),
+                       limits = c(0,1))
+
+  c80plot <- horizon_path_plot(cvgscores, "coverage_80", "CI Coverage - 80", facet = "error_method") +
+    geom_hline(aes(yintercept = 0.8)) +
+    scale_y_continuous(labels = paste0(seq(0, 100, by = 25), "%"),
+                       breaks = seq(0,1, by = 0.25),
+                       limits = c(0,1))
+
+  erow <-  ggplot() + theme_void()
+
+  aeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meanae", "Absolute Error")
+
+  squeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meansque", "Squared Error")
+
+  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample")
+
+  crpsplot_loo <- horizon_path_plot(crps_scores_loo |>.d(, error_method := "directional"), "score", "CRPS by Sample")
+
+  ovr_plot <- 
+    (dir_wis_plot | abs_wis_plot) /
+    (plot_spacer()) /
+    (plot_annotation(title = "hey")) /
+    (c50plot | c80plot) /
+    (plot_spacer()) /
+    (squeplot | aeplot | crpsplot_rw | crpsplot_loo) +
+    plot_layout(guides = "collect", 
+                heights = c(0.2, 0.05, 0.2, 0.05, 0.2)) &
+      plot_annotation(tag_levels = 'I')  &
+      theme(legend.position = 'bottom', 
+            legend.box="vertical", legend.margin=margin())
+
+  return(ovr_plot)
+}
+
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "pcpi_pch")
 

### 2023-09-12 manuscript/manuscript.tex
manuscript daily update

@@
 \usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
+\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{longtable,booktabs,array}
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#bring into long format}
+\NormalTok{long\_scores }\OtherTok{\textless{}{-}} \FunctionTok{gather\_scores}\NormalTok{(all\_scores, }\StringTok{"pcpi\_pch"}\NormalTok{)}
+
+\FunctionTok{scores\_to\_table}\NormalTok{(all\_scores, }\StringTok{"pcpi\_pch"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
 \begin{longtable}{l|rrr}
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\includegraphics{manuscript_files/figure-latex/cpitileplot-1.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{manuscript_files/figure-latex/gdptileplot-1.pdf}
+
+\begin{verbatim}
+## Warning: Using alpha for a discrete variable is not advised.
+## Using alpha for a discrete variable is not advised.
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/overall_assessment-1.pdf}
 

### 2023-09-15 manuscript/manuscript.Rmd
manuscript updates

@@
 
-# A short note on error handling
+```{r loaddata, echo = FALSE}
+scores <- fread(here("scores", "ci_scores.csv"))
 
-In almost all 72 cases, absolute error handling gives lower scores than directional error handling.
-The only exception is the inflation series for the IMF forecasts and horizon 0, where the expanding window and rolling window method give \textit{slightly} lower scores for the directional methodology.
-We thus decide to focus on the absolute errors in this document.
-
-```{r loaddata, echo = FALSE}
-scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
-
-wis_scores <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
+wis_scores <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
   data.table::copy() |>
@@
 
-crps_scores <- fread(here("quantile_forecasts", "sample_scores.csv"))
+crps_scores <- fread(here("scores", "sample_scores.csv"))
 
@@
 
-```
+########
 
-# Scores, by estimation method, Horizon and forecast source 
-```{r, cpitable = FALSE}
-#bring into long format
-long_scores <- gather_scores(all_scores, "pcpi_pch")
+bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  .d(,model := "bvar_qu") |>
+  setnames("model", "source") |>
+  .d(,error_method := "directional") |>
+  .d(,method := "rolling window") #change later
 
-scores_to_table(all_scores, "pcpi_pch")
+bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores |> copy() |> .d(, error_method := "absolute"))
 
@@
 
+# Scores, by error method, Horizon and forecast source
+
 ## Inflation
 
-```{r cpitileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
+```{r overall_assessment_ew, fig.dim=c(12,12), echo = FALSE, warning = FALSE}
 
-plots_is <- vector(mode = "list", length = 4)
-plots_cr <- vector(mode = "list", length = 4)
-
-hor_list <- as.list(1:4)
-
-plots_is <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "interval"))
-plots_cr <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "crps"))
-
-ovr_plot <- 
-  (plots_is[[1]] + plots_cr[[1]]) /
-  (plots_is[[2]] + plots_cr[[2]]) /
-  (plots_is[[3]] + plots_cr[[3]]) /
-  (plots_is[[4]] + plots_cr[[4]]) +
-  plot_layout(heights = c(1, 1,1,1)) &
-    plot_annotation(tag_levels = 'I')  &
-    theme(legend.position = 'right', 
-          legend.box="vertical", legend.margin=margin())
-
-ovr_plot
-
-```
-
-## GDP
-
-```{r gdptable, echo = FALSE}
-
-long_scores <- gather_scores(all_scores, "ngdp_rpch")
-scores_to_table(all_scores, "ngdp_rpch")
-
-```
-
-```{r gdptileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
-
-plots_is <- vector(mode = "list", length = 4)
-plots_cr <- vector(mode = "list", length = 4)
-
-hor_list <- as.list(1:4)
-
-plots_is <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "interval"))
-plots_cr <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "crps"))
-
-ovr_plot <- 
-  (plots_is[[1]] + plots_cr[[1]]) /
-  (plots_is[[2]] + plots_cr[[2]]) /
-  (plots_is[[3]] + plots_cr[[3]]) /
-  (plots_is[[4]] + plots_cr[[4]]) +
-  plot_layout(heights = c(1, 1,1,1)) &
-    plot_annotation(tag_levels = 'I')  &
-    theme(legend.position = 'right', 
-          legend.box="vertical", legend.margin=margin())
-
-ovr_plot
-
-```
-
-```{r overall_assessment, fig.dim=c(12,12), echo = FALSE}
-
-scores_cvgshort <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
+scores_cvgshort <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
   setnames("model", "source", skip_absent = TRUE)
 
-point_scores <- data.table::fread(here("quantile_forecasts", "pointfc_scores.csv"))
+bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE) |>
+  .d(, source := "bvar_qu") |>
+  .d(, method := "rolling window") |>
+  .d(, error_method := "absolute")
+
+bvar_scores_cvgshort <- rbind(bvar_scores_cvgshort, bvar_scores_cvgshort |> copy() |> .d(, error_method := "directional"))
+
+point_scores <- data.table::fread(here("scores", "pointfc_scores.csv"))
+
+wis_scores <- rbind(wis_scores, bvar_wis_scores)
+scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
 
@@
     if(error_m == "directional"){
-      plot_name <- "Directional Errors"
+      plot_name <- "WIS - Directional Errors"
     } else {
-      plot_name <- "Absolute Errors"
+      plot_name <- "WIS - Absolute Errors"
     }
@@
       scale_x_discrete(name = "",
-                       breaks = c("IMF", "bvar", "ar"),
-                       labels = c("IMF", "BVAR", "AR")) +
+                       breaks = c("IMF", "bvar", "bvar_qu", "ar"),
+                       labels = c("IMF", "BVAR", "BVAR_QU", "AR")) +
       scale_y_continuous(name = "WIS", limits = c(0, maxval)) +
-      scale_fill_brewer(palette = "Set2", 
-                        name = "Model Type")+
+      scale_fill_met_d("Hokusai1") +
+      #scale_fill_brewer(palette = "Set2", 
+      #                  name = "Model Type")+
       xlab("") +
@@
                                 ylab = score_rule, 
-                                facet = NULL){
+                                facet = NULL,
+                                title = NULL){
 
@@
                color = source)) +
-      scale_color_brewer(palette = "Set2") +
+
+      scale_color_met_d("Hokusai1", breaks = c("IMF", "bvar", "ar", "bvar_qu"),
+                       labels = c("IMF", "BVAR", "AR", "BVAR_QU")) +
+
+      #scale_color_brewer(palette = "Set2") +
       geom_line() +
@@
       theme(legend.title=element_blank(),
-            legend.position = "none")
+            legend.position = "none") +
+      ggtitle(title)
 
@@
 
-  c50plot <- horizon_path_plot(cvgscores, "coverage_50", "CI Coverage - 50", facet = "error_method") +
+  c50plot <- horizon_path_plot(cvgscores, "coverage_50", "CI Coverage - 50", facet = "error_method", title = "Central Interval Coverage - alpha = 50") +
     geom_hline(aes(yintercept = 0.5)) +
@@
 
-  c80plot <- horizon_path_plot(cvgscores, "coverage_80", "CI Coverage - 80", facet = "error_method") +
+  c80plot <- horizon_path_plot(cvgscores, "coverage_80", "CI Coverage - 80", facet = "error_method", title = "Central Interval Coverage - alpha = 80") +
     geom_hline(aes(yintercept = 0.8)) +
@@
 
-  aeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meanae", "Absolute Error")
+  aeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meanae", "Absolute Error", title = "Point Forecast - Abs. Error")
 
-  squeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meansque", "Squared Error")
+  squeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meansque", "Squared Error", title = "Point Forecast - Squ. Error")
 
-  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample")
+  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - Rolling Window") +
+    scale_y_continuous(limits = c(0.07,1.05))
 
-  crpsplot_loo <- horizon_path_plot(crps_scores_loo |>.d(, error_method := "directional"), "score", "CRPS by Sample")
+  crpsplot_loo <- horizon_path_plot(crps_scores_loo |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - LOO") +
+    scale_y_continuous(limits = c(0.07,1.05))
 
@@
     (plot_spacer()) /
-    (plot_annotation(title = "hey")) /
     (c50plot | c80plot) /
@@
 ```
+\newpage
+Some notes:
+\begin{itemize}
+\item Inflation: directional vs. absolute errors:
+\begin{itemize}
+\item difference small for IMF method, absolute slighly better, likely due to longer central intervals
+\item AR and BVAR profit more from directional correction (upward bias)
+\item for expanding window method, difference in coverage is smaller (-> structural breaks)
+
+\end{itemize}
+\item Inflation overall scores: IMF forecasts outperform others
+\begin{itemize}
+\item lower scores for point forecasts
+\item lower WIS 
+\item lower bias (compute directly?)
+\end{itemize}
+
+\item GDP Growth: more similar results for different sources
+\begin{itemize}
+\item lower scores at shorter horizons, more similar at larger horizons
+\item IMF forecasts better only for absolute error method
+\end{itemize}
+\end{itemize}
+
+\newpage
+
+## GDP
+
+```{r gdpovr_ew, echo = FALSE, warning = TRUE, fig.dim=c(12,12)}
+
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch")
+```
+
+# Expanding Window - Scores, by error method, Horizon and forecast source
+
+## Inflation
+
+```{r overall_assessment, fig.dim=c(12,12), echo = FALSE, warning = FALSE}
+
+scores_cvgshort <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE)
+
+bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE) |>
+  .d(, source := "bvar_qu") |>
+  .d(, method := "expanding window") |>
+  .d(, error_method := "absolute")
+
+bvar_scores_cvgshort <- rbind(bvar_scores_cvgshort, bvar_scores_cvgshort |> copy() |> .d(, error_method := "directional"))
+
+point_scores <- data.table::fread(here("scores", "pointfc_scores.csv"))
+
+wis_scores <- rbind(wis_scores, bvar_wis_scores)
+scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
+
+ovr_assessment_plot <- function(wis_scoredat, cvg_scoredat, point_scores, crps_scores, trgt){
+
+  cvgscores <- cvg_scoredat |>
+    .d(method == "expanding window") |>
+    .d(target == trgt) |>
+    .d(, target := NULL) |>
+    .d(, method := NULL) #|>
+
+  decomp_data <- wis_scoredat |>
+    .d(method == "expanding window") |>
+    .d(target == trgt) |>
+    .d(, target := NULL) |>
+    .d(, method := NULL) #|>
+
+  point_scores <- point_scores |>
+    .d(target == trgt) |>
+    .d(, target := NULL) |>
+    .d(, meanae := mean(ae), by = c("source", "horizon")) |>
+    .d(, meansque := mean(sque), by = c("source", "horizon")) |>
+    .d(, .(source, country, horizon, meanae, meansque)) |>
+    unique()
+
+  crps_scores_rw <- crps_scores |>
+    .d(method == "expanding window") |>
+    .d(target == trgt) |>
+    .d(, target := NULL)
+
+  crps_scores_loo <- crps_scores |>
+    .d(method == "leave-one-out") |>
+    .d(target == trgt) |>
+    .d(, target := NULL)
+
+  xmax <- max(decomp_data$interval_score)
+
+  decomp_data <- decomp_data |>
+    data.table::melt(id.vars = c("source", "error_method", "horizon"),
+                     value.name = "score",
+                     variable.name = "type") |>
+    .d(type != "interval_score") # filter out total score, only interested in decomposition
+
+  #check arguments of function!
+  wis_plot <- function(decompdat, error_m, maxval){
+
+    if(error_m == "directional"){
+      plot_name <- "WIS - Directional Errors"
+    } else {
+      plot_name <- "WIS - Absolute Errors"
+    }
+
+    plt <- ggplot(decomp_data |> .d(error_method == error_m),
+                          aes(x = source, 
+                              fill = source,
+                              y = score,
+                              alpha = type)) +
+      geom_bar(position="stack", stat="identity") +
+      facet_wrap(~ horizon,
+                 labeller = as_labeller(plot_horizon_label_short(4)),
+                 nrow = 1) +
+      #geom_hline(yintercept = 1) +
+      scale_alpha_discrete(range = c(0.35,1),
+                           labels = c("Overprediction",
+                                      "Underprediction",
+                                      "Dispersion"),
+                           name = "Components of the WIS") +
+      scale_x_discrete(name = "",
+                       breaks = c("IMF", "bvar", "bvar_qu", "ar"),
+                       labels = c("IMF", "BVAR", "BVAR_QU", "AR")) +
+      scale_y_continuous(name = "WIS", limits = c(0, maxval)) +
+      scale_fill_met_d("Hokusai1") +
+      #scale_fill_brewer(palette = "Set2", 
+      #                  name = "Model Type")+
+      xlab("") +
+      #labs(fill = "Model Type") +
+      theme_uqimf() %+replace%
+      theme(axis.text.x = element_text(size = 8, angle = 90, hjust = .5, vjust = .5, face = "plain"),
+            strip.text = element_text(size = 8)) +
+      ggtitle(plot_name) +
+      theme(#legend.title=element_blank(),
+            legend.position = "none")
+
+    return(plt)
+
+  }
+
+  horizon_path_plot <- function(score_data,
+                                score_rule,
+                                ylab = score_rule, 
+                                facet = NULL,
+                                title = NULL){
+
+    path_plot <- ggplot(score_data, 
+           aes(x = horizon,
+               y = get(score_rule), 
+               color = source)) +
+
+      scale_color_met_d("Hokusai1", breaks = c("IMF", "bvar", "ar", "bvar_qu"),
+                       labels = c("IMF", "BVAR", "AR", "BVAR_QU")) +
+
+      #scale_color_brewer(palette = "Set2") +
+      geom_line() +
+      geom_point() +
+      ylab(ylab) +
+      xlab("Forecast Horizon") +
+      guides(fill = "none", colour = "none") +
+      theme_uqimf() %+replace%
+      theme(legend.title=element_blank(),
+            legend.position = "none") +
+      ggtitle(title)
+
+    if(!is.null(facet)){
+
+      path_plot <- path_plot +
+      facet_wrap(~ get(facet),
+                 scales = "free") 
+    }
+
+    return(path_plot)
+
+  }
+
+  dir_wis_plot <- wis_plot(decomp_data, "directional", xmax)
+  abs_wis_plot <- wis_plot(decomp_data, "absolute", xmax)
+
+  c50plot <- horizon_path_plot(cvgscores, "coverage_50", "CI Coverage - 50", facet = "error_method", title = "Central Interval Coverage - alpha = 50") +
+    geom_hline(aes(yintercept = 0.5)) +
+    scale_y_continuous(labels = paste0(seq(0, 100, by = 25), "%"),
+                       breaks = seq(0,1, by = 0.25),
+                       limits = c(0,1))
+
+  c80plot <- horizon_path_plot(cvgscores, "coverage_80", "CI Coverage - 80", facet = "error_method", title = "Central Interval Coverage - alpha = 80") +
+    geom_hline(aes(yintercept = 0.8)) +
+    scale_y_continuous(labels = paste0(seq(0, 100, by = 25), "%"),
+                       breaks = seq(0,1, by = 0.25),
+                       limits = c(0,1))
+
+  erow <-  ggplot() + theme_void()
+
+  aeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meanae", "Absolute Error", title = "Point Forecast - Abs. Error")
+
+  squeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meansque", "Squared Error", title = "Point Forecast - Squ. Error")
+
+  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - expanding window") +
+    scale_y_continuous(limits = c(0.07,1.05))
+
+  crpsplot_loo <- horizon_path_plot(crps_scores_loo |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - LOO") +
+    scale_y_continuous(limits = c(0.07,1.05))
+
+  ovr_plot <- 
+    (dir_wis_plot | abs_wis_plot) /
+    (plot_spacer()) /
+    (c50plot | c80plot) /
+    (plot_spacer()) /
+    (squeplot | aeplot | crpsplot_rw | crpsplot_loo) +
+    plot_layout(guides = "collect", 
+                heights = c(0.2, 0.05, 0.2, 0.05, 0.2)) &
+      plot_annotation(tag_levels = 'I')  &
+      theme(legend.position = 'bottom', 
+            legend.box="vertical", legend.margin=margin())
+
+  return(ovr_plot)
+}
+
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "pcpi_pch")
+
+```
+\newpage
+
+## GDP
+
+```{r gdpovr, echo = FALSE, warning = TRUE, fig.dim=c(12,12)}
+
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch")
+```
 
@@
 
-scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
-scores_cvgshort <- fread(here("quantile_forecasts", "cvg_pooled.csv"))
+scores <- fread(here("scores", "ci_scores.csv"))
+scores_cvgshort <- fread(here("scores", "cvg_pooled.csv"))
 
@@
 
-cvgdat_cpin <- data.table::fread(here("quantile_forecasts", "cvg_pooled_directionalsymmetric.csv")) |>
+cvgdat_cpin <- data.table::fread(here("scores", "cvg_pooled_directionalsymmetric.csv")) |>
   setnames("model", "source") |>
@@
 
-cvgdat_gdpn <- data.table::fread(here("quantile_forecasts", "cvg_pooled_directionalsymmetric.csv")) |>
+cvgdat_gdpn <- data.table::fread(here("scores", "cvg_pooled_directionalsymmetric.csv")) |>
   setnames("model", "source") |>
@@
 ```
+
+\newpage
+```{r, cpitable = FALSE, echo=FALSE}
+#bring into long format
+long_scores <- gather_scores(all_scores, "pcpi_pch")
+
+scores_to_table(all_scores, "pcpi_pch")
+
+```
+
+## Inflation
+
+```{r cpitileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
+
+plots_is <- vector(mode = "list", length = 4)
+plots_cr <- vector(mode = "list", length = 4)
+
+hor_list <- as.list(1:4)
+
+plots_is <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "interval"))
+plots_cr <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "crps"))
+
+ovr_plot <- 
+  (plots_is[[1]] + plots_cr[[1]]) /
+  (plots_is[[2]] + plots_cr[[2]]) /
+  (plots_is[[3]] + plots_cr[[3]]) /
+  (plots_is[[4]] + plots_cr[[4]]) +
+  plot_layout(heights = c(1, 1,1,1)) &
+    plot_annotation(tag_levels = 'I')  &
+    theme(legend.position = 'right', 
+          legend.box="vertical", legend.margin=margin())
+
+ovr_plot
+
+```
+
+## GDP
+
+```{r gdptable, echo = FALSE}
+
+long_scores <- gather_scores(all_scores, "ngdp_rpch")
+scores_to_table(all_scores, "ngdp_rpch")
+
+```
+
+```{r gdptileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
+
+plots_is <- vector(mode = "list", length = 4)
+plots_cr <- vector(mode = "list", length = 4)
+
+hor_list <- as.list(1:4)
+
+plots_is <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "interval"))
+plots_cr <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "crps"))
+
+ovr_plot <- 
+  (plots_is[[1]] + plots_cr[[1]]) /
+  (plots_is[[2]] + plots_cr[[2]]) /
+  (plots_is[[3]] + plots_cr[[3]]) /
+  (plots_is[[4]] + plots_cr[[4]]) +
+  plot_layout(heights = c(1, 1,1,1)) &
+    plot_annotation(tag_levels = 'I')  &
+    theme(legend.position = 'right', 
+          legend.box="vertical", legend.margin=margin())
+
+ovr_plot
+
+```

### 2023-09-15 manuscript/manuscript.tex
manuscript updates

--- 2023-09-08 manuscript/manuscript.tex
@@
 \usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
+\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
 \usepackage{longtable,booktabs,array}
@@
 
-\hypertarget{a-short-note-on-error-handling}{%
-\section{A short note on error handling}\label{a-short-note-on-error-handling}}
+\hypertarget{scores-by-error-method-horizon-and-forecast-source}{%
+\section{Scores, by error method, Horizon and forecast source}\label{scores-by-error-method-horizon-and-forecast-source}}
 
-In almost all 72 cases, absolute error handling gives lower scores than directional error handling.
-The only exception is the inflation series for the IMF forecasts and horizon 0, where the expanding window and rolling window method give \textit{slightly} lower scores for the directional methodology.
-We thus decide to focus on the absolute errors in this document.
+\hypertarget{inflation}{%
+\subsection{Inflation}\label{inflation}}
 
-\hypertarget{scores-by-estimation-method-horizon-and-forecast-source}{%
-\section{Scores, by estimation method, Horizon and forecast source}\label{scores-by-estimation-method-horizon-and-forecast-source}}
+\includegraphics{manuscript_files/figure-latex/overall_assessment_ew-1.pdf}
+\newpage
+Some notes:
 
+\begin{itemize}
+\item Inflation: directional vs. absolute errors:
+\begin{itemize}
+\item difference small for IMF method, absolute slighly better, likely due to longer central intervals
+\item AR and BVAR profit more from directional correction (upward bias)
+\item for expanding window method, difference in coverage is smaller (-> structural breaks)
+
+\end{itemize}
+\item Inflation overall scores: IMF forecasts outperform others
+\begin{itemize}
+\item lower scores for point forecasts
+\item lower WIS 
+\item lower bias (compute directly?)
+\end{itemize}
+
+\item GDP Growth: more similar results for different sources
+\begin{itemize}
+\item lower scores at shorter horizons, more similar at larger horizons
+\item IMF forecasts better only for absolute error method
+\end{itemize}
+\end{itemize}
+
+\newpage
+
+\hypertarget{gdp}{%
+\subsection{GDP}\label{gdp}}
+
+\begin{verbatim}
+## Warning: Using alpha for a discrete variable is not advised.
+## Using alpha for a discrete variable is not advised.
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: Removed 1 rows containing missing values (`geom_bar()`).
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/gdpovr_ew-1.pdf}
+
+\hypertarget{expanding-window---scores-by-error-method-horizon-and-forecast-source}{%
+\section{Expanding Window - Scores, by error method, Horizon and forecast source}\label{expanding-window---scores-by-error-method-horizon-and-forecast-source}}
+
+\hypertarget{inflation-1}{%
+\subsection{Inflation}\label{inflation-1}}
+
+\includegraphics{manuscript_files/figure-latex/overall_assessment-1.pdf}
+\newpage
+
+\hypertarget{gdp-1}{%
+\subsection{GDP}\label{gdp-1}}
+
+\begin{verbatim}
+## Warning: Using alpha for a discrete variable is not advised.
+## Using alpha for a discrete variable is not advised.
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: Removed 1 rows containing missing values (`geom_bar()`).
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/gdpovr-1.pdf}
+
+\hypertarget{coverage-by-target-methods-and-source}{%
+\section{Coverage, by target, methods and source}\label{coverage-by-target-methods-and-source}}
+
+\includegraphics{manuscript_files/figure-latex/cvgplot-1.pdf}
+
+\newpage
 \begin{longtable}{l|rrr}
@@
 
-\hypertarget{inflation}{%
-\subsection{Inflation}\label{inflation}}
+\hypertarget{inflation-2}{%
+\subsection{Inflation}\label{inflation-2}}
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\includegraphics{manuscript_files/figure-latex/cpitileplot-1.pdf}
 
-\hypertarget{gdp}{%
-\subsection{GDP}\label{gdp}}
+\hypertarget{gdp-2}{%
+\subsection{GDP}\label{gdp-2}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-
-\hypertarget{coverage-by-target-methods-and-source}{%
-\section{Coverage, by target, methods and source}\label{coverage-by-target-methods-and-source}}
-
-\includegraphics{manuscript_files/figure-latex/cvgplot-1.pdf}
+\includegraphics{manuscript_files/figure-latex/gdptileplot-1.pdf}
 

### 2023-09-15 scripts/toy-scripts/bvar_overprediction.R
document overprediction issue

@@ -1,0 +1,89 @@
+#why do directional errors give lower coverage?
+
+library(here)
+library(data.table)
+library(ggplot2)
+
+devtools::load_all()
+
+.d <- `[`
+
+cnt <- "ITA"
+trgtyr <- 2010
+
+
+qus <- ci_to_quantiles(as.numeric(c(.5,.8)), "directional") #always directional
+
+n_qus <- length(qus)
+
+no_pairs <- floor(n_qus/2)
+
+
+alpha_vals <- seq(0.5, 0.75, length.out = no_pairs)
+
+#inner and outer quantile levels
+qu_lvls <- lapply(seq_along(1:no_pairs),
+                  function(ind) c(qus[ind], qus[(n_qus)-(ind-1)], alpha_vals[ind]))
+
+
+
+
+sub_weodat <- data.table::fread(here("WEOforecasts_tidy.csv")) |>
+  .d(g7 == 1) |>
+  .d(horizon < 2)
+
+fcdat <- bvar_qus |>
+  .d(!is.na(horizon)) |>
+  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
+  .d(target == "pcpi_pch")
+
+
+
+pldat <- fcdat |>
+  .d(,.(country, target, horizon, quantile,prediction, target_year)) |>
+  .d(, quantile := paste0("quant", quantile)) |>
+  data.table::dcast(country + target + horizon  + target_year ~ quantile,
+                    value.var = "prediction")
+
+
+fctodis <- fcdat |>
+  .d(target_year == trgtyr) |>
+  .d(country == cnt) |>
+  .d(horizon < 2)
+
+
+year_range <- unique(fcdat$target_year)
+
+ggplot() +
+  geom_line(
+    aes(x = target_year, y = true_value,
+        group = country, color = country),
+    data = fcdat |>
+      .d(country == cnt) |>
+      .d(target_year %in% year_range)) +
+  ggtitle(paste0("BVAR predictions, for ", cnt)) +
+  ylab("True value") +
+
+  lapply(qu_lvls, function(qupr){
+    geom_linerange(
+      aes(x = target_year,
+          ymin = get(paste0("quant", qupr[1])),
+          ymax = get(paste0("quant", qupr[2])),
+          color = country),
+      data = pldat |>
+        .d(country == cnt) ,
+      lwd = 1.5, alpha = qupr[3], show.legend = TRUE)
[…]

### 2023-09-26 scripts/ci_lengths.R
ci lengths plot

@@ -1,0 +1,124 @@
+imf_fc <- fread(here("quantile_forecasts", "quantile_forecasts.csv")) |>
+  .d(source == "IMF") |>
+  .d(country == "DEU") |>
+  .d(error_method == "absolute") |>
+  .d(method == "rolling window") |>
+  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
+  .d(, quantile := paste0("q", quantile)) |>
+  .d(, .(country, target, target_year, horizon, quantile, prediction)) |>
+  dcast(country + target + target_year + horizon ~ quantile) |>
+  .d(, cil5 := q0.75-q0.25) |>
+  .d(, cil9 := q0.9 - q0.1) |>
+  .d(, meancil5 := round(mean(cil5),1), by = c("horizon", "target")) |>
+  .d(, meancil9 := round(mean(cil9),1), by = c("horizon", "target")) |>
+  .d(, .(target, horizon, meancil5, meancil9)) |>
+  unique() |>
+  #.d(, target := factor(ifelse(target == "pcpi_pch", "Inflation", "GDP Growth")),)
+  .d(, target := factor(target,
+                        levels = c("pcpi_pch", "ngdp_rpch"),
+                        labels = c("Inflation", "GDP Growth"),
+                        ordered = "TRUE") )
+
+print(imf_fc)
+
+baseval <- 0
+
+imf_fc <- imf_fc |>
+  .d(, q0.1 := baseval -meancil9/2) |>
+  .d(, q0.25 := baseval -meancil5/2) |>
+  .d(, q0.75 := baseval + meancil5/2) |>
+  .d(, q0.9 := baseval + meancil9/2) |>
+  .d(, .(target, horizon, q0.1, q0.25, q0.75, q0.9)) #|>
+  #melt(id.vars = c("target", "horizon"), value.name = "prediction", variable.name = "quantile")
+
+imf_fc$target_year <- factor(rep(1:4, 2),
+                             levels = 1:4,
+                             labels = c("Fall, same year", "Spring, same year",
+                             "Fall, next year", "Spring, next year"),
+                            ordered = TRUE)
+
+#imf_fc$target_year <- rep(1:4, times = 2)
+
+
+
+qu_lvlss <- function(lvls){
+
+  qus <- ci_to_quantiles(lvls, "directional") #always directional
+
+  n_qus <- length(qus)
+
[…]

### 2023-09-26 presentation/presentation.tex
presentation files

%% Beispiel-Präsentation mit LaTeX Beamer im KIT-Design
%% entsprechend den Gestaltungsrichtlinien vom 1. August 2020
%%
%% Siehe https://sdqweb.ipd.kit.edu/wiki/Dokumentvorlagen

%% Beispiel-Präsentation
\documentclass[en]{sdqbeamer} 
\usepackage{graphicx}

%% Titelbild
\titleimage{banner_2020_kit}

%% Gruppenlogo
\grouplogo{logo_empty.jpg}

%% Gruppenname und Breite (Standard: 50 mm)
\groupname{}
%\groupnamewidth{50mm}

% Beginn der Präsentation

\title[Simple Prediction Intervals]{Simple and Transparent Macroeconomic Prediction Intervals}
\subtitle{} 
\author[Friederike Becker, Fabian Krüger, Melanie Schienle]{Friederike Becker, Fabian Krüger, Melanie Schienle}

\date[28.\,9.\,2023]{September 28, 2023}

% Literatur

\usepackage[citestyle=authoryear,bibstyle=numeric,hyperref,backend=biber]{biblatex}
\addbibresource{presentation.bib}
\bibhang1em

\begin{document}
\setbeamertemplate{caption}{\raggedright\insertcaption\par}

%Titelseite
\KITtitleframe

%Inhaltsverzeichnis
\begin{frame}{Overview}
\tableofcontents
\end{frame}

\section{Setting}

%\subsection{Fixed-Event forecasting in Economics}
\begin{frame}{An economist's favorite pastime}
	\begin{itemize}
	    \item various institutions issue forecasts for annual macroeconomic targets
     \begin{itemize}
        \item most prominent targets: (real) GDP growth and inflation
        \item for Germany, sources are (among others) the Bundesbank, the ifo institute, the OECD
         \item fixed-event forecasts: target date is fixed, forecast date is not
     \end{itemize}
     \item forecasts are often disseminated widely
     \begin{itemize}
         \item extensive media coverage, influence on political discussions
         \item relevant for real-world outcomes (public budget planning, collective bargaining)
     \end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}[t]{Can we really be that sure?}

\begin{columns}
\begin{column}{0.4\textwidth}
   	\begin{itemize}
         \item usual practice: issue point forecasts only
         \begin{itemize}
	    \item uncertainty is at best acknowledged, rarely quantified
	\end{itemize}
        %\item media reception often fixated on zero
        \item forecasts of different horizons are often left uncontextualized
        \item distributional forecasts supposedly would require extra modeling effort
    \end{itemize}
    \vspace{2cm}
\end{column}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\textwidth]{figures/recession_light_underlined_green_smaller_date.jpg} 
        \caption{Source: tagesschau.de}
        \label{fig:enter-label}
    \end{figure}     
\end{column}
\end{columns}
\end{frame}

\begin{frame}[t]{Contributions of this work}
\begin{itemize}
    \item simple and transparent method of attaching prediction intervals 
\item show that attaching distributional forecasts to an existing
\item evaluate on years 1999-2021
\end{itemize}
\end{frame}

% \begin{flushright}
% \includegraphics[width = 8cm]{figures/recession_light.JPG}    
% \end{flushright}

%\subsection{Data Source: IMF World Economic Outlook}
\begin{frame}{Data Source: IMF World Economic Outlook}
	\begin{itemize}
		\item survey by the IMF staff, published bi-annually
		\begin{itemize}
            \item contains forecasts with up to 6 years horizon and historic truth values
		    \item publication in April (horizon for current year $\approx$ 8 months) and in October ($\approx$ 2 months)
		\end{itemize}
    \item publicly available publication
    \item targets: real GDP growth and CPI inflation 
    \item available since 1990, giving $\sim$30 years of forecast-truth pairs per country and forecast horizon
    \item forecasts for G7 countries are (nearly) uninterrupted
    \begin{itemize}
        \item forecasts for 196 countries in total are available
    \end{itemize}
	\end{itemize}
\end{frame}

\section{Methods}
\begin{frame}{Methods}
We apply an attractively simple and cheap method. For a given country and target:
\begin{itemize}
    \item given forecasts $\hat{y}_{t, h}$ and the realized true values $y_{t}$ ...
    \begin{itemize}
        \item for target year $t$, horizon $h$
    \end{itemize}
    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-9 \leq t^* < t \}$, containing the last nine forecast errors
    \begin{itemize}
        \item based on \textit{absolute} errors $\hat{e} = |y_{t} - \hat{y}_{t, h}| $
        \item sets are stratified by country, target and horizon
    \end{itemize}
    \item for $\alpha \in \{0.5, 0.8\}$, compute $q^{\alpha}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \alpha \right)$
    \item and compute the upper and lower endpoints of a central prediction interval as 
    \begin{itemize}
        \item $u^{\alpha}_{t,h} = \hat{y}_{t, h} + q^{\alpha}_{t, h}$ 
        \item $l^{\alpha}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\alpha}_{t, h}$
    \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Benchmarks}
    We compare with benchmarks:
\begin{enumerate}
    \item same methodology, alternative point forecasts
    \begin{itemize}
        \item autoregressive (AR) model
        \item Primiceri Bayesian vector autoregressive (BVAR) model
    \end{itemize}
    \item directly generated distributional forecasts
    \begin{itemize}
        \item obtained from the BVAR model
    \end{itemize}
\end{enumerate}
\begin{itemize}
    \item trained on quarterly data, with \textit{slight informational advantage - specify this!} 
\end{itemize}

\end{frame}

\section{Results}
\begin{frame}{Scores - GDP Growth}
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp_new.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

%\begin{frame}{Scores - Inflation}
%%    \begin{figure}
 %       \centering
 %       \includegraphics[width=0.45\textwidth]{figures/scores_absolute errors_cpi.JPG} 
 %       \label{fig:enter-label}
 %   \end{figure} 
%\end{frame}

\begin{frame}{Calibration - Interval Coverage Levels}
%\textit{Here, I'll instead map the colors to the different forecast sources (currently mapped to the window method), so we'll just have one plot each}
    %Coverage at the 50\% and 80\% central interval: \\ 
    \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/coverage.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}
\end{frame}

\begin{frame}{Increasing Uncertainty}
%Width of Prediction Intervals, by Horizon
%\textit{include graphic or table showing increasing uncertainty with rising horizons}\\

\begin{columns}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{figures/horizon_uncc.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}
\end{column}
\begin{column}{0.4\textwidth}
\centering
\textbf{Average length of intervals}
\begin{table}
\begin{tabular}{ l c c }
&   50\%  & 80\%\\[0.3em]
\multicolumn{3}{c}{\textbf{GDP Growth}}\\
Fall,  SY & 0.5 & 0.9\\ 
Spring, SY &0.8 &2.1 \\ 
Fall, NY & 2.2 & 3.9\\ 
Spring, NY &2.4 &4.9 \\[0.3em] 
\multicolumn{3}{c}{\textbf{Inflation}}\\
%&   50\%  & 80\%\\[0.3em]
Fall,  SY & 0.3 & 0.6\\ 
Spring, SY &0.5 &1.3 \\ 
Fall, NY & 1.2 & 2.2\\ 
Spring, NY &1.9 &2.4 \\ 
\end{tabular}
\end{table}
\vspace{1.25cm}
%\begin{table}
%\begin{tabular}{ l c c }
%\multicolumn{3}{c}{\textbf{Inflation}}\\
%%&   50\%  & 80\%\\[0.3em]
%Fall,  SY & 0.3 & 0.6\\ 
%Spring, SY &0.5 &1.3 \\ 
%Fall, NY & 1.2 & 2.2\\ 
%Spring, NY &1.9 &2.4 \\ 
%\end{tabular}
%\end{table}
\end{column}
\end{columns}

%\textit{relate back to article shown in the beginning, which also mentions IMF forecast of 0.1 percent $\rightarrow$ almost 50\% of any predictive intervals at this time would actually be below zero}
\end{frame}

\begin{frame}{Robustness Checks}
\textit{each will be linked to a short slide in Appendix giving the alternative results}
\begin{itemize}
    \item error extraction method: absolute vs. directional errors
    \item window method
    \item potential dependency of results on discretization \\
    \textit{what I mean by this: does the fact that we are extracting quantiles from the samples influence the results? Show results for sample-based CRPS}
\end{itemize}
\end{frame}

\section{Outlook}

\begin{frame}{Summing up}
\begin{itemize}
\item Attaching distributional forecasts via past forecast errors to an existing base of point forecasts is
    \begin{itemize}
        \item cheap
        \item competitive
        \item transparent
    \end{itemize}
\item Attachment of uncertainty to point forecasts is often substantial, making its communication necessary
\item IMF forecasts are valuable source for distributional forecasts in their own right \bigskip \\
\item     Outlook
    \begin{itemize}
        \item employ method that ideally utilizes the cross-section dimension, e.g. via Hierarchical Bayesian Modeling
    \end{itemize}

\end{itemize}
\end{frame}

\begin{frame}{Making it public}
\textit{Refer to Shiny App}    
\end{frame}

%\begin{frame}{Beispielinhalt: Literatur}
%    Literaturzitat: \cite{klare2021jss}
%end{frame}
%\begin{frame}
%        Bei Frames ohne Titel wird die Kopfzeile nicht angezeigt, und  
%    der freie Platz kann für Inhalte genutzt werden.
%\end{frame}

%\begin{frame}[plain]
%    Bei Frames mit Option \texttt{[plain]} werden weder Kopf- noch Fußzeile angezeigt.
%\end{frame}

%\begin{frame}[t]{Beispielinhalt}
%    Bei Frames mit Option \texttt{[t]} werden die Inhalte nicht vertikal zentriert, sondern an der Oberkante begonnen.
%\end{frame}

\appendix
\beginbackup

%\begin{frame}{Literatur}
%\begin{exampleblock}{Backup-Teil}
%    Folien, die nach \texttt{\textbackslash beginbackup} eingefügt werden, zählen nicht in die Gesamtzahl der Folien.
%\end{exampleblock}

%\printbibliography
%\end{frame}

%\section{Farben}
%% ----------------------------------------
%% | Test-Folie mit definierten Farben |
%% ----------------------------------------
%% ----------------------------------------
%% | /Test-Folie mit definierten Farben |
%% ----------------------------------------
\backupend

\end{document}

### 2023-09-26 presentation/make_plots.R

@@ -1,0 +1,236 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+library(MetBrewer)
+library(purrr)
+library(lattice)
+library(gt)
+library(rlang)
+library(tidyverse)
+devtools::load_all()
+.d <- `[`
+
+
+######## WIS Data
+scores <- fread(here("scores", "ci_scores.csv"))
+
+wis_scores <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  setnames("model", "source")
+
+bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  .d(,model := "bvar_qu") |>
+  setnames("model", "source") |>
+  .d(,error_method := "directional") |>
+  .d(,method := "rolling window") #change later
+
+
+bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores |> copy() |> .d(, error_method := "absolute"))
+
+wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
+  .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
+                     label = c("IMF", "BVAR", "BVAR - direct", "AR")))
+
+
+####Coverage Data
+scores_cvgshort <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE)
+
+
+bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE) |>
+  .d(, source := "bvar_qu") |>
+  .d(, method := "rolling window") |>
+  .d(, error_method := "absolute")
+
+
+bvar_scores_cvgshort <- rbind(bvar_scores_cvgshort, bvar_scores_cvgshort |> copy() |> .d(, error_method := "directional"))
+
+
+point_scores <- data.table::fread(here("scores", "pointfc_scores.csv"))
+
+scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
+
+cpi_plot <- ovr_assessment_plot(wis_scores, "pcpi_pch")
[…]

### 2023-09-26 presentation/presentation.tex
update presentation files

@@
 \multicolumn{3}{c}{\textbf{GDP Growth}}\\
-Fall,  SY & 0.5 & 0.9\\ 
-Spring, SY &0.8 &2.1 \\ 
-Fall, NY & 2.2 & 3.9\\ 
-Spring, NY &2.4 &4.9 \\[0.3em] 
+Fall,  SY & 0.5 & 1.1\\ 
+Spring, SY &1.2 &2.1 \\ 
+Fall, NY & 1.9 & 3.5\\ 
+Spring, NY &2.2 &4.0 \\[0.3em] 
 \multicolumn{3}{c}{\textbf{Inflation}}\\
 %&   50\%  & 80\%\\[0.3em]
-Fall,  SY & 0.3 & 0.6\\ 
-Spring, SY &0.5 &1.3 \\ 
-Fall, NY & 1.2 & 2.2\\ 
-Spring, NY &1.9 &2.4 \\ 
+Fall,  SY & 0.3 & 0.5\\ 
+Spring, SY &0.6 &1.1 \\ 
+Fall, NY & 1.1 & 1.8\\ 
+Spring, NY &1.3 &2.1 \\ 
 \end{tabular}
@@
 \end{frame}
+\addtocounter{framenumber}{-1}
+\begin{frame}{Will Germany avoid recession?}
+%Width of Prediction Intervals, by Horizon
+%\textit{include graphic or table showing increasing uncertainty with rising horizons}\\ 
+\begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figures/horizon_uncc_germany2023.pdf}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure}
+
+%\textit{relate back to article shown in the beginning, which also mentions IMF forecast of 0.1 percent $\rightarrow$ almost 50\% of any predictive intervals at this time would actually be below zero}
+\end{frame}
 
@@
     \item window method
-    \item potential dependency of results on discretization \\
+    \item potential dependency of results on quantile extraction \\
     \textit{what I mean by this: does the fact that we are extracting quantiles from the samples influence the results? Show results for sample-based CRPS}

### 2023-09-26 presentation/make_plots.R

@@ -12,6 +12,8 @@ devtools::load_all()
 .d <- `[`
 
 
+chosen_method <- "rolling window"
+
 ######## WIS Data
 scores <- fread(here("scores", "ci_scores.csv"))
 
@@ -25,15 +27,17 @@ bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
   .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
   .d(,model := "bvar_qu") |>
   setnames("model", "source") |>
-  .d(,error_method := "directional") |>
-  .d(,method := "rolling window") #change later
+  .d(,error_method := "absolute") |>
+  .d(,method := chosen_method) #change later
 
 
-bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores |> copy() |> .d(, error_method := "absolute"))
+#bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores)# |> copy() |> .d(, error_method := "absolute"))
 
 wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
   .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
-                     label = c("IMF", "BVAR", "BVAR - direct", "AR")))
+                     label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
+  .d(method == chosen_method) |>
+  .d(error_method == "absolute")
 
 
 ####Coverage Data
@@ -44,7 +48,7 @@ scores_cvgshort <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
 bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
   setnames("model", "source", skip_absent = TRUE) |>
   .d(, source := "bvar_qu") |>
-  .d(, method := "rolling window") |>
+  .d(, method := chosen_method) |>
   .d(, error_method := "absolute")
 
 
@@ -78,7 +82,7 @@ scores <- fread(here("scores", "ci_scores.csv"))
 scores_cvgshort <- fread(here("scores", "cvg_pooled.csv")) |>
   rbind(fread(here("scores", "bvar_cvg_pooled.csv")) |>
           .d(, error_method := "absolute") |>
-          .d(, method := "rolling window"))
[…]

### 2023-09-26 scripts/ci_lengths.R

@@ -1,6 +1,20 @@
+library(here)
+library(data.table)
+devtools::load_all()
+
+source(here("specs", "specs.R"))
+
+.d <- `[`
+
+max_year <- specs$score_max_year
+min_year <- specs$min_year
+score_min_year <- specs$score_min_year
+tv_release <- specs$tv_release
+window_length <- specs$window_length
+
 imf_fc <- fread(here("quantile_forecasts", "quantile_forecasts.csv")) |>
+  .d(target_year <= max_year) |>
   .d(source == "IMF") |>
-  .d(country == "DEU") |>
   .d(error_method == "absolute") |>
   .d(method == "rolling window") |>
   .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>

### 2023-09-26 presentation/presentation.tex
update presentation plots and notes

@@
 
-\title[Simple Prediction Intervals]{Simple and Transparent Macroeconomic Prediction Intervals}
+\title[Simple Prediction Intervals]{Simple and Transparent Macroeconomic Distributional Forecasts}
 \subtitle{} 
@@
 \begin{itemize}
-    \item simple and transparent method of attaching prediction intervals 
-\item show that attaching distributional forecasts to an existing
-\item evaluate on years 1999-2021
+    \item show that attaching prediction intervals to an existing base of point forecasts can be 
+    \begin{itemize} 
+    \item simple
+    \item cheap
+    \end{itemize}   
+    \item provide solidly performing distributional forecasts for 
+    \begin{itemize}
+    \item  GDP growth and inflation
+    \item  all G7 countries
+    \item  current and next year 
+    \end{itemize}
+    %\item simple and transparent method of attaching prediction intervals 
+%\item show that attaching distributional forecasts to an existing
+%\item for up to one and a half years into the future 
+%\item evaluate on years 1999-2021
 \end{itemize}
@@
     \begin{itemize}
-        \item based on \textit{absolute} errors $\hat{e} = |y_{t} - \hat{y}_{t, h}| $
+        \item based on \textit{absolute} errors $\hat{e}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
         \item sets are stratified by country, target and horizon
@@
 \begin{itemize}
-    \item trained on quarterly data, with \textit{slight informational advantage - specify this!} 
+    \item trained on quarterly data, with slight informational advantage
 \end{itemize}
@@
 
-\begin{frame}{Robustness Checks}
-\textit{each will be linked to a short slide in Appendix giving the alternative results}
+\begin{frame}{Robustness Checks / Alternative Methods}
 \begin{itemize}
     \item error extraction method: absolute vs. directional errors
-    \item window method
+    \begin{itemize}
+    \item similar scores, worse calibration \hyperlink{errorextraction}{\beamerbutton{link}}
+    \end{itemize}
+    \item window method: rolling vs. expanding window
+    \begin{itemize}
+    \item slightly improved coverage and scores, at the cost of interpretability \hyperlink{extractionmethod}{\beamerbutton{link}}
+    \end{itemize}
     \item potential dependency of results on quantile extraction \\
-    \textit{what I mean by this: does the fact that we are extracting quantiles from the samples influence the results? Show results for sample-based CRPS}
+    \begin{itemize}
+        \item ordering between forecasts remains the same with sample-based CRPS \hyperlink{samplecrps}{\beamerbutton{link}}
+    \end{itemize}
 \end{itemize}
@@
     \end{itemize}
-\item Attachment of uncertainty to point forecasts is often substantial, making its communication necessary
+\item Uncertainty around point forecasts is often substantial, making its communication necessary
 \item IMF forecasts are valuable source for distributional forecasts in their own right \bigskip \\
@@
 \beginbackup
+\begin{frame}{Directional Errors - Scores}
+\label{errorextraction}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_directional.pdf}
+        %\caption{Coverage at the 50 and 80 percent level}
+    \end{figure}
+\end{frame}
+\begin{frame}{Directional Errors - Coverage}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/coverage_directional.pdf}
+        %\caption{Coverage at the 50 and 80 percent level}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Expanding Window - Scores}
+\label{extractionmethod}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_ew.pdf}
+        %\caption{Coverage at the 50 and 80 percent level}
+    \end{figure}
+\end{frame}
+\begin{frame}{Expanding Window - Coverage}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/coverage_ew.pdf}
+        %\caption{Coverage at the 50 and 80 percent level}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{CRPS by sample}
+\label{samplecrps}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.7\textwidth]{figures/crpssample.png}
+        %\caption{Coverage at the 50 and 80 percent level}
+    \end{figure}
+\end{frame}
 

### 2023-09-26 presentation/make_plots.R

@@ -13,6 +13,7 @@ devtools::load_all()
 
 
 chosen_method <- "rolling window"
+chosen_em <- "absolute"
 
 ######## WIS Data
 scores <- fread(here("scores", "ci_scores.csv"))
@@ -27,17 +28,17 @@ bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
   .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
   .d(,model := "bvar_qu") |>
   setnames("model", "source") |>
-  .d(,error_method := "absolute") |>
+  .d(,error_method := chosen_em) |>
   .d(,method := chosen_method) #change later
 
 
-#bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores)# |> copy() |> .d(, error_method := "absolute"))
+#bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores)# |> copy() |> .d(, error_method := chosen_em))
 
 wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
   .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
                      label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
   .d(method == chosen_method) |>
-  .d(error_method == "absolute")
+  .d(error_method == chosen_em)
 
 
 ####Coverage Data
@@ -49,7 +50,7 @@ bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
   setnames("model", "source", skip_absent = TRUE) |>
   .d(, source := "bvar_qu") |>
   .d(, method := chosen_method) |>
-  .d(, error_method := "absolute")
+  .d(, error_method := chosen_em)
 
 
 bvar_scores_cvgshort <- rbind(bvar_scores_cvgshort, bvar_scores_cvgshort |> copy() |> .d(, error_method := "directional"))
@@ -81,7 +82,7 @@ dev.off()
 scores <- fread(here("scores", "ci_scores.csv"))
 scores_cvgshort <- fread(here("scores", "cvg_pooled.csv")) |>
   rbind(fread(here("scores", "bvar_cvg_pooled.csv")) |>
-          .d(, error_method := "absolute") |>
+          .d(, error_method := chosen_em) |>
[…]

### 2023-09-26 scripts/ci_lengths_germany2023.R

@@ -1,0 +1,144 @@
+library(here)
+library(data.table)
+devtools::load_all()
+
+source(here("specs", "specs.R"))
+
+.d <- `[`
+
+max_year <- specs$score_max_year
+min_year <- specs$min_year
+score_min_year <- specs$score_min_year
+tv_release <- specs$tv_release
+window_length <- specs$window_length
+
+imf_fc <- fread(here("quantile_forecasts", "quantile_forecasts.csv")) |>
+  .d(target_year == 2023) |>
+  .d(source == "IMF") |>
+  .d(target == "ngdp_rpch") |>
+  .d(country == "DEU") |>
+  .d(error_method == "absolute") |>
+  .d(method == "rolling window") |>
+  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
+  .d(, quantile := paste0("q", quantile)) |>
+  .d(, .(country, target, target_year, horizon, quantile, error_prediction)) |>
+  dcast(country + target + target_year + horizon ~ quantile) |>
+  .d(, cil5 := q0.75-q0.25) |>
+  .d(, cil9 := q0.9 - q0.1) |>
+  .d(, meancil5 := round(mean(cil5),1), by = c("horizon", "target")) |>
+  .d(, meancil9 := round(mean(cil9),1), by = c("horizon", "target")) |>
+  .d(, .(target, horizon, meancil5, meancil9)) |>
+  unique() |>
+  #.d(, target := factor(ifelse(target == "pcpi_pch", "Inflation", "GDP Growth")),)
+  .d(, target := factor(target,
+                        levels = c("pcpi_pch", "ngdp_rpch"),
+                        labels = c("Inflation", "GDP Growth"),
+                        ordered = "TRUE") )
+
+print(imf_fc)
+
+baseval <- 0.1
+
+imf_fc <- imf_fc |>
+  .d(, q0.1 := baseval -meancil9/2) |>
+  .d(, q0.25 := baseval -meancil5/2) |>
+  .d(, q0.75 := baseval + meancil5/2) |>
+  .d(, q0.9 := baseval + meancil9/2) |>
+  .d(, .(target, horizon, q0.1, q0.25, q0.75, q0.9)) #|>
+#melt(id.vars = c("target", "horizon"), value.name = "prediction", variable.name = "quantile")
+
+imf_fc$target_year <- factor(rep(1:4, 1),
+                             levels = 1:4,
+                             labels = c("Fall, same year", "Spring, same year",
[…]

### 2023-10-02 presentation/presentation.tex
final presentation files

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=gray,
+    filecolor=magenta,      
+    urlcolor=cyan,
+    pdftitle={Overleaf Example},
+    pdfpagemode=FullScreen,
+    }
+
+\urlstyle{same}
 
@@
 
-\date[28.\,9.\,2023]{September 28, 2023}
+\date[29.\,9.\,2023]{September 29, 2023}
 
@@
          \begin{itemize}
-	    \item uncertainty is at best acknowledged, rarely quantified
+	    \item uncertainty is at best acknowledged, rarely quantified \bigskip
 	\end{itemize}
         %\item media reception often fixated on zero
-        \item forecasts of different horizons are often left uncontextualized
+        \item forecasts of different horizons are often left uncontextualized \bigskip
         \item distributional forecasts supposedly would require extra modeling effort
@@
     \item cheap
+    \item transparent
     \end{itemize}   
-    \item provide solidly performing distributional forecasts for 
+    \item provide competitively performing distributional forecasts for 
     \begin{itemize}
@@
     \item  all G7 countries
-    \item  current and next year 
+    \item  current and next year targets
     \end{itemize}
@@
 		\end{itemize}
-    \item publicly available publication
+    \item publicly available publication\footnote{International Monetary Fund. 2023. \textit{World Economic Outlook: A Rocky Recovery.} Washington, DC. April.}
     \item targets: real GDP growth and CPI inflation 
-    \item available since 1990, giving $\sim$30 years of forecast-truth pairs per country and forecast horizon
-    \item forecasts for G7 countries are (nearly) uninterrupted
-    \begin{itemize}
-        \item forecasts for 196 countries in total are available
-    \end{itemize}
+    \item time range: available since 1990, giving $\sim$30 years of forecast-truth pairs %per country and forecast horizon
+    \item target locations: forecasts are issued for 196 countries in total
+    %\begin{itemize}
+    %    \item forecasts for 196 countries in total are available
+    %\end{itemize}
 	\end{itemize}
@@
     \end{itemize}
+    \item assess central interval coverage, score via the weighted interval score (WIS)\footnote{Bracher, J. et al. 2021. \textit{Evaluating
+Epidemic Forecasts in an Interval Format.} PLoS Computational Biology 17 (2)}
 \end{itemize}
@@
         \item autoregressive (AR) model
-        \item Primiceri Bayesian vector autoregressive (BVAR) model
+        \item Primiceri Bayesian vector autoregressive (BVAR) model\footnote{Primiceri, G.
+2005.
+\textit{Time Varying Structural Vector Autoregressions and Monetary Policy.} Review of Economic Studies 72.}
     \end{itemize}
@@
 \section{Results}
-\begin{frame}{Scores - GDP Growth}
+\begin{frame}{Scores }
 %\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
@@
     \begin{itemize}
-        \item employ method that ideally utilizes the cross-section dimension, e.g. via Hierarchical Bayesian Modeling
+        \item scale to more countries and forecast sources
+        \item implement alternative method that  utilizes the cross-section dimension%, e.g. via Hierarchical Bayesian Modeling
+        \item make forecasts easily and publicly accessable via shiny app
     \end{itemize}
@@
 \begin{frame}{Making it public}
-\textit{Refer to Shiny App}    
+\url{https://fredbec.shinyapps.io/macropi/}
+\begin{columns}
+\begin{column}{0.2\textwidth}
+    \begin{figure}
+        \centering
+        \includegraphics[width=\textwidth]{figures/shinycap2.png}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure} 
+\end{column}
+\begin{column}{0.6\textwidth}
+    \begin{figure}
+        %\centering
+        \includegraphics[width=0.7\textwidth]{figures/shinycap.jpg}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure}   
+\end{column}
+\end{columns}
+
 \end{frame}

### 2023-10-02 presentation/make_more_plots.R

@@ -1,0 +1,241 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+library(MetBrewer)
+library(purrr)
+library(lattice)
+library(gt)
+library(rlang)
+library(tidyverse)
+devtools::load_all()
+.d <- `[`
+
+
+chosen_method <- "rolling window"
+chosen_em <- "directional"
+
+######## WIS Data
+scores <- fread(here("scores", "ci_scores.csv"))
+
+wis_scores <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  setnames("model", "source")
+
+bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  .d(,model := "bvar_qu") |>
+  setnames("model", "source") |>
+  .d(,error_method := chosen_em) |>
+  .d(,method := chosen_method) #change later
+
+
+#bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores)# |> copy() |> .d(, error_method := chosen_em))
+
+wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
+  .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
+                        label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
+  .d(method == chosen_method) |>
+  .d(error_method == chosen_em)
+
+
+####Coverage Data
+scores_cvgshort <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE)
+
+
+bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE) |>
+  .d(, source := "bvar_qu") |>
+  .d(, method := chosen_method) |>
+  .d(, error_method := chosen_em)
+
+
+bvar_scores_cvgshort <- rbind(bvar_scores_cvgshort, bvar_scores_cvgshort |> copy() |> .d(, error_method := "directional"))
+
+
+point_scores <- data.table::fread(here("scores", "pointfc_scores.csv"))
+
[…]

### 2023-10-02 manuscript/manuscript.tex
manuscript update

@@
 expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
-leave-one-out\_interval\_score & 0.114 & 0.122 & 0.122 \\ 
+leave-one-out\_interval\_score & 0.112 & 0.123 & 0.123 \\ 
 leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
@@
 expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
-leave-one-out\_interval\_score & 0.262 & 0.265 & 0.286 \\ 
+leave-one-out\_interval\_score & 0.257 & 0.257 & 0.276 \\ 
 leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
@@
 expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
-leave-one-out\_interval\_score & 0.453 & 0.739 & 0.584 \\ 
+leave-one-out\_interval\_score & 0.443 & 0.746 & 0.587 \\ 
 leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
@@
 expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
-leave-one-out\_interval\_score & 0.486 & 1.025 & 0.760 \\ 
+leave-one-out\_interval\_score & 0.488 & 1.021 & 0.756 \\ 
 leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
@@
 expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
-leave-one-out\_interval\_score & 0.237 & 0.297 & 0.294 \\ 
+leave-one-out\_interval\_score & 0.235 & 0.297 & 0.295 \\ 
 leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
@@
 expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
-leave-one-out\_interval\_score & 0.411 & 0.540 & 0.489 \\ 
+leave-one-out\_interval\_score & 0.406 & 0.532 & 0.482 \\ 
 leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
@@
 expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
-leave-one-out\_interval\_score & 0.831 & 1.086 & 0.943 \\ 
+leave-one-out\_interval\_score & 0.833 & 1.083 & 0.933 \\ 
 leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
@@
 expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
-leave-one-out\_interval\_score & 1.038 & 1.284 & 1.099 \\ 
+leave-one-out\_interval\_score & 1.030 & 1.292 & 1.109 \\ 
 leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 

### 2023-10-02 macroPI/app.R
init shiny app to publish

@@ -1,0 +1,460 @@
+library(shiny)
+library(ggplot2)
+library(here)
+library(data.table)
+library(patchwork)
+library(MetBrewer)
+
+devtools::load_all()
+
+.d <- `[`
+
+# Define UI for app that draws a histogram ----
+ui <- fluidPage(
+
+  # App title ----
+  titlePanel("IMF Empirical Quantile Forecasts"),
+
+  # Sidebar layout with input and output definitions ----
+
+  fluidRow(
+    column(6,
+
+
+      # Input: Slider for the number of bins ----
+      radioButtons(inputId = "target",
+                   choices = setNames(c("ngdp_rpch", "pcpi_pch"),
+                                      c("GDP Growth", "Inflation")),
+                   selected = "pcpi_pch",
+                   label = "Forecast Target"),
+
+      radioButtons(inputId = "error_method",
+                   choices = c("directional", "absolute"),
+                   selected = "absolute",
+                   label = "Error Method"),
+
+      radioButtons(inputId = "method",
+                   label = "Estimation Method",
+                   choices = c("leave-one-out", "rolling window", "expanding window"),
+                   selected = "rolling window"),
+
+      numericInput(inputId = "window",
+                   label = "Window length (for rolling window)",
+                   value = 7,
+                   min = 4,
+                   max = 10),
+
+      numericInput(inputId = "target_year",
+                   label = "Target Year",
+                   value = 2000,
+                   min = 1990,
+                   max = 2009)
+    ),
+    column(6,
+
+      checkboxGroupInput("ci_lvls", label = "Prediction Intervals",
+                         choices = list("30%" = 0.3, "50%" = 0.5, "80%" = 0.8, "90%" = 0.9),
+                         selected = c(0.5,0.8)),
+
+      selectInput(inputId = "country",
+                  label = "Country to highlight",
+                  choices = c("Canada", "France", "Germany", "Italy",
+                              "Japan", "United Kingdom", "United States")),
+
+      radioButtons(inputId = "trueval",
+                   choices = c("0.5", "1", "1.5", "2"),
+                   selected = "1",
+                   label = "True Value release"),
+
+      radioButtons(inputId = "zoomin",
+                   label = "Zoom in?",
+                   choices = c("TRUE", "FALSE"),
+                   selected = "TRUE"),
+
+
[…]

### 2023-10-17 manuscript/manuscript.Rmd
move more functions to designated plot file

@@
 
-ovr_assessment_plot <- function(wis_scoredat, cvg_scoredat, point_scores, crps_scores, trgt){
+ovr_assessment_plot <- function(wis_scoredat, cvg_scoredat, point_scores, crps_scores, trgt, window_method){
 
   cvgscores <- cvg_scoredat |>
-    .d(method == "rolling window") |>
+    .d(method == window_method) |>
     .d(target == trgt) |>
     .d(, target := NULL) |>
-    .d(, method := NULL) #|>
+    .d(, method := NULL)
 
   decomp_data <- wis_scoredat |>
-    .d(method == "rolling window") |>
-    .d(target == trgt) |>
-    .d(, target := NULL) |>
-    .d(, method := NULL) #|>
+    .d(method == window_method) |>
+    .d(, method := NULL)
+
+  xmax <- max(decomp_data |> copy() |> .d(target == trgt) |> .d(, .(interval_score))) + 0.01
 
@@
   crps_scores_rw <- crps_scores |>
-    .d(method == "rolling window") |>
+    .d(method == window_method) |>
     .d(target == trgt) |>
@@
 
-  xmax <- max(decomp_data$interval_score)
-
-  decomp_data <- decomp_data |>
-    data.table::melt(id.vars = c("source", "error_method", "horizon"),
-                     value.name = "score",
-                     variable.name = "type") |>
-    .d(type != "interval_score") # filter out total score, only interested in decomposition
-
-  #check arguments of function!
-  wis_plot <- function(decompdat, error_m, maxval){
-
-    if(error_m == "directional"){
-      plot_name <- "WIS - Directional Errors"
-    } else {
-      plot_name <- "WIS - Absolute Errors"
-    }
-
-    plt <- ggplot(decomp_data |> .d(error_method == error_m),
-                          aes(x = source, 
-                              fill = source,
-                              y = score,
-                              alpha = type)) +
-      geom_bar(position="stack", stat="identity") +
-      facet_wrap(~ horizon,
-                 labeller = as_labeller(plot_horizon_label_short(4)),
-                 nrow = 1) +
-      #geom_hline(yintercept = 1) +
-      scale_alpha_discrete(range = c(0.35,1),
-                           labels = c("Overprediction",
-                                      "Underprediction",
-                                      "Dispersion"),
-                           name = "Components of the WIS") +
-      scale_x_discrete(name = "",
-                       breaks = c("IMF", "bvar", "bvar_qu", "ar"),
-                       labels = c("IMF", "BVAR", "BVAR_QU", "AR")) +
-      scale_y_continuous(name = "WIS", limits = c(0, maxval)) +
-      scale_fill_met_d("Hokusai1") +
-      #scale_fill_brewer(palette = "Set2", 
-      #                  name = "Model Type")+
-      xlab("") +
-      #labs(fill = "Model Type") +
-      theme_uqimf() %+replace%
-      theme(axis.text.x = element_text(size = 8, angle = 90, hjust = .5, vjust = .5, face = "plain"),
-            strip.text = element_text(size = 8)) +
-      ggtitle(plot_name) +
-      theme(#legend.title=element_blank(),
-            legend.position = "none")
-
-    return(plt)
-
-  }
-
-  horizon_path_plot <- function(score_data,
-                                score_rule,
-                                ylab = score_rule, 
-                                facet = NULL,
-                                title = NULL){
-
-    path_plot <- ggplot(score_data, 
-           aes(x = horizon,
-               y = get(score_rule), 
-               color = source)) +
-
-      scale_color_met_d("Hokusai1", breaks = c("IMF", "bvar", "ar", "bvar_qu"),
-                       labels = c("IMF", "BVAR", "AR", "BVAR_QU")) +
-
-      #scale_color_brewer(palette = "Set2") +
-      geom_line() +
-      geom_point() +
-      ylab(ylab) +
-      xlab("Forecast Horizon") +
-      guides(fill = "none", colour = "none") +
-      theme_uqimf() %+replace%
-      theme(legend.title=element_blank(),
-            legend.position = "none") +
-      ggtitle(title)
-
-    if(!is.null(facet)){
-
-      path_plot <- path_plot +
-      facet_wrap(~ get(facet),
-                 scales = "free") 
-    }
-
-    return(path_plot)
-
-  }
-
-  dir_wis_plot <- wis_plot(decomp_data, "directional", xmax)
-  abs_wis_plot <- wis_plot(decomp_data, "absolute", xmax)
+  dir_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "directional"), trgt, xmax = xmax, plot_name = "WIS - Directional Errors")
+  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt, xmax = xmax, plot_name = "WIS - Absolute Errors")
 
@@
 
-  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - Rolling Window") +
+  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = paste0("CRPS - ", window_method)) +
     scale_y_continuous(limits = c(0.07,1.05))
@@
 
-ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "pcpi_pch")
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, trgt = "pcpi_pch", window_method = "rolling window")
 
@@
 \begin{itemize}
-\item difference small for IMF method, absolute slighly better, likely due to longer central intervals
+\item difference small for IMF method, absolute slightly better, likely due to longer central intervals
 \item AR and BVAR profit more from directional correction (upward bias)
@@
 
-```{r gdpovr_ew, echo = FALSE, warning = TRUE, fig.dim=c(12,12)}
+```{r gdpovr_rw, echo = FALSE, warning = TRUE, fig.dim=c(12,12), warning = FALSE}
 
-ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch")
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch", window_method = "rolling window")
 ```
@@
 ## Inflation
+```{r infklovr_ew, echo = FALSE, warning = TRUE, fig.dim=c(12,12), warning = FALSE}
 
-```{r overall_assessment, fig.dim=c(12,12), echo = FALSE, warning = FALSE}
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch", window_method = "expanding window")
+```
 
-scores_cvgshort <- fread(here("scores", "ci_scores_avgcnt.csv")) |>
-  setnames("model", "source", skip_absent = TRUE)
-
-bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
-  setnames("model", "source", skip_absent = TRUE) |>
-  .d(, source := "bvar_qu") |>
-  .d(, method := "expanding window") |>
-  .d(, error_method := "absolute")
-
-bvar_scores_cvgshort <- rbind(bvar_scores_cvgshort, bvar_scores_cvgshort |> copy() |> .d(, error_method := "directional"))
-
-point_scores <- data.table::fread(here("scores", "pointfc_scores.csv"))
-
-wis_scores <- rbind(wis_scores, bvar_wis_scores)
-scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
-
-ovr_assessment_plot <- function(wis_scoredat, cvg_scoredat, point_scores, crps_scores, trgt){
-
-  cvgscores <- cvg_scoredat |>
-    .d(method == "expanding window") |>
-    .d(target == trgt) |>
-    .d(, target := NULL) |>
-    .d(, method := NULL) #|>
-
-  decomp_data <- wis_scoredat |>
-    .d(method == "expanding window") |>
-    .d(target == trgt) |>
-    .d(, target := NULL) |>
-    .d(, method := NULL) #|>
-
-  point_scores <- point_scores |>
-    .d(target == trgt) |>
-    .d(, target := NULL) |>
-    .d(, meanae := mean(ae), by = c("source", "horizon")) |>
-    .d(, meansque := mean(sque), by = c("source", "horizon")) |>
-    .d(, .(source, country, horizon, meanae, meansque)) |>
-    unique()
-
-  crps_scores_rw <- crps_scores |>
-    .d(method == "expanding window") |>
-    .d(target == trgt) |>
-    .d(, target := NULL)
-
-  crps_scores_loo <- crps_scores |>
-    .d(method == "leave-one-out") |>
-    .d(target == trgt) |>
-    .d(, target := NULL)
-
-  xmax <- max(decomp_data$interval_score)
-
-  decomp_data <- decomp_data |>
-    data.table::melt(id.vars = c("source", "error_method", "horizon"),
-                     value.name = "score",
-                     variable.name = "type") |>
-    .d(type != "interval_score") # filter out total score, only interested in decomposition
-
-  #check arguments of function!
-  wis_plot <- function(decompdat, error_m, maxval){
-
-    if(error_m == "directional"){
-      plot_name <- "WIS - Directional Errors"
-    } else {
-      plot_name <- "WIS - Absolute Errors"
-    }
-
-    plt <- ggplot(decomp_data |> .d(error_method == error_m),
-                          aes(x = source, 
-                              fill = source,
-                              y = score,
-                              alpha = type)) +
-      geom_bar(position="stack", stat="identity") +
-      facet_wrap(~ horizon,
-                 labeller = as_labeller(plot_horizon_label_short(4)),
-                 nrow = 1) +
-      #geom_hline(yintercept = 1) +
-      scale_alpha_discrete(range = c(0.35,1),
-                           labels = c("Overprediction",
-                                      "Underprediction",
-                                      "Dispersion"),
-                           name = "Components of the WIS") +
-      scale_x_discrete(name = "",
-                       breaks = c("IMF", "bvar", "bvar_qu", "ar"),
-                       labels = c("IMF", "BVAR", "BVAR_QU", "AR")) +
-      scale_y_continuous(name = "WIS", limits = c(0, maxval)) +
-      scale_fill_met_d("Hokusai1") +
-      #scale_fill_brewer(palette = "Set2", 
-      #                  name = "Model Type")+
-      xlab("") +
-      #labs(fill = "Model Type") +
-      theme_uqimf() %+replace%
-      theme(axis.text.x = element_text(size = 8, angle = 90, hjust = .5, vjust = .5, face = "plain"),
-            strip.text = element_text(size = 8)) +
-      ggtitle(plot_name) +
-      theme(#legend.title=element_blank(),
-            legend.position = "none")
-
-    return(plt)
-
-  }
-
-  horizon_path_plot <- function(score_data,
-                                score_rule,
-                                ylab = score_rule, 
-                                facet = NULL,
-                                title = NULL){
-
-    path_plot <- ggplot(score_data, 
-           aes(x = horizon,
-               y = get(score_rule), 
-               color = source)) +
-
-      scale_color_met_d("Hokusai1", breaks = c("IMF", "bvar", "ar", "bvar_qu"),
-                       labels = c("IMF", "BVAR", "AR", "BVAR_QU")) +
-
-      #scale_color_brewer(palette = "Set2") +
-      geom_line() +
-      geom_point() +
-      ylab(ylab) +
-      xlab("Forecast Horizon") +
-      guides(fill = "none", colour = "none") +
-      theme_uqimf() %+replace%
-      theme(legend.title=element_blank(),
-            legend.position = "none") +
-      ggtitle(title)
-
-    if(!is.null(facet)){
-
-      path_plot <- path_plot +
-      facet_wrap(~ get(facet),
-                 scales = "free") 
-    }
-
-    return(path_plot)
-
-  }
-
-  dir_wis_plot <- wis_plot(decomp_data, "directional", xmax)
-  abs_wis_plot <- wis_plot(decomp_data, "absolute", xmax)
-
-  c50plot <- horizon_path_plot(cvgscores, "coverage_50", "CI Coverage - 50", facet = "error_method", title = "Central Interval Coverage - alpha = 50") +
-    geom_hline(aes(yintercept = 0.5)) +
-    scale_y_continuous(labels = paste0(seq(0, 100, by = 25), "%"),
-                       breaks = seq(0,1, by = 0.25),
-                       limits = c(0,1))
-
-  c80plot <- horizon_path_plot(cvgscores, "coverage_80", "CI Coverage - 80", facet = "error_method", title = "Central Interval Coverage - alpha = 80") +
-    geom_hline(aes(yintercept = 0.8)) +
-    scale_y_continuous(labels = paste0(seq(0, 100, by = 25), "%"),
-                       breaks = seq(0,1, by = 0.25),
-                       limits = c(0,1))
-
-  erow <-  ggplot() + theme_void()
-
-  aeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meanae", "Absolute Error", title = "Point Forecast - Abs. Error")
-
-  squeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meansque", "Squared Error", title = "Point Forecast - Squ. Error")
-
-  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - expanding window") +
-    scale_y_continuous(limits = c(0.07,1.05))
-
-  crpsplot_loo <- horizon_path_plot(crps_scores_loo |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - LOO") +
-    scale_y_continuous(limits = c(0.07,1.05))
-
-  ovr_plot <- 
-    (dir_wis_plot | abs_wis_plot) /
-    (plot_spacer()) /
-    (c50plot | c80plot) /
-    (plot_spacer()) /
-    (squeplot | aeplot | crpsplot_rw | crpsplot_loo) +
-    plot_layout(guides = "collect", 
-                heights = c(0.2, 0.05, 0.2, 0.05, 0.2)) &
-      plot_annotation(tag_levels = 'I')  &
-      theme(legend.position = 'bottom', 
-            legend.box="vertical", legend.margin=margin())
-
-  return(ovr_plot)
-}
-
-ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "pcpi_pch")
-
-```
 \newpage
@@
 
-```{r gdpovr, echo = FALSE, warning = TRUE, fig.dim=c(12,12)}
+```{r gdpovr, echo = FALSE, warning = TRUE, fig.dim=c(12,12), warning = FALSE}
 
-ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch")
+ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch", window_method = "expanding window")
 ```

### 2023-10-17 R/plot.R

@@ -1,82 +1,62 @@
-
-ovr_assessment_plot <- function(wis_scoredat, trgt){
-
-
-  decomp_data <- wis_scoredat |>
-    #.d(method == "rolling window") |>
-    .d(target == trgt) |>
-    .d(, target := NULL) |>
-    .d(, method := NULL) #|>
-
-
-  xmax <- max(decomp_data$interval_score) + 0.05
-
-  decomp_data <- decomp_data |>
-    data.table::melt(id.vars = c("source", "error_method", "horizon"),
-                     value.name = "score",
-                     variable.name = "type") |>
-    .d(type != "interval_score") # filter out total score, only interested in decomposition
-
-
-
-
-  #return(decomp_data)
-  dir_wis_plot <- wis_plot(decomp_data, "directional", xmax)
-  abs_wis_plot <- wis_plot(decomp_data, "absolute", xmax)
-
-
-
-  #ovr_plot <-
-  #  (dir_wis_plot | abs_wis_plot) +
-  #  plot_layout(guides = "collect",
-  #              heights = c(0.2, 0.05, 0.2, 0.05, 0.2)) &
-  #  plot_annotation(tag_levels = 'I')  &
-  #  theme(legend.position = 'bottom',
-  #        legend.box="vertical", legend.margin=margin())
-
-
-
-  return(dir_wis_plot)
-}
-
-
-#check arguments of function!
-wis_plot <- function(wis_scoredat, trgt, error_m){
+#' Plot decomposition of WIS by horizon and forecast source
+#'
+#' @param score_data score data that includes WIS values, prefiltered! by desired
+#' error_method and method
+#' @param trgt target variable for which the plot should be produced
+#' @param tolerance deviation to be exceeded, to be considered violator
+#' @param exclude_h1.5 if TRUE, excludes the largest horizon to calculate violators
+#' @param fcsource forecast source for which to calculate violators
+#' @param upper_lim upper limit for plotting legend
+#' @return nothing, saves tidied data in directory
+#' @export
+#'
+wis_plot_new <- function(wis_scoredat,
+                                trgt = c("pcpi_pch", "ngdp_rpch"),
+                         xmax = NULL,
+                                plot_name = NULL){
 
   if(length(unique(wis_scoredat$error_method)) > 1){
-    stop("only one error method allowed")
+    stop("Only one error method allowed. Prefilter data")
   }
 
   if(length(unique(wis_scoredat$method)) > 1){
-    stop("only one method allowed")
[…]

### 2023-10-17 manuscript/manuscript.tex

@@
 
-\begin{verbatim}
-## Warning: Using alpha for a discrete variable is not advised.
-## Using alpha for a discrete variable is not advised.
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: Removed 1 rows containing missing values (`geom_bar()`).
-\end{verbatim}
-
-\includegraphics{manuscript_files/figure-latex/gdpovr_ew-1.pdf}
+\includegraphics{manuscript_files/figure-latex/gdpovr_rw-1.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/overall_assessment-1.pdf}
+\includegraphics{manuscript_files/figure-latex/infklovr_ew-1.pdf}
+
 \newpage
@@
 \subsection{GDP}\label{gdp-1}}
-
-\begin{verbatim}
-## Warning: Using alpha for a discrete variable is not advised.
-## Using alpha for a discrete variable is not advised.
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: Removed 1 rows containing missing values (`geom_bar()`).
-\end{verbatim}
 

### 2023-10-17 manuscript/sub_manuscripts/quantile_coverage.Rmd

---
title: "IMF and Benchmark Forecasts"
header-includes:
    - \usepackage{lineno}
    - \linenumbers
    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
    toc: false
linestretch: 2 
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"

---

```{r setup, include=FALSE}
library(data.table)
library(here)
library(ggplot2)
library(patchwork)
library(MetBrewer)
library(purrr)
library(lattice)
library(gt)
library(rlang)
library(tidyverse)
devtools::load_all()
knitr::opts_chunk$set(echo = TRUE)
.d <- `[`

source(here("specs", "specs.R"))
```

```{r, echo = FALSE}
bvarqufcs <- fread(here("benchmarks", "quantile_benchmarks_processed.csv"))|>
  setnames("tv_1", "true_value") |>
  .d(target_year <= specs$score_max_year) |>
  .d(, grouped := source) |>
  .d(, error_method := "absolute") |>
  .d(target_year >= 1999) |>
  .d(,.(country, target, horizon, target_year, true_value, prediction, quantile,  grouped, source, error_method))

qufcs <- fread(here("quantile_forecasts", "quantile_forecasts.csv")) |>
  .d(method == "expanding window") |>
  .d(, grouped := paste0(source, "_", error_method))  |>
  .d(,.(country, target, horizon, target_year, true_value, prediction, quantile, grouped, source, error_method)) |>
  .d(target_year <= specs$score_max_year) |>
  rbind(bvarqufcs) |>
  .d(quantile %in% specs$qu_levels)
```

```{r, echo = FALSE}
exceed <- qufcs |>
  .d(,below_ci := ifelse(true_value < prediction, 1, 0)) |>
  .d(, below_ci := ifelse(quantile %in% c(0.1, 0.25), below_ci, NA)) |>
  .d(,above_ci := ifelse(true_value > prediction, 1, 0)) |>
  .d(, above_ci := ifelse(quantile %in% c(0.75, 0.9), above_ci, NA)) |>
  .d(, meanexc_below := mean(below_ci), by = c("target", "horizon", "grouped", "quantile")) |>
  .d(, meanexc_above := mean(above_ci), by = c("target", "horizon", "grouped", "quantile") )  |>
  .d(, target := ifelse(target == "pcpi_pch", "Inflation", "GDP Growth"))

keep_exceed <- exceed |> copy()

below <- exceed |>
  copy() |>
  .d(quantile %in% c(0.1, 0.25)) |>
  .d(, .(target, horizon, grouped, source, error_method, quantile, meanexc_below)) |>
  unique()|>
  setnames("meanexc_below", "exc")

above <- exceed |>
  copy() |>
  .d(quantile %in% c(0.75, 0.9)) |>
  .d(, .(target, horizon, grouped, source, error_method, quantile, meanexc_above)) |>
  unique() |>
  setnames("meanexc_above", "exc")

exceed <- rbind(below, above)
```
# This document

Here we document the proportion of true values that "miss" the 50% and 80% central prediction intervals - that is, the proportions of observations that falls \textit{below} the 0.1-quantile and 0.25-quantile and the proportion that falls \textit{above} the 0.75-quantile and 0.9-quantile.

The respective proportions are calculated separately for each forecast source (IMF, ar, bvar, bvarqu\footnote{bvarqu denotes the quantile forecasts that are taken directly from the BVAR model, while bvar denotes the quantile forecasts that are drawn from past point forecast errors of the BVAR model (analagously to the IMF and ar forecasts)}, target (GDP Growth and Inflation) and horizon (0 - "Fall, same year" to 1.5 - "Spring, previous year"). We treat absolute error handling as the default, and show results for directional error handling in the same respective source's color, but in a lighter shade. This plot is shown on page 3, with desired nominal exceedance proportions shown as dashed lines.

On page 4, we also plot exceedance levels for the bvarqu model separately for two equally sized parts of the time period under study. Differences in coverage between the two time periods at the respective quantile levels seem non-substantial.

# GDP growth forecasts

Overall, the forecasts that stem (a) from the directional error methods for the ar and bvar forecasts and (b) the IMF forecasts in general tend to be better calibrated, especially at the lower quantile levels.

The bvarqu forecasts show relatively large\footnote{in relation to the respective desired nominal level} exceedance proportions at the lower quantile levels (q = 0.1, q = 0.25) and small exceedance proportions at the upper quantile levels, an indication of overprediction. The respective forecast intervals "cover too much ground" in the direction of positive deviations of the realized values from the point prediction, while simultaneously "covering too little" in the other direction. Similarly, this is also an issue for the absolute ar, bvar and (albeit to a slightly lesser extent) IMF forecasts.

Lastly, the bvarqu forecasts appear to be too narrow at the shortest horizon (0 - "Fall, same year") only, since they show relatively large exceedances at both the lower and the upper quantile levels.

# Inflation forecasts

For the inflation forecasts, the bvarqu model (along with absolute ar and bvar to a lesser extent) show small exceedance proportions at the upper quantiles, especially for the 0.9-quantile and larger horizons, indicating intervals that are too long in the region above the point forecast. This also explains the aggregate near-zero underprediction scores for these methods (see other pdf).

Interestingly, the directional methods show the opposite issue, in that they have a too large proportion of exceedances at the upper quantile levels.

At the lower quantile levels, all methods appear to be better calibrated.

# Overall

In summary, it appears that for GDP, the entire distributions seem to be biased (shifted) upwards for the bvarqu and absolute ar and bvar models. For inflation, it seems that they are just too long at the top, while being better calibrated at the bottom.

```{r, echo = FALSE}

qpathplot <- function(scoredat, quantl){

  if(quantl > 0.5){
    lineh <- 1-quantl
  } else {
    lineh <- quantl
  }

  pldat <- scoredat |>
    .d(quantile == quantl)

  qplot <- ggplot(pldat, 
           aes(x = horizon,
               y = exc,
               color = source,
               alpha = error_method)) +
    scale_alpha_manual(values = c("directional" = 0.4, "absolute" = 1)) +
      #scale_color_brewer(palette = "Set2") +
      geom_line(lwd = 1.2) +
      geom_point(size = 2)  +
    scale_color_met_d("Egypt") +
      xlab("Forecast Horizon") +
      theme_uqimf() +
    geom_hline(aes(yintercept = lineh), linetype = "dashed") +
  facet_wrap(~target )

  return(qplot)
}

myplot <- qpathplot(above, 0.75)
plotlist <- vector(mode = "list", 4)
qus <- c(0.1, 0.25, 0.75, 0.9)
textqus <- c("BELOW", "BELOW", "ABOVE", "ABOVE")

for(i in seq_along(qus)){

  plotlist[[i]] <- qpathplot(exceed, qus[i]) +
    ggtitle(paste0("Exceedance at Quantile Level q = ", qus[i], ". Proportion of observations that fell ", textqus[i], " the respective quantile"))
}

 ovr_plot <- 
    (plotlist[[1]]) /
    (plotlist[[2]]) /
    (plotlist[[3]]) /
    (plotlist[[4]]) +
    plot_layout(guides = "collect", 
                heights = c(0.2, 0.2, 0.2, 0.2)) &
      plot_annotation(tag_levels = 'I')  &
      theme(legend.position = 'bottom', 
            legend.box="vertical", legend.margin=margin())

```

```{r, fig.dim=c(12,17), echo = FALSE}
ovr_plot
```

# Exceedance for bvarqu, by time period

```{r, echo = FALSE, fig.dim=c(12,12)}
bvardat <- keep_exceed |> .d(source == "bvar_qu") |> 
  .d(, yrsec := ifelse(target_year %in% 1999:2005, "1999-2005", "")) |>
  .d(, yrsec2 := ifelse(target_year %in% 2006:2012, "2006-2012", "")) |>
  #.d(, yrsec3 := ifelse(target_year %in% 2009:2012, "2009-2012", "")) |>
  .d(, yrsec := paste0(yrsec, yrsec2)) |>
  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
  .d(, meanexc_below := mean(below_ci), by = c("target", "horizon", "grouped", "quantile", "yrsec")) |>  
  .d(, meanexc_above := mean(above_ci), by = c("target", "horizon", "grouped", "quantile", "yrsec")) |>  
  .d(, meanexc_below := ifelse(is.na(meanexc_below), meanexc_above, meanexc_below)) |>
  .d(, .(target, horizon, grouped, yrsec, quantile, meanexc_below)) |> 
  unique() |>
  setnames("meanexc_below", "exc")

qpathplot <- function(scoredat, quantl){

  if(quantl > 0.5){
    lineh <- 1-quantl
  } else {
    lineh <- quantl
  }

  pldat <- scoredat |>
    .d(quantile == quantl)

  qplot <- ggplot(pldat, 
           aes(x = horizon,
               y = exc,
               color = yrsec)) +
    scale_alpha_manual(values = c("directional" = 0.4, "absolute" = 1)) +
      #scale_color_brewer(palette = "Set2") +
      geom_line(lwd = 1.2) +
      geom_point(size = 2)  +
    scale_color_met_d("Egypt") +
      xlab("Forecast Horizon") +
      theme_uqimf() +
    geom_hline(aes(yintercept = lineh), linetype = "dashed") +
  facet_wrap(~target )

  return(qplot)
}

plotlist <- vector(mode = "list", 4)
qus <- c(0.1, 0.25, 0.75, 0.9)
textqus <- c("BELOW", "BELOW", "ABOVE", "ABOVE")

for(i in seq_along(qus)){

  plotlist[[i]] <- qpathplot(bvardat, qus[i]) +
    ggtitle(paste0("Exceedance at Quantile Level q = ", qus[i], ". Proportion of observations that fell ", textqus[i], " the respective predicted quantile values"))
}

 ovr_plot <- 
    (plotlist[[1]]) /
    (plotlist[[2]]) /
   (plotlist[[3]]) /
   (plotlist[[4]]) +
    plot_layout(guides = "collect", 
                heights = c(0.2, 0.2, 0.2, 0.2)) &
      plot_annotation(tag_levels = 'I')  &
      theme(legend.position = 'bottom', 
            legend.box="vertical", legend.margin=margin())

ovr_plot
```

### 2023-10-17 manuscript/sub_manuscripts/quantile_coverage.tex

--- 2023-10-17 manuscript/manuscript.tex
@@
 \usepackage{float}
-\usepackage{booktabs}
-\usepackage{caption}
-\usepackage{longtable}
 \ifLuaTeX
@@
 \setstretch{2}
-\hypertarget{extracting-error-quantiles}{%
-\section{Extracting error quantiles}\label{extracting-error-quantiles}}
+\hypertarget{this-document}{%
+\section{This document}\label{this-document}}
 
-Consider a forecast that stems from a source \(s\) for a specific target \(k\) in a country \(j\), for target year \(t\) and with forecast horizon \(h\):
-\[
-\hat{y}_{s,k,j,t,h}
-\]
-For example, this could be a forecast stemming from the International Monetary Fund World Economic Outlook (\(s = IMF\)) for real GDP growth (\(k = gdpg\)) in Canada (\(j = Canada\)) for the year \(2022\) (\(t=2022\)).
-\(h\) then indexes the forecast horizon, where we code:
-\[
-h = \left\{
-\begin{array}{ll} 
-      0, & \textrm{for forecasts made in October of the same year} \\
-      0.5, & \textrm{for forecasts made in April of the same year} \\
-      1, & \textrm{for forecasts made in October of the previous year} \\
-      1.5, & \textrm{for forecasts made in April of the previous year} \\
-\end{array}\right. 
-\]
-After the target year has completed, we obtain the realized value for the quantity of interest.
-For these, the WEO updates publishes biannual updates for two years, yielding \(4\) versions of the realized value.
-In accordance with previous literature (\textit{cite Timmermann 2008}), we use the version that is published in October of the following year and thereby don't index the true value by its publishing date (\textit{rephrase}).
-We thus write the true value as
-\[
-\hat{y}_{k,j,t}
-\]
-Given the forecast and the realized value for the quantity of interest, we can calculate the respective forecast error as
-\[
-e^{d}_{s,k,j,t,h} = y_{k,j,t} - \hat{y}_{s,k,j,t,h}
-\]
+Here we document the proportion of true values that ``miss'' the 50\% and 80\% central prediction intervals - that is, the proportions of observations that falls \textit{below} the 0.1-quantile and 0.25-quantile and the proportion that falls \textit{above} the 0.75-quantile and 0.9-quantile.
 
-for the ``directional'' error method and as
-\[
-e^{a}_{s,k,j,t,h} = \left|y_{k,j,t} - \hat{y}_{s,k,j,t,h}\right|
-\]
-for the ``absolute'' error method.
+The respective proportions are calculated separately for each forecast source (IMF, ar, bvar, bvarqu\footnote{bvarqu denotes the quantile forecasts that are taken directly from the BVAR model, while bvar denotes the quantile forecasts that are drawn from past point forecast errors of the BVAR model (analagously to the IMF and ar forecasts)}, target (GDP Growth and Inflation) and horizon (0 - ``Fall, same year'' to 1.5 - ``Spring, previous year'').
+We treat absolute error handling as the default, and show results for directional error handling in the same respective source's color, but in a lighter shade.
+This plot is shown on page 3, with desired nominal exceedance proportions shown as dashed lines.
 
-The objective is to extract quantiles from sets of errors \(\mathcal{E}_{s,k,j,t,h}\) constructed of certain years, depending on the estimation method \(m\), to be able to quantify the uncertainty inherent in the forecasts via central prediction intervals of level \(\alpha = \{0.5, 0.8\}\).
-For the estimation method, we consider a ``rolling window'' method, an ``expanding window'' method, and a ``leave-one-out'' method.
-For the rolling window method (\(m = rw\)), the errors of the last nine years enter into the estimation.
-For the expanding window method (\(m = ew\)), all previous years are considered, leaving a nine year window up front for the first estimation.
-For the leave-one-out method, all years except the current target year enter the estimation set.
-The latter is of course equivalent to the expanding window method in a real time setting and is considered in the scope of this analysis as a mere check \textit{rephrase}.
-As an example, the error set for the ``directional'' error method and the rolling window approach is
-\[
-\mathcal{E}^{d,rw}_{s,k,j,t,h} =  \left\{  e^{d}_{s,k,j,t^*,h} | t-9\leq t^* < t \right\}
-\]
-Insert reasoning to use the past \(9\) errors.
+On page 4, we also plot exceedance levels for the bvarqu model separately for two equally sized parts of the time period under study.
+Differences in coverage between the two time periods at the respective quantile levels seem non-substantial.
 
-To now obtain the lower \(l\) and upper \(u\) values for a central prediction interval of level \(\alpha\), we take quantiles of these sets and add them to the current prediction:
+\hypertarget{gdp-growth-forecasts}{%
+\section{GDP growth forecasts}\label{gdp-growth-forecasts}}
 
-For the directional method:
-\[
-l^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 - \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
-\]
-\[
-u^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 + \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
-\]
+Overall, the forecasts that stem (a) from the directional error methods for the ar and bvar forecasts and (b) the IMF forecasts in general tend to be better calibrated, especially at the lower quantile levels.
 
-And for the absolute method:
+The bvarqu forecasts show relatively large\footnote{in relation to the respective desired nominal level} exceedance proportions at the lower quantile levels (q = 0.1, q = 0.25) and small exceedance proportions at the upper quantile levels, an indication of overprediction.
+The respective forecast intervals ``cover too much ground'' in the direction of positive deviations of the realized values from the point prediction, while simultaneously ``covering too little'' in the other direction.
+Similarly, this is also an issue for the absolute ar, bvar and (albeit to a slightly lesser extent) IMF forecasts.
 
-\[
- l^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} -  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
-\]
-\[
-u^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} +  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
-\]
+Lastly, the bvarqu forecasts appear to be too narrow at the shortest horizon (0 - ``Fall, same year'') only, since they show relatively large exceedances at both the lower and the upper quantile levels.
 
-Two different philosophies.
+\hypertarget{inflation-forecasts}{%
+\section{Inflation forecasts}\label{inflation-forecasts}}
 
-The absolute method will always yield symmetric central prediction intervals around the forecast value, while the directional method will in general yield asymmetric intervals.
-They thus result in different central intervals, unless the errors in \(\mathcal{E}\) are perfectly symmetric around zero\footnote{Not totally correct, actually.
-For this to hold exactly, the error set would need to be augmented with one zero value.}.
-In fact, the directional method can yield central prediction intervals that do not even contain the forecast value, in cases where the \((0.5 - \alpha/2)\)-quantile is positive or the \((0.5 + \alpha/2)\)-quantile is negative.
+For the inflation forecasts, the bvarqu model (along with absolute ar and bvar to a lesser extent) show small exceedance proportions at the upper quantiles, especially for the 0.9-quantile and larger horizons, indicating intervals that are too long in the region above the point forecast.
+This also explains the aggregate near-zero underprediction scores for these methods (see other pdf).
 
-\hypertarget{scores-by-error-method-horizon-and-forecast-source}{%
-\section{Scores, by error method, Horizon and forecast source}\label{scores-by-error-method-horizon-and-forecast-source}}
+Interestingly, the directional methods show the opposite issue, in that they have a too large proportion of exceedances at the upper quantile levels.
 
-\hypertarget{inflation}{%
-\subsection{Inflation}\label{inflation}}
+At the lower quantile levels, all methods appear to be better calibrated.
 
-\includegraphics{manuscript_files/figure-latex/overall_assessment_ew-1.pdf}
-\newpage
-Some notes:
+\hypertarget{overall}{%
+\section{Overall}\label{overall}}
 
-\begin{itemize}
-\item Inflation: directional vs. absolute errors:
-\begin{itemize}
-\item difference small for IMF method, absolute slightly better, likely due to longer central intervals
-\item AR and BVAR profit more from directional correction (upward bias)
-\item for expanding window method, difference in coverage is smaller (-> structural breaks)
+In summary, it appears that for GDP, the entire distributions seem to be biased (shifted) upwards for the bvarqu and absolute ar and bvar models.
+For inflation, it seems that they are just too long at the top, while being better calibrated at the bottom.
 
-\end{itemize}
-\item Inflation overall scores: IMF forecasts outperform others
-\begin{itemize}
-\item lower scores for point forecasts
-\item lower WIS 
-\item lower bias (compute directly?)
-\end{itemize}
+\includegraphics{quantile_coverage_files/figure-latex/unnamed-chunk-4-1.pdf}
 
-\item GDP Growth: more similar results for different sources
-\begin{itemize}
-\item lower scores at shorter horizons, more similar at larger horizons
-\item IMF forecasts better only for absolute error method
-\end{itemize}
-\end{itemize}
+\hypertarget{exceedance-for-bvarqu-by-time-period}{%
+\section{Exceedance for bvarqu, by time period}\label{exceedance-for-bvarqu-by-time-period}}
 
-\newpage
-
-\hypertarget{gdp}{%
-\subsection{GDP}\label{gdp}}
-
-\includegraphics{manuscript_files/figure-latex/gdpovr_rw-1.pdf}
-
-\hypertarget{expanding-window---scores-by-error-method-horizon-and-forecast-source}{%
-\section{Expanding Window - Scores, by error method, Horizon and forecast source}\label{expanding-window---scores-by-error-method-horizon-and-forecast-source}}
-
-\hypertarget{inflation-1}{%
-\subsection{Inflation}\label{inflation-1}}
-
-\includegraphics{manuscript_files/figure-latex/infklovr_ew-1.pdf}
-
-\newpage
-
-\hypertarget{gdp-1}{%
-\subsection{GDP}\label{gdp-1}}
-
-\includegraphics{manuscript_files/figure-latex/gdpovr-1.pdf}
-
-\hypertarget{coverage-by-target-methods-and-source}{%
-\section{Coverage, by target, methods and source}\label{coverage-by-target-methods-and-source}}
-
-\includegraphics{manuscript_files/figure-latex/cvgplot-1.pdf}
-
-\newpage
-\begin{longtable}{l|rrr}
-\toprule
-\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 0} \\ 
-\midrule
-expanding window\_interval\_score & 0.115 & 0.123 & 0.122 \\ 
-expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
-leave-one-out\_interval\_score & 0.112 & 0.123 & 0.123 \\ 
-leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
-rolling window\_interval\_score & 0.119 & 0.128 & 0.126 \\ 
-rolling window\_sample\_crps & 0.094 & 0.097 & 0.098 \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 0.5} \\ 
-\midrule
-expanding window\_interval\_score & 0.258 & 0.272 & 0.296 \\ 
-expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
-leave-one-out\_interval\_score & 0.257 & 0.257 & 0.276 \\ 
-leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
-rolling window\_interval\_score & 0.261 & 0.266 & 0.288 \\ 
-rolling window\_sample\_crps & 0.191 & 0.201 & 0.235 \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 1} \\ 
-\midrule
-expanding window\_interval\_score & 0.448 & 0.737 & 0.590 \\ 
-expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
-leave-one-out\_interval\_score & 0.443 & 0.746 & 0.587 \\ 
-leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
-rolling window\_interval\_score & 0.451 & 0.739 & 0.591 \\ 
-rolling window\_sample\_crps & 0.333 & 0.514 & 0.434 \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 1.5} \\ 
-\midrule
-expanding window\_interval\_score & 0.495 & 1.044 & 0.800 \\ 
-expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
-leave-one-out\_interval\_score & 0.488 & 1.021 & 0.756 \\ 
-leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
-rolling window\_interval\_score & 0.494 & 1.041 & 0.779 \\ 
-rolling window\_sample\_crps & 0.347 & 0.632 & 0.570 \\ 
-\bottomrule
-\end{longtable}
-
-\hypertarget{inflation-2}{%
-\subsection{Inflation}\label{inflation-2}}
-
-\includegraphics{manuscript_files/figure-latex/cpitileplot-1.pdf}
-
-\hypertarget{gdp-2}{%
-\subsection{GDP}\label{gdp-2}}
-
-\begin{longtable}{l|rrr}
-\toprule
-\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 0} \\ 
-\midrule
-expanding window\_interval\_score & 0.241 & 0.301 & 0.298 \\ 
-expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
-leave-one-out\_interval\_score & 0.235 & 0.297 & 0.295 \\ 
-leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
-rolling window\_interval\_score & 0.240 & 0.302 & 0.297 \\ 
-rolling window\_sample\_crps & 0.178 & 0.211 & 0.204 \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 0.5} \\ 
-\midrule
-expanding window\_interval\_score & 0.416 & 0.540 & 0.493 \\ 
-expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
-leave-one-out\_interval\_score & 0.406 & 0.532 & 0.482 \\ 
-leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
-rolling window\_interval\_score & 0.416 & 0.554 & 0.504 \\ 
-rolling window\_sample\_crps & 0.297 & 0.405 & 0.373 \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 1} \\ 
-\midrule
-expanding window\_interval\_score & 0.837 & 1.090 & 0.942 \\ 
-expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
-leave-one-out\_interval\_score & 0.833 & 1.083 & 0.933 \\ 
-leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
-rolling window\_interval\_score & 0.851 & 1.122 & 0.970 \\ 
-rolling window\_sample\_crps & 0.663 & 0.875 & 0.815 \\ 
-\midrule
-\multicolumn{4}{l}{horizon = 1.5} \\ 
-\midrule
-expanding window\_interval\_score & 1.045 & 1.288 & 1.102 \\ 
-expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
-leave-one-out\_interval\_score & 1.030 & 1.292 & 1.109 \\ 
-leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
-rolling window\_interval\_score & 1.056 & 1.312 & 1.143 \\ 
-rolling window\_sample\_crps & 0.831 & 0.985 & 0.949 \\ 
-\bottomrule
-\end{longtable}
-
-\includegraphics{manuscript_files/figure-latex/gdptileplot-1.pdf}
+\includegraphics{quantile_coverage_files/figure-latex/unnamed-chunk-5-1.pdf}
 

### 2023-10-17 README.Rmd
test update Readme

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# uqimf

<!-- badges: start -->
<!-- badges: end -->

The goal of uqimf is to ...

## Contents of the repository
The folders of this repository contain the following:
* `R`: all functions and that the analysis is based on
  - `plot.R`: plotting files 
  - `score.R`: functions to score quantile forecasts (coverage, interval_score, crps by sample)
  - `uqfc.R`: functions to generate quantile forecasts from past errors
  - `uqimf-package.R` some stuff, as this is technically an R package
  - `utils.R` miscellaneous small functions
  - `utils-manuscript.R` miscellaneous small functions for manuscript

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

### 2023-10-17 README.Rmd
fix itemization

@@
 ## Contents of the repository
+
 The folders of this repository contain the following:
-* `R`: all functions and that the analysis is based on
+
+- `R`: all functions and that the analysis is based on
+
   - `plot.R`: plotting files
+
   - `score.R`: functions to score quantile forecasts (coverage, interval_score, crps by sample)
+
   - `uqfc.R`: functions to generate quantile forecasts from past errors
+
   - `uqimf-package.R` some stuff, as this is technically an R package
+
   - `utils.R` miscellaneous small functions
+
   - `utils-manuscript.R` miscellaneous small functions for manuscript

### 2023-10-17 README.Rmd
update Readme

@@
 
-The goal of uqimf is to ...
+This repo contains code to generate simple and transparent prediction intervals for the IMF World Economic Outlook forecasts [1].
+Central prediction intervals are generated at the 50% and 80% levels for CPI inflation and real GDP growth, based on past forecast errors.
+See below for documentation on which files the respective folders contain.
+
+[1]: International Monetary Fund. 2023. \textit{World Economic Outlook: A Rocky Recovery.} Washington, DC. April.
 
@@
 
-- `R`: all functions and that the analysis is based on
+- `R`: All functions that the analysis is based on. Scripts that process data based on these functions are in `scripts`
 
@@
 
-  - `uqimf-package.R` some stuff, as this is technically an R package
+  - `uqimf-package.R`: some stuff, as this is technically an R package
 
-  - `utils.R` miscellaneous small functions
+  - `utils.R`: miscellaneous small functions
 
-  - `utils-manuscript.R` miscellaneous small functions for manuscript
+  - `utils-manuscript.R`: miscellaneous small functions for manuscript
 
-```{r cars}
-summary(cars)
-```
+- `benchmarks`: benchmark forecasts and the scripts that generate them.
 
-You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.
+  - `point_benchmarks_processed.csv`: point benchmark forecasts (AR and BVAR model) as generated by `scripts/process-benchmarks`, see below
 
-You can also embed plots, for example:
+  - `quantile_benchmarks_processed.csv`: quantile benchmark forecasts (BVAR model) as generated by `scripts/process-benchmarks`, see below
 
-```{r pressure, echo = FALSE}
-plot(pressure)
-```
+- `data`: WEO and merged data
 
-In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
+  - `weodat.csv`: tidy IMF WEO data, for G7 countries only
+  - `point_forecasts.csv`: all point forecasts (weo and benchmarks), generated by `scripts/process-benchmarks`, see below
+
+- `manuscript`: files to write manuscript. Abandoned now, in favor of `uqimf-manuscript` repository
+
+- `oecd_data`: contains annual and quarterly truth data for inflation and GDP growth, as published by the OECD.
+Also contains R markdown scripts that check (and verify) compatibility of annual OECD truth values with annual IMF truth values
+
+- `plots`: you get what you bargain for
+
+- `presentation`: some files for the presentation of the project at the MathSEE Symposium
+
+- `quantile-forecasts`: contains quantile forecasts as produced by `scripts/make-forecasts`, see below
+
+- `scores`: Contains scores of forecasts in `quantile-forecasts` and BVAR benchmarks, at various levels of resolutions. Contains its own Readme file to explain what scores the different files contain.
+
+- `scripts`: Contains scripts that process data based on the function in `R`
+
+  - `toy-scripts`: small scripts to explore data
+
+  - `plot-scripts`: scripts to generate plots
+
+  - `download_data.R`: download IMF data
+
+  - `make-forecasts.R`: generate quantile forecasts based (`data/point-forecasts.csv` to `quantile_forecasts/quantile_forecasts.csv`)
+
+  - `process-benchmarks.R` process benchmarks to bring into compatible format with `weodat.csv`.
+Generates file that contains point forecasts from all sources in long format (`data/point_forecasts.csv`)
+
+  - `process-weo.R`: short script to filter and process WEO data
+
+  - `score-forecasts.R`: score quantile forecasts, those generated here and the benchmark BVAR quantile forecasts.
+
+- `specs`: contains file to specify global settings (window length, etc.)

### 2023-10-17 README.Rmd
formatting

@@
 
-This repo contains code to generate simple and transparent prediction intervals for the IMF World Economic Outlook forecasts [1].
+This repo contains code to generate simple and transparent prediction intervals for the IMF World Economic Outlook forecasts (see references).
 Central prediction intervals are generated at the 50% and 80% levels for CPI inflation and real GDP growth, based on past forecast errors.
 See below for documentation on which files the respective folders contain.
-
-[1]: International Monetary Fund. 2023. \textit{World Economic Outlook: A Rocky Recovery.} Washington, DC. April.
 
@@
 - `specs`: contains file to specify global settings (window length, etc.)
+
+## References
+
+International Monetary Fund. 2023. *World Economic Outlook: A Rocky Recovery.* Washington, DC. April.

### 2023-10-24 R/plot.R
shiny visualisation plot output

@@ -238,17 +238,23 @@ horizon_path_plot <- function(score_data,
 #'
 shinyplot <- function(realized_series,
                       linerange_data,
+                      point_forecasts,
+                      future_realized,
                       labels_currentyear,
                       labels_nextyear,
                       plot_country,
                       colorscale,
-                      cis){
+                      cis,
+                      ylimmax = 9.5){
 
+  .d <- `[`
+
+  trgt <- unique(realized_series$target)
   qus_list <- qu_lvls(cis) |>
     lapply(as.list)
 
-  qus_list[[1]][[4]] <- "50% Interval"
-  qus_list[[2]][[4]] <- "80% Interval"
+  qus_list[[1]][[4]] <- "80% Interval"
+  qus_list[[2]][[4]] <- "50% Interval"
 
   minval <- min(realized_series$true_value) - 0.5
 
@@ -256,16 +262,16 @@ shinyplot <- function(realized_series,
     geom_line(
       aes(x = target_year, y = true_value),
       color = colorscale[plot_country],
-      data = realized_vals |> .d(country == plot_country),
+      data = realized_series |> .d(country == plot_country),
       lwd = 0.75) +
     geom_point(
       aes(x = target_year, y = true_value),
       color = colorscale[plot_country],
-      data = realized_vals |> .d(country == plot_country),
+      data = realized_series |> .d(country == plot_country),
       size = 0.95) +
     ggtitle(paste0("Actual Series, with forecast for year ", 2023)) +
     ylab(plot_target_label()[trgt]) +
-    ylim(minval, 9.5) +
+    ylim(minval, ylimmax) +
     xlab("Target Year") +
     ggtitle(plot_country_label()[plot_country]) +
     scale_color_met_d("Hokusai1") +
@@ -276,8 +282,9 @@ shinyplot <- function(realized_series,
             ymax = get(paste0("quantile", qupr[[2]])),
             alpha = qupr[[4]]),
         color = colorscale[plot_country],
-        data = linerange_dat |> .d(country == plot_country),
+        data = linerange_data |> .d(country == plot_country),
         lwd = 2.15)
+
     }) +
 
     geom_point(
@@ -290,7 +297,7 @@ shinyplot <- function(realized_series,
     geom_line(
       aes(x = target_year, y = prediction),
       color = colorscale[plot_country],
-      data = dashed_line |> .d(country == plot_country),
+      data = future_realized |> .d(country == plot_country),
[…]

### 2023-10-24 scripts/plot-scripts/plot_shiny-vis.R

@@ -26,7 +26,7 @@ linerange_dat <- qufcs |>
   dcast(country + target + target_year + horizon ~ quantile, value.var = "prediction")
 
 
-point_forecasts <- fread(here("data", "point_forecasts.csv")) |>
+point_fcs <- fread(here("data", "point_forecasts.csv")) |>
   .d(source == "IMF") |>
   .d(target == trgt) |>
   .d(,fltr := target_year - horizon) |>
@@ -42,7 +42,7 @@ realized_vals <- qufcs |>
   unique()
 
 
-dashed_line <- rbind(point_forecasts, realized_vals |> copy() |> setnames("true_value", "prediction") |> .d(target_year > 2020))
+dashed_line <- rbind(point_fcs, realized_vals |> copy() |> setnames("true_value", "prediction") |> .d(target_year > 2020))
 
 
 ###########################################################################
@@ -72,7 +72,7 @@ names(colors) <- unique(qufcs$country)
 
 
 plotlist <- lapply(as.list(unique(qufcs$country)),
-                   function(pltc) shinyplot(realized_vals, linerange_dat, labeldat_2022, labeldat_2023, pltc, colors, cis))
+                   function(pltc) shinyplot(realized_vals, linerange_dat, point_fcs, labeldat_2022, labeldat_2023, pltc, colors, cis))
 
 
 spacer <- 150

### 2023-10-24 test-macropi/app.R
test-macropi app (deployed)

@@ -1,0 +1,357 @@
+library(data.table)
+library(ggplot2)
+library(MetBrewer)
+library(patchwork)
+
+#source(here("test-macropi", "shiny-plot-deploy-function.R"))
+
+.d <- `[`
+
+
+
+# Define UI for app that draws a histogram ----
+ui <- fluidPage(
+
+  # App title ----
+  titlePanel("IMF Empirical Quantile Forecasts"),
+
+  # Sidebar layout with input and output definitions ----
+
+  fluidRow(
+    column(12,
+
+           h2("Visualisation of quantile forecasts"),
+
+           # Output: Tabset w/ plot, summary, and table ----
+           tabsetPanel(type = "tabs",
+                       tabPanel("Inflation", plotOutput(outputId = "allcplot_inflation",
+                                                   height = 800, width = 800)),
+                       tabPanel("GDP Growth", plotOutput(outputId = "allcplot_gdp",
+                                                      height = 800, width = 800))
+           )
+    )
+  )
+)
+
+
+server <- function(input, output) {
+  .d <- `[`
+
+
+  #######################################FUNS#####################################
+  qu_lvls <- function(cis){
+
+    qus <- ci_to_quantiles(cis, "directional") #always directional
+
+    n_qus <- length(qus)
+
+    no_pairs <- floor(n_qus/2)
+
+
+    alpha_vals <- seq(0.5, 0.75, length.out = no_pairs)
+
+    #inner and outer quantile levels
+    lapply(seq_along(1:no_pairs),
+           function(ind) c(qus[ind], qus[(n_qus)-(ind-1)], alpha_vals[ind]))
+
+
+  }
+
+  ci_to_quantiles <- function(ci_levels,
+                              error_method){
+
+    if(error_method == "directional"){
+
+      qu_down <- 0.5 - ci_levels / 2
+      qu_up <- 0.5 + ci_levels / 2
+
+      qus <- c(qu_down, qu_up) |>
+        unique() |> #in case of median
+        sort()
+
+    } else if (error_method == "absolute"){
+
+      qus <- ci_levels
+    }
+
+    return(qus)
+  }
+
+
+  plot_target_label <- function(){
+
+    ptl <- c(`pcpi_pch` = "Inflation",
+             `ngdp_rpch` = "Real GDP Growth")
+
+    return(ptl)
+  }
+
+
+  plot_country_label <- function(){
+
+    pcl <- c(`CAN` = "Canada",
+             `DEU` = "Germany",
+             `FRA` = "France",
[…]

### 2023-10-24 test-macropi/data_loadsave.R

@@ -1,0 +1,44 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(MetBrewer)
+library(patchwork)
+devtools::load_all()
+
+.d <- `[`
+
+cis <- c(0.5, 0.8)
+qus <- c(0.1, 0.25, 0.75, 0.9)
+
+qufcs <- fread(here("quantile_forecasts", "quantile_forecasts.csv")) |>
+  .d(source == "IMF") |>
+  .d(error_method == "absolute") |>
+  .d(method == "rolling window") |>
+  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
+  .d(,forecast_season := ifelse(horizon %% 1 == 0, "F", "S")) |>
+  .d(, forecast_year := target_year - floor(horizon)) |>
+  .d(, .(country, target, forecast_year, forecast_season, target_year, quantile, prediction, horizon, true_value)) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "gdp_growth", "inflation"))
+
+qufcs_to_save <- qufcs |>
+  .d(, fltr := target_year - horizon) |>
+  .d(fltr == 2021.5) |>
+  .d(, .(country, target, forecast_year, forecast_season, target_year, quantile, prediction))
+
+realized_vals <- qufcs |>
+  .d(target_year > 2013) |>
+  .d(, .(country, target, target_year, true_value)) |>
+  .d(!is.na(true_value)) |>
+  unique()
+
+point_forecasts <- fread(here("data", "point_forecasts.csv")) |>
+  .d(source == "IMF") |>
+  .d(,fltr := target_year - horizon) |>
+  .d(fltr == 2021.5) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "gdp_growth", "inflation")) |>
+  .d(, .(country, target, target_year, prediction))
+
+
+data.table::fwrite(qufcs_to_save, file = here("test-macropi", "forecasts", "forecasts_Spring2022.csv"))
+data.table::fwrite(realized_vals, file = here("test-macropi", "extra-data", "historicvalues_Spring2022.csv"))
+data.table::fwrite(point_forecasts, file = here("test-macropi", "extra-data", "pointforecasts_Spring2022.csv"))

### 2023-10-24 test-macropi/plot_shiny-vis.R

@@ -1,0 +1,77 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(MetBrewer)
+library(patchwork)
+devtools::load_all()
+
+.d <- `[`
+
+trgt <- "inflation"
+cis <- c(0.5, 0.8)
+qus <- c(0.1, 0.25, 0.75, 0.9)
+
+qufcs <- fread(here("test-macropi", "forecasts", "forecasts_Spring2022.csv"))
+
+linerange_dat <- qufcs |>
+  .d(target == trgt) |>
+  .d(,quantile := paste0("quantile", quantile)) |>
+  .d(,season_helper := ifelse(forecast_season == "S", 0.5, 0)) |>
+  .d(,horizon := (target_year - forecast_year) + season_helper) |>
+  .d(, .(country, target, target_year, horizon, quantile, prediction)) |>
+  dcast(country + target + target_year + horizon ~ quantile, value.var = "prediction")
+
+realized_vals <- fread(here("test-macropi", "extra-data", "historicvalues_Spring2022.csv"))|>
+  .d(target == trgt)
+point_fcs <- fread(here("test-macropi", "extra-data", "pointforecasts_Spring2022.csv"))|>
+  .d(target == trgt)
+
+dashed_line <- rbind(point_fcs, realized_vals |> copy() |> setnames("true_value", "prediction") |> .d(target_year > 2020))
+
+
+###########################################################################
+cols <- paste0("quantile", qus)
+
+labeldat_2022 <- linerange_dat |>
+  .d(target_year == 2022) |>
+  .d(, x := 2016.25) |>
+  .d(, y := 8.2) |>
+  .d(, (cols) := lapply(.SD, function(val) as.character(round(val, 1))), .SDcols = cols) |>
+  .d(, (cols) := lapply(.SD, function(val) ifelse(grepl("[.]", val), val, paste0(val, ".0"))), .SDcols = cols) |>
+  .d(, label := paste0("2022\n", "50% PI: ", quantile0.25, " - ", quantile0.75, "\n",
+                       "80% PI: ", quantile0.1, " - ", quantile0.9))
+
+labeldat_2023 <- linerange_dat |>
+  .d(target_year == 2023) |>
+  .d(, x := 2016.75) |>
+  .d(, y := 5.0) |>
+  .d(, (cols) := lapply(.SD, function(val) as.character(round(val, 1))), .SDcols = cols) |>
[…]

### 2023-10-24 theoretical/PAVAReorderingHorizons.tex
pava reordering

\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}

\usepackage{natbib}
\bibliographystyle{abbrvnat}

\usepackage[colorlinks=false, allcolors=blue]{hyperref}

\title{PAVA-Reordering \\ Horizon Monotonicity Violations}
\author{Rike Becker}
\date{October 23, 2023}

\begin{document}
\maketitle
\noindent
This is an outline for how the PAVA-Algorithm would apply in our case. Main reference is \cite{pavaref2008}, which contains the most accessible explanation of the PAVA-Algorithm that I could find. \bigskip \\ 
\noindent
We want to obtain central prediction intervals of level $\alpha \in \{0.5, 0.8\}$, based on quantile forecasts $q^{\tau}_{t, h}$ for a quantity $y_{t}$. $\tau \in (0,1)$ is the quantile level, $t \in \{1,...T\}$ is target year, $h \in \{2, 8, 14, 20\}$ indexes the forecast horizon (monthly units). The length of the corresponding central prediction intervals should be monotic with respect to $h$, that is, \\
\begin{align}\label{eq:constraint}
  c^{\alpha}_{t,h} &\leq  c^{\alpha}_{t,h+1}, \quad \textrm{for all } t,h; \quad \textrm{where} \\ 
 c^{\alpha}_{t,h} &:= q^{1-\alpha/2}_{t,h} - q^{\alpha/2}_{t,h}
 \end{align}
Assuming we have a minimal information set $\mathcal{A}_{0}$ consisting only of past forecast-observation pairs $(\hat{y}_{t,h}, y_t)_{t = 1}^T$ and further assuming (some sort of) stationarity in the series of forecast errors $\hat{e} = y_t - \hat{y}_{t,h}$, the optimal $\tau-$quantile forecast in terms of the weighted interval score should be the respective $\tau-$quantile in the set of past forecast errors 
\begin{align}\label{eq:solution}
 \mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-R \leq t^* < t \},
\end{align}
where we denote the value of the quantile with $q^{\tau, \mathcal{E}}_{t, h}$.\footnote{If we set R = 21, we can extract quantiles directly from the order statistics, simplifying the question of which interpolation method would be optimal.}\\ 
Of course, while there is a natural tendency for the quantiles obtained from \eqref{eq:solution} to fulfill constraint \eqref{eq:constraint}, there is no guarantee for this and we practically observe a considerable proportion of violations in our setting. \medskip \\
I would propose that applying the pool-adjacent-violators algorithm as detailed in section 3.1. in \cite{pavaref2008} to this problem would look like the following:\footnote{For a given $t$ and $\alpha$ - respective indices dropped for simplicity.}\\ 
The initial solution is simply $q_h^{(0)} := q_h^{\mathcal{E}}$. The index for the blocks is $r = 1, . . . , B$ where at the initial step we have $B := 4$. Then:
\begin{enumerate}
\item Merge $q^{(l)}-$values from blocks $r$ and $r+1$ into block $r$ if $c_{r+1}^{(l)}<c_{r}^{(l)}$
\item Choose $q_{r}^{(l+1)}$ such that our loss function is optimized.\footnote{I would suspect that in terms of the WIS, this would amount to taking an average of the respective quantiles.} 
\item Go back to 1. in case of any further violations. 
\end{enumerate}
Basically, we would simply merge horizons if they don't uphold the natural ordering for a given $\alpha$ and set the respective quantiles to the same (average) value.\bigskip\\ 
\noindent
\textbf{Some things to note/discuss:}
\begin{enumerate}
	\item To my (albeit relatively new) knowledge of the algorithm, it is unusual that the violators are not registered on the same level that they are treated. That is, here we check for violators on the level of the central interval lengths, but we treat them directly on the quantiles. 
	\item This is inherently a "univariate" method with respect to the horizon monotonicity constraint. We of course have a second monotonicity constraint with respect to the quantile levels, that is, we require $q^{\tau} \leq q^{\tau'}$ for $\tau < \tau'$ (note that this constraint is again formulated for the quantiles, not for the length of the central intervals).\\ 
	This could simply be accounted for with a step 3., where we either (a) automatically pool all other quantiles in block $r$ or (b) do so in cases where quantile ordering is not upheld across that block. 
	\item Note that this document was formulated for the \textit{directional} error method. This is due to the fact that I suspect that the quantiles of \eqref{eq:solution} are the optimal solution in that case only. In the case of absolute error treatment, choosing the new pooled value in step 2. of the algorithm could perhaps not be theoretically motivated in terms of a loss function, at least not in a way that is immediately obvious to me.\footnote{I would still argue in favor of absolute error treatment however, as it empirically shows much better coverage levels.} \\ 
	At least, in the case of absolute errors, we would diagnose and treat violations on the same level (that is, length of the central intervals).
\end{enumerate}
\bibliographystyle{IEEEannot}
\bibliography{biblio}

\end{document}

### 2023-10-25 manuscript/manuscript.tex
change year-sampling: now depends on horizon -> real-time compatible

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{setspace}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{longtable}
+\usepackage{colortbl}
+\usepackage{array}
 \ifLuaTeX
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \multicolumn{1}{l}{} & IMF & ar & bvar \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 0} \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 expanding window\_interval\_score & 0.115 & 0.123 & 0.122 \\ 
@@
 rolling window\_sample\_crps & 0.094 & 0.097 & 0.098 \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 0.5} \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 expanding window\_interval\_score & 0.258 & 0.272 & 0.296 \\ 
@@
 rolling window\_sample\_crps & 0.191 & 0.201 & 0.235 \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 1} \\ 
-\midrule
-expanding window\_interval\_score & 0.448 & 0.737 & 0.590 \\ 
+\midrule\addlinespace[2.5pt]
+expanding window\_interval\_score & 0.447 & 0.740 & 0.595 \\ 
 expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
@@
 leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
-rolling window\_interval\_score & 0.451 & 0.739 & 0.591 \\ 
+rolling window\_interval\_score & 0.458 & 0.744 & 0.601 \\ 
 rolling window\_sample\_crps & 0.333 & 0.514 & 0.434 \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 1.5} \\ 
-\midrule
-expanding window\_interval\_score & 0.495 & 1.044 & 0.800 \\ 
+\midrule\addlinespace[2.5pt]
+expanding window\_interval\_score & 0.503 & 1.051 & 0.812 \\ 
 expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
@@
 leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
-rolling window\_interval\_score & 0.494 & 1.041 & 0.779 \\ 
+rolling window\_interval\_score & 0.506 & 1.043 & 0.790 \\ 
 rolling window\_sample\_crps & 0.347 & 0.632 & 0.570 \\ 
@@
 \multicolumn{1}{l}{} & IMF & ar & bvar \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 0} \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 expanding window\_interval\_score & 0.241 & 0.301 & 0.298 \\ 
@@
 rolling window\_sample\_crps & 0.178 & 0.211 & 0.204 \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 0.5} \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 expanding window\_interval\_score & 0.416 & 0.540 & 0.493 \\ 
@@
 rolling window\_sample\_crps & 0.297 & 0.405 & 0.373 \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 1} \\ 
-\midrule
-expanding window\_interval\_score & 0.837 & 1.090 & 0.942 \\ 
+\midrule\addlinespace[2.5pt]
+expanding window\_interval\_score & 0.846 & 1.094 & 0.947 \\ 
 expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
@@
 leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
-rolling window\_interval\_score & 0.851 & 1.122 & 0.970 \\ 
+rolling window\_interval\_score & 0.858 & 1.121 & 0.973 \\ 
 rolling window\_sample\_crps & 0.663 & 0.875 & 0.815 \\ 
-\midrule
+\midrule\addlinespace[2.5pt]
 \multicolumn{4}{l}{horizon = 1.5} \\ 
-\midrule
-expanding window\_interval\_score & 1.045 & 1.288 & 1.102 \\ 
+\midrule\addlinespace[2.5pt]
+expanding window\_interval\_score & 1.063 & 1.297 & 1.113 \\ 
 expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
@@
 leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
-rolling window\_interval\_score & 1.056 & 1.312 & 1.143 \\ 
+rolling window\_interval\_score & 1.075 & 1.313 & 1.150 \\ 
 rolling window\_sample\_crps & 0.831 & 0.985 & 0.949 \\ 

### 2023-10-25 R/uqfc.R

@@ -137,7 +137,21 @@ empFC <- function(weodat,
 
     #get empirical quantiles
     quSet <- weodat |>
-      .d(target_year %in% yearset) |>
+      #####This block is for not incorrectly sampling target_years when horizon >=1
+      #e.g. when horizon = 1, this means making a forecast for e.g. 2020 in fall
+      #of 2019, so in a real-time setting you wouldn't have access to the resolution
+      #of the horizon-1 forecast for 2019 (so you need your error sample to start in 2018)
+      #this code is set so that the window methods honor this, but the leave-one-out
+      #method doesnt't (since it has access to the future anyways)
+      .d(,target_method := method) |>
+      .d(,helper_horizon := ifelse(target_method == "leave-one-out",
+                                   0, #no shift in loo method
+                                   horizon)) |>
+      .d(, effective_target_year := target_year + floor(helper_horizon)) |>
+      .d(effective_target_year %in% yearset) |>
+      .d(, c("target_method", "helper_horizon", "effective_target_year") := NULL) |>
+      #####And now back to your regularly scheduled program
+      #.d(target_year %in% yearset) |>
       empQU(error_fct = error_fct,
             quantiles = quantiles,
             tv_release = tv_release) |>

### 2023-10-25 scripts/toy-scripts/compare-afterbefore-horizonshift.R

@@ -1,0 +1,116 @@
+library(data.table)
+library(here)
+devtools::load_all()
+#this file was run once before and once after changing the code in uqfc.R
+#for 'correctly'/honestly sampling with respect to horizon
+#only last line (name of saved file) was changed
+
+source(here("specs", "specs.R"))
+
+.d <- `[`
+
+max_year_imf <- specs$max_year_imf
+max_year_others <- specs$max_year_others
+min_year <- 2000
+tv_release <- specs$tv_release
+window_length <- specs$window_length
+
+cis <- specs$ci_levels_make
+
+#make all combinations of settings
+combs <- data.table::fread(here("quantile_forecasts", "setting_combinations.csv"))
+
+
+fcdat <- data.table::fread(here("data", "point_forecasts.csv")) |>
+  .d(country %in% c("CAN", "JAP"))
+
+#make quantile forecasts for all combinations in combs
+testqus <- lapply(1:nrow(combs),
+                function(idxsub){
+
+                  setting <- combs[idxsub]
+
+                  if(setting[, "method"] == "leave-one-out"){
+
+                    start_year <- min_year
+                  } else {
+
+                    start_year <- min_year + window_length
+                  }
+
+                  subdat <- fcdat |>
+                    .d(source == setting[, "source"]) |>
+                    .d(target == setting[, "target"]) |>
+                    .d(, source := NULL)
+
+                  if (setting[, "source"] %in% c("bvar", "ar")) {
+                    max_year <- specs$max_year_others
+                  } else {
+
+                    max_year <- specs$max_year_imf
+                  }
+
+                  empFC(subdat,
+                        target_year = start_year:max_year,
+                        tv_release = tv_release,
+                        error_method = setting[, "error_method"],
+                        method = setting[, "method"],
+                        window_length = window_length,
+                        ci_levels = cis) |>
+                    .d(, source := setting[, "source"]) |>
+                    .d(, error_method := setting[, "error_method"]) |>
+                    .d(, method := setting[, "method"])
+
+                }
+) |>
+  rbindlist() |>
+  setnames(paste0("tv_", tv_release), "true_value")
+
+#fwrite(testqus, here("qufcs_beforehorshift.csv"))
+fwrite(testqus, here("qufcs_afterhorshift.csv"))
+
+
+
+
+
+
+
+
+
+
[…]

### 2023-11-28 scripts/master.R
allow quantile type specification

@@ -5,7 +5,7 @@ devtools::load_all()
 .d <- `[`
 
 #first check if new download is/should be available
-download <- TRUE #could be automated, but don't see the need right now
+download <- FALSE #could be automated, but don't see the need right now
 
 if(download){
   source(here("scripts", "download-data.R"))

### 2023-11-28 specs/specs.R

@@ -17,7 +17,8 @@ specs <- list(
   ci_levels_eval = c(0.5, 0.8),
   ci_levels_eval_su = c(50, 80), #for scoringutils wrapper
   ci_levels_make =  seq(0.1, 0.9, by = 0.1),
-  qu_levels = c(0.1, 0.25, 0.75, 0.9)
+  qu_levels = c(0.1, 0.25, 0.75, 0.9),
+  qutype = 7
 )
 
 

### 2023-11-28 manuscript/manuscript.tex
update manuscript

@@
 expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
-leave-one-out\_interval\_score & 0.112 & 0.123 & 0.123 \\ 
+leave-one-out\_interval\_score & 0.113 & 0.123 & 0.123 \\ 
 leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
@@
 expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
-leave-one-out\_interval\_score & 0.257 & 0.257 & 0.276 \\ 
+leave-one-out\_interval\_score & 0.256 & 0.257 & 0.276 \\ 
 leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
@@
 expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
-leave-one-out\_interval\_score & 0.443 & 0.746 & 0.587 \\ 
+leave-one-out\_interval\_score & 0.440 & 0.752 & 0.586 \\ 
 leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
@@
 expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
-leave-one-out\_interval\_score & 0.488 & 1.021 & 0.756 \\ 
+leave-one-out\_interval\_score & 0.490 & 1.033 & 0.761 \\ 
 leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
@@
 expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
-leave-one-out\_interval\_score & 0.235 & 0.297 & 0.295 \\ 
+leave-one-out\_interval\_score & 0.232 & 0.297 & 0.295 \\ 
 leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
@@
 expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
-leave-one-out\_interval\_score & 0.406 & 0.532 & 0.482 \\ 
+leave-one-out\_interval\_score & 0.404 & 0.532 & 0.482 \\ 
 leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
@@
 expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
-leave-one-out\_interval\_score & 0.833 & 1.083 & 0.933 \\ 
+leave-one-out\_interval\_score & 0.830 & 1.076 & 0.932 \\ 
 leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
@@
 expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
-leave-one-out\_interval\_score & 1.030 & 1.292 & 1.109 \\ 
+leave-one-out\_interval\_score & 1.034 & 1.288 & 1.107 \\ 
 leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 

### 2023-12-12 presentation/presentation.tex
presentation updates

@@
 
-\title[Simple Prediction Intervals]{Simple and Transparent Macroeconomic Distributional Forecasts}
+\title[Simple Prediction Intervals]{Simple Macroeconomic Forecast Distributions}
 \subtitle{} 
@@
 
-\date[29.\,9.\,2023]{September 29, 2023}
+\date[05.\,12.\,2023]{December 5, 2023}
 
@@
 		\end{itemize}
-    \item publicly available publication\footnote{International Monetary Fund. 2023. \textit{World Economic Outlook: A Rocky Recovery.} Washington, DC. April.}
+    \item publicly available\footnote{International Monetary Fund. 2023. \textit{World Economic Outlook: Navigating Global Divergences.} Washington, DC. October.} in an accessible format
     \item targets: real GDP growth and CPI inflation 
@@
     \end{itemize}
-    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-9 \leq t^* < t \}$, containing the last nine forecast errors
+    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-R \leq t^* < t \}$, containing the last $R$ forecast errors
     \begin{itemize}
         \item based on \textit{absolute} errors $\hat{e}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
-        \item sets are stratified by country, target and horizon
+        \item currently: $R=9$
+        %\item sets are stratified by country, target and horizon
     \end{itemize}
@@
     \end{itemize}
+    \item use PAVA-type reordering if intervals shrink with increasing horizon
     \item assess central interval coverage, score via the weighted interval score (WIS)\footnote{Bracher, J. et al. 2021. \textit{Evaluating
@@
 
-%\begin{frame}{Scores - Inflation}
-%%    \begin{figure}
- %       \centering
- %       \includegraphics[width=0.45\textwidth]{figures/scores_absolute errors_cpi.JPG} 
- %       \label{fig:enter-label}
- %   \end{figure} 
-%\end{frame}
-
 \begin{frame}{Calibration - Interval Coverage Levels}
@@
 %\textit{include graphic or table showing increasing uncertainty with rising horizons}\\ 
-
 \begin{columns}
@@
 \vspace{1.25cm}
-%\begin{table}
-%\begin{tabular}{ l c c }
-%\multicolumn{3}{c}{\textbf{Inflation}}\\
-%%&   50\%  & 80\%\\[0.3em]
-%Fall,  SY & 0.3 & 0.6\\ 
-%Spring, SY &0.5 &1.3 \\ 
-%Fall, NY & 1.2 & 2.2\\ 
-%Spring, NY &1.9 &2.4 \\ 
-%\end{tabular}
-%\end{table}
 \end{column}
@@
         \centering
-        \includegraphics[width=0.6\textwidth]{figures/horizon_uncc_germany2023.pdf}
+        \includegraphics[width=0.6\textwidth]{figures/horizon_uncc_germany2023_current.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
@@
 \begin{frame}{Making it public}
-\url{https://fredbec.shinyapps.io/macropi/}
 \begin{columns}
-\begin{column}{0.2\textwidth}
-    \begin{figure}
-        \centering
-        \includegraphics[width=\textwidth]{figures/shinycap2.png}
-        %\caption{Coverage at the 50 and 80 percent level}
-        \label{fig:enter-label}
-    \end{figure} 
+\begin{column}{0.3\textwidth}
+Shiny App: \\
+   \url{https://probability-forecasting.shinyapps.io/macropi/} \vspace{0.5cm} \\ 
+GitHub repo with our forecasts: \\
+    \url{https://github.com/MacroPrediction/MacroPI}
+    \vspace*{2cm}
 \end{column}
-\begin{column}{0.6\textwidth}
+\begin{column}{0.7\textwidth}
+\vspace*{-10mm}
     \begin{figure}
         %\centering
-        \includegraphics[width=0.7\textwidth]{figures/shinycap.jpg}
+        \includegraphics[width=0.55\textwidth]{figures/shinycap_newhost.jpg}
         %\caption{Coverage at the 50 and 80 percent level}

### 2023-12-12 presentation/make_more_plots.R
separate wis plot for presentation

@@ -11,6 +11,7 @@ library(tidyverse)
 devtools::load_all()
 .d <- `[`
 
+source(here("presentation", "wis_plot_presentation_function.R"))
 
 chosen_method <- "rolling window"
 chosen_em <- "directional"
@@ -60,8 +61,8 @@ point_scores <- data.table::fread(here("scores", "pointfc_scores.csv"))
 
 scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
 
-cpi_plot <- ovr_assessment_plot(wis_scores, "pcpi_pch")
-gdp_plot <- ovr_assessment_plot(wis_scores, "ngdp_rpch")
+cpi_plot <- wis_plot_pres(wis_scores, "pcpi_pch")
+gdp_plot <- wis_plot_pres(wis_scores, "ngdp_rpch")
 
 
 

### 2023-12-12 presentation/make_plots.R

@@ -11,6 +11,7 @@ library(tidyverse)
 devtools::load_all()
 .d <- `[`
 
+source(here("presentation", "wis_plot_presentation_function.R"))
 
 chosen_method <- "rolling window"
 chosen_em <- "absolute"
@@ -60,8 +61,10 @@ point_scores <- data.table::fread(here("scores", "pointfc_scores.csv"))
 
 scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
 
-cpi_plot <- ovr_assessment_plot(wis_scores, "pcpi_pch")
-gdp_plot <- ovr_assessment_plot(wis_scores, "ngdp_rpch")
+cpi_plot <- wis_plot_pres(wis_scores, "pcpi_pch")
+gdp_plot <- wis_plot_pres(wis_scores, "ngdp_rpch")
+#cpi_plot <- ovr_assessment_plot(wis_scores, "pcpi_pch")
+#gdp_plot <- ovr_assessment_plot(wis_scores, "ngdp_rpch")
 
 
 

### 2023-12-12 presentation/wis_plot_presentation_function.R

@@ -1,0 +1,76 @@
+wis_plot_pres <- function(wis_scoredat,
+                         trgt = c("pcpi_pch", "ngdp_rpch"),
+                         xmax = NULL,
+                         plot_name = NULL){
+
+  if(length(unique(wis_scoredat$error_method)) > 1){
+    stop("Only one error method allowed. Prefilter data")
+  }
+
+  if(length(unique(wis_scoredat$method)) > 1){
+    stop("Only one method allowed. Prefilter data")
+  }
+
+  if(length(trgt) > 1){
+    stop("need to supply single value for trgt")
+  }
+
+  if(is.null(plot_name)){
+    plot_name <- plot_target_label()[trgt]
+  }
+
+  decomp_data <- wis_scoredat |>
+    .d(target == trgt) |>
+    .d(, target := NULL) |>
+    .d(, method := NULL) |>
+    .d(, error_method := NULL)
+
+
+  #prespecify xmax (otherwise, largest values are sometimes cut off)
+  if(is.null(xmax)){
+    xmax <- max(decomp_data$interval_score) + 0.02
+  }
+
+  decomp_data <- decomp_data |>
+    .d(, .(source, horizon, dispersion, underprediction, overprediction)) |>
+    data.table::melt(id.vars = c("source", "horizon"),
+                     value.name = "score",
+                     variable.name = "type") |>
+    # is technically already filtered out, but just to make sure
+    .d(type != "interval_score")
+
+
+
+  decomp_plot <- ggplot(decomp_data, aes(x = source,
+                                         fill = source,
+                                         y = score,
+                                         alpha = type)) +
+    geom_bar(position="stack", stat="identity") +
+    facet_wrap(~ horizon,
+               labeller = as_labeller(plot_horizon_label_short(4)),
+               nrow = 1) +
+    scale_alpha_discrete(range = c(0.35,1),
+                         labels = c("Overprediction",
+                                    "Underprediction",
+                                    "Dispersion"),
+                         name = "Components of the WIS") +
+    scale_x_discrete(name = "",
+                     breaks = c("IMF", "BVAR", "BVAR - direct", "AR"),
+                     labels = c("IMF", "BVAR", "BVAR - direct", "AR")) +
+
+    scale_y_continuous(name = "Weighted Interval Score", limits = c(0, xmax)) +
+    scale_fill_met_d("Hokusai1",
[…]

### 2023-12-13 presentation/presentation.tex
better naming of figures

@@
         \centering
-        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp_new.pdf} 
+        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp.pdf} 
         \label{fig:enter-label}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_directional.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_directional.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_ew.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_expandingwindow.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/coverage_ew.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/coverage_expandingwindow.pdf}
         %\caption{Coverage at the 50 and 80 percent level}

### 2023-12-13 presentation/make_figures/plots_absolute_expandingwindow.R

@@ -13,7 +13,7 @@ devtools::load_all()
 
 source(here("presentation", "presentation_plot_functions.R"))
 
-chosen_method <- "rolling window"
+chosen_method <- "expanding window"
 chosen_em <- "absolute"
 
 #############################################################################
@@ -39,7 +39,7 @@ bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
 
 wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
   .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
-                     label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
+                        label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
   .d(method == chosen_method) |>
   .d(error_method == chosen_em)
 
@@ -50,7 +50,7 @@ gdp_plot <- wis_plot_pres(wis_scores, "ngdp_rpch")
 
 
 #paste together and save as pdf
-pdf(file = here("presentation", "figures", "wis_cpigdp_new.pdf"), width = 9.5, height = 4)
+pdf(file = here("presentation", "figures", "wis_cpigdp_expandingwindow.pdf"), width = 9.5, height = 4)
 ovr_plot <-
   (cpi_plot | gdp_plot) +
   plot_layout(guides = "collect",
@@ -121,7 +121,7 @@ plot_cpi <- coverage_plot_pres(cvgdat_cpi, "pcpi_pch", large_cvgdat)
 plot_gdp <- coverage_plot_pres(cvgdat_gdp, "ngdp_rpch", large_cvgdat)
 
 
-pdf(file = here("presentation", "figures", "coverage.pdf"), width = 9.5, height = 4)
+pdf(file = here("presentation", "figures", "coverage_expandingwindow.pdf"), width = 9.5, height = 4)
 ovr_plot <-
   (plot_cpi | plot_gdp) +
   plot_layout(guides = "collect",

### 2023-12-13 presentation/make_figures/plots_absolute_rollingwindow.R

@@ -14,8 +14,7 @@ devtools::load_all()
 source(here("presentation", "presentation_plot_functions.R"))
 
 chosen_method <- "rolling window"
-chosen_em <- "directional"
-
+chosen_em <- "absolute"
 
 #############################################################################
 #############################################################################
@@ -40,7 +39,7 @@ bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
 
 wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
   .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
-                        label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
+                     label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
   .d(method == chosen_method) |>
   .d(error_method == chosen_em)
 
@@ -51,7 +50,7 @@ gdp_plot <- wis_plot_pres(wis_scores, "ngdp_rpch")
 
 
 #paste together and save as pdf
-pdf(file = here("presentation", "figures", "wis_cpigdp_new_directional.pdf"), width = 9.5, height = 4)
+pdf(file = here("presentation", "figures", "wis_cpigdp.pdf"), width = 9.5, height = 4)
 ovr_plot <-
   (cpi_plot | gdp_plot) +
   plot_layout(guides = "collect",
@@ -122,7 +121,7 @@ plot_cpi <- coverage_plot_pres(cvgdat_cpi, "pcpi_pch", large_cvgdat)
 plot_gdp <- coverage_plot_pres(cvgdat_gdp, "ngdp_rpch", large_cvgdat)
 
 
-pdf(file = here("presentation", "figures", "coverage_directional.pdf"), width = 9.5, height = 4)
+pdf(file = here("presentation", "figures", "coverage.pdf"), width = 9.5, height = 4)
 ovr_plot <-
   (plot_cpi | plot_gdp) +
   plot_layout(guides = "collect",

### 2023-12-13 presentation/make_figures/plots_directional_rollingwindow.R

@@ -13,8 +13,9 @@ devtools::load_all()
 
 source(here("presentation", "presentation_plot_functions.R"))
 
-chosen_method <- "expanding window"
-chosen_em <- "absolute"
+chosen_method <- "rolling window"
+chosen_em <- "directional"
+
 
 #############################################################################
 #############################################################################
@@ -50,7 +51,7 @@ gdp_plot <- wis_plot_pres(wis_scores, "ngdp_rpch")
 
 
 #paste together and save as pdf
-pdf(file = here("presentation", "figures", "wis_cpigdp_new_ew.pdf"), width = 9.5, height = 4)
+pdf(file = here("presentation", "figures", "wis_cpigdp_directional.pdf"), width = 9.5, height = 4)
 ovr_plot <-
   (cpi_plot | gdp_plot) +
   plot_layout(guides = "collect",
@@ -121,7 +122,7 @@ plot_cpi <- coverage_plot_pres(cvgdat_cpi, "pcpi_pch", large_cvgdat)
 plot_gdp <- coverage_plot_pres(cvgdat_gdp, "ngdp_rpch", large_cvgdat)
 
 
-pdf(file = here("presentation", "figures", "coverage_ew.pdf"), width = 9.5, height = 4)
+pdf(file = here("presentation", "figures", "coverage_directional.pdf"), width = 9.5, height = 4)
 ovr_plot <-
   (plot_cpi | plot_gdp) +
   plot_layout(guides = "collect",

### 2023-12-15 manuscript/manuscript.tex
change to window size 11

@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.115 & 0.123 & 0.122 \\ 
-expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
-leave-one-out\_interval\_score & 0.113 & 0.123 & 0.123 \\ 
+expanding window\_interval\_score & 0.114 & 0.124 & 0.122 \\ 
+expanding window\_sample\_crps & 0.087 & 0.093 & 0.092 \\ 
+leave-one-out\_interval\_score & 0.110 & 0.122 & 0.121 \\ 
 leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
-rolling window\_interval\_score & 0.119 & 0.128 & 0.126 \\ 
-rolling window\_sample\_crps & 0.094 & 0.097 & 0.098 \\ 
+rolling window\_interval\_score & 0.117 & 0.126 & 0.124 \\ 
+rolling window\_sample\_crps & 0.090 & 0.093 & 0.092 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.258 & 0.272 & 0.296 \\ 
-expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
-leave-one-out\_interval\_score & 0.256 & 0.257 & 0.276 \\ 
+expanding window\_interval\_score & 0.255 & 0.280 & 0.305 \\ 
+expanding window\_sample\_crps & 0.179 & 0.205 & 0.235 \\ 
+leave-one-out\_interval\_score & 0.254 & 0.267 & 0.289 \\ 
 leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
-rolling window\_interval\_score & 0.261 & 0.266 & 0.288 \\ 
-rolling window\_sample\_crps & 0.191 & 0.201 & 0.235 \\ 
+rolling window\_interval\_score & 0.256 & 0.272 & 0.292 \\ 
+rolling window\_sample\_crps & 0.184 & 0.196 & 0.223 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.447 & 0.740 & 0.595 \\ 
-expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
-leave-one-out\_interval\_score & 0.440 & 0.752 & 0.586 \\ 
+expanding window\_interval\_score & 0.464 & 0.764 & 0.607 \\ 
+expanding window\_sample\_crps & 0.344 & 0.547 & 0.448 \\ 
+leave-one-out\_interval\_score & 0.456 & 0.776 & 0.600 \\ 
 leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
-rolling window\_interval\_score & 0.458 & 0.744 & 0.601 \\ 
-rolling window\_sample\_crps & 0.333 & 0.514 & 0.434 \\ 
+rolling window\_interval\_score & 0.471 & 0.768 & 0.611 \\ 
+rolling window\_sample\_crps & 0.347 & 0.550 & 0.452 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.503 & 1.051 & 0.812 \\ 
-expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
-leave-one-out\_interval\_score & 0.490 & 1.033 & 0.761 \\ 
+expanding window\_interval\_score & 0.517 & 1.043 & 0.807 \\ 
+expanding window\_sample\_crps & 0.367 & 0.635 & 0.612 \\ 
+leave-one-out\_interval\_score & 0.507 & 1.023 & 0.755 \\ 
 leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
-rolling window\_interval\_score & 0.506 & 1.043 & 0.790 \\ 
-rolling window\_sample\_crps & 0.347 & 0.632 & 0.570 \\ 
+rolling window\_interval\_score & 0.521 & 1.042 & 0.787 \\ 
+rolling window\_sample\_crps & 0.361 & 0.623 & 0.576 \\ 
 \bottomrule
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.241 & 0.301 & 0.298 \\ 
-expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
-leave-one-out\_interval\_score & 0.232 & 0.297 & 0.295 \\ 
+expanding window\_interval\_score & 0.229 & 0.295 & 0.291 \\ 
+expanding window\_sample\_crps & 0.168 & 0.200 & 0.195 \\ 
+leave-one-out\_interval\_score & 0.222 & 0.292 & 0.291 \\ 
 leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
-rolling window\_interval\_score & 0.240 & 0.302 & 0.297 \\ 
-rolling window\_sample\_crps & 0.178 & 0.211 & 0.204 \\ 
+rolling window\_interval\_score & 0.232 & 0.292 & 0.287 \\ 
+rolling window\_sample\_crps & 0.169 & 0.197 & 0.190 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.416 & 0.540 & 0.493 \\ 
-expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
-leave-one-out\_interval\_score & 0.404 & 0.532 & 0.482 \\ 
+expanding window\_interval\_score & 0.408 & 0.558 & 0.510 \\ 
+expanding window\_sample\_crps & 0.289 & 0.390 & 0.370 \\ 
+leave-one-out\_interval\_score & 0.396 & 0.550 & 0.500 \\ 
 leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
-rolling window\_interval\_score & 0.416 & 0.554 & 0.504 \\ 
-rolling window\_sample\_crps & 0.297 & 0.405 & 0.373 \\ 
+rolling window\_interval\_score & 0.411 & 0.565 & 0.519 \\ 
+rolling window\_sample\_crps & 0.290 & 0.402 & 0.374 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.846 & 1.094 & 0.947 \\ 
-expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
-leave-one-out\_interval\_score & 0.830 & 1.076 & 0.932 \\ 
+expanding window\_interval\_score & 0.878 & 1.176 & 1.018 \\ 
+expanding window\_sample\_crps & 0.664 & 0.861 & 0.801 \\ 
+leave-one-out\_interval\_score & 0.866 & 1.159 & 1.005 \\ 
 leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
-rolling window\_interval\_score & 0.858 & 1.121 & 0.973 \\ 
-rolling window\_sample\_crps & 0.663 & 0.875 & 0.815 \\ 
+rolling window\_interval\_score & 0.901 & 1.201 & 1.044 \\ 
+rolling window\_sample\_crps & 0.682 & 0.901 & 0.841 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 1.063 & 1.297 & 1.113 \\ 
-expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
-leave-one-out\_interval\_score & 1.034 & 1.288 & 1.107 \\ 
+expanding window\_interval\_score & 1.126 & 1.387 & 1.198 \\ 
+expanding window\_sample\_crps & 0.841 & 0.977 & 0.956 \\ 
+leave-one-out\_interval\_score & 1.097 & 1.381 & 1.195 \\ 
 leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
-rolling window\_interval\_score & 1.075 & 1.313 & 1.150 \\ 
-rolling window\_sample\_crps & 0.831 & 0.985 & 0.949 \\ 
+rolling window\_interval\_score & 1.139 & 1.411 & 1.235 \\ 
+rolling window\_sample\_crps & 0.864 & 1.022 & 1.005 \\ 
 \bottomrule

### 2023-12-15 specs/specs.R

@@ -4,7 +4,7 @@ library(data.table)
 #set project wide specifications
 
 min_year <- 1990
-window_length <- 9
+window_length <- 11
 
 specs <- list(
   tv_release = 1,

### 2024-03-18 presentation/presentation_svr.tex
presentation files

--- 2023-12-13 presentation/presentation.tex
@@
 \title[Simple Prediction Intervals]{Simple Macroeconomic Forecast Distributions}
-\subtitle{} 
+%\subtitle{Einfache makroökonomische probabilistische Vorhersagen} 
 \author[Friederike Becker, Fabian Krüger, Melanie Schienle]{Friederike Becker, Fabian Krüger, Melanie Schienle}
 
-\date[05.\,12.\,2023]{December 5, 2023}
+\date[28.\,02.\,2024]{February 28, 2024}
 
@@
 
-\section{Setting}
+\begin{frame}{Small Note on Terminology}
+Some terms are used interchangeably within the context of this presentation
+\begin{itemize}
+\item probabilistic - distributional
+\item forecast - prediction - projection 
+\end{itemize}
+\end{frame}
+
+\section{Setting and Motivation}
 
@@
 
+\begin{frame}[t]{Why should we explicitly quantify uncertainty?}
+\begin{itemize}
+    \item more honest and transparent \smallskip
+    \item can increase trust in forecasts \smallskip
+    \item broader information base facilitates better decision making \smallskip
+    \item better evaluation and accountability
+    %\item simple and transparent method of attaching prediction intervals 
+%\item show that attaching distributional forecasts to an existing
+%\item for up to one and a half years into the future 
+%\item evaluate on years 1999-2021
+\end{itemize}
+\end{frame}
+
 \begin{frame}[t]{Can we really be that sure?}
@@
 \begin{columns}
-\begin{column}{0.4\textwidth}
+\begin{column}{0.45\textwidth}
    	\begin{itemize}
@@
          \begin{itemize}
-	    \item uncertainty is at best acknowledged, rarely quantified \bigskip
+	    \item uncertainty is at best acknowledged, rarely quantified \smallskip
 	\end{itemize}
         %\item media reception often fixated on zero
-        \item forecasts of different horizons are often left uncontextualized \bigskip
-        \item distributional forecasts supposedly would require extra modeling effort
+        \item we observe artefacts in reporting 
+        \begin{itemize}
+            \item fixation on values slightly above/below zero
+            \item different horizons are often left uncontextualized \bigskip
+        \end{itemize}
+        \item distributional forecasts supposedly require additional ...
+        \begin{itemize}
+        \item ... modeling effort (forecast issuer)
+        \item ... cognitive load (forecast user)
+        \end{itemize}
     \end{itemize}
@@
 \end{column}
-\begin{column}{0.6\textwidth}
+\begin{column}{0.55\textwidth}
+\vspace*{-2.05cm}
     \begin{figure}
@@
 
+\begin{frame}[t]{Types of probabilistic forecasts}
+
+\begin{columns}
+\begin{column}{0.39\textwidth}
+    \begin{itemize}
+\item full probability distribution
+\item histogram
+\item samples from distribution
+\item \textbf{quantiles or prediction intervals}
+\end{itemize}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.8\textwidth]{figures_svr/densityfc.pdf} 
+        \label{fig:enter-label}
+    \end{figure}
+\end{column}
+\begin{column}{0.52\textwidth}
+\vspace*{-1.55cm}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.7\textwidth]{figures_svr/CI_illustration.pdf} 
+        \label{fig:enter-label}
+    \end{figure}     
+\end{column}
+\begin{column}{0.01\textwidth}
+
+\end{column}
+\end{columns}
+\end{frame}
+
+\addtocounter{framenumber}{-1}
+\begin{frame}[t]{Example 1: Weather Forecasting}
+\begin{columns}
+\begin{column}{0.35\textwidth}
+Uncertainty is communicated via \smallskip
+    \begin{itemize}
+         \item $80\%$ prediction interval for temperature \medskip
+         \item probability for precipitation and adverse weather events
+    \end{itemize}
+    \vspace{2cm}
+\end{column}
+\begin{column}{0.65\textwidth}
+\vspace*{-.05cm}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\textwidth]{figures_svr/Probcast.jpg} 
+        \caption{Source: Mass, C. et al. 2009. \textit{PROBCAST}, BAMS}
+    \end{figure}
+\end{column}
+\end{columns}
+\end{frame}
+
+\addtocounter{framenumber}{-1}
+\begin{frame}[t]{Example 2: Forecasting Covid-19}
+\begin{columns}
+\begin{column}{0.35\textwidth}
+Uncertainty is communicated via \smallskip
+    \begin{itemize}
+         \item granular prediction intervals for Covid-19 Cases and Deaths \medskip
+         \item main prediction intervals ($50\%$, $95\%$) are highlighted
+    \end{itemize}
+    \vspace{2cm}
+\end{column}
+\begin{column}{0.65\textwidth}
+\vspace*{-.05cm}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.65\textwidth]{figures_svr/covid19.jpg} 
+        \caption{Source: https://viz.covid19forecasthub.org}
+    \end{figure}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}[t]{The makings of a good probabilistic forecast}
+\vspace*{-0.25cm}
+\begin{itemize}
+\item central paradigm: \textbf{sharpness subject to calibration}\footnote{Gneiting, T. et al. 2007. \textit{Probabilistic forecasts, calibration and sharpness.} JRSS}
+\item calibration alone can be easily asserted
+\begin{itemize}
+\item most important metric for a trustworthy forecast
+\end{itemize}
+\item \textbf{proper scoring rules} check calibration and sharpness simultaneously
+\end{itemize}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.61\textwidth]{figures_svr/sharp_calib.pdf} 
+    \end{figure}
+\end{frame}
+
+\section{Methods}
 \begin{frame}[t]{Contributions of this work}
@@
     \item  GDP growth and inflation
-    \item  all G7 countries
+    \item  all G-7 countries
     \item  current and next year targets
@@
 
-\section{Methods}
+%\section{Methods}
 \begin{frame}{Methods}
@@
     \end{itemize}
-    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-R \leq t^* < t \}$, containing the last $R$ forecast errors
+    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}^{a}_{t^*, h}  | t-R \leq t^* < t \}$, containing the last $R$ forecast errors
     \begin{itemize}
-        \item based on \textit{absolute} errors $\hat{e}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
-        \item currently: $R=9$
+        \item based on \textit{absolute} errors $\hat{e}^{a}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
+        \item currently: $R=11$
         %\item sets are stratified by country, target and horizon
     \end{itemize}
-    \item for $\alpha \in \{0.5, 0.8\}$, compute $q^{\alpha}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \alpha \right)$
+    \item for each desired confidence level $\tau$, compute $q^{\tau}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \tau \right)$
+    \begin{itemize}
+    \item  for conciseness, we choose $\tau  \in \{0.5, 0.8\}$
+    \end{itemize}
     \item and compute the upper and lower endpoints of a central prediction interval as 
     \begin{itemize}
-        \item $u^{\alpha}_{t,h} = \hat{y}_{t, h} + q^{\alpha}_{t, h}$ 
-        \item $l^{\alpha}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\alpha}_{t, h}$
+        \item $u^{\tau}_{t,h} = \hat{y}_{t, h} + q^{\tau}_{t, h}$ 
+        \item $l^{\tau}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\tau}_{t, h}$
     \end{itemize}
-    \item use PAVA-type reordering if intervals shrink with increasing horizon
-    \item assess central interval coverage, score via the weighted interval score (WIS)\footnote{Bracher, J. et al. 2021. \textit{Evaluating
+    %\item use PAVA-type reordering if intervals shrink with increasing horizon
+
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Methods, continued}
+\begin{itemize}
+\item Notwithstanding the method's simplicity, the following constraints are imposed
+\begin{itemize}
+    \item point forecast lies at the center of each prediction interval  
+    \item intervals are reordered if their length does not increase with distance to target 
+\end{itemize}
+\item as an alternative, ``directional'' errors are also considered \bigskip
+\item assess central interval coverage and score via the weighted interval score (WIS)\footnote{Bracher, J. et al. 2021. \textit{Evaluating
 Epidemic Forecasts in an Interval Format.} PLoS Computational Biology 17 (2)}
+\begin{equation*} \label{eq:interval_score}
+IS_{\tau}(F, y) = (u-l) + \frac{2}{1-\tau}(l - y)1(y < l) + \frac{2}{1-\tau}(y - u)1(y > u).
+\end{equation*}
 \end{itemize}
-
 \end{frame}
@@
 \section{Results}
-\begin{frame}{Scores }
+\begin{frame}{Scores - Inflation}
 %\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
+
+\begin{columns}
+\begin{column}{0.35\textwidth}
+    \begin{itemize}
+         \item IMF-based forecasts perform relatively well 
+         \begin{itemize}
+         \item more so at long horizons\medskip
+         \end{itemize}
+         \item overprediction contributes most to scores
+    \end{itemize}
+    \vspace{2cm}
+\end{column}
+\begin{column}{0.65\textwidth}
+\vspace*{-.95cm}
     \begin{figure}
         \centering
-        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp.pdf} 
+        \includegraphics[width=0.8\textwidth]{figures_svr/svr_wis_pcpi_pch_absolute_rollingwindow.pdf} 
+        \label{fig:enter-label}
+    \end{figure} 
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Scores - GDP Growth}
+%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
+\begin{columns}
+\begin{column}{0.35\textwidth}
+    \begin{itemize}
+         \item IMF-based forecasts perform slightly better 
+         \begin{itemize}
+         \item across all horizons\medskip
+         \end{itemize}
+         \item dispersion and overprediction contribute most to scores
+    \end{itemize}
+    \vspace{2cm}
+\end{column}
+\begin{column}{0.65\textwidth}
+\vspace*{-.95cm}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\textwidth]{figures_svr/svr_wis_ngdp_rpch_absolute_rollingwindow.pdf} 
+        \label{fig:enter-label}
+    \end{figure} 
+\end{column}
+\end{columns}
+\end{frame}
+
+%\begin{frame}{Calibration - Interval Coverage Levels}
+%\textit{Here, I'll instead map the colors to the different forecast sources (currently mapped to the window method), so we'll just have one plot each}
+    %Coverage at the 50\% and 80\% central interval: \\
+
+%    \begin{figure}
+%        \centering
+%        \includegraphics[width=0.9\textwidth]{figures/coverage.pdf}
+%        %\caption{Coverage at the 50 and 80 percent level}
+%        \label{fig:enter-label}
+%    \end{figure}
+%\end{frame}
+
+\begin{frame}{Calibration - Interval Coverage Levels - Inflation}
+%\textit{Here, I'll instead map the colors to the different forecast sources (currently mapped to the window method), so we'll just have one plot each}
+    %Coverage at the 50\% and 80\% central interval: \\ 
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.98\textwidth]{figures_svr/svr_coverage_pcpi_pch_absolute_rollingwindow.pdf}
+        %\caption{Coverage at the 50 and 80 percent level}
         \label{fig:enter-label}
@@
 
-\begin{frame}{Calibration - Interval Coverage Levels}
+\begin{frame}{Calibration - Interval Coverage Levels - GDP Growth}
 %\textit{Here, I'll instead map the colors to the different forecast sources (currently mapped to the window method), so we'll just have one plot each}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/coverage.pdf}
+        \includegraphics[width=0.98\textwidth]{figures_svr/svr_coverage_ngdp_rpch_absolute_rollingwindow.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
@@
         \centering
-        \includegraphics[width=\textwidth]{figures/horizon_uncc.pdf}
+        \includegraphics[width=\textwidth]{figures/horizon_uncc_new.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
@@
 
+%\textit{relate back to article shown in the beginning, which also mentions IMF forecast of 0.1 percent $\rightarrow$ almost 50\% of any predictive intervals at this time would actually be below zero}
+
+\addtocounter{framenumber}{-1}
+\begin{frame}{Making it Public - GitHub}
+%Width of Prediction Intervals, by Horizon
+%\textit{include graphic or table showing increasing uncertainty with rising horizons}\\ 
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.5\textwidth]{figures_svr/GitHub_Capture2.jpg}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure}
+\end{frame}
+
+\addtocounter{framenumber}{-1}
+\begin{frame}{Making it Public - GitHub}
+%Width of Prediction Intervals, by Horizon
+%\textit{include graphic or table showing increasing uncertainty with rising horizons}\\ 
+\begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figures_svr/GitHub_Capture1.jpg}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure}
+
+%\textit{relate back to article shown in the beginning, which also mentions IMF forecast of 0.1 percent $\rightarrow$ almost 50\% of any predictive intervals at this time would actually be below zero}
+\end{frame}
+
 \appendix
 \beginbackup
+\begin{frame}{WIS}
+\begin{equation}
+WIS_{\tau_{0:K}}(F,y) = \frac{1}{K + 1/2}\left(w_{0}|y-m| + \sum_{k=1}^{K}\left(w_k IS_{\tau_{k}}(F, y)\right)\right), 
+\vspace*{5.5mm}
+\end{equation}
+\hspace*{3cm} with $w_k = (1-\tau)/2$
+\end{frame}
 \begin{frame}{Directional Errors - Scores}
@@
 \end{document}
+ 

### 2024-04-17 manuscript/manuscript.Rmd
update processing according to new benchmark format

@@
   .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
-  .d(,model := "bvar_qu") |>
+  .d(,model := ifelse(model == "bvar_qu", "bvar_qu", "bvar_ciss")) |>
   setnames("model", "source") |>
@@
   setnames("model", "source", skip_absent = TRUE) |>
-  .d(, source := "bvar_qu") |>
+  .d(, source := ifelse(source == "bvar_qu", "bvar_qu", "bvar_ciss")) |>
   .d(, method := "rolling window") |>

### 2024-04-17 scripts/process-benchmarks.R

@@ -33,9 +33,9 @@ truth <- data.table::fread(
 #point forecasts
 #read in data, rename target
 fcdat <- data.table::fread(
-  here("benchmarks", "raw", "forecast_long.csv")
+  here("benchmarks", "raw", "forecasts_March2024.csv")
 ) |>
-  .d(, V1 := NULL) |>
+  .d(quantile_level == 0.5) |> #only point forecast for this dataset
   .d(, target := ifelse(var == "cpi", "pcpi_pch", "ngdp_rpch")) |>
   .d(, var := NULL)
 
@@ -71,14 +71,13 @@ weodat <- fread(here("data", "weodat.csv")) |>
 ################################################################################
 #quantile forecasts
 bvar_qufcs <- data.table::fread(
-  here("benchmarks", "raw", "forecast_quantiles.csv")
+  here("benchmarks", "raw", "forecasts_March2024.csv")
   ) |>
-  .d(, V1 := NULL) |>
-  .d(method == "BVAR") |> #remove Truth and IMF forecasts
+  .d(method %in% c("bvar", "bvar_ciss")) |> #remove Truth and IMF forecasts
   .d(, target := ifelse(var == "cpi", "pcpi_pch", "ngdp_rpch")) |>
   .d(, var := NULL) |>
   setnames("method", "source") |>
-  .d(, source := "bvar_qu")
+  .d(, source := ifelse(source == "bvar", "bvar_qu", "bvar_ciss"))
 
 bvar_fc <- hordat[bvar_qufcs, on = c("target_year", "forecast_year", "season")] |>
   .d(!is.na(horizon)) |>

### 2024-04-30 benchmarks/bvar_forecast_cluster_quantiles.R
cleanup

@@ -1,139 +1,0 @@
-rm(list = ls())
-setwd("/home/fabian/Schreibtisch/notes_and_ideas/IMF/")
-
-library(dplyr)
-library(zoo)
-library(bvarsv)
-library(tidyr)
-
-# setting 
-g7_oecd <- c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")
-vnms_oecd <- c("cpi", "gdp")
-yrs_fcst <- 1989:2021
-n_draws <- 2e4
-weights <- c(1:4, 3:1)/4
-weights_mat <- matrix(weights, n_draws, 7, byrow = TRUE)
-quantile_grid = seq(from = .05, to = .95, by = .05)
-n_q <- length(quantile_grid)
-
-# data frame holding all settings to be run
-all_settings <- data.frame(country = rep(g7_oecd, each = 2), 
-                           season = rep(c("S", "F"), 7))
-
-# get iteration (job id)
-#iter <- as.integer(as.character(Sys.getenv("SLURM_ARRAY_TASK_ID")))
-iter <- 2
-
-# set random seed
-set.seed(iter)
-
-cc <- all_settings$country[iter]
-fcst_season <- all_settings$season[iter]
-
-# load cpi data, transform date
-cpi0 <- read.csv("oecd_cpi_quarterly_new.csv") 
-cpi_q <- cpi0 %>%
-  transmute(ccode, y = value, 
-            dt = as.yearqtr(date)) %>%
-  na.omit 
-gdp0 <- read.csv("oecd_gdp_quarterly_annual.csv") 
-gdp_q <- gdp0 %>% 
-  filter(ccode %in% g7_oecd, quarter %in% 1:4, type == "prv_period") %>% 
-  transmute(ccode, dt = as.yearqtr(paste0(target_year, "Q", quarter)), 
-            y = value)
-# Put both into one data frame
-oecd_q <- rbind(data.frame(cpi_q, target = "cpi"), 
-                data.frame(gdp_q, target = "gdp")) %>%
-  pivot_wider(names_from = "target", values_from = "y") %>%
-  na.omit %>% filter(dt >= 1962)
-
-# initialize data frame
-df_all <- data.frame()
-
-# loop over forecast years
-for (yy in yrs_fcst){
-  
-  # identify latest data
-  if (fcst_season == "S"){
-    last_q <- yy # up until Q1 of forecast year
-  } else {
-    last_q <- yy + .5 # up until Q3 of forecast year
-  }
-  
-  # filter data accordingly
[…]

### 2024-04-30 manuscript/oecdactuals_bvarspecs.Rmd
comparison of bvar specifications

--- 2024-04-17 manuscript/manuscript.Rmd
@@
 ---
-title: "IMF and Benchmark Forecasts"
-header-includes:
-    - \usepackage{lineno}
-    - \linenumbers
-    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-output: 
-  bookdown::pdf_document2:
-    extra_dependencies: ["float"]
-    keep_tex:  true
-    toc: false
-linestretch: 2 
-geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
-bibliography:
-  - references.bib
-csl: vancouver.csl
+title: "OECD Actuals and BVAR Specifications"
+author: "Rike"
+date: "2024-04-18"
+output: pdf_document
 ---
@@
 ```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
+```{r cars, echo =FALSE, message=FALSE}
+library(here)
 library(data.table)
-library(here)
 library(ggplot2)
+library(MetBrewer)
 library(patchwork)
-library(MetBrewer)
-library(purrr)
-library(lattice)
-library(gt)
-library(rlang)
-library(tidyverse)
+
 devtools::load_all()
-knitr::opts_chunk$set(echo = TRUE)
+
 .d <- `[`
@@
 
-# Extracting error quantiles
+### OECD actuals vs. IMF actuals
 
-Consider a forecast that stems from a source $s$ for a specific target $k$ in a country $j$, for target year $t$ and with forecast horizon $h$:
-\[
-\hat{y}_{s,k,j,t,h}
-\]
-For example, this could be a forecast stemming from the International Monetary Fund World Economic Outlook ($s = IMF$) for real GDP growth ($k = gdpg$) in Canada ($j = Canada$) for the year $2022$ ($t=2022$).
-$h$ then indexes the forecast horizon, where we code:
-\[
-h = \left\{
-\begin{array}{ll} 
-      0, & \textrm{for forecasts made in October of the same year} \\
-      0.5, & \textrm{for forecasts made in April of the same year} \\
-      1, & \textrm{for forecasts made in October of the previous year} \\
-      1.5, & \textrm{for forecasts made in April of the previous year} \\
-\end{array}\right. 
-\]
-After the target year has completed, we obtain the realized value for the quantity of interest.
-For these, the WEO updates publishes biannual updates for two years, yielding $4$ versions of the realized value.
-In accordance with previous literature (\textit{cite Timmermann 2008}), we use the version that is published in October of the following year and thereby don't index the true value by its publishing date (\textit{rephrase}).
-We thus write the true value as
-\[
-\hat{y}_{k,j,t}
-\]
-Given the forecast and the realized value for the quantity of interest, we can calculate the respective forecast error as
-\[
-e^{d}_{s,k,j,t,h} = y_{k,j,t} - \hat{y}_{s,k,j,t,h}
-\]
+```{r pressure, echo=FALSE}
+oecdbv <- fread(here("scores", "alt_scores", "oecd_bvar_ci_scores.csv"))|>
+  .d(model == "bvar_qu")|>
+  .d(,truth := "oecd") |>
+  .d(, c("model", "country", "target", "horizon", "truth", "interval_score"))
+oecdimf <- fread(here("scores", "alt_scores", "oecd_ci_scores_pava.csv"))|>
+  .d(model == "IMF")|>
+  .d(,truth := "oecd") |>
+  .d(, c("model", "country", "target", "horizon", "truth", "interval_score")) |>
+  rbind(oecdbv) |>
+  dcast(country + target + horizon + truth ~ model, value.var = "interval_score")
 
-for the "directional" error method and as 
-\[
-e^{a}_{s,k,j,t,h} = \left|y_{k,j,t} - \hat{y}_{s,k,j,t,h}\right|
-\]
-for the "absolute" error method.
+imfbv <- fread(here("scores", "alt_scores", "imf_bvar_ci_scores.csv")) |>
+  .d(model == "bvar_qu")|>
+  .d(,truth := "imf") |>
+  .d(, c("model", "country", "target", "horizon", "truth", "interval_score"))
+imfimf <- fread(here("scores", "alt_scores", "imf_ci_scores_pava.csv")) |>
+  .d(model == "IMF") |>
+  .d(,truth := "imf") |>
+  .d(, c("model", "country", "target", "horizon", "truth", "interval_score")) |>
+  rbind(imfbv) |>
+  dcast(country + target + horizon + truth ~ model, value.var = "interval_score") |>
+  rbind(oecdimf)
 
-The objective is to extract quantiles from sets of errors $\mathcal{E}_{s,k,j,t,h}$ constructed of certain years, depending on the estimation method $m$, to be able to quantify the uncertainty inherent in the forecasts via central prediction intervals of level $\alpha = \{0.5, 0.8\}$.
-For the estimation method, we consider a "rolling window" method, an "expanding window" method, and a "leave-one-out" method.
-For the rolling window method ($m = rw$), the errors of the last nine years enter into the estimation.
-For the expanding window method ($m = ew$), all previous years are considered, leaving a nine year window up front for the first estimation.
-For the leave-one-out method, all years except the current target year enter the estimation set.
-The latter is of course equivalent to the expanding window method in a real time setting and is considered in the scope of this analysis as a mere check \textit{rephrase}.
-As an example, the error set for the "directional" error method and the rolling window approach is
-\[
-\mathcal{E}^{d,rw}_{s,k,j,t,h} =  \left\{  e^{d}_{s,k,j,t^*,h} | t-9\leq t^* < t \right\}
-\]
-Insert reasoning to use the past $9$ errors.
+```
 
-To now obtain the lower $l$ and upper $u$ values for a central prediction interval of level $\alpha$, we take quantiles of these sets and add them to the current prediction:
+```{r, echo = FALSE}
+allscores <- imfimf |>
+  .d(, relwis := IMF - bvar_qu) |>
+  dcast(country + target + horizon ~ truth, value.var = "relwis") |>
+  .d(,horizon := factor(horizon, levels = c(0, 0.5, 1, 1.5), labels = 
+                         c("Fall, same year", "Spring, same year",
+                           "Fall, next year", "Spring, next year")))
 
-For the directional method:
-\[
-l^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 - \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
-\]
-\[
-u^{\alpha, d}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} + q^{0.5 + \alpha/2 } \left(\mathcal{E}^{d, m}_{t,h,v,l,j}  \right)
-\]
+ggplot(aes(x = imf, y = oecd, color = as.factor(horizon)), data = allscores) +
+  geom_point() +
+  geom_hline(aes(yintercept = 0)) +
+  geom_vline(aes(xintercept = 0)) +
+  scale_color_met_d("VanGogh2") +
+  theme_uqimf() +
+  scale_x_continuous(limits =  c(-0.55, 0.55)) +
+  scale_y_continuous(limits =  c(-0.55, 0.55)) +
+  ylab("OECD truth") +
+  xlab("IMF truth")
 
-And for the absolute method:
+```
 
-\[
- l^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} -  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
-\]
-\[
-u^{\alpha, a}_{t,h,v,l,j} = \hat{y}_{t, h, l, j} +  q^{\alpha} \left(\mathcal{E}^{m, a}_{t,h,v,l,j}  \right)
-\]
+## GDP separate
 
-Two different philosophies.
+```{r, echo = FALSE, fig.dim=c(7,4)}
+allscores <- imfimf |>
+  .d(, relwis := IMF/bvar_qu) |>
+  dcast(country + target + horizon ~ truth, value.var = "relwis") |>
+  .d(,horizon := factor(horizon, levels = c(0, 0.5, 1, 1.5), labels = 
+                         c("Fall, same year", "Spring, same year",
+                           "Fall, next year", "Spring, next year")))
 
-The absolute method will always yield symmetric central prediction intervals around the forecast value, while the directional method will in general yield asymmetric intervals.
-They thus result in different central intervals, unless the errors in $\mathcal{E}$ are perfectly symmetric around zero\footnote{Not totally correct, actually.
-For this to hold exactly, the error set would need to be augmented with one zero value.}.
-In fact, the directional method can yield central prediction intervals that do not even contain the forecast value, in cases where the $(0.5 - \alpha/2)$-quantile is positive or the $(0.5 + \alpha/2)$-quantile is negative.
+ggplot(aes(x = imf, y = oecd, color = as.factor(horizon)), data = allscores |> .d(target == "ngdp_rpch")) +
+  geom_point() +
+  geom_hline(aes(yintercept = 1)) +
+  geom_vline(aes(xintercept = 1)) +
+  scale_color_met_d("VanGogh2") +
+  theme_uqimf() +
+  scale_x_continuous(limits =  c(0, 5)) +
+  ylab("OECD truth") +
+  xlab("IMF truth")
+
+```
+
+## GDP separate
+
+```{r, echo = FALSE, fig.dim=c(7,4)}
+allscores <- imfimf |>
+  .d(, relwis := IMF/bvar_qu) |>
+  dcast(country + target + horizon ~ truth, value.var = "relwis") |>
+  .d(,horizon := factor(horizon, levels = c(0, 0.5, 1, 1.5), labels = 
+                         c("Fall, same year", "Spring, same year",
+                           "Fall, next year", "Spring, next year")))
+
+ggplot(aes(x = imf, y = oecd, color = as.factor(horizon)), data = allscores |> .d(target == "pcpi_pch")) +
+  geom_point() +
+  geom_hline(aes(yintercept = 1)) +
+  geom_vline(aes(xintercept = 1)) +
+  scale_color_met_d("VanGogh2") +
+  theme_uqimf() +
+  scale_x_continuous(limits =  c(0, 5)) +
+  ylab("OECD truth") +
+  xlab("IMF truth")
+
+```
+
+\newpage
+
+# Two BVAR specifications
 
@@
 
-# Scores, by error method, Horizon and forecast source
-
 ## Inflation
 
-```{r overall_assessment_ew, fig.dim=c(12,12), echo = FALSE, warning = FALSE}
+```{r overall_assessment_ew, fig.dim=c(12,12), echo = FALSE, warning = FALSE, fig.height=5, fig.width=9}
 
@@
 
-wis_scores <- rbind(wis_scores, bvar_wis_scores)
-scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
+wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
+    .d(source %in% c("IMF", "bvar_qu", "bvar_ciss"))
+scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)|>
+    .d(source %in% c("imf", "bvar_qu", "bvar_ciss"))
 
@@
 
-  dir_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "directional"), trgt, xmax = xmax, plot_name = "WIS - Directional Errors")
-  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt, xmax = xmax, plot_name = "WIS - Absolute Errors")
+  dir_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "directional"), trgt, xmax = xmax, plot_name = "WIS - Directional Errors", metcolor = "VanGogh2")
+  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt, xmax = xmax, plot_name = "WIS - Absolute Errors", metcolor = "VanGogh2")
 
@@
   ovr_plot <- 
-    (dir_wis_plot | abs_wis_plot) /
-    (plot_spacer()) /
-    (c50plot | c80plot) /
-    (plot_spacer()) /
-    (squeplot | aeplot | crpsplot_rw | crpsplot_loo) +
+    (abs_wis_plot) +
     plot_layout(guides = "collect", 
-                heights = c(0.2, 0.05, 0.2, 0.05, 0.2)) &
+                heights = c(0.5, 0.5)) &
       plot_annotation(tag_levels = 'I')  &
@@
 ```
-\newpage
-Some notes:
-\begin{itemize}
-\item Inflation: directional vs. absolute errors:
-\begin{itemize}
-\item difference small for IMF method, absolute slightly better, likely due to longer central intervals
-\item AR and BVAR profit more from directional correction (upward bias)
-\item for expanding window method, difference in coverage is smaller (-> structural breaks)
-
-\end{itemize}
-\item Inflation overall scores: IMF forecasts outperform others
-\begin{itemize}
-\item lower scores for point forecasts
-\item lower WIS 
-\item lower bias (compute directly?)
-\end{itemize}
-
-\item GDP Growth: more similar results for different sources
-\begin{itemize}
-\item lower scores at shorter horizons, more similar at larger horizons
-\item IMF forecasts better only for absolute error method
-\end{itemize}
-\end{itemize}
-
-\newpage
 
@@
 
-# Expanding Window - Scores, by error method, Horizon and forecast source
+## Histogram 
+Values < 1 mean that the CISS-BVAR is better
 
-## Inflation
-```{r infklovr_ew, echo = FALSE, warning = TRUE, fig.dim=c(12,12), warning = FALSE}
+```{r, echo=FALSE}
+bvar_twospec <- fread(here("scores", "bvar_ci_scores.csv")) |>
+  .d(model %in% c("bvar_qu", "bvar_ciss")) |>
+  dcast(target + horizon  + country ~ model, value.var = "interval_score") |>
+  .d(!is.na(bvar_ciss)) |> # no data for CAN, JPN 
+  .d(, relwis := bvar_ciss/bvar_qu)
 
-ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch", window_method = "expanding window")
+ggplot(aes(x = relwis), data = bvar_twospec) +
+  geom_histogram(binwidth = 0.13345, color = "steelblue4", fill = "steelblue3") +
+  theme_uqimf() +
+  xlab("Relative WIS (CISS.BVAR / Reg.BVAR)")
 ```
-
-\newpage
-
-## GDP
-
-```{r gdpovr, echo = FALSE, warning = TRUE, fig.dim=c(12,12), warning = FALSE}
-
-ovr_assessment_plot(wis_scores, scores_cvgshort, point_scores, all_scores, "ngdp_rpch", window_method = "expanding window")
-```
-
-```{r cvgdat, include=FALSE, echo = FALSE}
-
-scores <- fread(here("scores", "ci_scores.csv"))
-scores_cvgshort <- fread(here("scores", "cvg_pooled.csv"))
-
-cvg_rg <- c(50, 80)
-
-cols <- paste0("coverage_", cvg_rg)
-
-large_cvgdat <- scores |>
-  setnames("model", "source") |>
-  .d(, c("country", "horizon", "target", "error_method", "method", "source", cols), with = FALSE) |>
-  melt(id.vars = c("country", "horizon", "target", "error_method", "method", "source"),
-       variable.name = "pilvl",
-       value.name = "coverage") |>
-  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
-  .d(, pilvl := as.numeric(pilvl)/100) |>
-  .d(, idcol := paste0(horizon, country, method)) |>
-  .d(, country := NULL) |>
-  .d(, horizon := NULL)
-
-cvgdat <- scores_cvgshort |>
-  setnames("model", "source") |>
-  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
-  melt(id.vars = c("target", "error_method", "method", "source"),
-       variable.name = "pilvl",
-       value.name = "coverage") |>
-  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
-  .d(, pilvl := as.numeric(pilvl)/100)
-
-cvgdat_cpi <- cvgdat |>
-  .d(target == "pcpi_pch")
-
-cvgdat_gdp <- cvgdat |>
-  .d(target == "ngdp_rpch")
-
-#############block to merge with cvgdat symmetric
-
-cvgdat_cpin <- data.table::fread(here("scores", "cvg_pooled_directionalsymmetric.csv")) |>
-  setnames("model", "source") |>
-  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
-  melt(id.vars = c("target", "error_method", "method", "source"),
-       variable.name = "pilvl",
-       value.name = "coverage") |>
-  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
-  .d(, pilvl := as.numeric(pilvl)/100) |>
-  .d(target == "pcpi_pch") |>
-  rbind(cvgdat_cpi)
-
-cvgdat_cpi <- cvgdat_cpin
-
-cvgdat_gdpn <- data.table::fread(here("scores", "cvg_pooled_directionalsymmetric.csv")) |>
-  setnames("model", "source") |>
-  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
-  melt(id.vars = c("target", "error_method", "method", "source"),
-       variable.name = "pilvl",
-       value.name = "coverage") |>
-  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
-  .d(, pilvl := as.numeric(pilvl)/100) |>
-  .d(target == "ngdp_rpch") |>
-  rbind(cvgdat_gdp)
-
-cvgdat_gdp <- cvgdat_gdpn
-
-plot_cpi <- ggplot() +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                group = idcol),
-            data = large_cvgdat |> .d(target == "pcpi_pch"),
-            alpha = 0.4,
-            color = "gray") +
-  geom_point(aes(x = pilvl,
-                 y = coverage,
-                 color = method),
-             data = cvgdat_cpi,
-             size = 3) +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                color = method),
-            data = cvgdat_cpi,
-            lwd = 1.25) +
-  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
-               color = "black",
-               linetype = "dashed",
-               data = cvgdat_cpi) +
-  #scale_color_brewer(palette = "Set1") +
-  facet_grid(source ~ error_method)+
-
-  ggtitle("Inflation") +
-
-  scale_color_met_d("Hokusai1") +
-
-  ylab("Empirical Coverage Level (Central PI)") +
-  xlab("Nominal Coverage (Central PI)") +
-  theme_uqimf()
-
-plot_gdp <- ggplot() +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                group = idcol),
-            data = large_cvgdat |> .d(target == "ngdp_rpch"),
-            alpha = 0.4,
-            color = "gray") +
-  geom_point(aes(x = pilvl,
-                 y = coverage,
-                 color = method),
-             data = cvgdat_gdp,
-             size = 3) +
-  geom_line(aes(x = pilvl,
-                y = coverage,
-                color = method),
-            data = cvgdat_gdp,
-            lwd = 1.25) +
-  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
-               color = "black",
-               linetype = "dashed",
-               data = cvgdat_gdp) +
-  #scale_color_brewer(palette = "Set1") +
-  facet_grid(source ~ error_method)+
-
-  ggtitle("Real GDP Growth") +
-
-  scale_color_met_d("Hokusai1") +
-
-  ylab("Empirical Coverage Level (Central PI)") +
-  xlab("Nominal Coverage (Central PI)") +
-  theme_uqimf()
-
-```
-
-# Coverage, by target, methods and source
-
-```{r cvgplot, fig.dim = c(10, 12), echo = FALSE}
-
-ovr_plot <- 
-  (plot_gdp) /
-  (plot_cpi) +
-  plot_layout(guides = "collect", 
-              heights = c(1, 1)) &
-    plot_annotation(tag_levels = 'I')  &
-    theme(legend.position = 'bottom', 
-          legend.box="vertical", legend.margin=margin())
-
-ovr_plot
-
-```
-
-\newpage
-```{r, cpitable = FALSE, echo=FALSE}
-#bring into long format
-long_scores <- gather_scores(all_scores, "pcpi_pch")
-
-scores_to_table(all_scores, "pcpi_pch")
-
-```
-
-## Inflation
-
-```{r cpitileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
-
-plots_is <- vector(mode = "list", length = 4)
-plots_cr <- vector(mode = "list", length = 4)
-
-hor_list <- as.list(1:4)
-
-plots_is <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "interval"))
-plots_cr <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "crps"))
-
-ovr_plot <- 
-  (plots_is[[1]] + plots_cr[[1]]) /
-  (plots_is[[2]] + plots_cr[[2]]) /
-  (plots_is[[3]] + plots_cr[[3]]) /
-  (plots_is[[4]] + plots_cr[[4]]) +
-  plot_layout(heights = c(1, 1,1,1)) &
-    plot_annotation(tag_levels = 'I')  &
-    theme(legend.position = 'right', 
-          legend.box="vertical", legend.margin=margin())
-
-ovr_plot
-
-```
-
-## GDP
-
-```{r gdptable, echo = FALSE}
-
-long_scores <- gather_scores(all_scores, "ngdp_rpch")
-scores_to_table(all_scores, "ngdp_rpch")
-
-```
-
-```{r gdptileplot, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}
-
-plots_is <- vector(mode = "list", length = 4)
-plots_cr <- vector(mode = "list", length = 4)
-
-hor_list <- as.list(1:4)
-
-plots_is <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "interval"))
-plots_cr <- lapply(hor_list, function(i) tile_plot(long_scores, hor = (i-1)*0.5, "crps"))
-
-ovr_plot <- 
-  (plots_is[[1]] + plots_cr[[1]]) /
-  (plots_is[[2]] + plots_cr[[2]]) /
-  (plots_is[[3]] + plots_cr[[3]]) /
-  (plots_is[[4]] + plots_cr[[4]]) +
-  plot_layout(heights = c(1, 1,1,1)) &
-    plot_annotation(tag_levels = 'I')  &
-    theme(legend.position = 'right', 
-          legend.box="vertical", legend.margin=margin())
-
-ovr_plot
-
-```

### 2024-04-30 manuscript-plots/coverage_plots.R
cleanup

@@ -1,0 +1,105 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+library(MetBrewer)
+library(tidyverse)
+devtools::load_all()
+.d <- `[`
+
+
+chosen_method <- "rolling window"
+chosen_em <- "absolute"
+chosen_target <- "ngdp_rpch"
+prefix <- "ho_"
+
+
+#when using absolute errors, read in scores of pava corrected forecasts
+if(chosen_em == "absolute"){
+  pasteon_filename <- "_pava"
+} else {
+  pasteon_filename <- ""
+}
+
+
+####Read and filter coverage data
+#Scores by average country
+scores_cvgshort <- fread(here("scores", paste0("ci_scores_avgcnt", pasteon_filename, ".csv"))) |>
+  setnames("model", "source", skip_absent = TRUE)
+
+bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE) |>
+  .d(, source := "bvar_qu") |>
+  .d(, method := chosen_method) |>
+  .d(, error_method := chosen_em)
+
+scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)
+
+
+
+scores_cvgaggregate <- fread(here("scores", paste0("cvg_pooled", pasteon_filename, ".csv"))) |>
+  rbind(fread(here("scores", "bvar_cvg_pooled.csv")) |>
+          .d(, error_method := chosen_em) |>
+          .d(, method := chosen_method)) |>
+  .d(error_method == chosen_em) |>
+  .d(method == chosen_method)
+
+
+#non aggregated
+scores <- fread(here("scores", paste0("ci_scores", pasteon_filename, ".csv"))) |>
+  .d(error_method == chosen_em) |>
+  .d(method == chosen_method)
+
+#############################################################################
+plot_marg <- 5
+
+cvgplot <- coverage_plot_aggregate(scores_cvgaggregate,
+                         scores,
+                         cvg_rg = c(50,80),
+                         chosen_target,
+                         textsize_y = 17,
+                         plot_title = "",
+                         metcolor = "Hokusai3")+
+  theme(plot.margin = margin(t=0,b=0,r=plot_marg,l=plot_marg, unit = "pt"))
+
+
+
+
+
[…]

### 2024-04-30 manuscript-plots/wis_plots.R

@@ -1,0 +1,66 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+library(MetBrewer)
+devtools::load_all()
+.d <- `[`
+
+
+chosen_method <- "rolling window"
+chosen_em <- "absolute"
+chosen_target <- "pcpi_pch"
+prefix <- "ho_"
+
+
+#when using absolute errors, read in scores of pava corrected forecasts
+if(chosen_em == "absolute"){
+  pasteon_filename <- "_pava"
+} else {
+  pasteon_filename <- ""
+}
+
+
+######## WIS Data
+scores <- fread(here("scores", "ci_scores_pava.csv"))
+
+
+wis_scores <- fread(here("scores", paste0("ci_scores_avgcnt", pasteon_filename, ".csv"))) |>
+  data.table::copy() |>
+  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  setnames("model", "source")
+
+
+bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  .d(model == "bvar_qu") |>
+  setnames("model", "source") |>
+  .d(,error_method := chosen_em) |>
+  .d(,method := chosen_method) #change later
+
+
+wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
+  .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
+                        label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
+  .d(method == chosen_method) |>
+  .d(error_method == chosen_em)
+
+
+wis_plot <- wis_plot_new(wis_scores, chosen_target, plot_name = "", textsize_y = 17, metcolor = "Hokusai3") +
+  theme(axis.text.x = element_blank(),
+        #axis.text.x = element_text(size = textsize_y, angle = 90, hjust = .5, vjust = .5, face = "plain"),
+        #strip.text = element_text(size = 8),
+        axis.text.y = element_text(size = 24),
+        axis.title.y = element_text(size = 24),
+        strip.text = element_text(size=24),
+        legend.text=element_text(size=24),
+        text = element_text(family = "serif"),
[…]

### 2024-05-08 manuscript/compare_oecd_imf.Rmd
comparison of scores - oecd and imf actuals

--- 2024-04-30 manuscript/oecdactuals_bvarspecs.Rmd
@@
 ---
-title: "OECD Actuals and BVAR Specifications"
+title: "OECDactuals"
 author: "Rike"
-date: "2024-04-18"
-output: pdf_document
+date: "2024-04-17"
+output: html_document
 ---
@@
 
-```{r cars, echo =FALSE, message=FALSE}
+```{r cars, echo =FALSE}
 library(here)
@@
 
-### OECD actuals vs. IMF actuals
+##
 
@@
 allscores <- imfimf |>
-  .d(, relwis := IMF - bvar_qu) |>
+  .d(, relwis := IMF/bvar_qu) |>
   dcast(country + target + horizon ~ truth, value.var = "relwis") |>
@@
 ggplot(aes(x = imf, y = oecd, color = as.factor(horizon)), data = allscores) +
-  geom_point() +
-  geom_hline(aes(yintercept = 0)) +
-  geom_vline(aes(xintercept = 0)) +
-  scale_color_met_d("VanGogh2") +
-  theme_uqimf() +
-  scale_x_continuous(limits =  c(-0.55, 0.55)) +
-  scale_y_continuous(limits =  c(-0.55, 0.55)) +
-  ylab("OECD truth") +
-  xlab("IMF truth")
-
-```
-
-## GDP separate
-
-```{r, echo = FALSE, fig.dim=c(7,4)}
-allscores <- imfimf |>
-  .d(, relwis := IMF/bvar_qu) |>
-  dcast(country + target + horizon ~ truth, value.var = "relwis") |>
-  .d(,horizon := factor(horizon, levels = c(0, 0.5, 1, 1.5), labels = 
-                         c("Fall, same year", "Spring, same year",
-                           "Fall, next year", "Spring, next year")))
-
-ggplot(aes(x = imf, y = oecd, color = as.factor(horizon)), data = allscores |> .d(target == "ngdp_rpch")) +
-  geom_point() +
-  geom_hline(aes(yintercept = 1)) +
-  geom_vline(aes(xintercept = 1)) +
-  scale_color_met_d("VanGogh2") +
-  theme_uqimf() +
-  scale_x_continuous(limits =  c(0, 5)) +
-  ylab("OECD truth") +
-  xlab("IMF truth")
-
-```
-
-## GDP separate
-
-```{r, echo = FALSE, fig.dim=c(7,4)}
-allscores <- imfimf |>
-  .d(, relwis := IMF/bvar_qu) |>
-  dcast(country + target + horizon ~ truth, value.var = "relwis") |>
-  .d(,horizon := factor(horizon, levels = c(0, 0.5, 1, 1.5), labels = 
-                         c("Fall, same year", "Spring, same year",
-                           "Fall, next year", "Spring, next year")))
-
-ggplot(aes(x = imf, y = oecd, color = as.factor(horizon)), data = allscores |> .d(target == "pcpi_pch")) +
   geom_point() +
@@
 
-```{r overall_assessment_ew, fig.dim=c(12,12), echo = FALSE, warning = FALSE, fig.height=5, fig.width=9}
+```{r overall_assessment_ew, fig.dim=c(12,12), echo = FALSE, warning = FALSE}
 
@@
   dir_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "directional"), trgt, xmax = xmax, plot_name = "WIS - Directional Errors", metcolor = "VanGogh2")
-  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt, xmax = xmax, plot_name = "WIS - Absolute Errors", metcolor = "VanGogh2")
+  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt, xmax = xmax, plot_name = "WIS - Absolute Errors")
 
@@
     plot_layout(guides = "collect", 
-                heights = c(0.5, 0.5)) &
+                heights = c(0.2, 0.05, 0.2, 0.05, 0.2)) &
       plot_annotation(tag_levels = 'I')  &
@@
 ```
-
 ## GDP
@@
 ## Histogram
-Values < 1 mean that the CISS-BVAR is better
 
-```{r, echo=FALSE}
+```{r}
 bvar_twospec <- fread(here("scores", "bvar_ci_scores.csv")) |>
@@
   theme_uqimf() +
-  xlab("Relative WIS (CISS.BVAR / Reg.BVAR)")
+  xlab("Relative WIS (Reg.BVAR/CISS.BVAR)")
 ```

### 2024-05-08 presentation/make_figures/plot_ci_lengths.R
old plotting files

@@ -105,7 +105,7 @@ ggplot(aes(group = target), data = imf_fc) +
 }
 
 
-pdf(file = here("presentation", "figures", "horizon_uncc.pdf"), width = 5, height = 3.35)
+pdf(file = here("presentation", "figures", "horizon_uncc_new.pdf"), width = 5, height = 3.35)
 ggplot(aes(x = target_year, group = target, color = target), data = imf_fc) +
   geom_linerange(
     aes(x = target_year,
@@ -126,7 +126,7 @@ ggplot(aes(x = target_year, group = target, color = target), data = imf_fc) +
     lwd = 3
   ) +
   xlab("") +
-  scale_color_met_d("Hokusai1") +
+  scale_color_met_d("Hokusai2") +
   #geom_hline(aes(yintercept = 0), linetype = "dashed") +
   theme_uqimf() %+replace%
   theme(

### 2024-05-08 presentation/make_plots.R

@@ -1,0 +1,244 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+library(MetBrewer)
+library(purrr)
+library(lattice)
+library(gt)
+library(rlang)
+library(tidyverse)
+devtools::load_all()
+.d <- `[`
+
+
+chosen_method <- "rolling window"
+chosen_em <- "absolute"
+
+######## WIS Data
+scores <- fread(here("scores", "ci_scores_pava.csv"))
+
+wis_scores <- fread(here("scores", "ci_scores_avgcnt_pava.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  setnames("model", "source")
+
+bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  data.table::copy() |>
+  .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+  .d(,model := "bvar_qu") |>
+  setnames("model", "source") |>
+  .d(,error_method := chosen_em) |>
+  .d(,method := chosen_method) #change later
+
+
+#bvar_wis_scores <- rbind(bvar_wis_scores, bvar_wis_scores)# |> copy() |> .d(, error_method := chosen_em))
+
+wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
+  .d(, source := factor(source, levels = c("IMF", "bvar", "bvar_qu", "ar"),
+                     label = c("IMF", "BVAR", "BVAR - direct", "AR"))) |>
+  .d(method == chosen_method) |>
+  .d(error_method == chosen_em)
+
+
+####Coverage Data
+scores_cvgshort <- fread(here("scores", "ci_scores_avgcnt_pava.csv")) |>
+  setnames("model", "source", skip_absent = TRUE)
+
+
+bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
+  setnames("model", "source", skip_absent = TRUE) |>
+  .d(, source := "bvar_qu") |>
+  .d(, method := chosen_method) |>
+  .d(, error_method := chosen_em)
+
+
+bvar_scores_cvgshort <- rbind(bvar_scores_cvgshort, bvar_scores_cvgshort |> copy() |> .d(, error_method := "directional"))
+
+
[…]

### 2024-08-28 manuscript/manuscript.tex
old documentation (pre major manuscript)

@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.114 & 0.124 & 0.122 \\ 
-expanding window\_sample\_crps & 0.087 & 0.093 & 0.092 \\ 
-leave-one-out\_interval\_score & 0.110 & 0.122 & 0.121 \\ 
-leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
-rolling window\_interval\_score & 0.117 & 0.126 & 0.124 \\ 
-rolling window\_sample\_crps & 0.090 & 0.093 & 0.092 \\ 
+expanding window\_interval\_score & 0.142 & 0.088 & 0.078 \\ 
+expanding window\_sample\_crps & 0.105 & 0.068 & 0.059 \\ 
+leave-one-out\_interval\_score & 0.136 & 0.084 & 0.076 \\ 
+leave-one-out\_sample\_crps & 0.107 & 0.049 & 0.046 \\ 
+rolling window\_interval\_score & 0.141 & 0.087 & 0.078 \\ 
+rolling window\_sample\_crps & 0.105 & 0.068 & 0.060 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.255 & 0.280 & 0.305 \\ 
-expanding window\_sample\_crps & 0.179 & 0.205 & 0.235 \\ 
-leave-one-out\_interval\_score & 0.254 & 0.267 & 0.289 \\ 
-leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
-rolling window\_interval\_score & 0.256 & 0.272 & 0.292 \\ 
-rolling window\_sample\_crps & 0.184 & 0.196 & 0.223 \\ 
+expanding window\_interval\_score & 0.228 & 0.275 & 0.274 \\ 
+expanding window\_sample\_crps & 0.164 & 0.190 & 0.210 \\ 
+leave-one-out\_interval\_score & 0.228 & 0.268 & 0.263 \\ 
+leave-one-out\_sample\_crps & 0.161 & 0.192 & 0.206 \\ 
+rolling window\_interval\_score & 0.226 & 0.269 & 0.267 \\ 
+rolling window\_sample\_crps & 0.166 & 0.183 & 0.204 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.464 & 0.764 & 0.607 \\ 
-expanding window\_sample\_crps & 0.344 & 0.547 & 0.448 \\ 
-leave-one-out\_interval\_score & 0.456 & 0.776 & 0.600 \\ 
-leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
-rolling window\_interval\_score & 0.471 & 0.768 & 0.611 \\ 
-rolling window\_sample\_crps & 0.347 & 0.550 & 0.452 \\ 
+expanding window\_interval\_score & 0.420 & 0.757 & 0.595 \\ 
+expanding window\_sample\_crps & 0.300 & 0.530 & 0.448 \\ 
+leave-one-out\_interval\_score & 0.412 & 0.768 & 0.591 \\ 
+leave-one-out\_sample\_crps & 0.272 & 0.440 & 0.388 \\ 
+rolling window\_interval\_score & 0.420 & 0.765 & 0.600 \\ 
+rolling window\_sample\_crps & 0.301 & 0.542 & 0.456 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.517 & 1.043 & 0.807 \\ 
-expanding window\_sample\_crps & 0.367 & 0.635 & 0.612 \\ 
-leave-one-out\_interval\_score & 0.507 & 1.023 & 0.755 \\ 
-leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
-rolling window\_interval\_score & 0.521 & 1.042 & 0.787 \\ 
-rolling window\_sample\_crps & 0.361 & 0.623 & 0.576 \\ 
+expanding window\_interval\_score & 0.465 & 1.037 & 0.819 \\ 
+expanding window\_sample\_crps & 0.323 & 0.603 & 0.613 \\ 
+leave-one-out\_interval\_score & 0.456 & 1.013 & 0.765 \\ 
+leave-one-out\_sample\_crps & 0.312 & 0.567 & 0.566 \\ 
+rolling window\_interval\_score & 0.463 & 1.039 & 0.799 \\ 
+rolling window\_sample\_crps & 0.319 & 0.604 & 0.582 \\ 
 \bottomrule
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.229 & 0.295 & 0.291 \\ 
-expanding window\_sample\_crps & 0.168 & 0.200 & 0.195 \\ 
-leave-one-out\_interval\_score & 0.222 & 0.292 & 0.291 \\ 
-leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
-rolling window\_interval\_score & 0.232 & 0.292 & 0.287 \\ 
-rolling window\_sample\_crps & 0.169 & 0.197 & 0.190 \\ 
+expanding window\_interval\_score & 0.365 & 0.110 & 0.099 \\ 
+expanding window\_sample\_crps & 0.254 & 0.083 & 0.076 \\ 
+leave-one-out\_interval\_score & 0.356 & 0.112 & 0.099 \\ 
+leave-one-out\_sample\_crps & 0.269 & 0.077 & 0.068 \\ 
+rolling window\_interval\_score & 0.368 & 0.112 & 0.100 \\ 
+rolling window\_sample\_crps & 0.267 & 0.086 & 0.079 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.408 & 0.558 & 0.510 \\ 
-expanding window\_sample\_crps & 0.289 & 0.390 & 0.370 \\ 
-leave-one-out\_interval\_score & 0.396 & 0.550 & 0.500 \\ 
-leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
-rolling window\_interval\_score & 0.411 & 0.565 & 0.519 \\ 
-rolling window\_sample\_crps & 0.290 & 0.402 & 0.374 \\ 
+expanding window\_interval\_score & 0.446 & 0.506 & 0.455 \\ 
+expanding window\_sample\_crps & 0.324 & 0.369 & 0.329 \\ 
+leave-one-out\_interval\_score & 0.435 & 0.512 & 0.451 \\ 
+leave-one-out\_sample\_crps & 0.331 & 0.348 & 0.314 \\ 
+rolling window\_interval\_score & 0.448 & 0.519 & 0.464 \\ 
+rolling window\_sample\_crps & 0.331 & 0.379 & 0.338 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 0.878 & 1.176 & 1.018 \\ 
-expanding window\_sample\_crps & 0.664 & 0.861 & 0.801 \\ 
-leave-one-out\_interval\_score & 0.866 & 1.159 & 1.005 \\ 
-leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
-rolling window\_interval\_score & 0.901 & 1.201 & 1.044 \\ 
-rolling window\_sample\_crps & 0.682 & 0.901 & 0.841 \\ 
+expanding window\_interval\_score & 0.922 & 1.198 & 1.070 \\ 
+expanding window\_sample\_crps & 0.709 & 0.882 & 0.828 \\ 
+leave-one-out\_interval\_score & 0.902 & 1.187 & 1.051 \\ 
+leave-one-out\_sample\_crps & 0.627 & 0.732 & 0.703 \\ 
+rolling window\_interval\_score & 0.922 & 1.208 & 1.082 \\ 
+rolling window\_sample\_crps & 0.720 & 0.906 & 0.854 \\ 
 \midrule\addlinespace[2.5pt]
@@
 \midrule\addlinespace[2.5pt]
-expanding window\_interval\_score & 1.126 & 1.387 & 1.198 \\ 
-expanding window\_sample\_crps & 0.841 & 0.977 & 0.956 \\ 
-leave-one-out\_interval\_score & 1.097 & 1.381 & 1.195 \\ 
-leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
-rolling window\_interval\_score & 1.139 & 1.411 & 1.235 \\ 
-rolling window\_sample\_crps & 0.864 & 1.022 & 1.005 \\ 
+expanding window\_interval\_score & 1.163 & 1.424 & 1.271 \\ 
+expanding window\_sample\_crps & 0.894 & 0.998 & 0.985 \\ 
+leave-one-out\_interval\_score & 1.135 & 1.400 & 1.227 \\ 
+leave-one-out\_sample\_crps & 0.765 & 0.855 & 0.838 \\ 
+rolling window\_interval\_score & 1.170 & 1.431 & 1.270 \\ 
+rolling window\_sample\_crps & 0.900 & 1.028 & 1.008 \\ 
 \bottomrule

### 2024-08-28 manuscript/oecdactuals_bvarspecs.Rmd
old documentation (pre major manuscript)

@@
 scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort)|>
-    .d(source %in% c("imf", "bvar_qu", "bvar_ciss"))
+    .d(source %in% c("imf", "bvar_qu", "bvar_ciss")) |>
+  setnames("source", "model")
 
@@
 
-  dir_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "directional"), trgt, xmax = xmax, plot_name = "WIS - Directional Errors", metcolor = "VanGogh2")
-  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt, xmax = xmax, plot_name = "WIS - Absolute Errors", metcolor = "VanGogh2")
+  abs_wis_plot <- wis_plot_new(decomp_data |> .d(error_method  == "absolute"), trgt = trgt, xmax = xmax, plot_name = "WIS - Absolute Errors", metcolor = "VanGogh2")
 
@@
 
-  aeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meanae", "Absolute Error", title = "Point Forecast - Abs. Error")
-
-  squeplot <- horizon_path_plot(point_scores |> .d(, error_method := "directional"), "meansque", "Squared Error", title = "Point Forecast - Squ. Error")
-
-  crpsplot_rw <- horizon_path_plot(crps_scores_rw |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = paste0("CRPS - ", window_method)) +
-    scale_y_continuous(limits = c(0.07,1.05))
-
-  crpsplot_loo <- horizon_path_plot(crps_scores_loo |>.d(, error_method := "directional"), "score", "CRPS by Sample", title = "CRPS - LOO") +
-    scale_y_continuous(limits = c(0.07,1.05))
-
   ovr_plot <- 
-    (abs_wis_plot) +
+    #(abs_wis_plot) +
+    (c50plot / c80plot) +
     plot_layout(guides = "collect", 

### 2024-08-28 scores/R_value_scores/plot-scores-alt-R-values.R
change AIS to IS in y-axis

@@ -30,7 +30,7 @@ for(m in 1:nrow(all_plotcombs)){
 
 
   filenames <- c("wis", "c80", "c50")
-  ylabs <- c("Average Interval Score", "80% Interval Coverage", "50% Interval Coverage")
+  ylabs <- c("Interval Score", "80% Interval Coverage", "50% Interval Coverage")
 
   names(filenames) <- c("interval_score", "coverage_80", "coverage_50")
   names(ylabs) <- c("interval_score", "coverage_80", "coverage_50")

### 2024-08-28 miscellaneous/presentation/presentation.tex
restucture I (move non-main files to misc folder)

--- 2023-12-12 presentation/presentation.tex
@@
 \usepackage{hyperref}
+\usepackage{subcaption}
+\usepackage{multirow}
 \hypersetup{
@@
     filecolor=magenta,      
-    urlcolor=cyan,
+    urlcolor=black,
     pdftitle={Overleaf Example},
@@
 %% Gruppenlogo
-\grouplogo{logo_empty.jpg}
+\grouplogo{KIT_STAT_Logo_rgb.png}
 
@@
 
-\date[05.\,12.\,2023]{December 5, 2023}
+\date[30.\,07.\,2024]{July 30, 2024}
 
@@
 		\end{itemize}
-    \item publicly available\footnote{International Monetary Fund. 2023. \textit{World Economic Outlook: Navigating Global Divergences.} Washington, DC. October.} in an accessible format
-    \item targets: real GDP growth and CPI inflation 
-    \item time range: available since 1990, giving $\sim$30 years of forecast-truth pairs %per country and forecast horizon
+    \item publicly available\footnote{International Monetary Fund.
+2024.
+\textit{World Economic Outlook Database}, available at \url{https://www.imf.org/en/Publications/WEO/weo-database/2024/April}} in an accessible format
+    \item targets: real GDP growth, CPI inflation, current account balance
+    \item time range: available since 1990, giving $>$30 years of forecast-truth pairs %per country and forecast horizon
     \item target locations: forecasts are issued for 196 countries in total
@@
     \end{itemize}
-    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-R \leq t^* < t \}$, containing the last $R$ forecast errors
+    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}^{abs}_{t^*, h}  | t-R \leq t^* < t \}$, containing the last $R=11$ forecast errors
     \begin{itemize}
-        \item based on \textit{absolute} errors $\hat{e}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
-        \item currently: $R=9$
+        \item based on \textit{absolute} errors $\hat{e}^{abs}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
         %\item sets are stratified by country, target and horizon
     \end{itemize}
-    \item for $\alpha \in \{0.5, 0.8\}$, compute $q^{\alpha}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \alpha \right)$
+    \item for $\tau \in \{0.5, 0.8\}$, compute $q^{\tau}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \tau \right)$
+    \begin{itemize}
+        \item with $R=11$, quantiles can be taken directly from the order statistics
+    \end{itemize}
     \item and compute the upper and lower endpoints of a central prediction interval as 
     \begin{itemize}
-        \item $u^{\alpha}_{t,h} = \hat{y}_{t, h} + q^{\alpha}_{t, h}$ 
-        \item $l^{\alpha}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\alpha}_{t, h}$
+        \item $u^{\tau}_{t,h} = \hat{y}_{t, h} + q^{\tau}_{t, h}$ 
+        \item $l^{\tau}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\tau}_{t, h}$
     \end{itemize}
-    \item use PAVA-type reordering if intervals shrink with increasing horizon
-    \item assess central interval coverage, score via the weighted interval score (WIS)\footnote{Bracher, J. et al. 2021. \textit{Evaluating
-Epidemic Forecasts in an Interval Format.} PLoS Computational Biology 17 (2)}
+    \item assess central interval coverage, score via the interval score%\footnote{Bracher, J. et al. 2021. \textit{Evaluating
+%Epidemic Forecasts in an Interval Format.} PLoS Computational Biology 17 (2)}
 \end{itemize}
+\end{frame}
 
+\begin{frame}{Methods - Visualized}
+\begin{figure}
+        \centering
+        \includegraphics[width=0.65\textwidth]{figures/illustration_quantileextraction.pdf} 
+        \label{fig:enter-label}
+    \end{figure} 
 \end{frame}
@@
     \begin{itemize}
-        \item autoregressive (AR) model
-        \item Primiceri Bayesian vector autoregressive (BVAR) model\footnote{Primiceri, G.
+        \item autoregressive model ("AR")
+        \item Primiceri Bayesian vector autoregressive model\footnote{Primiceri, G.
 2005.
-\textit{Time Varying Structural Vector Autoregressions and Monetary Policy.} Review of Economic Studies 72.}
+\textit{Time Varying Structural Vector Autoregressions and Monetary Policy.} Review of Economic Studies 72.} ("BVAR")
     \end{itemize}
@@
     \begin{itemize}
-        \item obtained from the BVAR model
+        \item obtained from the BVAR model ("BVAR - direct")
     \end{itemize}
@@
 \begin{itemize}
-    \item trained on quarterly data, with slight informational advantage
+    \item trained on quarterly data
 \end{itemize}
@@
 \section{Results}
-\begin{frame}{Scores }
+\begin{frame}{Scores on holdout data 2013-2023 - Inflation}
 %\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
@@
         \centering
-        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp_new.pdf} 
+        \includegraphics[width=0.45\textwidth]{figures/ho_wis_pcpi_pch_absolute_rollingwindow.pdf} 
         \label{fig:enter-label}
@@
 
-\begin{frame}{Calibration - Interval Coverage Levels}
+\begin{frame}{Scores on holdout data 2013-2023 - GDP Growth}
+%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.45\textwidth]{figures/ho_wis_ngdp_rpch_absolute_rollingwindow.pdf} 
+        \label{fig:enter-label}
+    \end{figure} 
+\end{frame}
+
+\begin{frame}{Calibration - on holdout data 2013-2023}
 %\textit{Here, I'll instead map the colors to the different forecast sources (currently mapped to the window method), so we'll just have one plot each}
@@
 \begin{figure}
+  \begin{subfigure}{0.385\textwidth}
   \centering
-        \includegraphics[width=0.9\textwidth]{figures/coverage.pdf}
-        %\caption{Coverage at the 50 and 80 percent level}
-        \label{fig:enter-label}
+    \includegraphics[width=\textwidth]{figures/ho_coverage_pcpi_pch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+  \end{subfigure}
+  \hspace*{12mm}
+  %\hfill  % maximize separation between the subfigures
+  \begin{subfigure}{0.385\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/ho_coverage_ngdp_rpch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+  \end{subfigure}%
 \end{figure}
+
 \end{frame}
@@
         \centering
-        \includegraphics[width=\textwidth]{figures/horizon_uncc.pdf}
+        \includegraphics[width=\textwidth]{figures/cilength_byhorizon.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
@@
 Fall,  SY & 0.5 & 1.1\\ 
-Spring, SY &1.2 &2.1 \\ 
-Fall, NY & 1.9 & 3.5\\ 
-Spring, NY &2.2 &4.0 \\[0.3em] 
+Spring, SY &1.0 &2.1 \\ 
+Fall, NY & 1.7 & 3.3\\ 
+Spring, NY &2.1 &4.0 \\[0.3em] 
 \multicolumn{3}{c}{\textbf{Inflation}}\\
@@
 Fall,  SY & 0.3 & 0.5\\ 
-Spring, SY &0.6 &1.1 \\ 
-Fall, NY & 1.1 & 1.8\\ 
-Spring, NY &1.3 &2.1 \\ 
+Spring, SY &0.6 &1.2 \\ 
+Fall, NY & 1.2 & 2.0\\ 
+Spring, NY &1.4 &2.2 \\ 
 \end{tabular}
@@
     \end{itemize}
-    \item potential dependency of results on quantile extraction \\
+
+    \item alternative truth values from the OECD
     \begin{itemize}
-        \item ordering between forecasts remains the same with sample-based CRPS \hyperlink{samplecrps}{\beamerbutton{link}}
+    \item influences evaluation results at the shortest horizon \hyperlink{alternativetruth}{\beamerbutton{link}}
+    \end{itemize}
+    \item alternative BVAR specification
+    \begin{itemize}
+    \item similar scores and calibration \hyperlink{alternativebvar}{\beamerbutton{link}}
     \end{itemize}
@@
         \item cheap
+        \item transparent
         \item competitive
-        \item transparent
     \end{itemize}
-\item Uncertainty around point forecasts is often substantial, making its communication necessary
-\item IMF forecasts are valuable source for distributional forecasts in their own right \bigskip \\
-\item     Outlook
+\item IMF forecasts are valuable source for distributional forecasts 
+\item Uncertainty around point forecasts is often substantial, making its communication necessary\bigskip \\
+\item Potential Extensions / Outlook
     \begin{itemize}
-        \item scale to more countries and forecast sources
-        \item implement alternative method that  utilizes the cross-section dimension%, e.g. via Hierarchical Bayesian Modeling
-        \item make forecasts easily and publicly accessable via shiny app
+        \item scale to more countries
+        %\item implement alternative method that  utilizes the cross-section dimension%, e.g. via Hierarchical Bayesian Modeling
+        \item make forecasts easily and publicly accessible via shiny app
+        \item preregistration of real-time forecasts
     \end{itemize}
@@
         %\centering
-        \includegraphics[width=0.55\textwidth]{figures/shinycap_newhost.jpg}
+        \includegraphics[width=0.55\textwidth]{figures/shinycap_final.jpg}
         %\caption{Coverage at the 50 and 80 percent level}
@@
 \end{columns}
+
+\end{frame}
+
+\begin{frame}{Making it public - Timestamped Forecast Publication I}
+
+    \begin{figure}
+        %\centering
+        \includegraphics[width=0.65\textwidth]{figures/Capture_GitHub.jpg}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure}
+
+\end{frame}
+
+\begin{frame}{Making it public - Timestamped Forecast Publication II}
+
+    \begin{figure}
+        %\centering
+        \includegraphics[width=0.65\textwidth]{figures/Capture_GitHubforecasts.jpg}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure}
+
+\end{frame}
+
+\begin{frame}{Making it public - Visualization}
+
+    \begin{figure}
+        %\centering
+        \includegraphics[width=0.85\textwidth]{figures/shinycap_enlarged.jpg}
+        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
+    \end{figure}
 
@@
 \beginbackup
-\begin{frame}{Directional Errors - Scores}
+\begin{frame}{Directional Errors - Scores on years 2001-2012}
 \label{errorextraction}
-\begin{figure}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_directional.pdf}
-       %\caption{Coverage at the 50 and 80 percent level}
-    \end{figure}
-\end{frame}
-\begin{frame}{Directional Errors - Coverage}
-\begin{figure}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/coverage_directional.pdf}
-        %\caption{Coverage at the 50 and 80 percent level}
-    \end{figure}
+\begin{table}
+\begin{center}
+\begin{tabular}{lccccccc}
+ & & \multicolumn{2}{c}{Interval Score} & \multicolumn{2}{c}{50\% Cvg.} & \multicolumn{2}{c}{80\% Cvg.} \\[0.2em]
+ & Horizon & absolute & directional & absolute & directional & absolute & directional\\[0.5em]
+\multirow{4}{*}{\rotatebox[origin=c]{90}{GDP Growth}} & Fall, Current & \textbf{0.23} & 0.24 & \textbf{0.49} & 0.43 & \textbf{0.76} & 0.65\\
+ & Spring, Current & 0.41 & \textbf{0.41} & 0.56 & \textbf{0.54} & \textbf{0.76} & 0.67\\
+ & Fall, Next & 0.91 & \textbf{0.88} & \textbf{0.49} & 0.42 & \textbf{0.73} & 0.70\\
+ & Spring, Next & \textbf{1.14} & 1.15 & \textbf{0.50} & 0.40 & \textbf{0.64} & 0.55\\[1em]
+\multirow{4}{*}{\rotatebox[origin=c]{90}{Inflation}} & Fall, Current & \textbf{0.12} & 0.12 & \textbf{0.52} & 0.44 & \textbf{0.76} & 0.64\\
+ & Spring, Current & 0.26 & \textbf{0.25} & \textbf{0.43} & 0.39 & \textbf{0.75} & 0.65\\
+& Fall, Next & \textbf{0.47} & 0.50 & \textbf{0.40} & 0.31 & \textbf{0.67} & 0.54\\
+ & Spring, Next & \textbf{0.52} & 0.55 & \textbf{0.42} & 0.38 & \textbf{0.67} & 0.54\\
+
+\end{tabular}
+\end{center}
+\end{table}
 \end{frame}
@@
 \label{extractionmethod}
+\end{frame}
+
+\begin{frame}{Alternative truth value - Scores}
+\label{alternativetruth}
     \begin{figure}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_ew.pdf}
+        %\centering
+        \includegraphics[width=0.55\textwidth]{figures/oecdvsimf.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
-    \end{figure}
-\end{frame}
-\begin{frame}{Expanding Window - Coverage}
-\begin{figure}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/coverage_ew.pdf}
-        %\caption{Coverage at the 50 and 80 percent level}
+        \label{fig:enter-label}
     \end{figure}   
@@
 
-\begin{frame}{CRPS by sample}
-\label{samplecrps}
+\begin{frame}{Alternative BVAR specification - Scores}
+\label{alternativebvar}
 \begin{figure}
+  \begin{subfigure}{0.45\textwidth}
   \centering
-        \includegraphics[width=0.7\textwidth]{figures/crpssample.png}
-        %\caption{Coverage at the 50 and 80 percent level}
+    \includegraphics[width=\textwidth]{figures/ho_bvarspecs_wis_pcpi_pch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+    \caption{Inflation}
+  \end{subfigure}
+  \hspace*{8mm}
+  %\hfill  % maximize separation between the subfigures
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/ho_bvarspecs_wis_ngdp_rpch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+    \caption{GDP Growth}
+  \end{subfigure}%
 \end{figure}

### 2024-08-28 miscellaneous/simulations/sim_cilength.Rmd
restucture I (move non-main files to misc folder)

---
title: "CI lengths simulation"
author: "Rike"
date: "2023-11-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(here)
library(ggplot2)
library(MetBrewer)
.d <- `[`
devtools::load_all()
set.seed(42)
```

```{r simfunction, echo = FALSE}
qumeth <- c(1, 7, 8)

simcilength <- function(n, nits, lvl = 0.8, qumeth = c(1,7,8)){
  res <- vector(mode = "list", length = nits)
  res_cmp <- vector(mode = "list", length = nits)

  if(lvl == 0.8){
    upper <- 0.9
    lower <- 0.1
  } else if (lvl == 0.5){
    upper <- 0.75
    lower <- 0.25
  }

  for(i in 1:nits){

    resvec <- rep(NA, 2*length(qumeth))
    names(resvec) <- apply(expand.grid(c("absolute", "directional"), paste0("q", qumeth)), 1, paste, collapse="_")

    resvec_cmp <- rep(NA, length(qumeth))
    names(resvec) <- paste0("q", qumeth)

    dat <- rnorm(n = n)

    for(k in seq_along(qumeth)){
      resdir <-  quantile(dat, upper, type = qumeth[k]) - quantile(dat, lower, type = qumeth[k])
      resabs <-  2* quantile(abs(dat), type = qumeth[k], lvl)
      resvec[2*k - 1] <- resdir
      resvec[2*k] <- resabs

      resvec_cmp[k] <- (resabs - resdir) > 0
    }

    res[[i]] <- data.table(t(resvec))
    res_cmp[[i]] <- data.table(t(resvec_cmp))
  }
  res <- data.table::rbindlist(res)
  res_cmp <- data.table::rbindlist(res_cmp)
  names(res) <- apply(expand.grid(c("absolute", "directional"), paste0("q", qumeth)), 1, paste, collapse="_")
  names(res_cmp) <- paste0("q", qumeth)

  result <- apply(res_cmp, 2, mean) |> t() |> as.data.table()

  return(list(res, res_cmp, result))
}
```

```{r generate_data80, echo=FALSE}
nits <- 10000

valsn <- c(9, 21, 150, 5000)

simdat2 <- lapply(valsn, function(nval){
  simcilength(nval, nits, lvl = 0.8)[[3]] |>
  melt(measure.vars = paste0("q", c(1,7,8)), variable.name = "quantile_function",
       value = "proportion") |> 
  .d(,n := nval) |>
    .d(, quantile_function := factor(quantile_function,
                                        levels = c("q1", "q7", "q8"),
                                        labels = c("type = 1", "type = 7", "type = 8")))
  }
) |>
  rbindlist()

```

# Simulation results
For each run, we simulated $n$ observations from a standard normal distribution and subsequently calculated the following two interval lengths:
\begin{itemize}
\item $l_1 = Q \left((X_i)_{i=1}^{n}, 0.9\right) - Q\left((X_i)_{i=1}^{n}, 0.1\right) $ \quad \quad \quad "directional method"
\item $l_2 = 2 \cdot Q\left((|X_i|)_{i=1}^{n}, 0.8\right)$ \quad \quad \quad \quad \quad \quad \quad \quad \quad "absolute method"
\end{itemize}

where $(X_i)_{i=1}^{n}$ is the simulated data and $Q(\cdot, \tau)$ is the quantile function at level $\tau$. In a finite sample setting, there are different ways of calculating $Q$: we use methods 1, 7, 8 from the $\texttt{quantile()}$ function ($\texttt{type}$ argument). See short note at the bottom of this page.

In the previous IMF application, we have observed that $l_2$ is usually larger, using the default quantile calculation method $\texttt{type=7}$.

To investigate whether this is a more universal result, we simulate data with $n \in [7, 50000]$ (evenly spaced on a log scale) and $10000$ iterations each. For each $n$, we record the proportion of instances where $l_2 > l_1$, dependent on the quantile calculation method. The simulation results are shown in the plots on the following page, separately for the two confidence levels.

### Short note on the different types
The following is taken from (Hyndman & Fan 1996: \textit{Sample Quantile in Statistical Packages}). Fore more details, we refer to that text. 
\begin{itemize}
\item $\texttt{type = 1}$ does not interpolate between observations. As the inverse of the empirical distribution function, it always "jumps to the upper value". Thus, severe discontinuties can arise (see following plots)
\item $\texttt{type = 7}$ and $\texttt{type = 8}$ linearly interpolate between observed data points, but do so in different ways, i.e. they choose different midpoints between different values for the cumulative probabilities (see Hyndman)
\end{itemize}

\newpage

## For confidence level 80%
```{r read80data}
simdat <- data.table::fread(here("simulations", "results", "simdat_props80.csv"))
```

```{r, echo = FALSE, fig.dim=c(7,3.8)}
ggplot(aes(x = n, y = proportion, color = quantile_function, group = quantile_function), data = simdat) +
  geom_line() +
  geom_hline(aes(yintercept = 0.5), linetype = "dashed") +
  scale_color_met_d("Archambault") +
  scale_x_continuous(trans='log2') +
  ggtitle("Prop. of longer intervals in absolute method, depending on type option in quantile()") +
  ylab("proportion of absolute intervals larger") +
  xlab("number of simulated observations") +
  theme_uqimf()
```

```{r, echo = FALSE}
ggplot(aes(x = quantile_function, y = as.factor(n), fill = proportion), data = simdat2) +
  geom_tile() +
  geom_text(aes(label=proportion)) +
  ylab("number of observations") +
  xlab("Interpolation method (q_'x' corresponds to type = 'x' in quantile() function)") +
  theme_uqimf()
```

\vspace{0.5cm}

## For confidence level 50%
```{r generate_data50, echo=FALSE, eval = FALSE}

valsn <- exp(seq(2,10, by = 0.05)) |> floor() |> as.list()

simdat <- lapply(valsn, function(nval){
  simcilength(nval, nits, lvl = 0.5)[[3]] |>
  melt(measure.vars = paste0("q", c(1,7,8)), variable.name = "quantile_function",
       value = "proportion") |> 
  .d(,n := nval) |>
    .d(, quantile_function := factor(quantile_function,
                                        levels = c("q1", "q7", "q8"),
                                        labels = c("type = 1", "type = 7", "type = 8")))
  }
) |>
  rbindlist()

```

```{r read50data}
simdat <- data.table::fread(here("simulations", "results", "simdat_props50.csv"))
```

```{r, echo = FALSE, fig.dim=c(7,3.8)}
ggplot(aes(x = n, y = proportion, color = quantile_function, group = quantile_function), data = simdat) +
  geom_line() +
  geom_hline(aes(yintercept = 0.5), linetype = "dashed") +
  scale_color_met_d("Archambault") +
  scale_x_continuous(trans='log2') +
  ggtitle("Prop. of longer intervals in absolute method, depending on type option in quantile()") +
  ylab("proportion of absolute intervals larger") +
  xlab("number of simulated observations") +
  theme_uqimf()
```

We observe that the relative length of the two interval methods vastly differs between the 3 types. $\texttt{type = 1}$ is highly discontinuous and "switches around" substantially with rising $n$. The two interpolating types $\texttt{type = 7}$ and $\texttt{type = 8}$ both approach $0.5$ with increasing $n$. Importantly, for $\texttt{type = 8}$, the interval lenghts for the two methods are overall closer to $0.5$ and thus more balanced.

# What does this mean for the IMF project

So far, we used $\texttt{type = 7}$, the default for the $\texttt{quantile()}$ function - here, in $\sim 80$ percent of cases for both the $50$% and $80$% interval, the absolute method produced longer intervals. We reran the analysis for $\texttt{type = 8}$ - now this is only the case for $\sim 60$ percent of cases.

Importantly, the coverage improves slightly for the directional method and coverage rates are closer to nominal levels (coverage for the absolute method specifically remain mostly unchanged).

More detailed investigation should perhaps be done, but I think this could be a real argument for using $\texttt{type = 8}$ interpolation method and, additionally, perhaps considering changing to directional errors as a default after all.

(Scores overall and in particular ordering between forecast sources also remain mostly the same, so are not included here.)

## GDP Growth
![Changes in central interval coverage - GDP Growth.](type7vs8gdp.png)

## Inflation
![Changes in central interval coverage - Inflation.](type7vs8inflation.png)

### 2024-08-28 miscellaneous/simulations/servercode/job_cilength.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+#SBATCH --ntasks=5
+#SBATCH --time=00:30:00
+#SBATCH --job-name=cilength
+
+module load math/R/4.1.2
+
+R --no-save < sim_cilength.R > Simulation.out

### 2024-08-28 miscellaneous/simulations/servercode/sim_cilength.R

@@ -1,0 +1,136 @@
+knitr::opts_chunk$set(echo = TRUE)
+library(data.table)
+.d <- `[`
+set.seed(42)
+
+
+###SETTINGS##########################
+nits <- 10000
+valsn <- exp(seq(2,10, by = 0.05)) |> floor() |> as.list()
+qumeth <- c(1, 7, 8)
+
+
+
+###FUNCTION##########################
+simcilength <- function(n, nits, lvl = 0.8, qumeth = c(1,7,8)){
+  res <- vector(mode = "list", length = nits)
+  res_cmp <- vector(mode = "list", length = nits)
+
+  if(lvl == 0.8){
+    upper <- 0.9
+    lower <- 0.1
+  } else if (lvl == 0.5){
+    upper <- 0.75
+    lower <- 0.25
+  }
+
+  for(i in 1:nits){
+
+    resvec <- rep(NA, 2*length(qumeth))
+    names(resvec) <- apply(expand.grid(c("absolute", "directional"), paste0("q", qumeth)), 1, paste, collapse="_")
+
+    resvec_cmp <- rep(NA, length(qumeth))
+    names(resvec) <- paste0("q", qumeth)
+
+
+    dat <- rnorm(n = n)
+
+
+    for(k in seq_along(qumeth)){
+      resdir <-  quantile(dat, upper, type = qumeth[k]) - quantile(dat, lower, type = qumeth[k])
+      resabs <-  2* quantile(abs(dat), type = qumeth[k], lvl)
+      resvec[2*k - 1] <- resdir
+      resvec[2*k] <- resabs
+
+      resvec_cmp[k] <- (resabs - resdir) > 0
+    }
+
+    res[[i]] <- data.table(t(resvec))
+    res_cmp[[i]] <- data.table(t(resvec_cmp))
+  }
+  res <- data.table::rbindlist(res)
+  res_cmp <- data.table::rbindlist(res_cmp)
+  names(res) <- apply(expand.grid(c("absolute", "directional"), paste0("q", qumeth)), 1, paste, collapse="_")
+  names(res_cmp) <- paste0("q", qumeth)
+
+  result <- apply(res_cmp, 2, mean) |> t() |> as.data.table()
+
+  return(list(res, res_cmp, result))
+}
+
+
+###SIMULATE 80% CI##########################
+simdat <- lapply(valsn, function(nval){
+  simdat_both <- simcilength(nval, nits, lvl = 0.8)
+
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/length_ci_directionalvsabsolute.Rmd
restructure II: miscellaneous folder cleanup (move things, minor changes to scripts for functionality)

---
title: "Length of Central Intervals"
author: "Rike"
date: "2023-09-08"
output: pdf_document
---

```{r setup, include=FALSE}
library(data.table)
library(here)
library(ggplot2)
library(patchwork)
library(MetBrewer)
library(purrr)
library(lattice)
library(gt)
library(rlang)
library(tidyverse)
devtools::load_all()
knitr::opts_chunk$set(echo = TRUE)
.d <- `[`
```

```{r loaddata}
fcdat <- data.table::fread(here("quantile_forecasts", "quantile_forecasts.csv")) 
```

## Investigate width of intervals

```{r width, echo=FALSE}
ci_width <- fcdat |>
  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
  .d(, .(country, target, horizon, quantile, error_prediction, source, error_method, method, target_year)) |>
  .d(,quantile := paste0("q", quantile)) |>
  dcast(country + target + horizon + source + error_method + method + target_year ~ quantile, value.var = "error_prediction") |>
  .d(, width5 := q0.75 - q0.25) |>
  .d(, width8 := q0.9 - q0.1) |>
  #.d(, med := median(width), by = .(country, target, horizon, source, error_method, method)) |>
  .d(, .(country, target, horizon, source, error_method, method, width5,width8, target_year)) |>
  unique() |>
  dcast(country + target+ horizon + source + method + target_year ~ error_method, 
        value.var = c("width8", "width5")) |>
  .d(, is_longer0.8 := width8_absolute  > width8_directional) |>
  .d(, is_longer0.5 := width5_absolute  > width5_directional)
```

In `r round(mean(ci_width$is_longer0.5), 2)` of cases, the 50% prediction interval is longer for the absolute error method. 
In `r round(mean(ci_width$is_longer0.8), 2)` of cases, the 80% prediction interval is longer for the absolute error method.

### 2024-08-29 miscellaneous/exploratory_scripts/length_ci_dirvsabs.Rmd
restructure II: miscellaneous folder cleanup (move things, minor changes to scripts for functionality)

---
title: "Absolute vs. Directional"
author: "Rike"
date: "2023-11-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(data.table)
```

## In the limit: no difference
```{r cars, echo = FALSE}
n <- 10000
dat <- rnorm(n)
dat <- data.table(x = dat)
ggplot(data = dat, aes(x = x)) +
  geom_histogram(color = "steelblue4", fill = "steelblue3") +
  theme_minimal() +
  geom_vline(aes(xintercept = quantile(dat$x, 0.1)), color = "firebrick") + 
  geom_vline(aes(xintercept = quantile(dat$x, 0.9)), color = "firebrick") +
  geom_vline(aes(xintercept = quantile(abs(dat$x), 0.8)), color = "grey20") +
  geom_vline(aes(xintercept = -1*quantile(abs(dat$x), 0.8)), color = "grey20")

```

## Small sample and not symmetric around zero: difference

```{r, echo = FALSE}
library(data.table)
nits <- 100000
n <- 9
set.seed(45)
res15 <- vector(mode = "list", length = nits)
stopp <- TRUE
par(mfrow = c(2,3)) 
k <- 0
resdat <- vector(mode = "list", length = 6)
while(stopp){

  resvec <- c(NA, NA)
  names(resvec) <- c("directional", "absolute")

  dat <- rnorm(n = n)

  resvec[1] <- quantile(dat, 0.9) - quantile(dat, 0.1)
  resvec[2] <- 2*quantile(abs(dat), 0.8)

  if(resvec[2] > resvec[1] + 0.1){
    resdat[[k+1]] <- dat  
    k <- k + 1
  }
  if(k == 6){
    stopp <- FALSE
  }
}

dat <- data.table(x = resdat[[2]])
ggplot(data = dat, aes(x = x)) +
  geom_histogram(bins = 4, color = "steelblue4", fill = "steelblue3") +
  theme_minimal() +
  geom_vline(aes(xintercept = quantile(dat$x, 0.1)), color = "firebrick") + 
  geom_vline(aes(xintercept = quantile(dat$x, 0.9)), color = "firebrick") +
  geom_vline(aes(xintercept = quantile(dat$x, 0.1, type = 8)), color = "grey40") + 
  geom_vline(aes(xintercept = quantile(dat$x, 0.9, type = 8)), color = "grey40") +
  geom_vline(aes(xintercept = quantile(dat$x, 0.1, type = 1)), color = "chartreuse4") + 
  geom_vline(aes(xintercept = quantile(dat$x, 0.9, type = 1)), color = "chartreuse4") +
  geom_vline(aes(xintercept = quantile(dat$x, 0.9)), color = "firebrick") +
  geom_vline(aes(xintercept = quantile(abs(dat$x), 0.8)), color = "red") +
  geom_vline(aes(xintercept = -1*quantile(abs(dat$x), 0.8)), color = "red") +
  geom_vline(aes(xintercept = quantile(abs(dat$x), 0.8, type = 8)), color = "grey10") +
  geom_vline(aes(xintercept = -1*quantile(abs(dat$x), 0.8, type = 8)), color = "grey10") +
  geom_vline(aes(xintercept = quantile(abs(dat$x), 0.8, type = 1)), color = "chartreuse2") +
  geom_vline(aes(xintercept = -1*quantile(abs(dat$x), 0.8, type = 1)), color = "chartreuse2") +
  geom_vline(aes(xintercept = 0), color = "black")

```

## Simulation with 9 samples from normal distribution

```{r, echo = FALSE}
nits <- 10000
n <- 9

res16 <- vector(mode = "list", length = nits)
for(i in 1:nits){

  resvec <- c(NA, NA)
  names(resvec) <- c("directional", "absolute")

  dat <- rnorm(n = n)

  resvec[1] <- quantile(dat, 0.9) - quantile(dat, 0.1)
  resvec[2] <- 2* quantile(abs(dat), 0.8)

  res16[[i]] <- data.table(t(resvec))
}
res16 <- data.table::rbindlist(res16)

res16$diff <- (res16$absolute - res16$directional) > 0

```
```{r, echo = FALSE}
summary(res16$diff)
```
## Simulation with 150 samples from normal distribution
```{r, echo = FALSE}
nits <- 10000
n <- 20000

res16 <- vector(mode = "list", length = nits)
for(i in 1:nits){

  resvec <- c(NA, NA)
  names(resvec) <- c("directional", "absolute")

  dat <- rnorm(n = n)

  resvec[1] <- quantile(dat, 0.9) - quantile(dat, 0.1)
  resvec[2] <- 2* quantile(abs(dat), 0.8)

  res16[[i]] <- data.table(t(resvec))
}
res16 <- data.table::rbindlist(res16)

res16$diff <- (res16$absolute - res16$directional) > 0

```
```{r, echo = FALSE}
summary(res16$diff)
```

### 2024-08-29 miscellaneous/exploratory_scripts/corr_tv05tv1.R

@@ -1,0 +1,27 @@
+library(patchwork)
+
+weodatcpi <- weodat |> .d(target == "pcpi_pch") |> .d(!is.na(tv_1))
+weodatgdp <- weodat |> .d(target == "ngdp_rpch")|> .d(!is.na(tv_1))
+
+
+val1 <- cor(weodatcpi$tv_0.5, weodatcpi$tv_1)
+val2 <- mean(abs(weodatcpi$tv_0.5 - weodatcpi$tv_1))
+val3 <- mean(abs(weodatcpi$tv_1))
+plot1 <- ggplot(aes(x = tv_0.5, y = tv_1), data = weodatcpi) + geom_point() + geom_abline(aes(intercept = 0, slope = 1)) +
+  theme_uqimf() +
+  xlab("True Value Spring, Inflation") +
+  ylab("True Value Fall, Inflation") +
+  ggtitle("Inflation") +
+  annotate(geom="text", x=2, y=9, label=paste0("correlation: ", round(val1,4), "\n mean absolute difference: ", round(val2,4), "\n mean value of vintage: ", round(val3,4)))
+
+val1 <- cor(weodatgdp$tv_0.5, weodatgdp$tv_1)
+val2 <- mean(abs(weodatgdp$tv_0.5 - weodatgdp$tv_1))
+val3 <- mean(abs(weodatgdp$tv_1))
+plot2 <- ggplot(aes(x = tv_0.5, y = tv_1), data = weodatgdp) + geom_point() + geom_abline(aes(intercept = 0, slope = 1)) +
+  theme_uqimf() +
+  xlab("True Value Spring, GDP Growth") +
+  ylab("True Value Fall, GDP Growth") +
+  ggtitle("GDP Growth") +
+  annotate(geom="text", x=-5, y=7, label=paste0("correlation: ", round(val1,4), "\n mean absolute difference: ", round(val2,4), "\n mean value of vintage: ", round(val3,4)))
+
+ovr_plot <- (plot1 + plot2)

### 2024-08-29 miscellaneous/exploratory_scripts/old/absolute_quantile_transform.R

@@ -1,0 +1,121 @@
+# make toy data to check function
+library(here)
+library(data.table)
+.d <- `[`
+
+toyweo <- data.table::fread(here("WEOforecasts_tidy.csv")) |>
+  .d(ISOAlpha_3Code %in% c("USA", "GER")) |>
+  .d(horizon %in% c(0)) |>
+  .d(target_year <= 2011) |>
+  .d(, .(ISOAlpha_3Code, target, target_year, horizon, forecast_year, prediction, tv_1)) |>
+  #setnames("tv_1", "true_value") |>
+  .d(, tv_1 := 0) |>
+  setnames("ISOAlpha_3Code", "country")
+
+step <- diff(seq(-2, 2, length.out = 21))[1]
+
+toyweo$prediction <- rep(c(seq(-2, 2, length.out = 21), 2+step) , 2)
+
+
+empFC(toyweo,
+      target_years = 2010,
+      tv_release = 1,
+      error_method = "absolute",
+      method = "leave-one-out",
+      ci_levels = c(0.5)
+    )
+
+
+errors <- seq(-10, 10, length.out = 51)
+
+errors <- errors[which(abs(errors)>4)]
+
+errors <- res[[1000]]
+
+quantile(errors, 0.75) - quantile(errors, 0.25)
+quantile(abs(errors), 0.5) * 2
+
+identical(unname(quantile(errors, c(0.25, 0.75))),
+          unname(c(-quantile(abs(errors),  c(0.5)), quantile(abs(errors),  c(0.5)))))
+
+
+
+
+numits <- 100000
+res <- vector(mode = "list", length = numits)
+res1 <- vector(mode = "list", length = numits)
+
+set.seed(2912)
+for (i in 1:numits){
+
+
+  #n <- round(runif(1, 11, 20))
+
+  n <- 33
+
+  sig <- round(runif(1, 1, 5))
+
+  errors <- rnorm(n, 0, 1)
+  #errors <- runif(n, -sig, sig)
+
+  #if(i < 10){
+  #  print(errors)
+  #}
+
+
+  #if(length(errors[which(abs(errors)>0.5)]) < 9){
+  #  next
+  #}
+
+  qus_d <- quantile(errors, c(0.25, 0.75), type = 1)
+
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/plot-scripts/plot_horizon_violations.R

@@ -1,74 +1,0 @@
-library(data.table)
-library(here)
-library(ggplot2)
-library(patchwork)
-devtools::load_all()
-
-.d <- `[`
-
-
-plot_width <- 7
-plot_height <- 10
-
-make_ovrplot <- function(plot1, plot2, plot3){
-  ovrplot <-
-    (plot1) /
-    (plot2) /
-    (plot3) +
-    plot_layout(guides = "collect",
-                heights = c(1, 1, 1)) &
-    plot_annotation(tag_levels = 'I')  &
-    theme(legend.position = 'bottom',
-          legend.box="vertical", legend.margin=margin())
-  ovrplot
-}
-
-
-qufcs <- fread(here("quantile_forecasts", "quantile_forecasts.csv"))
-
-#################CI 0.8#########################################
-plot_0 <- horizon_violators(qufcs, 0.8, 0, exclude_h1.5 = FALSE)
-plot_wo15 <- horizon_violators(qufcs, 0.8, 0, exclude_h1.5 = TRUE)
-plot_025 <- horizon_violators(qufcs, 0.8, 0.25, exclude_h1.5 = FALSE)
-
-pdf(file = here("plots", "horizon_violations_ci8_windowlength9.pdf"), width = plot_width, height = plot_height)
-make_ovrplot(plot_0, plot_wo15, plot_025) +
-   plot_annotation(
-    title = 'CI 80, Window Length 9')
-dev.off()
-
-#################CI 0.5#########################################
-plot_0 <- horizon_violators(qufcs, 0.5, 0, exclude_h1.5 = FALSE)
-plot_wo15 <- horizon_violators(qufcs, 0.5, 0, exclude_h1.5 = TRUE)
-plot_025 <- horizon_violators(qufcs, 0.5, 0.25, exclude_h1.5 = FALSE)
-
-pdf(file = here("plots", "horizon_violations_ci5_windowlength9.pdf"), width = plot_width, height = plot_height)
-make_ovrplot(plot_0, plot_wo15, plot_025) +
-  plot_annotation(
-    title = 'CI 50, Window Length 9')
-dev.off()
-
-
-qufcs <- fread(here("quantile_forecasts", "quantile_forecasts21.csv"))
-
-#################CI 0.8#########################################
-plot_0 <- horizon_violators(qufcs, 0.8, 0, exclude_h1.5 = FALSE)
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/plot-scripts/plot_shiny-vis.R

@@ -1,100 +1,0 @@
-library(data.table)
-library(here)
-library(ggplot2)
-library(MetBrewer)
-library(patchwork)
-devtools::load_all()
-
-.d <- `[`
-
-trgt <- "pcpi_pch"
-cis <- c(0.5, 0.8)
-qus <- c(0.1, 0.25, 0.75, 0.9)
-
-qufcs <- fread(here("quantile_forecasts", "quantile_forecasts.csv"))
-
-linerange_dat <- qufcs |>
-  .d(source == "IMF") |>
-  .d(error_method == "absolute") |>
-  .d(method == "rolling window") |>
-  .d(target == trgt) |>
-  .d(quantile %in% qus) |>
-  .d(,quantile := paste0("quantile", quantile)) |>
-  .d(,fltr := target_year - horizon) |>
-  .d(fltr == 2021.5) |>
-  .d(, .(country, target, target_year, horizon, quantile, prediction)) |>
-  dcast(country + target + target_year + horizon ~ quantile, value.var = "prediction")
-
-
-point_fcs <- fread(here("data", "point_forecasts.csv")) |>
-  .d(source == "IMF") |>
-  .d(target == trgt) |>
-  .d(,fltr := target_year - horizon) |>
-  .d(fltr == 2021.5) |>
-  .d(, .(country, target, target_year, prediction))
-
-
-realized_vals <- qufcs |>
-  .d(target_year > 2013) |>
-  .d(target == trgt) |>
-  .d(, .(country, target, target_year, true_value)) |>
-  .d(!is.na(true_value)) |>
-  unique()
-
-
-dashed_line <- rbind(point_fcs, realized_vals |> copy() |> setnames("true_value", "prediction") |> .d(target_year > 2020))
-
-
-###########################################################################
-cols <- paste0("quantile", qus)
-
-labeldat_2022 <- linerange_dat |>
-  .d(target_year == 2022) |>
-  .d(, x := 2016.25) |>
-  .d(, y := 8.2) |>
-  .d(, (cols) := lapply(.SD, function(val) as.character(round(val, 1))), .SDcols = cols) |>
-  .d(, (cols) := lapply(.SD, function(val) ifelse(grepl("[.]", val), val, paste0(val, ".0"))), .SDcols = cols) |>
-  .d(, label := paste0("2022\n", "50% PI: ", quantile0.25, " - ", quantile0.75, "\n",
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/plot_horizon_violations.R

@@ -1,0 +1,49 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+devtools::load_all()
+
+.d <- `[`
+
+
+plot_width <- 7
+plot_height <- 10
+
+make_ovrplot <- function(plot1, plot2, plot3){
+  ovrplot <-
+    (plot1) /
+    (plot2) /
+    (plot3) +
+    plot_layout(guides = "collect",
+                heights = c(1, 1, 1)) &
+    plot_annotation(tag_levels = 'I')  &
+    theme(legend.position = 'bottom',
+          legend.box="vertical", legend.margin=margin())
+  ovrplot
+}
+
+
+qufcs <- fread(here("quantile_forecasts", "quantile_forecasts.csv"))
+
+#################CI 0.8#########################################
+plot_0 <- horizon_violators(qufcs, 0.8, 0, exclude_h1.5 = FALSE)
+plot_wo15 <- horizon_violators(qufcs, 0.8, 0, exclude_h1.5 = TRUE)
+plot_025 <- horizon_violators(qufcs, 0.8, 0.25, exclude_h1.5 = FALSE)
+
+pdf(file = here("plots", "horizon_violations_ci8_windowlength9.pdf"), width = plot_width, height = plot_height)
+make_ovrplot(plot_0, plot_wo15, plot_025) +
+   plot_annotation(
+    title = 'CI 80, Window Length 9')
+dev.off()
+
+#################CI 0.5#########################################
+plot_0 <- horizon_violators(qufcs, 0.5, 0, exclude_h1.5 = FALSE)
+plot_wo15 <- horizon_violators(qufcs, 0.5, 0, exclude_h1.5 = TRUE)
+plot_025 <- horizon_violators(qufcs, 0.5, 0.25, exclude_h1.5 = FALSE)
+
+pdf(file = here("plots", "horizon_violations_ci5_windowlength9.pdf"), width = plot_width, height = plot_height)
+make_ovrplot(plot_0, plot_wo15, plot_025) +
+  plot_annotation(
+    title = 'CI 50, Window Length 9')
+dev.off()

### 2024-08-29 miscellaneous/exploratory_scripts/plot_series_with_forecasts.R

@@ -1,0 +1,93 @@
+#why do directional errors give lower coverage?
+
+library(here)
+library(data.table)
+library(ggplot2)
+library(MetBrewer)
+
+devtools::load_all()
+
+.d <- `[`
+
+cnt <- "CAN"
+trgtyr <- 2010
+
+
+qus <- ci_to_quantiles(as.numeric(c(.5,.8)), "directional") #always directional
+
+n_qus <- length(qus)
+
+no_pairs <- floor(n_qus/2)
+
+
+alpha_vals <- seq(0.5, 0.75, length.out = no_pairs)
+
+#inner and outer quantile levels
+qu_lvls <- lapply(seq_along(1:no_pairs),
+       function(ind) c(qus[ind], qus[(n_qus)-(ind-1)], alpha_vals[ind]))
+
+
+
+
+sub_weodat <- data.table::fread(here("WEOforecasts_tidy.csv")) |>
+  .d(g7 == 1) |>
+  .d(horizon < 2)
+
+fcdat <- data.table::fread(here("quantile_forecasts", "quantile_forecasts.csv"))
+
+fcdat <- bvarq
+
+
+
+pldat <- fcdat |>
+  .d(source == "IMF") |>
+  .d(method == "leave-one-out") |>
+  .d(,.(country, target, horizon, quantile,prediction, target_year, error_method)) |>
+  .d(, quantile := paste0("quant", quantile)) |>
+  data.table::dcast(country + target + horizon + error_method + target_year ~ quantile,
+                    value.var = "prediction")
+
+
+fctodis <- fcdat |>
+  .d(target_year == trgtyr) |>
+  .d(country == cnt) |>
+  .d(source == "IMF") |>
+  .d(horizon < 2)
+
+
+year_range <- unique(fcdat$target_year)
+
+ggplot() +
+  geom_line(
+    aes(x = target_year, y = get(paste0("tv_", 1)),
+        group = country, color = country),
+    data = sub_weodat |>
+      .d(ISOAlpha_3Code == cnt) |>
+      .d(target_year %in% year_range)) +
+  ggtitle(paste0("Actual Series, with forecast for year ", trgtyr)) +
+  ylab("True value") +
+
+  lapply(qu_lvls, function(qupr){
+    geom_linerange(
+      aes(x = target_year,
+          ymin = get(paste0("quant", qupr[1])),
+          ymax = get(paste0("quant", qupr[2])),
+          color = country),
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/plot_shiny-vis.R

@@ -1,0 +1,106 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(MetBrewer)
+library(patchwork)
+library(lubridate)
+devtools::load_all()
+
+.d <- `[`
+
+trgt <- "pcpi_pch"
+season <- "S"
+
+cis <- c(0.5, 0.8)
+qus <- c(0.1, 0.25, 0.75, 0.9)
+
+horshift <- ifelse(season == "S", 0.5, 0)
+cyear <- lubridate::year(Sys.Date())
+
+qufcs <- fread(here("quantile_forecasts", "quantile_forecasts.csv"))
+
+linerange_dat <- qufcs |>
+  .d(source == "IMF") |>
+  .d(error_method == "absolute") |>
+  .d(method == "rolling window") |>
+  .d(target == trgt) |>
+  .d(quantile %in% qus) |>
+  .d(,quantile := paste0("quantile", quantile)) |>
+  .d(,fltr := target_year - horizon) |>
+  .d(fltr == cyear - horshift) |>
+  .d(, .(country, target, target_year, horizon, quantile, prediction)) |>
+  dcast(country + target + target_year + horizon ~ quantile, value.var = "prediction")
+
+
+point_fcs <- fread(here("data", "point_forecasts.csv")) |>
+  .d(source == "IMF") |>
+  .d(target == trgt) |>
+  .d(,fltr := target_year - horizon) |>
+  .d(fltr == cyear - horshift) |>
+  .d(, .(country, target, target_year, prediction))
+
+
+realized_vals <- qufcs |>
+  .d(target_year > 2013) |>
+  .d(target == trgt) |>
+  .d(, .(country, target, target_year, true_value)) |>
+  .d(!is.na(true_value)) |>
+  unique()
+
+
+dashed_line <- rbind(point_fcs, realized_vals |> copy() |> setnames("true_value", "prediction") |> .d(target_year > 2020))
+
+
+###########################################################################
+cols <- paste0("quantile", qus)
+
+labeldat_2022 <- linerange_dat |>
+  .d(target_year == cyear) |>
+  .d(, x := 2016.25) |>
+  .d(, y := 8.2) |>
+  .d(, (cols) := lapply(.SD, function(val) as.character(round(val, 1))), .SDcols = cols) |>
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/toy-scripts/absolute_quantile_transform.R

@@ -1,121 +1,0 @@
-# make toy data to check function
-library(here)
-library(data.table)
-.d <- `[`
-
-toyweo <- data.table::fread(here("WEOforecasts_tidy.csv")) |>
-  .d(ISOAlpha_3Code %in% c("USA", "GER")) |>
-  .d(horizon %in% c(0)) |>
-  .d(target_year <= 2011) |>
-  .d(, .(ISOAlpha_3Code, target, target_year, horizon, forecast_year, prediction, tv_1)) |>
-  #setnames("tv_1", "true_value") |>
-  .d(, tv_1 := 0) |>
-  setnames("ISOAlpha_3Code", "country")
-
-step <- diff(seq(-2, 2, length.out = 21))[1]
-
-toyweo$prediction <- rep(c(seq(-2, 2, length.out = 21), 2+step) , 2)
-
-
-empFC(toyweo,
-      target_years = 2010,
-      tv_release = 1,
-      error_method = "absolute",
-      method = "leave-one-out",
-      ci_levels = c(0.5)
-    )
-
-
-errors <- seq(-10, 10, length.out = 51)
-
-errors <- errors[which(abs(errors)>4)]
-
-errors <- res[[1000]]
-
-quantile(errors, 0.75) - quantile(errors, 0.25)
-quantile(abs(errors), 0.5) * 2
-
-identical(unname(quantile(errors, c(0.25, 0.75))),
-          unname(c(-quantile(abs(errors),  c(0.5)), quantile(abs(errors),  c(0.5)))))
-
-
-
-
-numits <- 100000
-res <- vector(mode = "list", length = numits)
-res1 <- vector(mode = "list", length = numits)
-
-set.seed(2912)
-for (i in 1:numits){
-
-
-  #n <- round(runif(1, 11, 20))
-
-  n <- 33
-
-  sig <- round(runif(1, 1, 5))
-
-  errors <- rnorm(n, 0, 1)
-  #errors <- runif(n, -sig, sig)
-
-  #if(i < 10){
-  #  print(errors)
-  #}
-
-
-  #if(length(errors[which(abs(errors)>0.5)]) < 9){
-  #  next
-  #}
-
-  qus_d <- quantile(errors, c(0.25, 0.75), type = 1)
-
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/toy-scripts/bvar_overprediction.R

@@ -1,83 +1,0 @@
-#why do directional errors give lower coverage?
-
-library(here)
-library(data.table)
-library(ggplot2)
-
-devtools::load_all()
-
-.d <- `[`
-
-cnt <- "ITA"
-trgtyr <- 2010
-
-
-qus <- ci_to_quantiles(as.numeric(c(.5,.8)), "directional") #always directional
-
-n_qus <- length(qus)
-
-no_pairs <- floor(n_qus/2)
-
-
-alpha_vals <- seq(0.5, 0.75, length.out = no_pairs)
-
-#inner and outer quantile levels
-qu_lvls <- lapply(seq_along(1:no_pairs),
-                  function(ind) c(qus[ind], qus[(n_qus)-(ind-1)], alpha_vals[ind]))
-
-
-fcdat <- bvar_qus |>
-  .d(!is.na(horizon)) |>
-  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
-  .d(target == "pcpi_pch")
-
-
-
-pldat <- fcdat |>
-  .d(,.(country, target, horizon, quantile,prediction, target_year)) |>
-  .d(, quantile := paste0("quant", quantile)) |>
-  data.table::dcast(country + target + horizon  + target_year ~ quantile,
-                    value.var = "prediction")
-
-
-fctodis <- fcdat |>
-  .d(target_year == trgtyr) |>
-  .d(country == cnt) |>
-  .d(horizon < 2)
-
-
-year_range <- unique(fcdat$target_year)
-
-ggplot() +
-  geom_line(
-    aes(x = target_year, y = true_value,
-        group = country, color = country),
-    data = fcdat |>
-      .d(country == cnt) |>
-      .d(target_year %in% year_range)) +
-  ggtitle(paste0("BVAR predictions, for ", cnt)) +
-  ylab("True value") +
-
-  lapply(qu_lvls, function(qupr){
-    geom_linerange(
-      aes(x = target_year,
-          ymin = get(paste0("quant", qupr[1])),
-          ymax = get(paste0("quant", qupr[2])),
-          color = country),
-      data = pldat |>
-        .d(country == cnt) ,
-      lwd = 1.5, alpha = qupr[3], show.legend = TRUE)
-  }) +
-
-  #geom_point(
-  #  aes(x = target_year, y = imf_pp, color = country),
-  #  data = fctodis
-  #) +
-
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/toy-scripts/compare-afterbefore-horizonshift.R

@@ -1,116 +1,0 @@
-library(data.table)
-library(here)
-devtools::load_all()
-#this file was run once before and once after changing the code in uqfc.R
-#for 'correctly'/honestly sampling with respect to horizon
-#only last line (name of saved file) was changed
-
-source(here("specs", "specs.R"))
-
-.d <- `[`
-
-max_year_imf <- specs$max_year_imf
-max_year_others <- specs$max_year_others
-min_year <- 2000
-tv_release <- specs$tv_release
-window_length <- specs$window_length
-
-cis <- specs$ci_levels_make
-
-#make all combinations of settings
-combs <- data.table::fread(here("quantile_forecasts", "setting_combinations.csv"))
-
-
-fcdat <- data.table::fread(here("data", "point_forecasts.csv")) |>
-  .d(country %in% c("CAN", "JAP"))
-
-#make quantile forecasts for all combinations in combs
-testqus <- lapply(1:nrow(combs),
-                function(idxsub){
-
-                  setting <- combs[idxsub]
-
-                  if(setting[, "method"] == "leave-one-out"){
-
-                    start_year <- min_year
-                  } else {
-
-                    start_year <- min_year + window_length
-                  }
-
-                  subdat <- fcdat |>
-                    .d(source == setting[, "source"]) |>
-                    .d(target == setting[, "target"]) |>
-                    .d(, source := NULL)
-
-                  if (setting[, "source"] %in% c("bvar", "ar")) {
-                    max_year <- specs$max_year_others
-                  } else {
-
-                    max_year <- specs$max_year_imf
-                  }
-
-                  empFC(subdat,
-                        target_year = start_year:max_year,
-                        tv_release = tv_release,
-                        error_method = setting[, "error_method"],
-                        method = setting[, "method"],
-                        window_length = window_length,
-                        ci_levels = cis) |>
-                    .d(, source := setting[, "source"]) |>
-                    .d(, error_method := setting[, "error_method"]) |>
-                    .d(, method := setting[, "method"])
-
-                }
-) |>
-  rbindlist() |>
-  setnames(paste0("tv_", tv_release), "true_value")
-
-#fwrite(testqus, here("qufcs_beforehorshift.csv"))
-fwrite(testqus, here("qufcs_afterhorshift.csv"))
-
-
-
-
-
-
-
-
-
-
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/toy-scripts/corr_tv05tv1.R

@@ -1,27 +1,0 @@
-library(patchwork)
-
-weodatcpi <- weodat |> .d(target == "pcpi_pch") |> .d(!is.na(tv_1))
-weodatgdp <- weodat |> .d(target == "ngdp_rpch")|> .d(!is.na(tv_1))
-
-
-val1 <- cor(weodatcpi$tv_0.5, weodatcpi$tv_1)
-val2 <- mean(abs(weodatcpi$tv_0.5 - weodatcpi$tv_1))
-val3 <- mean(abs(weodatcpi$tv_1))
-plot1 <- ggplot(aes(x = tv_0.5, y = tv_1), data = weodatcpi) + geom_point() + geom_abline(aes(intercept = 0, slope = 1)) +
-  theme_uqimf() +
-  xlab("True Value Spring, Inflation") +
-  ylab("True Value Fall, Inflation") +
-  ggtitle("Inflation") +
-  annotate(geom="text", x=2, y=9, label=paste0("correlation: ", round(val1,4), "\n mean absolute difference: ", round(val2,4), "\n mean value of vintage: ", round(val3,4)))
-
-val1 <- cor(weodatgdp$tv_0.5, weodatgdp$tv_1)
-val2 <- mean(abs(weodatgdp$tv_0.5 - weodatgdp$tv_1))
-val3 <- mean(abs(weodatgdp$tv_1))
-plot2 <- ggplot(aes(x = tv_0.5, y = tv_1), data = weodatgdp) + geom_point() + geom_abline(aes(intercept = 0, slope = 1)) +
-  theme_uqimf() +
-  xlab("True Value Spring, GDP Growth") +
-  ylab("True Value Fall, GDP Growth") +
-  ggtitle("GDP Growth") +
-  annotate(geom="text", x=-5, y=7, label=paste0("correlation: ", round(val1,4), "\n mean absolute difference: ", round(val2,4), "\n mean value of vintage: ", round(val3,4)))
-
-ovr_plot <- (plot1 + plot2)

### 2024-08-29 miscellaneous/exploratory_scripts/toy-scripts/investigate_error_direction.R

@@ -1,86 +1,0 @@
-
-library(here)
-library(data.table)
-library(ggplot2)
-
-library(patchwork)
-
-.d <- `[`
-
-qufcs <- data.table::fread(here("quantile_forecasts", "quantile_forecasts.csv"))
-scores <- data.table::fread(here("quantile_forecasts", "ci_scores.csv"))
-
-mydat <- qufcs |> .d(source == "IMF" & country == "USA" & horizon == 1.0 & quantile %in% c(0.1, 0.25, 0.75, 0.9)) |> .d(target == "pcpi_pch") |>
-.d(method %in% c("rolling window", "leave-one-out"))
-
-
-pldat <- mydat |>
-  .d(method %in% c("rolling window", "leave-one-out")) |>
-  .d(,.(country, target, horizon, quantile,prediction, target_year, error_method, method)) |>
-  .d(, quantile := paste0("quant", quantile)) |>
-  data.table::dcast(country + target + horizon + target_year + error_method + method~ quantile,
-                    value.var = "prediction")
-
-
-pldat0 <- mydat |>
-  .d(quantile == 0.25) |>
-  .d(error_method == "directional" & method == "leave-one-out")
-
-qu_lvls <- list(
-  c(0.1, 0.9, 0.25),
-  c(0.25, 0.75, 0.5)
-)
-
-plot1 <- ggplot() +
-  geom_line(aes(x = target_year, y = true_value), data = mydat |> .d(quantile == 0.25), color = "steelblue") +
-  geom_point(aes(x = target_year, y = imf_pp), data = mydat |> .d(quantile == 0.25), color = "darkgreen") +
-  lapply(qu_lvls, function(qupr){
-    geom_linerange(
-      aes(x = target_year,
-          ymin = get(paste0("quant", qupr[1])),
-          ymax = get(paste0("quant", qupr[2])),
-          color = country),
-      data = pldat,
-      lwd = 1.5, alpha = qupr[3], show.legend = TRUE)
-  }) +
-  facet_wrap(~error_method + method)
-
-
-transdat <- mydat |>
-  .d(,error := ifelse(error_method == "absolute", abs(error), error))
-
-plot2 <- ggplot() +
-  geom_boxplot(aes(x = error_method, y = error), data = transdat)
-
-plot0 <- ggplot() +
-  geom_line(aes(x = target_year, y = error), data = pldat0) +
[…]

### 2024-08-29 miscellaneous/exploratory_scripts/toy-scripts/plot_series_with_forecasts.R

@@ -1,92 +1,0 @@
-#why do directional errors give lower coverage?
-
-library(here)
-library(data.table)
-library(ggplot2)
-
-devtools::load_all()
-
-.d <- `[`
-
-cnt <- "CAN"
-trgtyr <- 2010
-
-
-qus <- ci_to_quantiles(as.numeric(c(.5,.8)), "directional") #always directional
-
-n_qus <- length(qus)
-
-no_pairs <- floor(n_qus/2)
-
-
-alpha_vals <- seq(0.5, 0.75, length.out = no_pairs)
-
-#inner and outer quantile levels
-qu_lvls <- lapply(seq_along(1:no_pairs),
-       function(ind) c(qus[ind], qus[(n_qus)-(ind-1)], alpha_vals[ind]))
-
-
-
-
-sub_weodat <- data.table::fread(here("WEOforecasts_tidy.csv")) |>
-  .d(g7 == 1) |>
-  .d(horizon < 2)
-
-fcdat <- data.table::fread(here("quantile_forecasts", "quantile_forecasts.csv"))
-
-fcdat <- bvarq
-
-
-
-pldat <- fcdat |>
-  .d(source == "IMF") |>
-  .d(method == "leave-one-out") |>
-  .d(,.(country, target, horizon, quantile,prediction, target_year, error_method)) |>
-  .d(, quantile := paste0("quant", quantile)) |>
-  data.table::dcast(country + target + horizon + error_method + target_year ~ quantile,
-                    value.var = "prediction")
-
-
-fctodis <- fcdat |>
-  .d(target_year == trgtyr) |>
-  .d(country == cnt) |>
-  .d(source == "IMF") |>
-  .d(horizon < 2)
-
-
-year_range <- unique(fcdat$target_year)
-
-ggplot() +
-  geom_line(
-    aes(x = target_year, y = get(paste0("tv_", 1)),
-        group = country, color = country),
-    data = sub_weodat |>
-      .d(ISOAlpha_3Code == cnt) |>
-      .d(target_year %in% year_range)) +
-  ggtitle(paste0("Actual Series, with forecast for year ", trgtyr)) +
-  ylab("True value") +
-
-  lapply(qu_lvls, function(qupr){
-    geom_linerange(
-      aes(x = target_year,
-          ymin = get(paste0("quant", qupr[1])),
-          ymax = get(paste0("quant", qupr[2])),
-          color = country),
-      data = pldat |>
[…]

### 2024-09-03 README.Rmd
Update Readme

@@
 
-# uqimf
+# Simple Macroeconomic Forecast Distributions for the G7 Economies
 
@@
 
-This repo contains code to generate simple and transparent prediction intervals for the IMF World Economic Outlook forecasts (see references).
-Central prediction intervals are generated at the 50% and 80% levels for CPI inflation and real GDP growth, based on past forecast errors.
-See below for documentation on which files the respective folders contain.
+This repository contains the documentation, results, and code of a project where we produce simple macroeconomic forecast distributions for the G7 economies, in the form of prediction intervals.
+It also contains code to continue to produce these forecasts in real-time.
+See the documentation below for further details.
 
-## Contents of the repository
+## Short summary of the project
+
+We generate easy-to-understand forecast intervals for output growth and inflation in the G7 economies, using the point forecasts published in the International Monetary Fund World Economic Outlook (IMF WEO).
+The forecast intervals are generated at the 50% and 80% levels in a simple and transparent manner, using empirical quantiles of the past history of point forecast errors in the IMF WEO.
+For more details, please refer to the working paper below.
+
+## Citation
+
+The working paper can be found on arXiv. Please cite this using the following:
+
+> Becker, Krüger, and Schienle. 2024 “Simple Macroeconomic Forecast Distributions for the G7 Economies” arXiv. https://doi.org/10.48550/arXiv.2408.08304.
+
+```
+@unpublished{Beckeretal_2024,
+  title={Simple Macroeconomic Forecast Distributions for the G7 Economies},
+  author={Becker, Friederike and Kr{\"u}ger, Fabian and Schienle, Melanie},
+  note={Preprint, arXiv:2408.08304},
+  year={2024}
+}
+```
+
+## Further links
+
+This repository mainly contains files for the retrospective analysis in the working paper, see above.
+Please visit the following repository to find the forecasts as they are published in real-time, as well as further links to a dashboard, a preregistration protocol, etc.
+
+> https://github.com/KITmetricslab/MacroPI
+
+## Contents of this repository
+
+More details on each folder can be found further below.
+
+Folder | Purpose
+---|---
+[`benchmarks`](benchmarks/) | Code and forecast data of benchmark forecasts.
+[`data`](data/) | Processed WEO and benchmark forecast data. from `data-raw` ready to be used in the paper analysis.
+[`miscellanous`](miscellanous/) | Files that are not relevant for the final analysis (exploratory scripts, presentation files, etc). Kept for transparency.
+[`oecd_data`](oecd_data/) | OECD truth data used for fitting benchmarks and for robustness checks.
+[`quantile_forecasts`](quantile_forecasts/) | The generated forecast intervals, recorded via their upper and lower endpoints. 
+[`R`](R/) | R functions used in the analysis and for evaluation.
+[`scores`](scores/) | Scores of forecasts.
+[`scripts`](scripts/) | Executive scripts to produce all results.
+[`specs`](specs/) | Specifications and global options for the analysis.
+
+Forecast intervals at the 50% and 80% are recorded via their upper and lower endpoints, that is, the 0.25 and 0.75 predictive quantiles for the 50% interval, and the 0.1 and 0.9 predictive quantiles for the 90% interval.
 

### 2024-09-03 README.Rmd
update Readme

@@
 
-This repository contains the documentation, results, and code of a project where we produce simple macroeconomic forecast distributions for the G7 economies, in the form of prediction intervals.
+This repository contains the documentation, results, and code of a project where we produce simple macroeconomic forecast distributions for the G7 economies.
 It also contains code to continue to produce these forecasts in real-time.
@@
 We generate easy-to-understand forecast intervals for output growth and inflation in the G7 economies, using the point forecasts published in the International Monetary Fund World Economic Outlook (IMF WEO).
-The forecast intervals are generated at the 50% and 80% levels in a simple and transparent manner, using empirical quantiles of the past history of point forecast errors in the IMF WEO.
+Our forecast intervals are generated at the 50% and 80% levels in a simple and transparent manner, using empirical quantiles of the past history of point forecast errors in the IMF WEO.
 For more details, please refer to the working paper below.
@@
 
-More details on each folder can be found further below.
+More details on each folder can be found in its own respective section further below.
 
@@
 [`benchmarks`](benchmarks/) | Code and forecast data of benchmark forecasts.
-[`data`](data/) | Processed WEO and benchmark forecast data. from `data-raw` ready to be used in the paper analysis.
-[`miscellanous`](miscellanous/) | Files that are not relevant for the final analysis (exploratory scripts, presentation files, etc). Kept for transparency.
+[`data`](data/) | Processed WEO and benchmark forecast data. 
+[`miscellanous`](miscellanous/) | Files that are not relevant for the final analysis (exploratory scripts, presentation files, etc). Kept for completeness and transparency.
 [`oecd_data`](oecd_data/) | OECD truth data used for fitting benchmarks and for robustness checks.
@@
 
-Forecast intervals at the 50% and 80% are recorded via their upper and lower endpoints, that is, the 0.25 and 0.75 predictive quantiles for the 50% interval, and the 0.1 and 0.9 predictive quantiles for the 90% interval.
+## General notes on naming data files
 
-The folders of this repository contain the following:
+Note that data files in this repository are generally identified with some "core-name", e.g.
+quantile_forecasts, and then with prefixes and/or suffixes that further describe deviations from the default setting.
+
+- Default setting: training data (target years 2001-2012); absolute error method; IMF WEO truth data; complete data before discarding instances for scoring
+- "ho" suffix: holdout data (target years 2013-2023)
+- "directional" suffix: directional error method
+- "oecd" prefix: OECD truth data (used for robustness check)
+- "to_score" prefix: excludes some instances for scoring data. All scores in scores/ folder are calculated based on these data versions.
+
+### R folder
 
@@
 
-- `benchmarks`: benchmark forecasts and the scripts that generate them.
+### benchmarks folder
 
@@
 
-- `data`: WEO and merged data
+### data folder
 
@@
 
-- `manuscript`: files to write manuscript. Abandoned now, in favor of `uqimf-manuscript` repository
+### oecd_data folder
 
@@
 
-- `plots`: you get what you bargain for
+### quantile_forecasts folder
 
-- `presentation`: some files for the presentation of the project at the MathSEE Symposium
+- `quantile-forecasts`: contains forecasts as produced by `scripts/make-forecasts`, see below.
+Note that the forecast intervals are identified via their upper and lower endpoints.
+That is, for the 50% interval, the 0.25 and 0.75 predictive quantiles, and for the 80% interval, the 0.1 and 0.9 predictive quantiles.
+Also note the naming data notes outlined above.
 
-- `quantile-forecasts`: contains quantile forecasts as produced by `scripts/make-forecasts`, see below
+### scores folder
 
-- `scores`: Contains scores of forecasts in `quantile-forecasts` and BVAR benchmarks, at various levels of resolutions. Contains its own Readme file to explain what scores the different files contain.
+- `scores`: Contains scores of forecasts in `quantile-forecasts` and BVAR benchmarks, at various levels of resolutions.
+Contains its own Readme file to explain what scores the different files contain.
+Also note the naming data notes outlined above.
 
-- `scripts`: Contains scripts that process data based on the function in `R`
+### scripts
 
-  - `toy-scripts`: small scripts to explore data
-
-  - `plot-scripts`: scripts to generate plots
+- `scripts`: Contains scripts that process data based on the functions in `R`
+  - `master.R`: produces all results based on the following sub-scripts (listed in the order as they appear in master.R, so not alphabetical)
 
@@
 
-  - `make-forecasts.R`: generate quantile forecasts based (`data/point-forecasts.csv` to `quantile_forecasts/quantile_forecasts.csv`)
+  - `process-weo.R`: short script to filter and process WEO data
 
@@
 
-  - `process-weo.R`: short script to filter and process WEO data
+  - `encode-missing-predictions.R` explicitly encode missing data (although we actually have no missing data, but just for completenss)
 
-  - `score-forecasts.R`: score quantile forecasts, those generated here and the benchmark BVAR quantile forecasts.
+  - `make-forecasts.R`: generate forecast intervals
+
+  - `exclude-from-scoring.R`: exclude any instances that are listed in `specs/specs.R` from scoring
+
+  - `score-forecasts.R`: score quantile forecasts, those generated in `make-forecasts.R` and the benchmark BVAR quantile forecasts.
 

### 2024-10-29 miscellaneous/presentation/presentation.tex
presentation updates

@@
 \begin{frame}{Scores on holdout data 2013-2023 - Inflation}
-%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
     \begin{figure}
         \centering
-        \includegraphics[width=0.45\textwidth]{figures/ho_wis_pcpi_pch_absolute_rollingwindow.pdf} 
+        \includegraphics[width=0.45\textwidth]{figures/wis_pcpi_pch_ho.pdf} 
         \label{fig:enter-label}
@@
         \centering
-        \includegraphics[width=0.45\textwidth]{figures/ho_wis_ngdp_rpch_absolute_rollingwindow.pdf} 
+        \includegraphics[width=0.45\textwidth]{figures/wis_ngdp_rpch_ho.pdf} 
         \label{fig:enter-label}
@@
 \begin{frame}{Calibration - on holdout data 2013-2023}
-%\textit{Here, I'll instead map the colors to the different forecast sources (currently mapped to the window method), so we'll just have one plot each}
-    %Coverage at the 50\% and 80\% central interval: \\ 
 \begin{figure}
@@
   \centering
-    \includegraphics[width=\textwidth]{figures/ho_coverage_pcpi_pch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+    \includegraphics[width=\textwidth]{figures/coverage_pcpi_pch_ho.pdf} %\vspace{0.3cm}
   \end{subfigure}
@@
   \centering
-    \includegraphics[width=\textwidth]{figures/ho_coverage_ngdp_rpch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+    \includegraphics[width=\textwidth]{figures/coverage_ngdp_rpch_ho.pdf} %\vspace{0.3cm}
   \end{subfigure}%
@@
 \begin{frame}{Increasing Uncertainty}
-%Width of Prediction Intervals, by Horizon
-%\textit{include graphic or table showing increasing uncertainty with rising horizons}\\ 
 \begin{columns}
@@
         \centering
-        \includegraphics[width=\textwidth]{figures/cilength_byhorizon.pdf}
+        \includegraphics[width=\textwidth]{figures/cilength_byhorizon_ho.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
@@
     \begin{itemize}
-    \item slightly improved coverage and scores, at the cost of interpretability \hyperlink{extractionmethod}{\beamerbutton{link}}
+    \item slightly improved coverage and scores, at the cost of interpretability 
     \end{itemize}
@@
 
-\begin{frame}{Expanding Window - Scores}
-\label{extractionmethod}
-\end{frame}
-
 \begin{frame}{Alternative truth value - Scores}
@@
         %\centering
-        \includegraphics[width=0.55\textwidth]{figures/oecdvsimf.pdf}
+        \includegraphics[width=0.55\textwidth]{figures/ho_oecdvsimf.pdf}
         %\caption{Coverage at the 50 and 80 percent level}
@@
   \centering
-    \includegraphics[width=\textwidth]{figures/ho_bvarspecs_wis_pcpi_pch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+    \includegraphics[width=\textwidth]{figures/bvarspecs_wis_pcpi_pch_ho.pdf} %\vspace{0.3cm}
     \caption{Inflation}
@@
   \centering
-    \includegraphics[width=\textwidth]{figures/ho_bvarspecs_wis_ngdp_rpch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
+    \includegraphics[width=\textwidth]{figures/bvarspecs_wis_ngdp_rpch_ho.pdf} %\vspace{0.3cm}
     \caption{GDP Growth}

### 2024-11-05 real_time_publication/macroPI_withpasteval/app.R
include stepback argument

@@ -1,3 +1,4 @@
+library(here)
 library(data.table)
 library(ggplot2)
 library(MetBrewer)
@@ -17,6 +18,35 @@ release_year <- ifelse(cmonth < 4, cyear - 1, cyear)
 release <- paste0(release_season, release_year)
 release_title <- paste(release_season, release_year)
 
+localrun <- TRUE
+
+
+stepback <- tryCatch({
+  # Attempt to read the file from the URL
+  if(localrun){
+    data.table::fread(here("real_time_publication", "forecasts", paste0("forecasts_", release, ".csv")))
+  }
+
+  else {
+    read.csv(paste0("https://raw.githubusercontent.com/MacroPrediction/MacroPI/main/forecasts/forecasts_", release, ".csv"))
+  }
+
+  FALSE
+
+}, error = function(e) {
+  # If an error occurs (e.g., file not found), set month to 9
+  #message("Current release not yet out, default to previous season")
+
+  return(TRUE)
+})
+
+if(stepback){
+
+  release_year <- ifelse(release_season == "Spring", release_year - 1, release_year)
+  release_season <- ifelse(release_season == "Spring", "Fall", "Spring")
+  release <- paste0(release_season, release_year)
+  release_title <- paste(release_season, release_year)
+}
 
 ui <- fluidPage(
 
@@ -249,13 +279,23 @@ server <- function(input, output) {
                  "by the IMF.",
                  sep = "\n"))
   }
-  #read in data
-  qufcs <- read.csv(paste0("https://raw.githubusercontent.com/MacroPrediction/MacroPI/main/forecasts/forecasts_", release, ".csv")) |>
-    setDT()
-  realized_vals <- read.csv(paste0("https://raw.githubusercontent.com/MacroPrediction/MacroPI/main/imf-data/historicvalues_", release, ".csv"))|>
-    setDT()
-  point_fcs <- read.csv(paste0("https://raw.githubusercontent.com/MacroPrediction/MacroPI/main/imf-data/pointforecasts_", release, ".csv"))|>
-    setDT()
+  if(localrun){
+
+    qufcs <- data.table::fread(here("real_time_publication", "forecasts", paste0("forecasts_", release, ".csv"))) |>
+      setDT()
+    realized_vals <- data.table::fread(here("real_time_publication", "imf-data", paste0("historicvalues_", release, ".csv"))) |>
+      setDT()
[…]

### 2024-11-05 README.Rmd
update Readme

@@
 
-## General notes on naming data files
+## General notes on the naming of data files
 
@@
 
-- Default setting: training data (target years 2001-2012); absolute error method; IMF WEO truth data; complete data before discarding instances for scoring
+- default setting: training data (target years 2001-2012); absolute error method; IMF WEO truth data; complete data before discarding instances for scoring
 - "ho" suffix: holdout data (target years 2013-2023)
@@
 - "to_score" prefix: excludes some instances for scoring data. All scores in scores/ folder are calculated based on these data versions.
+- "bvarspecs" prefix: for scoring different BVAR specifications (benchmark models) against each other. Excludes more instances, for data availability reasons.
+
+## Contents of individual folders
 

### 2025-04-06 manuscript_plots/revision/extcis_current.tex
automate more elements of table, fix order of footnotes

\begin{table}[!h]
\centering
\caption{Interval Scores with Minimums Highlighted}
\centering
\begin{tabular}[t]{llllllllllllllll}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{7}{c}{{Inflation\hspace*{15mm}}} & \multicolumn{7}{c}{{GDP Growth}} \\
\cmidrule(l{3pt}r{3pt}){3-9} \cmidrule(l{3pt}r{3pt}){10-16}
 &  & $\text{CRPS}^{1)}$-c & $\text{IS}_{W}^{2)}$-c & $\text{IS}_{W,b}^{2)}$-c & $\text{IS}_{U}^{2)}$-c & $\text{IS}_{50}^{2)}$-c & $\text{IS}_{80}^{2)}$-c & $\text{IS}_{\text{CISS}}^{2)}$-c & $\text{CRPS}^{1)}$-g & $\text{IS}_{W}^{2)}$-g & $\text{IS}_{W,b}^{2)}$-g & $\text{IS}_{U}^{2)}$-g & $\text{IS}_{50}^{2)}$-g & $\text{IS}_{80}^{2)}$-g & $\text{IS}_{\text{CISS}}^{2)}$-g\\
\midrule
\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{\textbf{0.103}} & \cellcolor{gray!35}{\textbf{0.106}} & \cellcolor{gray!35}{\textbf{0.093}} & \cellcolor{gray!35}{\textbf{0.522}} & \cellcolor{gray!35}{\textbf{0.46}} & \cellcolor{gray!35}{\textbf{0.741}} & \cellcolor{gray!35}{\textbf{0.089}} & \cellcolor{gray!35}{0.292} & \cellcolor{gray!35}{0.298} & \cellcolor{gray!35}{0.269} & \cellcolor{gray!35}{1.561} & \cellcolor{gray!35}{1.279} & \cellcolor{gray!35}{2.298} & \cellcolor{gray!35}{0.255}\\
\parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Fall, Current}}}
 & AR(1) & 0.195 & 0.198 & 0.177 & 1.034 & 0.839 & 1.484 & 0.214 & 0.337 & 0.344 & 0.298 & 1.697 & 1.485 & 2.355 & 0.302\\
 & AR(p) & 0.183 & 0.185 & 0.166 & 0.978 & 0.783 & 1.449 & 0.203 & 0.333 & 0.34 & 0.296 & 1.688 & 1.466 & 2.39 & 0.3\\
 & BVAR$^{3)}$ & 0.2 & 0.203 & 0.183 & 1.053 & 0.87 & 1.494 & 0.219 & 0.326 & 0.334 & 0.285 & 1.664 & 1.449 & 2.356 & 0.288\\
 & BVAR-Mix$^{3)}$ & 0.198 & 0.201 & 0.182 & 1.042 & 0.86 & 1.47 & 0.218 & 0.323 & 0.33 & 0.284 & 1.642 & 1.417 & 2.311 & 0.287\\
 & Direct$^{4)}$: AR(1) & 0.195 & 0.196 & 0.182 & 1.048 & 0.843 & 1.532 & 0.217 & 0.332 & 0.334 & 0.303 & 1.713 & 1.462 & 2.412 & 0.303\\
 & Direct$^{4)}$: AR(p) & 0.181 & 0.183 & 0.169 & 0.981 & 0.785 & 1.424 & 0.203 & 0.326 & 0.328 & 0.298 & 1.684 & 1.437 & 2.363 & 0.3\\
 & Direct$^{4)}$: AR-annual & 1.03 & 0.988 & 0.899 & 5.179 & 4.252 & 7.355 & 0.987 & 1.711 & 1.613 & 1.56 & 8.995 & 7.043 & 13.599 & 1.678\\
 & Direct$^{4)}$: ARX-annual & 0.133 & 0.134 & 0.121 & 0.653 & 0.616 & 0.879 & 0.121 & 0.33 & 0.324 & 0.297 & 1.67 & 1.435 & 2.359 & 0.301\\
 & Direct$^{4)}$: BVAR$^{3)}$ & 0.2 & 0.201 & 0.184 & 1.069 & 0.859 & 1.537 & 0.221 & 0.328 & 0.33 & 0.303 & 1.735 & 1.425 & 2.491 & 0.305\\
 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.244 & NA & NA & NA & NA & NA & NA & 0.344\\
 & Direct$^{4)}$: BVAR-Mix$^{3)}$ & 0.2 & 0.201 & 0.185 & 1.07 & 0.864 & 1.539 & 0.224 & 0.335 & 0.336 & 0.311 & 1.798 & 1.446 & 2.613 & 0.311\\
\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{0.145} & \cellcolor{gray!15}{0.147} & \cellcolor{gray!15}{0.132} & \cellcolor{gray!15}{0.752} & \cellcolor{gray!15}{0.636} & \cellcolor{gray!15}{1.063} & \cellcolor{gray!15}{0.156} & \cellcolor{gray!15}{\textbf{0.23}} & \cellcolor{gray!15}{\textbf{0.237}} & \cellcolor{gray!15}{\textbf{0.208}} & \cellcolor{gray!15}{\textbf{1.194}} & \cellcolor{gray!15}{\textbf{1.045}} & \cellcolor{gray!15}{\textbf{1.756}} & \cellcolor{gray!15}{\textbf{0.201}}\\
\addlinespace\addlinespace
\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{0.419} & \cellcolor{gray!35}{0.425} & \cellcolor{gray!35}{0.387} & \cellcolor{gray!35}{2.25} & \cellcolor{gray!35}{1.807} & \cellcolor{gray!35}{3.257} & \cellcolor{gray!35}{0.425} & \cellcolor{gray!35}{\textbf{0.506}} & \cellcolor{gray!35}{\textbf{0.518}} & \cellcolor{gray!35}{\textbf{0.466}} & \cellcolor{gray!35}{2.64} & \cellcolor{gray!35}{\textbf{2.254}} & \cellcolor{gray!35}{3.958} & \cellcolor{gray!35}{0.496}\\
\parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Spring, Current}}}
 & AR(1) & 0.454 & 0.46 & 0.405 & 2.319 & 1.958 & 3.243 & 0.441 & 0.816 & 0.829 & 0.742 & 4.292 & 3.487 & 6.189 & 0.699\\
 & AR(p) & 0.464 & 0.47 & 0.438 & 2.401 & 2.024 & 3.395 & 0.473 & 0.739 & 0.751 & 0.676 & 3.91 & 3.186 & 5.617 & 0.649\\
 & BVAR$^{3)}$ & 0.455 & 0.461 & 0.41 & 2.334 & 1.965 & 3.325 & 0.45 & 0.716 & 0.728 & 0.651 & 3.763 & 3.131 & 5.369 & 0.606\\
 & BVAR-Mix$^{3)}$ & 0.458 & 0.465 & 0.412 & 2.365 & 1.977 & 3.342 & 0.453 & 0.697 & 0.709 & 0.637 & 3.66 & 3.06 & 5.175 & 0.594\\
 & Direct$^{4)}$: AR(1) & 0.453 & 0.458 & 0.419 & 2.341 & 2.015 & 3.338 & 0.444 & 0.796 & 0.802 & 0.739 & 4.216 & 3.458 & 6.129 & 0.696\\
 & Direct$^{4)}$: AR(p) & 0.462 & 0.466 & 0.43 & 2.386 & 2.082 & 3.394 & 0.469 & 0.72 & 0.726 & 0.677 & 3.83 & 3.174 & 5.596 & 0.654\\
 & Direct$^{4)}$: AR-annual & 1.03 & 0.988 & 0.899 & 5.178 & 4.25 & 7.352 & 0.987 & 1.714 & 1.617 & 1.563 & 9.008 & 7.057 & 13.625 & 1.681\\
 & Direct$^{4)}$: ARX-annual & 0.474 & 0.462 & 0.424 & 2.402 & 2.024 & 3.413 & 0.476 & 0.529 & \textbf{0.518} & 0.468 & \textbf{2.615} & 2.28 & \textbf{3.667} & 0.511\\
 & Direct$^{4)}$: BVAR$^{3)}$ & 0.456 & 0.462 & 0.426 & 2.358 & 2.064 & 3.352 & 0.458 & 0.69 & 0.695 & 0.637 & 3.625 & 3.026 & 5.164 & 0.59\\
 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.502 & NA & NA & NA & NA & NA & NA & 0.671\\
 & Direct$^{4)}$: BVAR-Mix$^{3)}$ & 0.429 & 0.433 & 0.384 & 2.169 & 1.861 & 3.024 & 0.411 & 0.667 & 0.671 & 0.611 & 3.502 & 2.905 & 4.961 & 0.569\\
\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{\textbf{0.389}} & \cellcolor{gray!15}{\textbf{0.395}} & \cellcolor{gray!15}{\textbf{0.351}} & \cellcolor{gray!15}{\textbf{1.998}} & \cellcolor{gray!15}{\textbf{1.69}} & \cellcolor{gray!15}{\textbf{2.823}} & \cellcolor{gray!15}{\textbf{0.384}} & \cellcolor{gray!15}{0.559} & \cellcolor{gray!15}{0.571} & \cellcolor{gray!15}{0.508} & \cellcolor{gray!15}{2.893} & \cellcolor{gray!15}{2.474} & \cellcolor{gray!15}{4.154} & \cellcolor{gray!15}{\textbf{0.489}}\\
\bottomrule
\end{tabular}
\end{table}

### 2025-04-06 manuscript_plots/revision/extcis_next.tex
automate more elements of table, fix order of footnotes

\begin{table}[!h]
\centering
\caption{Interval Scores with Minimums Highlighted}
\centering
\begin{tabular}[t]{llllllllllllllll}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{7}{c}{{Inflation\hspace*{15mm}}} & \multicolumn{7}{c}{{GDP Growth}} \\
\cmidrule(l{3pt}r{3pt}){3-9} \cmidrule(l{3pt}r{3pt}){10-16}
 &  & $\text{CRPS}^{1)}$-c & $\text{IS}_{W}^{2)}$-c & $\text{IS}_{W,b}^{2)}$-c & $\text{IS}_{U}^{2)}$-c & $\text{IS}_{50}^{2)}$-c & $\text{IS}_{80}^{2)}$-c & $\text{IS}_{\text{CISS}}^{2)}$-c & $\text{CRPS}^{1)}$-g & $\text{IS}_{W}^{2)}$-g & $\text{IS}_{W,b}^{2)}$-g & $\text{IS}_{U}^{2)}$-g & $\text{IS}_{50}^{2)}$-g & $\text{IS}_{80}^{2)}$-g & $\text{IS}_{\text{CISS}}^{2)}$-g\\
\midrule
\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{0.914} & \cellcolor{gray!35}{0.925} & \cellcolor{gray!35}{0.825} & \cellcolor{gray!35}{4.863} & \cellcolor{gray!35}{3.869} & \cellcolor{gray!35}{6.935} & \cellcolor{gray!35}{0.899} & \cellcolor{gray!35}{\textbf{1.173}} & \cellcolor{gray!35}{\textbf{1.189}} & \cellcolor{gray!35}{\textbf{1.128}} & \cellcolor{gray!35}{\textbf{6.475}} & \cellcolor{gray!35}{\textbf{5.105}} & \cellcolor{gray!35}{\textbf{9.732}} & \cellcolor{gray!35}{\textbf{1.188}}\\
\parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Fall, Next}}}
 & AR(1) & 1.056 & 1.071 & 0.904 & 5.08 & 4.581 & 6.653 & 0.977 & 1.494 & 1.514 & 1.367 & 7.944 & 6.368 & 11.43 & 1.368\\
 & AR(p) & 0.955 & 0.968 & 0.851 & 4.903 & 4.147 & 6.713 & 0.9 & 1.427 & 1.446 & 1.32 & 7.689 & 6.109 & 11.154 & 1.328\\
 & BVAR$^{3)}$ & 1.006 & 1.02 & 0.857 & 4.883 & 4.373 & 6.403 & 0.954 & 1.368 & 1.387 & 1.289 & 7.437 & 5.841 & 11.009 & 1.313\\
 & BVAR-Mix$^{3)}$ & 0.876 & 0.888 & \textbf{0.758} & 4.332 & \textbf{3.776} & 5.85 & 0.854 & 1.334 & 1.352 & 1.26 & 7.269 & 5.699 & 10.737 & 1.287\\
 & Direct$^{4)}$: AR(1) & 1.037 & 1.049 & 0.91 & 5.052 & 4.52 & 6.898 & 0.973 & 1.487 & 1.497 & 1.381 & 7.978 & 6.388 & 11.644 & 1.383\\
 & Direct$^{4)}$: AR(p) & 0.93 & 0.938 & 0.844 & 4.689 & 4.136 & 6.546 & 0.88 & 1.417 & 1.427 & 1.34 & 7.701 & 6.16 & 11.392 & 1.349\\
 & Direct$^{4)}$: AR-annual & 1.374 & 1.301 & 1.194 & 6.913 & 5.582 & 9.935 & 1.354 & 1.545 & 1.476 & 1.424 & 8.127 & 6.49 & 12.253 & 1.524\\
 & Direct$^{4)}$: ARX-annual & 1.129 & 1.06 & 0.976 & 5.613 & 4.588 & 8.054 & 1.093 & 1.569 & 1.49 & 1.381 & 7.969 & 6.417 & 11.578 & 1.523\\
 & Direct$^{4)}$: BVAR$^{3)}$ & 0.995 & 1.007 & 0.887 & 4.903 & 4.389 & 6.76 & 0.952 & 1.361 & 1.37 & 1.29 & 7.458 & 5.904 & 11.035 & 1.31\\
 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 1.05 & NA & NA & NA & NA & NA & NA & 1.871\\
 & Direct$^{4)}$: BVAR-Mix$^{3)}$ & \textbf{0.857} & \textbf{0.866} & 0.771 & \textbf{4.215} & 3.86 & \textbf{5.766} & \textbf{0.851} & 1.338 & 1.346 & 1.27 & 7.428 & 5.735 & 11.058 & 1.286\\
\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{0.93} & \cellcolor{gray!15}{0.943} & \cellcolor{gray!15}{0.817} & \cellcolor{gray!15}{4.644} & \cellcolor{gray!15}{4.055} & \cellcolor{gray!15}{6.27} & \cellcolor{gray!15}{0.896} & \cellcolor{gray!15}{1.286} & \cellcolor{gray!15}{1.304} & \cellcolor{gray!15}{1.213} & \cellcolor{gray!15}{7.011} & \cellcolor{gray!15}{5.509} & \cellcolor{gray!15}{10.394} & \cellcolor{gray!15}{1.242}\\
\addlinespace\addlinespace
\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{1.108} & \cellcolor{gray!35}{1.119} & \cellcolor{gray!35}{1.013} & \cellcolor{gray!35}{5.895} & \cellcolor{gray!35}{\textbf{4.741}} & \cellcolor{gray!35}{8.397} & \cellcolor{gray!35}{1.123} & \cellcolor{gray!35}{\textbf{1.25}} & \cellcolor{gray!35}{\textbf{1.271}} & \cellcolor{gray!35}{\textbf{1.204}} & \cellcolor{gray!35}{\textbf{6.878}} & \cellcolor{gray!35}{\textbf{5.481}} & \cellcolor{gray!35}{\textbf{10.366}} & \cellcolor{gray!35}{\textbf{1.267}}\\
\parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Spring, Next}}}
 & AR(1) & 1.377 & 1.396 & 1.142 & 6.349 & 5.952 & 7.923 & 1.195 & 1.769 & 1.791 & 1.587 & 9.22 & 7.521 & 13.037 & 1.6\\
 & AR(p) & 1.113 & 1.126 & 0.975 & 5.683 & 4.767 & 8.025 & 1.057 & 1.757 & 1.781 & 1.608 & 9.347 & 7.532 & 13.432 & 1.667\\
 & BVAR$^{3)}$ & 1.346 & 1.363 & 1.122 & 6.304 & 5.764 & 7.996 & 1.215 & 1.686 & 1.708 & 1.571 & 9.124 & 7.245 & 13.281 & 1.635\\
 & BVAR-Mix$^{3)}$ & 1.126 & 1.141 & 0.962 & 5.408 & 4.86 & 7.137 & 1.06 & 1.635 & 1.656 & 1.535 & 8.874 & 7.051 & 12.98 & 1.607\\
 & Direct$^{4)}$: AR(1) & 1.35 & 1.365 & 1.131 & 6.367 & 5.788 & 8.156 & 1.185 & 1.763 & 1.775 & 1.601 & 9.183 & 7.581 & 13.06 & 1.609\\
 & Direct$^{4)}$: AR(p) & \textbf{1.095} & \textbf{1.106} & 1.002 & 5.63 & 4.804 & 8.023 & 1.061 & 1.719 & 1.731 & 1.579 & 9.111 & 7.365 & 13.16 & 1.646\\
 & Direct$^{4)}$: AR-annual & 1.373 & 1.301 & 1.194 & 6.912 & 5.582 & 9.933 & 1.354 & 1.546 & 1.477 & 1.424 & 8.128 & 6.493 & 12.253 & 1.525\\
 & Direct$^{4)}$: ARX-annual & 1.323 & 1.245 & 1.155 & 6.68 & 5.362 & 9.694 & 1.319 & 1.496 & 1.404 & 1.33 & 7.611 & 6.114 & 11.307 & 1.418\\
 & Direct$^{4)}$: BVAR$^{3)}$ & 1.336 & 1.352 & 1.133 & 6.39 & 5.697 & 8.41 & 1.194 & 1.651 & 1.661 & 1.533 & 8.848 & 7.14 & 12.818 & 1.601\\
 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 1.103 & NA & NA & NA & NA & NA & NA & 1.876\\
 & Direct$^{4)}$: BVAR-Mix$^{3)}$ & \textbf{1.095} & 1.107 & \textbf{0.942} & \textbf{5.254} & 4.804 & \textbf{6.82} & \textbf{1.02} & 1.611 & 1.62 & 1.501 & 8.729 & 6.942 & 12.659 & 1.575\\
\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{1.18} & \cellcolor{gray!15}{1.196} & \cellcolor{gray!15}{0.993} & \cellcolor{gray!15}{5.617} & \cellcolor{gray!15}{5.072} & \cellcolor{gray!15}{7.168} & \cellcolor{gray!15}{1.069} & \cellcolor{gray!15}{1.509} & \cellcolor{gray!15}{1.53} & \cellcolor{gray!15}{1.403} & \cellcolor{gray!15}{8.122} & \cellcolor{gray!15}{6.436} & \cellcolor{gray!15}{11.922} & \cellcolor{gray!15}{1.455}\\
\bottomrule
\end{tabular}
\end{table}

### 2025-04-06 manuscript_plots/revision/extcis_overview_table.R

@@ -79,14 +79,14 @@ crps_qus <- crps |>
 
 scoredat <- rbind(crps_qus, crps_base)
 
-create_latex_table2 <- function(dat){
+create_latex_table2 <- function(dat, mrow){
 
   #round_cols_new <- c("CRPS", "(Weighted) IS",  "Unweighted IS", "IS 50", "IS 80")#,
-                       #"Deviation 50","Deviation 80")
+  #"Deviation 50","Deviation 80")
 
-  round_cols_newer <- c("$\\text{CRPS}^{2)}$", "$\\text{IS}_{W}^{1)}$", "$\\text{IS}_{W,b}^{1)}$", "$\\text{IS}_{U}^{1)}$",
-                        "$\\text{IS}_{50}^{1)}$", "$\\text{IS}_{80}^{1)}$", "$\\text{IS}_{\\text{CISS}}^{1)}$")#,
-                        #"$\\text{Dev}_{50}$", "$\\text{Dev}_{80}$")
+  round_cols_newer <- c("$\\text{CRPS}^{1)}$", "$\\text{IS}_{W}^{2)}$", "$\\text{IS}_{W,b}^{2)}$", "$\\text{IS}_{U}^{2)}$",
+                        "$\\text{IS}_{50}^{2)}$", "$\\text{IS}_{80}^{2)}$", "$\\text{IS}_{\\text{CISS}}^{2)}$")#,
+  #"$\\text{Dev}_{50}$", "$\\text{Dev}_{80}$")
 
   singletab <- lapply(dat, function(dt){
 
@@ -120,7 +120,7 @@ create_latex_table2 <- function(dat){
       .d(, horizon := curr_hor) |>
       setnames(round_cols, round_cols_newer)
 
-    }
+  }
   )|>
     rbindlist() |>
     dcast(model + horizon ~ target, value.var = round_cols_newer)
@@ -132,24 +132,23 @@ create_latex_table2 <- function(dat){
     .d(model != "bvar") |> #exclude original bvar model due to stability issues
     .d(model != "bvar-qu-direct") |>
     .d(model != "bvar-ciss") |>
-    .d(, model := fifelse(model == "ar-direct", "Direct$^{3)}$: AR(1)",
-                          fifelse(model == "ar-annual-direct", "Direct$^{3)}$: AR-annual",
-                                  fifelse(model == "ar-bic-direct", "Direct$^{3)}$: AR(p)",
[…]

### 2025-04-06 manuscript_plots/revision/extcis_current.tex
small cosmetic improvements

@@
 \cmidrule(l{3pt}r{3pt}){3-9} \cmidrule(l{3pt}r{3pt}){10-16}
- &  & $\text{CRPS}^{1)}$-c & $\text{IS}_{W}^{2)}$-c & $\text{IS}_{W,b}^{2)}$-c & $\text{IS}_{U}^{2)}$-c & $\text{IS}_{50}^{2)}$-c & $\text{IS}_{80}^{2)}$-c & $\text{IS}_{\text{CISS}}^{2)}$-c & $\text{CRPS}^{1)}$-g & $\text{IS}_{W}^{2)}$-g & $\text{IS}_{W,b}^{2)}$-g & $\text{IS}_{U}^{2)}$-g & $\text{IS}_{50}^{2)}$-g & $\text{IS}_{80}^{2)}$-g & $\text{IS}_{\text{CISS}}^{2)}$-g\\
+ &  & $\text{CRPS}^{1)}$-gg & $\text{IS}_{W}^{2)}$-gg & $\text{IS}_{W,b}^{2)}$-gg & $\text{IS}_{U}^{2)}$-gg & $\text{IS}_{50}^{2)}$-gg & $\text{IS}_{80}^{2)}$-gg & $\text{IS}_{\text{CISS}}^{2)}$-gg & $\text{CRPS}^{1)}$-cc & $\text{IS}_{W}^{2)}$-cc & $\text{IS}_{W,b}^{2)}$-cc & $\text{IS}_{U}^{2)}$-cc & $\text{IS}_{50}^{2)}$-cc & $\text{IS}_{80}^{2)}$-cc & $\text{IS}_{\text{CISS}}^{2)}$-cc\\
 \midrule
@@
  & Direct$^{4)}$: BVAR$^{3)}$ & 0.2 & 0.201 & 0.184 & 1.069 & 0.859 & 1.537 & 0.221 & 0.328 & 0.33 & 0.303 & 1.735 & 1.425 & 2.491 & 0.305\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.244 & NA & NA & NA & NA & NA & NA & 0.344\\
+ & Direct$^{4)}$: BVAR-CISS$^{3)}$ & -- & -- & -- & -- & -- & -- & 0.244 & -- & -- & -- & -- & -- & -- & 0.344\\
  & Direct$^{4)}$: BVAR-Mix$^{3)}$ & 0.2 & 0.201 & 0.185 & 1.07 & 0.864 & 1.539 & 0.224 & 0.335 & 0.336 & 0.311 & 1.798 & 1.446 & 2.613 & 0.311\\
@@
  & Direct$^{4)}$: BVAR$^{3)}$ & 0.456 & 0.462 & 0.426 & 2.358 & 2.064 & 3.352 & 0.458 & 0.69 & 0.695 & 0.637 & 3.625 & 3.026 & 5.164 & 0.59\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.502 & NA & NA & NA & NA & NA & NA & 0.671\\
+ & Direct$^{4)}$: BVAR-CISS$^{3)}$ & -- & -- & -- & -- & -- & -- & 0.502 & -- & -- & -- & -- & -- & -- & 0.671\\
  & Direct$^{4)}$: BVAR-Mix$^{3)}$ & 0.429 & 0.433 & 0.384 & 2.169 & 1.861 & 3.024 & 0.411 & 0.667 & 0.671 & 0.611 & 3.502 & 2.905 & 4.961 & 0.569\\

### 2025-04-06 manuscript_plots/revision/extcis_next.tex
small cosmetic improvements

@@
  & Direct$^{4)}$: BVAR$^{3)}$ & 0.995 & 1.007 & 0.887 & 4.903 & 4.389 & 6.76 & 0.952 & 1.361 & 1.37 & 1.29 & 7.458 & 5.904 & 11.035 & 1.31\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 1.05 & NA & NA & NA & NA & NA & NA & 1.871\\
+ & Direct$^{4)}$: BVAR-CISS$^{3)}$ & -- & -- & -- & -- & -- & -- & 1.05 & -- & -- & -- & -- & -- & -- & 1.871\\
  & Direct$^{4)}$: BVAR-Mix$^{3)}$ & \textbf{0.857} & \textbf{0.866} & 0.771 & \textbf{4.215} & 3.86 & \textbf{5.766} & \textbf{0.851} & 1.338 & 1.346 & 1.27 & 7.428 & 5.735 & 11.058 & 1.286\\
@@
  & Direct$^{4)}$: BVAR$^{3)}$ & 1.336 & 1.352 & 1.133 & 6.39 & 5.697 & 8.41 & 1.194 & 1.651 & 1.661 & 1.533 & 8.848 & 7.14 & 12.818 & 1.601\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 1.103 & NA & NA & NA & NA & NA & NA & 1.876\\
+ & Direct$^{4)}$: BVAR-CISS$^{3)}$ & -- & -- & -- & -- & -- & -- & 1.103 & -- & -- & -- & -- & -- & -- & 1.876\\
  & Direct$^{4)}$: BVAR-Mix$^{3)}$ & \textbf{1.095} & 1.107 & \textbf{0.942} & \textbf{5.254} & 4.804 & \textbf{6.82} & \textbf{1.02} & 1.611 & 1.62 & 1.501 & 8.729 & 6.942 & 12.659 & 1.575\\

### 2025-04-06 manuscript_plots/revision/extcis_overview_table.R

@@ -155,10 +155,13 @@ create_latex_table2 <- function(dat, mrow){
   maxr <- nrow(singletab)
 
   singletab <- singletab[1:maxr, horizon := ""] |>
-    setnames(paste0(round_cols_newer, "_GDP"), paste0(round_cols_newer, "-g")) |>
-    setnames(paste0(round_cols_newer, "_CPI"), paste0(round_cols_newer, "-c")) |>
+    setnames(paste0(round_cols_newer, "_GDP"), paste0(round_cols_newer, "-cc")) |>
+    setnames(paste0(round_cols_newer, "_CPI"), paste0(round_cols_newer, "-gg")) |>
     setnames("horizon", "")  |>
     setnames("model", "")
+
+  #make NA's look cleaner in final table
+  singletab[is.na(singletab)] <- "--"
 
   dt_latex <- kable(singletab, format = "latex", escape = FALSE, booktabs = TRUE, linesep = c('', '', '', '','','','','','','','','', '\\addlinespace\\addlinespace'),
                     caption = "Interval Scores with Minimums Highlighted") %>%

### 2025-04-06 manuscript_plots/revision/extcis_overview_table.R
change location for saving tables

@@ -163,8 +163,7 @@ create_latex_table2 <- function(dat, mrow){
   #make NA's look cleaner in final table
   singletab[is.na(singletab)] <- "--"
 
-  dt_latex <- kable(singletab, format = "latex", escape = FALSE, booktabs = TRUE, linesep = c('', '', '', '','','','','','','','','', '\\addlinespace\\addlinespace'),
-                    caption = "Interval Scores with Minimums Highlighted") %>%
+  dt_latex <- kable(singletab, format = "latex", escape = FALSE, booktabs = TRUE, linesep = c('', '', '', '','','','','','','','','', '\\addlinespace')) %>%
     kable_styling(latex_options = c("hold_position")) |>
     add_header_above(
       c(" " = 2, "{Inflation\\\\hspace*{15mm}}" = 7, "{GDP Growth}" = 7),
@@ -209,9 +208,9 @@ scoredat_next <- scoredat |>
 table_current <- create_latex_table2(scoredat_current, mrow = "Current")
 table_next <- create_latex_table2(scoredat_next, mrow = "Next")
 
-writeLines(table_current, (here("manuscript_plots", "revision", "extcis_current.tex")))
+writeLines(table_current, (here("manuscript_plots", "revision", "results", "extcis_current.tex")))
 writeLines(table_current, (here("..", "uqimf-manuscript", "tables", "extcis_current.tex")))
 
-writeLines(table_next, (here("manuscript_plots", "revision", "extcis_next.tex")))
+writeLines(table_next, (here("manuscript_plots", "revision", "results", "extcis_next.tex")))
 writeLines(table_next, (here("..", "uqimf-manuscript", "tables", "extcis_next.tex")))
 

### 2025-04-06 manuscript_plots/revision/extctry_overview_table.R

@@ -1,7 +1,8 @@
 library(data.table)
 library(knitr)
 library(kableExtra)
-
+library(here)
+.d <- `[`
 prefix <- "extcntry_"
 
 
@@ -46,8 +47,8 @@ create_latex_table2 <- function(dat, tgt){
   round_cols_new <- c("CRPS", "(Weighted) IS", "Unweighted IS", "IS 50", "IS 80")#,
   #"Deviation 50","Deviation 80")
 
-  round_cols_newer <- c("$\\text{CRPS}$", "$\\text{IS}_{W}$", "$\\text{IS}_{U}$",
-                        "$\\text{IS}_{50}$", "$\\text{IS}_{80}$")#,
+  round_cols_newer <- c("$\\text{CRPS}^{1)}$", "$\\text{IS}_{W,b}^{2)}$", "$\\text{IS}_{U}^{2)}$",
+                        "$\\text{IS}_{50}^{2)}$", "$\\text{IS}_{80}^{2)}$")#,
   #"$\\text{Dev}_{50}$", "$\\text{Dev}_{80}$")
 
   singletab <- lapply(dat, function(dt){
@@ -97,16 +98,17 @@ create_latex_table2 <- function(dat, tgt){
   }
   singletab <- singletab |>
     .d(order(horizon)) |>
-    .d(, model := fifelse(model == "ar-direct", "Direct: AR",
-                          fifelse(model == "ar-annual-direct", "Direct: AR-annual",
-                                  fifelse(model == "ar-bic-direct", "Direct: AR-BIC",
-                                          fifelse(model == "bvar-const-direct", "Direct: BVAR-CP",
-                                                  fifelse(model == "bvar-qu-direct", "Direct: BVAR-SV",
+    #the following is copied over from extcis_overview_table, so some extra models are in this, but the extra ones just won't be used
+    .d(, model := fifelse(model == "ar-direct", "Direct$^{3)}$: AR",
+                          fifelse(model == "ar-annual-direct", "Direct$^{3)}$: AR-annual",
+                                  fifelse(model == "ar-bic-direct", "Direct$^{3)}$: AR-BIC",
+                                          fifelse(model == "bvar-const-direct", "Direct$^{3)}$: BVAR-CP",
+                                                  fifelse(model == "bvar-qu-direct", "Direct$^{3)}$: BVAR-SV",
                                                           fifelse(model == "ar", "AR",
                                                                   fifelse(model == "ar-bic", "AR-BIC",
[…]

### 2025-04-06 manuscript_plots/revision/sens_cov19_scores.R
move sensitivity score analysis

@@ -75,10 +75,10 @@ bvar_scores_cvgshort_ho <- scoreempQu(bvar_qus_ho, cvg_rg = cis100,
 
 
 ######################################Saving#######################################################
-data.table::fwrite(scores_ho, here("revision_plotstables", "cov_19scores", prefix, paste0(global_file_prefix, "ci_scores_ho.csv")))
-data.table::fwrite(scores_avgcountry_ho, here("revision_plotstables", "cov_19scores", prefix, paste0(global_file_prefix, "ci_scores_avgcnt_ho.csv")))
-data.table::fwrite(scores_cvgshort_ho, here("revision_plotstables", "cov_19scores", prefix, paste0(global_file_prefix, "cvg_pooled_ho.csv")))
-data.table::fwrite(bvar_scores_ho, here("revision_plotstables", "cov_19scores", prefix, paste0(global_file_prefix, "bvar_ci_scores_ho.csv")))
-data.table::fwrite(bvar_scores_cvgshort_ho, here("revision_plotstables", "cov_19scores", prefix, paste0(global_file_prefix, "bvar_cvg_pooled_ho.csv")))
-data.table::fwrite(bvar_scores_avgcountry_ho, here("revision_plotstables", "cov_19scores", prefix, paste0(global_file_prefix, "bvar_ci_scores_avgcnt_ho.csv")))
+data.table::fwrite(scores_ho, here("manuscript_plots", "revision", "results", "cov19_scores", prefix, paste0(global_file_prefix, "ci_scores_ho.csv")))
+data.table::fwrite(scores_avgcountry_ho, here("manuscript_plots", "revision", "results", "cov19_scores", prefix, paste0(global_file_prefix, "ci_scores_avgcnt_ho.csv")))
+data.table::fwrite(scores_cvgshort_ho, here("manuscript_plots", "revision", "results", "cov19_scores", prefix, paste0(global_file_prefix, "cvg_pooled_ho.csv")))
+data.table::fwrite(bvar_scores_ho, here("manuscript_plots", "revision", "results", "cov19_scores", prefix, paste0(global_file_prefix, "bvar_ci_scores_ho.csv")))
+data.table::fwrite(bvar_scores_cvgshort_ho, here("manuscript_plots", "revision", "results", "cov19_scores", prefix, paste0(global_file_prefix, "bvar_cvg_pooled_ho.csv")))
[…]

### 2025-04-06 manuscript_plots/revision/sens_cov19_scoretable.R

@@ -7,23 +7,24 @@ library(here)
 prefix <- ""
 
 
-ciscores <- fread(here("revision_plotstables", "cov_19scores", paste0(prefix, "ci_scores_avgcnt_ho.csv")))|>
+ciscores <- fread(here("manuscript_plots", "revision", "results", "cov19_scores", paste0(prefix, "ci_scores_avgcnt_ho.csv")))|>
   .d(, dev_50 := 100*coverage_50 - 50) |>
   .d(, dev_80 := 100*coverage_80 - 80) |>
   .d(, c("model", "target", "horizon", "interval_score", "unweighted_interval_score", "interval_score_50", "interval_score_80", "dev_50", "dev_80")) |>
   .d(, target := ifelse(target == "ngdp_rpch", "GDP", "CPI")) |>
-  .d(model == "IMF")
+  .d(model %in% c("IMF", "bvar_const", "ar")) |>
+  .d(, model := gsub("_", "-", model))
 
 
 
-ciscores2 <- fread(here("revision_plotstables", "cov_19scores", paste0(prefix, "bvar_ci_scores_avgcnt_ho.csv"))) |>
+ciscores2 <- fread(here("manuscript_plots", "revision", "results", "cov19_scores", paste0(prefix, "bvar_ci_scores_avgcnt_ho.csv"))) |>
   .d(, dev_50 := 100*coverage_50 - 50) |>
   .d(, dev_80 := 100*coverage_80 - 80) |>
   .d(, c("model", "target", "horizon", "interval_score", "unweighted_interval_score", "interval_score_50", "interval_score_80", "dev_50", "dev_80")) |>
   .d(, target := ifelse(target == "ngdp_rpch", "GDP", "CPI")) |>
   .d(, model := gsub("_", "-", model)) |>
   .d(, model := paste0(model, "-direct")) |>
-  .d(model %in% c("bvar-const-direct", "ar-direct"))
+  .d(model %in% c("bvar-const-direct"))#, "ar-direct"))
 
 scoredat <- rbind(ciscores, ciscores2)
 
@@ -33,9 +34,9 @@ create_latex_table2 <- function(dat, tgt){
   round_cols_new <- c("(Weighted) IS", "Unweighted IS", "IS 50", "IS 80")#,
   #"Deviation 50","Deviation 80")
 
-  round_cols_newer <- c("$\\text{IS}_{W}$", "$\\text{IS}_{U}$",
[…]

### 2025-04-06 scripts/process-benchmarks.R
extctry: full horizon set for 2013

@@ -194,12 +194,16 @@ if(specs$cset == "base"){
   bvar_qufcs <- NULL
 }
 
-bvar_qufcs_ciss <- data.table::fread(
-here("benchmarks", "raw", "forecasts_March2024.csv")) |>
-  .d(method %in% c("bvar_ciss")) |> #remove Truth and IMF forecasts, and old BVAR
-  .d(, target := ifelse(var == "cpi", "pcpi_pch", "ngdp_rpch")) |>
-  .d(, var := NULL) |>
-  setnames("method", "source")
+if(cset == "base"){
+  bvar_qufcs_ciss <- data.table::fread(
+  here("benchmarks", "raw", "forecasts_March2024.csv")) |>
+    .d(method %in% c("bvar_ciss")) |> #remove Truth and IMF forecasts, and old BVAR
+    .d(, target := ifelse(var == "cpi", "pcpi_pch", "ngdp_rpch")) |>
+    .d(, var := NULL) |>
+    setnames("method", "source")
+} else {
+  bvar_qufcs_ciss <- NULL
+}
 
 ar_qufcs <- fcdat_ar
 

### 2025-04-06 scripts/score-forecasts.R

@@ -120,7 +120,7 @@ bvar_qus_ho <- bvar_qus_ho |>
   .d(,.(country, target, horizon, target_year, true_value, prediction, quantile, source)) |>
   setnames("source", "model")
 
-if(prefix != "_bvarspecs"){ #only score in bvarspecs setting
+if(prefix != "_bvarspecs" & cset == "base"){ #only score in bvarspecs setting
   bvar_qus <- bvar_qus |>
     .d(model != "bvar_ciss")
 
@@ -314,7 +314,9 @@ data.table::fwrite(pp_scores, here("scores", prefix, paste0(global_file_prefix, 
 
 if(prefix != "_bvarspecs"){
   data.table::fwrite(all_crps_ho, here("scores", prefix, paste0(global_file_prefix, "crps_values_ho.csv")))
-  data.table::fwrite(all_crps_ho_byyr, here("scores", prefix, paste0(global_file_prefix, "crps_values_ho_byyr.csv")))
+  if(cset == "base"){
+    data.table::fwrite(all_crps_ho_byyr, here("scores", prefix, paste0(global_file_prefix, "crps_values_ho_byyr.csv")))
+  }
 }
 
 if(cset == "base"){

### 2025-04-10 manuscript_plots/revision/sens_cov19_scores.R
fix reading in of covid scores

@@ -7,7 +7,7 @@ source(here("specs", "specs.R"))
 .d <- `[`
 
 window_length <- specs$window_length
-tgt_yrs <- 2020:2022
+tgt_yrs <- 2020:2023
 
 global_file_prefix <- ""
 prefix <- ""
@@ -35,7 +35,8 @@ if(specs$ciset == "extended"){
 ####################################read in quantile forecasts########################
 
 qufcs_ho <- data.table::fread(here("quantile_forecasts",
-                                   paste0(global_file_prefix, "toscore", prefix, "_quantile_forecasts_ho.csv")))
+                                   paste0(global_file_prefix, "toscore", prefix, "_quantile_forecasts_ho.csv"))) |>
+  .d(target_year %in% tgt_yrs)
 
 
 #################score CI's####################################################
@@ -54,7 +55,8 @@ scores_cvgshort_ho <- scoreempQu(qufcs_ho, cvg_rg = cis100,
 
 bvar_qus_ho <- data.table::fread(here("benchmarks",
                                       paste0(global_file_prefix, "toscore", prefix, "_bvar_direct_quantile_forecasts_ho.csv"))) |>
-  setnames(paste0("tv_", tv_release), "true_value")
+  setnames(paste0("tv_", tv_release), "true_value") |>
+  .d(target_year %in% tgt_yrs)
 
 bvar_qus_ho <- bvar_qus_ho |>
   data.table::copy() |>

### 2025-04-10 manuscript_plots/revision/sens_cov19_scoretable.R

@@ -7,7 +7,7 @@ library(here)
 prefix <- ""
 
 
-ciscores <- fread(here("manuscript_plots", "revision", "results", "cov19_scores", paste0(prefix, "ci_scores_avgcnt_ho.csv")))|>
+ciscores <- fread(here("manuscript_plots", "revision", "results", "cov19_scores", paste0(prefix, "ci_scores_avgcnt_ho.csv"))) |>
   .d(, dev_50 := 100*coverage_50 - 50) |>
   .d(, dev_80 := 100*coverage_80 - 80) |>
   .d(, c("model", "target", "horizon", "interval_score", "unweighted_interval_score", "interval_score_50", "interval_score_80", "dev_50", "dev_80")) |>

### 2025-04-10 manuscript_plots/revision/extcis_overview_table.R
change labeling of AR models

@@ -134,14 +134,14 @@ create_latex_table2 <- function(dat, mrow){
     .d(model != "bvar") |> #exclude original bvar model due to stability issues
     .d(model != "bvar-qu-direct") |>
     .d(model != "bvar-ciss") |>
-    .d(, model := fifelse(model == "ar-direct", "Direct$^{4)}$: AR(1)",
+    .d(, model := fifelse(model == "ar-direct", "Direct$^{4)}$: AR",
                           fifelse(model == "ar-annual-direct", "Direct$^{4)}$: AR-annual",
-                                  fifelse(model == "ar-bic-direct", "Direct$^{4)}$: AR(p)",
+                                  fifelse(model == "ar-bic-direct", "Direct$^{4)}$: AR($p$)",
                                           fifelse(model == "bvar-const-direct", "Direct$^{4)}$: BVAR$^{3)}$",
                                                   fifelse(model == "bvar-ciss-direct", "Direct$^{4)}$: BVAR-CISS$^{3)}$",
-                                                          fifelse(model == "ar", "AR(1)",
+                                                          fifelse(model == "ar", "AR",
                                                                   fifelse(model == "arx-annual-direct", "Direct$^{4)}$: ARX-annual",
-                                                                          fifelse(model == "ar-bic", "AR(p)",
+                                                                          fifelse(model == "ar-bic", "AR($p$)",
                                                                                   fifelse(model == "bvar-ciss", "BVAR-CISS",
                                                                                           fifelse(model == "bvar-const", "BVAR$^{3)}$",
                                                                                                   fifelse(model == "bvar-mix", "BVAR-Mix$^{3)}$",

### 2025-04-15 manuscript_plots/revision/results/extcis_current.tex
change location for saving tables
extctry: full horizon set for 2013
improve layout, extend footnotes move IS scores to own table

--- 2025-04-06 manuscript_plots/revision/extcis_current.tex
@@
 \centering
-\caption{Interval Scores with Minimums Highlighted}
-\centering
-\begin{tabular}[t]{llllllllllllllll}
+\begin{tabular}{llllllllllll}
 \toprule
-\multicolumn{2}{c}{ } & \multicolumn{7}{c}{{Inflation\hspace*{15mm}}} & \multicolumn{7}{c}{{GDP Growth}} \\
-\cmidrule(l{3pt}r{3pt}){3-9} \cmidrule(l{3pt}r{3pt}){10-16}
- &  & $\text{CRPS}^{1)}$-c & $\text{IS}_{W}^{2)}$-c & $\text{IS}_{W,b}^{2)}$-c & $\text{IS}_{U}^{2)}$-c & $\text{IS}_{50}^{2)}$-c & $\text{IS}_{80}^{2)}$-c & $\text{IS}_{\text{CISS}}^{2)}$-c & $\text{CRPS}^{1)}$-g & $\text{IS}_{W}^{2)}$-g & $\text{IS}_{W,b}^{2)}$-g & $\text{IS}_{U}^{2)}$-g & $\text{IS}_{50}^{2)}$-g & $\text{IS}_{80}^{2)}$-g & $\text{IS}_{\text{CISS}}^{2)}$-g\\
+\multicolumn{2}{c}{ } & \multicolumn{5}{c}{{Inflation\hspace*{15mm}}} & \multicolumn{5}{c}{{GDP Growth}} \\
+\cmidrule(l{3pt}r{3pt}){3-7} \cmidrule(l{3pt}r{3pt}){8-12}
+ &  & $\text{CRPS}^{1)}$-cc & $\text{IS}_{W}^{2)}$-cc & $\text{IS}_{W,b}^{2)}$-cc & $\text{IS}_{U}^{2)}$-cc & $\text{IS}_{\text{CISS}}^{2)}$-cc & $\text{CRPS}^{1)}$-gg & $\text{IS}_{W}^{2)}$-gg & $\text{IS}_{W,b}^{2)}$-gg & $\text{IS}_{U}^{2)}$-gg & $\text{IS}_{\text{CISS}}^{2)}$-gg\\
 \midrule
-\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{\textbf{0.103}} & \cellcolor{gray!35}{\textbf{0.106}} & \cellcolor{gray!35}{\textbf{0.093}} & \cellcolor{gray!35}{\textbf{0.522}} & \cellcolor{gray!35}{\textbf{0.46}} & \cellcolor{gray!35}{\textbf{0.741}} & \cellcolor{gray!35}{\textbf{0.089}} & \cellcolor{gray!35}{0.292} & \cellcolor{gray!35}{0.298} & \cellcolor{gray!35}{0.269} & \cellcolor{gray!35}{1.561} & \cellcolor{gray!35}{1.279} & \cellcolor{gray!35}{2.298} & \cellcolor{gray!35}{0.255}\\
+\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{\textbf{0.103}} & \cellcolor{gray!35}{\textbf{0.106}} & \cellcolor{gray!35}{\textbf{0.093}} & \cellcolor{gray!35}{\textbf{0.522}} & \cellcolor{gray!35}{\textbf{0.089}} & \cellcolor{gray!35}{0.292} & \cellcolor{gray!35}{0.298} & \cellcolor{gray!35}{0.269} & \cellcolor{gray!35}{1.561} & \cellcolor{gray!35}{0.255}\\
 \parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Fall, Current}}}
- & AR(1) & 0.195 & 0.198 & 0.177 & 1.034 & 0.839 & 1.484 & 0.214 & 0.337 & 0.344 & 0.298 & 1.697 & 1.485 & 2.355 & 0.302\\
- & AR(p) & 0.183 & 0.185 & 0.166 & 0.978 & 0.783 & 1.449 & 0.203 & 0.333 & 0.34 & 0.296 & 1.688 & 1.466 & 2.39 & 0.3\\
- & BVAR$^{3)}$ & 0.2 & 0.203 & 0.183 & 1.053 & 0.87 & 1.494 & 0.219 & 0.326 & 0.334 & 0.285 & 1.664 & 1.449 & 2.356 & 0.288\\
- & BVAR-Mix$^{3)}$ & 0.198 & 0.201 & 0.182 & 1.042 & 0.86 & 1.47 & 0.218 & 0.323 & 0.33 & 0.284 & 1.642 & 1.417 & 2.311 & 0.287\\
- & Direct$^{4)}$: AR(1) & 0.195 & 0.196 & 0.182 & 1.048 & 0.843 & 1.532 & 0.217 & 0.332 & 0.334 & 0.303 & 1.713 & 1.462 & 2.412 & 0.303\\
- & Direct$^{4)}$: AR(p) & 0.181 & 0.183 & 0.169 & 0.981 & 0.785 & 1.424 & 0.203 & 0.326 & 0.328 & 0.298 & 1.684 & 1.437 & 2.363 & 0.3\\
- & Direct$^{4)}$: AR-annual & 1.03 & 0.988 & 0.899 & 5.179 & 4.252 & 7.355 & 0.987 & 1.711 & 1.613 & 1.56 & 8.995 & 7.043 & 13.599 & 1.678\\
- & Direct$^{4)}$: ARX-annual & 0.133 & 0.134 & 0.121 & 0.653 & 0.616 & 0.879 & 0.121 & 0.33 & 0.324 & 0.297 & 1.67 & 1.435 & 2.359 & 0.301\\
- & Direct$^{4)}$: BVAR$^{3)}$ & 0.2 & 0.201 & 0.184 & 1.069 & 0.859 & 1.537 & 0.221 & 0.328 & 0.33 & 0.303 & 1.735 & 1.425 & 2.491 & 0.305\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.244 & NA & NA & NA & NA & NA & NA & 0.344\\
- & Direct$^{4)}$: BVAR-Mix$^{3)}$ & 0.2 & 0.201 & 0.185 & 1.07 & 0.864 & 1.539 & 0.224 & 0.335 & 0.336 & 0.311 & 1.798 & 1.446 & 2.613 & 0.311\\
-\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{0.145} & \cellcolor{gray!15}{0.147} & \cellcolor{gray!15}{0.132} & \cellcolor{gray!15}{0.752} & \cellcolor{gray!15}{0.636} & \cellcolor{gray!15}{1.063} & \cellcolor{gray!15}{0.156} & \cellcolor{gray!15}{\textbf{0.23}} & \cellcolor{gray!15}{\textbf{0.237}} & \cellcolor{gray!15}{\textbf{0.208}} & \cellcolor{gray!15}{\textbf{1.194}} & \cellcolor{gray!15}{\textbf{1.045}} & \cellcolor{gray!15}{\textbf{1.756}} & \cellcolor{gray!15}{\textbf{0.201}}\\
-\addlinespace\addlinespace
-\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{0.419} & \cellcolor{gray!35}{0.425} & \cellcolor{gray!35}{0.387} & \cellcolor{gray!35}{2.25} & \cellcolor{gray!35}{1.807} & \cellcolor{gray!35}{3.257} & \cellcolor{gray!35}{0.425} & \cellcolor{gray!35}{\textbf{0.506}} & \cellcolor{gray!35}{\textbf{0.518}} & \cellcolor{gray!35}{\textbf{0.466}} & \cellcolor{gray!35}{2.64} & \cellcolor{gray!35}{\textbf{2.254}} & \cellcolor{gray!35}{3.958} & \cellcolor{gray!35}{0.496}\\
+ & AR$^{3)}$ & 0.195 & 0.198 & 0.177 & 1.034 & 0.214 & 0.337 & 0.344 & 0.298 & 1.697 & 0.302\\
+ & AR($p$)$^{3)}$ & 0.183 & 0.185 & 0.166 & 0.978 & 0.203 & 0.333 & 0.34 & 0.296 & 1.688 & 0.3\\
+ & BVAR$^{4)}$ & 0.2 & 0.203 & 0.183 & 1.053 & 0.219 & 0.326 & 0.334 & 0.285 & 1.664 & 0.288\\
+ & BVAR-Mix$^{4)}$ & 0.198 & 0.201 & 0.182 & 1.042 & 0.218 & 0.323 & 0.33 & 0.284 & 1.642 & 0.287\\
+ & Direct$^{5)}$: AR$^{3)}$ & 0.195 & 0.196 & 0.182 & 1.048 & 0.217 & 0.332 & 0.334 & 0.303 & 1.713 & 0.303\\
+ & Direct$^{5)}$: AR($p$)$^{3)}$ & 0.181 & 0.183 & 0.169 & 0.981 & 0.203 & 0.326 & 0.328 & 0.298 & 1.684 & 0.3\\
+ & Direct$^{5)}$: AR-annual$^{3)}$ & 0.984 & 0.988 & 0.899 & 5.179 & 0.987 & 1.604 & 1.613 & 1.56 & 8.995 & 1.678\\
+ & Direct$^{5)}$: ARX-annual$^{3)}$ & 0.133 & 0.134 & 0.121 & 0.653 & 0.121 & 0.321 & 0.324 & 0.297 & 1.67 & 0.301\\
+ & Direct$^{5)}$: BVAR$^{4)}$ & 0.2 & 0.201 & 0.184 & 1.069 & 0.221 & 0.328 & 0.33 & 0.303 & 1.735 & 0.305\\
+ & Direct$^{5)}$: BVAR-CISS$^{4)}$ & -- & -- & -- & -- & 0.244 & -- & -- & -- & -- & 0.344\\
+ & Direct$^{5)}$: BVAR-Mix$^{4)}$ & 0.2 & 0.201 & 0.185 & 1.07 & 0.224 & 0.335 & 0.336 & 0.311 & 1.798 & 0.311\\
+\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{6)}$} & \cellcolor{gray!15}{0.145} & \cellcolor{gray!15}{0.147} & \cellcolor{gray!15}{0.132} & \cellcolor{gray!15}{0.752} & \cellcolor{gray!15}{0.156} & \cellcolor{gray!15}{\textbf{0.23}} & \cellcolor{gray!15}{\textbf{0.237}} & \cellcolor{gray!15}{\textbf{0.208}} & \cellcolor{gray!15}{\textbf{1.194}} & \cellcolor{gray!15}{\textbf{0.201}}\\
+\addlinespace
+\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{0.419} & \cellcolor{gray!35}{0.425} & \cellcolor{gray!35}{0.387} & \cellcolor{gray!35}{2.25} & \cellcolor{gray!35}{0.425} & \cellcolor{gray!35}{\textbf{0.506}} & \cellcolor{gray!35}{\textbf{0.518}} & \cellcolor{gray!35}{\textbf{0.466}} & \cellcolor{gray!35}{2.64} & \cellcolor{gray!35}{0.496}\\
 \parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Spring, Current}}}
- & AR(1) & 0.454 & 0.46 & 0.405 & 2.319 & 1.958 & 3.243 & 0.441 & 0.816 & 0.829 & 0.742 & 4.292 & 3.487 & 6.189 & 0.699\\
- & AR(p) & 0.464 & 0.47 & 0.438 & 2.401 & 2.024 & 3.395 & 0.473 & 0.739 & 0.751 & 0.676 & 3.91 & 3.186 & 5.617 & 0.649\\
- & BVAR$^{3)}$ & 0.455 & 0.461 & 0.41 & 2.334 & 1.965 & 3.325 & 0.45 & 0.716 & 0.728 & 0.651 & 3.763 & 3.131 & 5.369 & 0.606\\
- & BVAR-Mix$^{3)}$ & 0.458 & 0.465 & 0.412 & 2.365 & 1.977 & 3.342 & 0.453 & 0.697 & 0.709 & 0.637 & 3.66 & 3.06 & 5.175 & 0.594\\
- & Direct$^{4)}$: AR(1) & 0.453 & 0.458 & 0.419 & 2.341 & 2.015 & 3.338 & 0.444 & 0.796 & 0.802 & 0.739 & 4.216 & 3.458 & 6.129 & 0.696\\
- & Direct$^{4)}$: AR(p) & 0.462 & 0.466 & 0.43 & 2.386 & 2.082 & 3.394 & 0.469 & 0.72 & 0.726 & 0.677 & 3.83 & 3.174 & 5.596 & 0.654\\
- & Direct$^{4)}$: AR-annual & 1.03 & 0.988 & 0.899 & 5.178 & 4.25 & 7.352 & 0.987 & 1.714 & 1.617 & 1.563 & 9.008 & 7.057 & 13.625 & 1.681\\
- & Direct$^{4)}$: ARX-annual & 0.474 & 0.462 & 0.424 & 2.402 & 2.024 & 3.413 & 0.476 & 0.529 & \textbf{0.518} & 0.468 & \textbf{2.615} & 2.28 & \textbf{3.667} & 0.511\\
- & Direct$^{4)}$: BVAR$^{3)}$ & 0.456 & 0.462 & 0.426 & 2.358 & 2.064 & 3.352 & 0.458 & 0.69 & 0.695 & 0.637 & 3.625 & 3.026 & 5.164 & 0.59\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.502 & NA & NA & NA & NA & NA & NA & 0.671\\
- & Direct$^{4)}$: BVAR-Mix$^{3)}$ & 0.429 & 0.433 & 0.384 & 2.169 & 1.861 & 3.024 & 0.411 & 0.667 & 0.671 & 0.611 & 3.502 & 2.905 & 4.961 & 0.569\\
-\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{\textbf{0.389}} & \cellcolor{gray!15}{\textbf{0.395}} & \cellcolor{gray!15}{\textbf{0.351}} & \cellcolor{gray!15}{\textbf{1.998}} & \cellcolor{gray!15}{\textbf{1.69}} & \cellcolor{gray!15}{\textbf{2.823}} & \cellcolor{gray!15}{\textbf{0.384}} & \cellcolor{gray!15}{0.559} & \cellcolor{gray!15}{0.571} & \cellcolor{gray!15}{0.508} & \cellcolor{gray!15}{2.893} & \cellcolor{gray!15}{2.474} & \cellcolor{gray!15}{4.154} & \cellcolor{gray!15}{\textbf{0.489}}\\
+ & AR$^{3)}$ & 0.454 & 0.46 & 0.405 & 2.319 & 0.441 & 0.816 & 0.829 & 0.742 & 4.292 & 0.699\\
+ & AR($p$)$^{3)}$ & 0.464 & 0.47 & 0.438 & 2.401 & 0.473 & 0.739 & 0.751 & 0.676 & 3.91 & 0.649\\
+ & BVAR$^{4)}$ & 0.455 & 0.461 & 0.41 & 2.334 & 0.45 & 0.716 & 0.728 & 0.651 & 3.763 & 0.606\\
+ & BVAR-Mix$^{4)}$ & 0.458 & 0.465 & 0.412 & 2.365 & 0.453 & 0.697 & 0.709 & 0.637 & 3.66 & 0.594\\
+ & Direct$^{5)}$: AR$^{3)}$ & 0.453 & 0.458 & 0.419 & 2.341 & 0.444 & 0.796 & 0.802 & 0.739 & 4.216 & 0.696\\
+ & Direct$^{5)}$: AR($p$)$^{3)}$ & 0.462 & 0.466 & 0.43 & 2.386 & 0.469 & 0.72 & 0.726 & 0.677 & 3.83 & 0.654\\
+ & Direct$^{5)}$: AR-annual$^{3)}$ & 0.983 & 0.988 & 0.899 & 5.178 & 0.987 & 1.607 & 1.617 & 1.563 & 9.008 & 1.681\\
+ & Direct$^{5)}$: ARX-annual$^{3)}$ & 0.46 & 0.462 & 0.424 & 2.402 & 0.476 & 0.514 & \textbf{0.518} & 0.468 & \textbf{2.615} & 0.511\\
+ & Direct$^{5)}$: BVAR$^{4)}$ & 0.456 & 0.462 & 0.426 & 2.358 & 0.458 & 0.69 & 0.695 & 0.637 & 3.625 & 0.59\\
+ & Direct$^{5)}$: BVAR-CISS$^{4)}$ & -- & -- & -- & -- & 0.502 & -- & -- & -- & -- & 0.671\\
+ & Direct$^{5)}$: BVAR-Mix$^{4)}$ & 0.429 & 0.433 & 0.384 & 2.169 & 0.411 & 0.667 & 0.671 & 0.611 & 3.502 & 0.569\\
+\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{6)}$} & \cellcolor{gray!15}{\textbf{0.389}} & \cellcolor{gray!15}{\textbf{0.395}} & \cellcolor{gray!15}{\textbf{0.351}} & \cellcolor{gray!15}{\textbf{1.998}} & \cellcolor{gray!15}{\textbf{0.384}} & \cellcolor{gray!15}{0.559} & \cellcolor{gray!15}{0.571} & \cellcolor{gray!15}{0.508} & \cellcolor{gray!15}{2.893} & \cellcolor{gray!15}{\textbf{0.489}}\\
 \bottomrule

### 2025-04-15 manuscript_plots/revision/extcis_isref_table.R

@@ -1,0 +1,157 @@
+library(data.table)
+library(knitr)
+library(kableExtra)
+
+prefix <- "extcis_"
+
+
+ciscores <- fread(here("scores", paste0(prefix, "ci_scores_avgcnt_ho_is.csv"))) |>
+  .d(, dev_50 := 100*coverage_50 - 50) |>
+  .d(, dev_80 := 100*coverage_80 - 80) |>
+  .d(, c("model", "target", "horizon", "interval_score_30", "interval_score_50", "interval_score_80", "interval_score_90")) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP", "CPI")) |>
+  .d(model %in% c("IMF", "ar", "bvar_const")) |>
+  .d(, model := gsub("_", "-", model))
+
+ciscores2 <- fread(here("scores", paste0(prefix, "bvar_ci_scores_avgcnt_ho_is.csv"))) |>
+  .d(, c("model", "target", "horizon", "interval_score_30", "interval_score_50", "interval_score_80", "interval_score_90")) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP", "CPI")) |>
+  .d(model == "bvar_const") |>
+  .d(, model := gsub("_", "-", model)) |>
+  .d(, model := paste0(model, "-direct"))
+
+scoredat <- rbind(ciscores, ciscores2)
+
+create_latex_table2 <- function(dat, mrow){
+
+  #round_cols_new <- c("CRPS", "(Weighted) IS",  "Unweighted IS", "IS 50", "IS 80")#,
+  #"Deviation 50","Deviation 80")
+
+  round_cols_newer <- c("$\\text{IS}_{30}^{1)}$", "$\\text{IS}_{50}^{1)}$", "$\\text{IS}_{80}^{1)}$", "$\\text{IS}_{90}^{1)}$")#,
+  #"$\\text{Dev}_{50}$", "$\\text{Dev}_{80}$")
+
+  singletab <- lapply(dat, function(dt){
+
+    curr_hor <- dt$horizon
+    curr_tgt <- dt$target
+
+    round_cols <- c("interval_score_30", "interval_score_50", "interval_score_80", "interval_score_90")#, "dev_50", "dev_80")
+    #round_cols_extra <- c("dev_50", "dev_80")
+
+    dt[, (round_cols) := lapply(.SD, round, 2), .SDcols = round_cols]
[…]

### 2025-04-15 manuscript_plots/revision/extcis_overview_table.R

@@ -87,7 +87,8 @@ create_latex_table2 <- function(dat, mrow){
   #"Deviation 50","Deviation 80")
 
   round_cols_newer <- c("$\\text{CRPS}^{1)}$", "$\\text{IS}_{W}^{2)}$", "$\\text{IS}_{W,b}^{2)}$", "$\\text{IS}_{U}^{2)}$",
-                        "$\\text{IS}_{50}^{2)}$", "$\\text{IS}_{80}^{2)}$", "$\\text{IS}_{\\text{CISS}}^{2)}$")#,
+                        #"$\\text{IS}_{50}^{2)}$", "$\\text{IS}_{80}^{2)}$",
+                        "$\\text{IS}_{\\text{CISS}}^{2)}$")#,
   #"$\\text{Dev}_{50}$", "$\\text{Dev}_{80}$")
 
   singletab <- lapply(dat, function(dt){
@@ -95,7 +96,7 @@ create_latex_table2 <- function(dat, mrow){
     curr_hor <- dt$horizon
     curr_tgt <- dt$target
 
-    round_cols <- c("crps", "interval_score", "base_interval_score", "unweighted_interval_score", "interval_score_50", "interval_score_80", "ciss_interval_score")#, "dev_50", "dev_80")
+    round_cols <- c("crps", "interval_score", "base_interval_score", "unweighted_interval_score", "ciss_interval_score")#, "dev_50", "dev_80")
     #round_cols_extra <- c("dev_50", "dev_80")
 
     dt[, (round_cols) := lapply(.SD, round, 3), .SDcols = round_cols]
@@ -134,31 +135,31 @@ create_latex_table2 <- function(dat, mrow){
     .d(model != "bvar") |> #exclude original bvar model due to stability issues
     .d(model != "bvar-qu-direct") |>
     .d(model != "bvar-ciss") |>
-    .d(, model := fifelse(model == "ar-direct", "Direct$^{4)}$: AR",
-                          fifelse(model == "ar-annual-direct", "Direct$^{4)}$: AR-annual",
-                                  fifelse(model == "ar-bic-direct", "Direct$^{4)}$: AR($p$)",
-                                          fifelse(model == "bvar-const-direct", "Direct$^{4)}$: BVAR$^{3)}$",
-                                                  fifelse(model == "bvar-ciss-direct", "Direct$^{4)}$: BVAR-CISS$^{3)}$",
-                                                          fifelse(model == "ar", "AR",
[…]

### 2025-04-15 manuscript_plots/revision/base_is5080table.R
table for base weighted is

@@ -1,0 +1,155 @@
+library(data.table)
+library(knitr)
+library(kableExtra)
+
+prefix <- "extcis_"
+
+
+ciscores <- fread(here("scores", paste0("ci_scores_avgcnt_ho.csv"))) |>
+  .d(, c("model", "target", "horizon", "interval_score_50", "interval_score_80")) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP", "CPI")) |>
+  .d(model %in% c("IMF", "ar", "bvar_const")) |>
+  .d(, model := gsub("_", "-", model))
+
+ciscores2 <- fread(here("scores", paste0("bvar_ci_scores_avgcnt_ho.csv"))) |>
+  .d(, c("model", "target", "horizon", "interval_score_50", "interval_score_80")) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP", "CPI")) |>
+  .d(model == "bvar_const") |>
+  .d(, model := gsub("_", "-", model)) |>
+  .d(, model := paste0(model, "-direct"))
+
+scoredat <- rbind(ciscores, ciscores2)
+
+create_latex_table2 <- function(dat, mrow){
+
+  #round_cols_new <- c("CRPS", "(Weighted) IS",  "Unweighted IS", "IS 50", "IS 80")#,
+  #"Deviation 50","Deviation 80")
+
+  round_cols_newer <- c("$\\text{IS}_{50}^{1)}$", "$\\text{IS}_{80}^{1)}$")#,
+  #"$\\text{Dev}_{50}$", "$\\text{Dev}_{80}$")
+
+  singletab <- lapply(dat, function(dt){
+
+    curr_hor <- dt$horizon
+    curr_tgt <- dt$target
+
+    round_cols <- c("interval_score_50", "interval_score_80")#, "dev_50", "dev_80")
+    #round_cols_extra <- c("dev_50", "dev_80")
+
+    dt[, (round_cols) := lapply(.SD, round, 2), .SDcols = round_cols]
+    #dt[, (round_cols_extra) := lapply(.SD, round, 2), .SDcols = round_cols_extra]
+
+    # Compute minimum values per horizon, with special handling for deviation
+    min_vals <- dt[, lapply(.SD, function(x) min(abs(x), na.rm = TRUE)), by = horizon, .SDcols = round_cols]
+    setnames(min_vals, old = round_cols, new = paste0("min_", round_cols))  # Rename min columns
+
[…]

### 2025-04-15 revision_plotstables/dir_vs_absolute_plot1.R
appendix plot directional, us inflation

@@ -252,4 +252,4 @@ ovrplot <- (plot_de + plot_ca) /
   (plot_it + plot_uk)
 }
 plot_de
-ggsave(here("revision_plotstables", "dirvsabs_plot1.pdf"), plot_de, width = 10, height = 7)
+ggsave(here("revision_plotstables", "dirvsabs_plot_usa.pdf"), plot_de, width = 10, height = 7)

### 2025-04-15 revision_plotstables/dir_vs_absolute_plot2.R

@@ -15,9 +15,11 @@ tgt <- "pcpi_pch"
 yr <- 2001
 hr <- 1
 rw <- 11
+textsize_y <- 18
+suffix <- "_directional"
 
 qufcs_dir <- data.table::fread(here("quantile_forecasts",
-                                    paste0("toscore", "", "_quantile_forecasts_directional.csv"))) |>
+                                    paste0("toscore", "", "_quantile_forecasts", suffix, ".csv"))) |>
   .d(country == ctry & target == tgt & horizon == hr) |>
   .d(target_year == yr) |>
   .d(source == "IMF")
@@ -25,13 +27,30 @@ qufcs_dir <- data.table::fread(here("quantile_forecasts",
 errordat2 <- fread(here("data", "weodat.csv")) |>
   .d(, fc_error := prediction - tv_1) |>
   .d(country == ctry & target == tgt & horizon == hr) |>
-  .d(target_year %in% seq(yr-(rw+floor(hr)), yr+5, 1))
+  .d(target_year %in% seq(yr-(rw+floor(hr)), yr+11, 1))
 
 qufcs_dir <- data.table::fread(here("quantile_forecasts",
-                                    paste0("toscore", "", "_quantile_forecasts_directional.csv"))) |>
+                                    paste0("toscore", "", "_quantile_forecasts", suffix, ".csv"))) |>
   .d(country == ctry & target == tgt & horizon == hr) |>
-  .d(target_year %in% yr:(yr+5)) |>
+  .d(target_year %in% (yr+1):(yr+11)) |>
   .d(source == "IMF")
+
+#Define segment function
+geom_segment_arrow <- function(x, y, xend, yend = y,
+                               lineend = "butt", linejoin = "round",
+                               color = "grey80", alpha = 0.8,
+                               linetype = "dashed", size = 0.25,
+                               arrow = NULL) {
+
+  geom_segment(
+    aes(x = x, y = y, xend = xend, yend = yend),
+    lineend = "butt", linejoin = "round",
+    color = "black", alpha = 1,
+    size = 0.5, arrow = arrow(length = unit(0.075, "inches"))
+  )
+}
+
+mycol <- met.brewer("Hokusai1", n = 7)[7]
 
 getlinerangedat2 <- function(dat, xpos){
 
@@ -56,28 +75,44 @@ errordat3$fc_error |> sort() |> quantile(c(0.1, 0.25, 0.75, 0.9))
 
[…]

### 2025-04-17 manuscript_plots/revision/base_is5080table.R
tables/plots: unify target and model labels

@@ -106,7 +106,7 @@ create_latex_table2 <- function(dat, mrow){
   dt_latex <- kable(singletab, format = "latex", escape = FALSE, booktabs = TRUE, linesep = c('', '', '', '\\addlinespace','', '', '', '\\addlinespace','', '', '', '\\addlinespace','', '', '')) %>%
     kable_styling(latex_options = c("hold_position")) |>
     add_header_above(
-      c(" " = 2, "{Inflation}" = 2, "{real GDP Growth}" = 2),
+      c(" " = 2, "{Inflation}" = 2, "{GDP Growth}" = 2),
       escape = FALSE
     )
   dt_latex <- dt_latex  |>

### 2025-04-17 manuscript_plots/revision/extcis_isref_table.R

@@ -77,15 +77,15 @@ create_latex_table2 <- function(dat, mrow){
     .d(, model := fifelse(model == "ar-direct", "Direct$^{2)}$: AR",
                           fifelse(model == "ar-annual-direct", "Direct$^{2)}$: AR-annual",
                                   fifelse(model == "ar-bic-direct", "Direct$^{2)}$: AR(p)",
-                                          fifelse(model == "bvar-const-direct", "Direct$^{2)}$: BVAR$$",
-                                                  fifelse(model == "bvar-ciss-direct", "Direct$^{2)}$: BVAR-CISS$$",
+                                          fifelse(model == "bvar-const-direct", "Direct$^{2)}$: BVAR",
+                                                  fifelse(model == "bvar-ciss-direct", "Direct$^{2)}$: BVAR-CISS",
                                                           fifelse(model == "ar", "AR",
                                                                   fifelse(model == "arx-annual-direct", "Direct$^{2)}$: ARX-annual",
                                                                           fifelse(model == "ar-bic", "AR(p)",
                                                                                   fifelse(model == "bvar-ciss", "BVAR-CISS",
-                                                                                          fifelse(model == "bvar-const", "BVAR$$",
-                                                                                                  fifelse(model == "bvar-mix", "BVAR-Mix$$",
-                                                                                                          fifelse(model == "bvar-mix-direct", "Direct$^{2)}$: BVAR-Mix$$",
+                                                                                          fifelse(model == "bvar-const", "BVAR",
+                                                                                                  fifelse(model == "bvar-mix", "BVAR-Mix",
+                                                                                                          fifelse(model == "bvar-mix-direct", "Direct$^{2)}$: BVAR-Mix",
                                                                                                                   fifelse(model == "mean-ensemble", "ZEnsemble",
                                                                                                                           fifelse(model == "IMF", "AAAIMF", model))))))))))))))) |>
     .d(order(horizon, model)) |>
@@ -108,7 +108,7 @@ create_latex_table2 <- function(dat, mrow){
   dt_latex <- kable(singletab, format = "latex", escape = FALSE, booktabs = TRUE, linesep = c('', '', '', '\\addlinespace','', '', '', '\\addlinespace','', '', '', '\\addlinespace','', '', '')) %>%
     kable_styling(latex_options = c("hold_position")) |>
     add_header_above(
[…]

### 2025-04-17 manuscript_plots/revision/extcis_qucvgplot.R

@@ -11,7 +11,7 @@ prefix <- "extcis_"
 ciscores <- fread(here("scores", paste0(prefix, "cvg_pooled_ho.csv"))) |>
   .d(model != "bvar") |> #filter out SV BVAR model (not used anymore)
   .d(, c("model", "target", paste0("qucoverage_", c(seq(5,45, by = 5), seq(55,95, by = 5))))) |>
-  .d(, target := ifelse(target == "ngdp_rpch", "real GDP Growth", "Inflation")) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP Growth", "Inflation")) |>
   .d(, model := gsub("_", "", model)) |>
   melt(id.vars = c("model", "target"), variable.name = "lvl", value.name = "cvg") |>
   .d(,lvl := as.numeric(substr(lvl, 12, 20)))
@@ -19,14 +19,14 @@ ciscores <- fread(here("scores", paste0(prefix, "cvg_pooled_ho.csv"))) |>
 ciscores2 <- fread(here("scores", paste0(prefix, "bvar_cvg_pooled_ho.csv"))) |>
   .d(model != "bvar_qu") |> #filter out SV BVAR model (not used anymore)
   .d(, c("model", "target", paste0("qucoverage_", c(seq(5,45, by = 5), seq(55,95, by = 5))))) |>
-  .d(, target := ifelse(target == "ngdp_rpch", "real GDP Growth", "Inflation")) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP Growth", "Inflation")) |>
   .d(, model := gsub("_", "", model)) |>
   .d(, model := paste0(model, "-direct")) |>
   melt(id.vars = c("model", "target"), variable.name = "lvl", value.name = "cvg") |>
   .d(,lvl := as.numeric(substr(lvl, 12, 20)))
 
 ciscores_perfect <- data.table(model = rep("nominal", 18),
-                               target = rep("real GDP Growth", 18),
+                               target = rep("GDP Growth", 18),
                                lvl = c(seq(5,45, by = 5), seq(55,95, by = 5)),
                                cvg = c(seq(5,45, by = 5), seq(55,95, by = 5))/100)
 
@@ -41,7 +41,7 @@ ciscores1 <- rbind(ciscores, ciscores_perfect) |>
   .d(, model := fifelse(model == "ar-direct", "Direct: AR",
                         fifelse(model == "arannual-direct", "Direct: AR-annual",
[…]

### 2025-04-17 manuscript_plots/revision/sens_cov19_scoretable.R

@@ -89,12 +89,12 @@ create_latex_table2 <- function(dat, tgt){
     .d(, model := fifelse(model == "ar-direct", "Direct: AR",
                           fifelse(model == "ar-annual-direct", "Direct: AR-annual",
                                   fifelse(model == "ar-bic-direct", "Direct: AR-BIC",
-                                          fifelse(model == "bvar-const-direct", "Direct: BVAR-Const.",
+                                          fifelse(model == "bvar-const-direct", "Direct: BVAR",
                                                   fifelse(model == "bvar-qu-direct", "Direct: BVAR-SV",
                                                           fifelse(model == "ar", "AR",
                                                                   fifelse(model == "ar-bic", "AR-BIC",
                                                                           fifelse(model == "bvar", "BVAR-SV",
-                                                                                  fifelse(model == "bvar-const", "BVAR-Const.",
+                                                                                  fifelse(model == "bvar-const", "BVAR",
                                                                                           fifelse(model == "arx-annual-direct", "Direct: ARX-annual",
                                                                                                   fifelse(model == "mean-ensemble", "AAEnsemble",
                                                                                                           fifelse(model == "IMF", "AAAIMF", model))))))))))))) |>

### 2025-04-29 benchmarks/raw/forecasts_2025/draft_table.tex

\documentclass[11pt]{article}
\usepackage{booktabs,natbib,graphicx}

\begin{document}

\section*{Draft table for additional benchmarks}

\begin{table}[htbp]	
\centering
\begin{tabular}{lcccc}
& Fall,&  Spring,  & 
Fall, & Spring, \\ 
& Current & Current & Next & Next \\ \toprule
IMF & & & & \\ \midrule
AR(1) & & & & \\	
AR(1) -- direct & & & & \\	
AR($p$) & & & & \\	
AR($p$) -- direct & & & & \\	
SV-BVAR & & & & \\	
SV-BVAR -- direct & & & & \\	
SV-BVAR -- direct+CISS & & & & \\	
BVAR & & & & \\	
BVAR -- direct & & & & \\	
BVAR -- direct+CISS & & & & \\\bottomrule
\end{tabular}
\caption{Inflation: Average interval scores over all countries.}
\end{table}

\begin{table}[htbp]	
	\centering
	\begin{tabular}{lcccc}
		& Fall,&  Spring,  & 
		Fall, & Spring, \\ 
		& Current & Current & Next & Next \\ \toprule
		IMF & & & & \\ \midrule
		AR(1) & & & & \\	
		AR(1) -- direct & & & & \\	
		AR($p$) & & & & \\	
		AR($p$) -- direct & & & & \\	
		SV-BVAR & & & & \\	
		SV-BVAR -- direct & & & & \\	
		SV-BVAR -- direct+CISS & & & & \\	
		BVAR & & & & \\	
		BVAR -- direct & & & & \\	
		BVAR -- direct+CISS & & & & \\\bottomrule
	\end{tabular}
	\caption{GDP growth: Average interval scores over all countries.}
\end{table}

\begin{itemize}
	\item If we include CISS here, we might drop Figure 10 from paper. 
	\item Does BVAR-CISS in Figure 10 refer to the direct or standard version of BVAR? In the former case, it should be called BVAR-direct+CISS 
\end{itemize}

\section*{Text snippets}

In the main paper, we consider an AR(1) benchmark model, with forecast distributions constructed based on past forecast errors as for the IMF method. Here we consider additional variants of the AR model.

First, we consider choosing the AR lag length $p$ based on the \cite{Schwarz1978} information criterion as stated in Equation 4.3.9 of \cite{Luetkepohl2005} and discussed in Section 4.3 of the latter reference. Figure \ref{fig:lag_length_choice} provides an overview of the lag orders chosen in the empirical analysis. While we allowed for a maximal lag order of eight, the largest order chosen in practice was six. For inflation, lag orders between three and five are most common, whereas choices for GDP are clearly smaller, with one being the most popular and three being the maximal choice.

Second, we consider using the analytical forecast distribution implied by the AR model, as opposed to the empirical distribution of its past forecast errors. We call this approach AR--direct, in analogy to our procedure for the BVAR.

\begin{figure}
\includegraphics[width =\textwidth]{ar_lag_length_choice.pdf}
\caption{Empirical frequency of lag length choices $p \in \{1, 2, \ldots, 6\}$ in the AR($p$) model, separately for inflation and GDP growth. Frequencies are pooled across the G7 countries as well as all forecasting years and the spring and fall seasons. \label{fig:lag_length_choice}}
\end{figure}

\bibliographystyle{ecta}
\bibliography{references}

\end{document}

### 2025-04-29 manuscript_plots/revision/results/extcis_next.tex
change location for saving tables
extctry: full horizon set for 2013

--- 2025-04-06 manuscript_plots/revision/extcis_next.tex
@@
 \centering
-\caption{Interval Scores with Minimums Highlighted}
-\centering
-\begin{tabular}[t]{llllllllllllllll}
+\begin{tabular}{llllllllllll}
 \toprule
-\multicolumn{2}{c}{ } & \multicolumn{7}{c}{{Inflation\hspace*{15mm}}} & \multicolumn{7}{c}{{GDP Growth}} \\
-\cmidrule(l{3pt}r{3pt}){3-9} \cmidrule(l{3pt}r{3pt}){10-16}
- &  & $\text{CRPS}^{1)}$-c & $\text{IS}_{W}^{2)}$-c & $\text{IS}_{W,b}^{2)}$-c & $\text{IS}_{U}^{2)}$-c & $\text{IS}_{50}^{2)}$-c & $\text{IS}_{80}^{2)}$-c & $\text{IS}_{\text{CISS}}^{2)}$-c & $\text{CRPS}^{1)}$-g & $\text{IS}_{W}^{2)}$-g & $\text{IS}_{W,b}^{2)}$-g & $\text{IS}_{U}^{2)}$-g & $\text{IS}_{50}^{2)}$-g & $\text{IS}_{80}^{2)}$-g & $\text{IS}_{\text{CISS}}^{2)}$-g\\
+\multicolumn{2}{c}{ } & \multicolumn{5}{c}{{Inflation\hspace*{15mm}}} & \multicolumn{5}{c}{{GDP Growth}} \\
+\cmidrule(l{3pt}r{3pt}){3-7} \cmidrule(l{3pt}r{3pt}){8-12}
+ &  & $\text{CRPS}^{1)}$-cc & $\text{IS}_{W}^{2)}$-cc & $\text{IS}_{W,b}^{2)}$-cc & $\text{IS}_{U}^{2)}$-cc & $\text{IS}_{\text{CISS}}^{2)}$-cc & $\text{CRPS}^{1)}$-gg & $\text{IS}_{W}^{2)}$-gg & $\text{IS}_{W,b}^{2)}$-gg & $\text{IS}_{U}^{2)}$-gg & $\text{IS}_{\text{CISS}}^{2)}$-gg\\
 \midrule
-\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{0.914} & \cellcolor{gray!35}{0.925} & \cellcolor{gray!35}{0.825} & \cellcolor{gray!35}{4.863} & \cellcolor{gray!35}{3.869} & \cellcolor{gray!35}{6.935} & \cellcolor{gray!35}{0.899} & \cellcolor{gray!35}{\textbf{1.173}} & \cellcolor{gray!35}{\textbf{1.189}} & \cellcolor{gray!35}{\textbf{1.128}} & \cellcolor{gray!35}{\textbf{6.475}} & \cellcolor{gray!35}{\textbf{5.105}} & \cellcolor{gray!35}{\textbf{9.732}} & \cellcolor{gray!35}{\textbf{1.188}}\\
+\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{0.914} & \cellcolor{gray!35}{0.925} & \cellcolor{gray!35}{0.825} & \cellcolor{gray!35}{4.863} & \cellcolor{gray!35}{0.899} & \cellcolor{gray!35}{\textbf{1.173}} & \cellcolor{gray!35}{\textbf{1.189}} & \cellcolor{gray!35}{\textbf{1.128}} & \cellcolor{gray!35}{\textbf{6.475}} & \cellcolor{gray!35}{\textbf{1.188}}\\
 \parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Fall, Next}}}
- & AR(1) & 1.056 & 1.071 & 0.904 & 5.08 & 4.581 & 6.653 & 0.977 & 1.494 & 1.514 & 1.367 & 7.944 & 6.368 & 11.43 & 1.368\\
- & AR(p) & 0.955 & 0.968 & 0.851 & 4.903 & 4.147 & 6.713 & 0.9 & 1.427 & 1.446 & 1.32 & 7.689 & 6.109 & 11.154 & 1.328\\
- & BVAR$^{3)}$ & 1.006 & 1.02 & 0.857 & 4.883 & 4.373 & 6.403 & 0.954 & 1.368 & 1.387 & 1.289 & 7.437 & 5.841 & 11.009 & 1.313\\
- & BVAR-Mix$^{3)}$ & 0.876 & 0.888 & \textbf{0.758} & 4.332 & \textbf{3.776} & 5.85 & 0.854 & 1.334 & 1.352 & 1.26 & 7.269 & 5.699 & 10.737 & 1.287\\
- & Direct$^{4)}$: AR(1) & 1.037 & 1.049 & 0.91 & 5.052 & 4.52 & 6.898 & 0.973 & 1.487 & 1.497 & 1.381 & 7.978 & 6.388 & 11.644 & 1.383\\
- & Direct$^{4)}$: AR(p) & 0.93 & 0.938 & 0.844 & 4.689 & 4.136 & 6.546 & 0.88 & 1.417 & 1.427 & 1.34 & 7.701 & 6.16 & 11.392 & 1.349\\
- & Direct$^{4)}$: AR-annual & 1.374 & 1.301 & 1.194 & 6.913 & 5.582 & 9.935 & 1.354 & 1.545 & 1.476 & 1.424 & 8.127 & 6.49 & 12.253 & 1.524\\
- & Direct$^{4)}$: ARX-annual & 1.129 & 1.06 & 0.976 & 5.613 & 4.588 & 8.054 & 1.093 & 1.569 & 1.49 & 1.381 & 7.969 & 6.417 & 11.578 & 1.523\\
- & Direct$^{4)}$: BVAR$^{3)}$ & 0.995 & 1.007 & 0.887 & 4.903 & 4.389 & 6.76 & 0.952 & 1.361 & 1.37 & 1.29 & 7.458 & 5.904 & 11.035 & 1.31\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 1.05 & NA & NA & NA & NA & NA & NA & 1.871\\
- & Direct$^{4)}$: BVAR-Mix$^{3)}$ & \textbf{0.857} & \textbf{0.866} & 0.771 & \textbf{4.215} & 3.86 & \textbf{5.766} & \textbf{0.851} & 1.338 & 1.346 & 1.27 & 7.428 & 5.735 & 11.058 & 1.286\\
-\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{0.93} & \cellcolor{gray!15}{0.943} & \cellcolor{gray!15}{0.817} & \cellcolor{gray!15}{4.644} & \cellcolor{gray!15}{4.055} & \cellcolor{gray!15}{6.27} & \cellcolor{gray!15}{0.896} & \cellcolor{gray!15}{1.286} & \cellcolor{gray!15}{1.304} & \cellcolor{gray!15}{1.213} & \cellcolor{gray!15}{7.011} & \cellcolor{gray!15}{5.509} & \cellcolor{gray!15}{10.394} & \cellcolor{gray!15}{1.242}\\
-\addlinespace\addlinespace
-\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{1.108} & \cellcolor{gray!35}{1.119} & \cellcolor{gray!35}{1.013} & \cellcolor{gray!35}{5.895} & \cellcolor{gray!35}{\textbf{4.741}} & \cellcolor{gray!35}{8.397} & \cellcolor{gray!35}{1.123} & \cellcolor{gray!35}{\textbf{1.25}} & \cellcolor{gray!35}{\textbf{1.271}} & \cellcolor{gray!35}{\textbf{1.204}} & \cellcolor{gray!35}{\textbf{6.878}} & \cellcolor{gray!35}{\textbf{5.481}} & \cellcolor{gray!35}{\textbf{10.366}} & \cellcolor{gray!35}{\textbf{1.267}}\\
+ & AR$^{3)}$ & 1.056 & 1.071 & 0.904 & 5.08 & 0.977 & 1.494 & 1.514 & 1.367 & 7.944 & 1.368\\
+ & AR($p$)$^{3)}$ & 0.955 & 0.968 & 0.851 & 4.903 & 0.9 & 1.427 & 1.446 & 1.32 & 7.689 & 1.328\\
+ & BVAR$^{4)}$ & 1.006 & 1.02 & 0.857 & 4.883 & 0.954 & 1.368 & 1.387 & 1.289 & 7.437 & 1.313\\
+ & BVAR-Mix$^{4)}$ & 0.876 & 0.888 & \textbf{0.758} & 4.332 & 0.854 & 1.334 & 1.352 & 1.26 & 7.269 & 1.287\\
+ & Direct$^{5)}$: AR$^{3)}$ & 1.037 & 1.049 & 0.91 & 5.052 & 0.973 & 1.487 & 1.497 & 1.381 & 7.978 & 1.383\\
+ & Direct$^{5)}$: AR($p$)$^{3)}$ & 0.93 & 0.938 & 0.844 & 4.689 & 0.88 & 1.417 & 1.427 & 1.34 & 7.701 & 1.349\\
+ & Direct$^{5)}$: AR-annual$^{3)}$ & 1.296 & 1.301 & 1.194 & 6.913 & 1.354 & 1.467 & 1.476 & 1.424 & 8.127 & 1.524\\
+ & Direct$^{5)}$: ARX-annual$^{3)}$ & 1.056 & 1.06 & 0.976 & 5.613 & 1.093 & 1.482 & 1.49 & 1.381 & 7.969 & 1.523\\
+ & Direct$^{5)}$: BVAR$^{4)}$ & 0.995 & 1.007 & 0.887 & 4.903 & 0.952 & 1.361 & 1.37 & 1.29 & 7.458 & 1.31\\
+ & Direct$^{5)}$: BVAR-CISS$^{4)}$ & -- & -- & -- & -- & 1.05 & -- & -- & -- & -- & 1.871\\
+ & Direct$^{5)}$: BVAR-Mix$^{4)}$ & \textbf{0.857} & \textbf{0.866} & 0.771 & \textbf{4.215} & \textbf{0.851} & 1.338 & 1.346 & 1.27 & 7.428 & 1.286\\
+\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{6)}$} & \cellcolor{gray!15}{0.93} & \cellcolor{gray!15}{0.943} & \cellcolor{gray!15}{0.817} & \cellcolor{gray!15}{4.644} & \cellcolor{gray!15}{0.896} & \cellcolor{gray!15}{1.286} & \cellcolor{gray!15}{1.304} & \cellcolor{gray!15}{1.213} & \cellcolor{gray!15}{7.011} & \cellcolor{gray!15}{1.242}\\
+\addlinespace
+\cellcolor{gray!35}{} & \cellcolor{gray!35}{IMF} & \cellcolor{gray!35}{1.108} & \cellcolor{gray!35}{1.119} & \cellcolor{gray!35}{1.013} & \cellcolor{gray!35}{5.895} & \cellcolor{gray!35}{1.123} & \cellcolor{gray!35}{\textbf{1.25}} & \cellcolor{gray!35}{\textbf{1.271}} & \cellcolor{gray!35}{\textbf{1.204}} & \cellcolor{gray!35}{\textbf{6.878}} & \cellcolor{gray!35}{\textbf{1.267}}\\
 \parbox[t]{2mm}{\multirow{13}{*}{\rotatebox[origin=c]{90}{\hspace{5mm}Spring, Next}}}
- & AR(1) & 1.377 & 1.396 & 1.142 & 6.349 & 5.952 & 7.923 & 1.195 & 1.769 & 1.791 & 1.587 & 9.22 & 7.521 & 13.037 & 1.6\\
- & AR(p) & 1.113 & 1.126 & 0.975 & 5.683 & 4.767 & 8.025 & 1.057 & 1.757 & 1.781 & 1.608 & 9.347 & 7.532 & 13.432 & 1.667\\
- & BVAR$^{3)}$ & 1.346 & 1.363 & 1.122 & 6.304 & 5.764 & 7.996 & 1.215 & 1.686 & 1.708 & 1.571 & 9.124 & 7.245 & 13.281 & 1.635\\
- & BVAR-Mix$^{3)}$ & 1.126 & 1.141 & 0.962 & 5.408 & 4.86 & 7.137 & 1.06 & 1.635 & 1.656 & 1.535 & 8.874 & 7.051 & 12.98 & 1.607\\
- & Direct$^{4)}$: AR(1) & 1.35 & 1.365 & 1.131 & 6.367 & 5.788 & 8.156 & 1.185 & 1.763 & 1.775 & 1.601 & 9.183 & 7.581 & 13.06 & 1.609\\
- & Direct$^{4)}$: AR(p) & \textbf{1.095} & \textbf{1.106} & 1.002 & 5.63 & 4.804 & 8.023 & 1.061 & 1.719 & 1.731 & 1.579 & 9.111 & 7.365 & 13.16 & 1.646\\
- & Direct$^{4)}$: AR-annual & 1.373 & 1.301 & 1.194 & 6.912 & 5.582 & 9.933 & 1.354 & 1.546 & 1.477 & 1.424 & 8.128 & 6.493 & 12.253 & 1.525\\
- & Direct$^{4)}$: ARX-annual & 1.323 & 1.245 & 1.155 & 6.68 & 5.362 & 9.694 & 1.319 & 1.496 & 1.404 & 1.33 & 7.611 & 6.114 & 11.307 & 1.418\\
- & Direct$^{4)}$: BVAR$^{3)}$ & 1.336 & 1.352 & 1.133 & 6.39 & 5.697 & 8.41 & 1.194 & 1.651 & 1.661 & 1.533 & 8.848 & 7.14 & 12.818 & 1.601\\
- & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 1.103 & NA & NA & NA & NA & NA & NA & 1.876\\
- & Direct$^{4)}$: BVAR-Mix$^{3)}$ & \textbf{1.095} & 1.107 & \textbf{0.942} & \textbf{5.254} & 4.804 & \textbf{6.82} & \textbf{1.02} & 1.611 & 1.62 & 1.501 & 8.729 & 6.942 & 12.659 & 1.575\\
-\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{5)}$} & \cellcolor{gray!15}{1.18} & \cellcolor{gray!15}{1.196} & \cellcolor{gray!15}{0.993} & \cellcolor{gray!15}{5.617} & \cellcolor{gray!15}{5.072} & \cellcolor{gray!15}{7.168} & \cellcolor{gray!15}{1.069} & \cellcolor{gray!15}{1.509} & \cellcolor{gray!15}{1.53} & \cellcolor{gray!15}{1.403} & \cellcolor{gray!15}{8.122} & \cellcolor{gray!15}{6.436} & \cellcolor{gray!15}{11.922} & \cellcolor{gray!15}{1.455}\\
+ & AR$^{3)}$ & 1.377 & 1.396 & 1.142 & 6.349 & 1.195 & 1.769 & 1.791 & 1.587 & 9.22 & 1.6\\
+ & AR($p$)$^{3)}$ & 1.113 & 1.126 & 0.975 & 5.683 & 1.057 & 1.757 & 1.781 & 1.608 & 9.347 & 1.667\\
+ & BVAR$^{4)}$ & 1.346 & 1.363 & 1.122 & 6.304 & 1.215 & 1.686 & 1.708 & 1.571 & 9.124 & 1.635\\
+ & BVAR-Mix$^{4)}$ & 1.126 & 1.141 & 0.962 & 5.408 & 1.06 & 1.635 & 1.656 & 1.535 & 8.874 & 1.607\\
+ & Direct$^{5)}$: AR$^{3)}$ & 1.35 & 1.365 & 1.131 & 6.367 & 1.185 & 1.763 & 1.775 & 1.601 & 9.183 & 1.609\\
+ & Direct$^{5)}$: AR($p$)$^{3)}$ & \textbf{1.095} & \textbf{1.106} & 1.002 & 5.63 & 1.061 & 1.719 & 1.731 & 1.579 & 9.111 & 1.646\\
+ & Direct$^{5)}$: AR-annual$^{3)}$ & 1.296 & 1.301 & 1.194 & 6.912 & 1.354 & 1.467 & 1.477 & 1.424 & 8.128 & 1.525\\
+ & Direct$^{5)}$: ARX-annual$^{3)}$ & 1.241 & 1.245 & 1.155 & 6.68 & 1.319 & 1.396 & 1.404 & 1.33 & 7.611 & 1.418\\
+ & Direct$^{5)}$: BVAR$^{4)}$ & 1.336 & 1.352 & 1.133 & 6.39 & 1.194 & 1.651 & 1.661 & 1.533 & 8.848 & 1.601\\
+ & Direct$^{5)}$: BVAR-CISS$^{4)}$ & -- & -- & -- & -- & 1.103 & -- & -- & -- & -- & 1.876\\
+ & Direct$^{5)}$: BVAR-Mix$^{4)}$ & \textbf{1.095} & 1.107 & \textbf{0.942} & \textbf{5.254} & \textbf{1.02} & 1.611 & 1.62 & 1.501 & 8.729 & 1.575\\
+\cellcolor{gray!15}{} & \cellcolor{gray!15}{Simple Ensemble$^{6)}$} & \cellcolor{gray!15}{1.18} & \cellcolor{gray!15}{1.196} & \cellcolor{gray!15}{0.993} & \cellcolor{gray!15}{5.617} & \cellcolor{gray!15}{1.069} & \cellcolor{gray!15}{1.509} & \cellcolor{gray!15}{1.53} & \cellcolor{gray!15}{1.403} & \cellcolor{gray!15}{8.122} & \cellcolor{gray!15}{1.455}\\
 \bottomrule

### 2025-10-15 miscellaneous/exploratory_scripts/DmTest_Options.Rmd
restructure I: move presentation plot files, analyses to own folder

---
title: "DM Test - Revision"
author: "Friederike Becker"
date: "2025-09-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(data.table)
library(sandwich)
library(DT)
.d <- `[`
```

*Internal discussion document - not polished*

## DM Test results

Show different results for the Diebold-Mariano panel test in R. We compare the results from test statistics $S^3$ and $\tilde{S}^3$ and additionally the effect of prewhitening for S3.

The test statistics $S^3$ and $\tilde{S}^3$ are based on Akgun et al (2024): *Equal predictive ability tests based on panel data with applications to OECD and IMF forecasts*. $S^3$ corresponds to the test statistic we've been using so far, while $\tilde{S}^3$  is also valid for small $T$ (uses the t-distribution) but assumes no serial correlation.

All results for test statistics, p-values and bandwidth are displayed with 5 decimal places.

## Code for DM - Test

This code is slightly adapted from Fabian's. It allows for different options in the NeweyWest-function and additionally calculates the test statistic needed for $\tilde{S}^3$.
```{r, dm_function}
dm_test <- function(loss1, loss2, lag = NULL, prewhite = TRUE, return_s3tilde = FALSE, df_corr = 1){

    #########################S3 (Fabians Code)###########################
    # make series of loss differences
    # loss1 is for model 1, loss2 is for model 2
    # smaller loss is better
    d <- loss1 - loss2
    # mean loss
    m <- mean(d)
    # variance estimated via Newey-West method
    # regression of d on intercept
    fit <- lm(d~1)
    # robust standard error
    s <- NeweyWest(fit, lag = lag, prewhite = prewhite) |> unname() |> sqrt() |> as.numeric()
    #s_var <- sqrt(sum(fit$residuals^2) / length(loss1))
    # t statistic
    # t > 0 indicates that model 2 is better
    # t < 0 indicates that model 1 is better
    t <- m/s
    # p-value (two-sided)
    p <- 2*pnorm(-abs(t))
    # lag length used by estimator
    k <- bwNeweyWest(fit, lag = lag, prewhite = prewhite)

    #########################S3-Tilde###########################
    #calculate variance estimate and t-stat for s3-tilde:
    std_var <- sum(fit$residuals^2) / (length(loss1) - df_corr)
    s_var <- sqrt(std_var / (length(loss1)))
    t_s3tilde <- m /s_var

    #########################Output###########################
    if(!return_s3tilde){
      list(t_stat = t, p_val = p, bandwidth = k, resids = fit$residuals) 
    } else {
      list(t_stat = t, p_val = p, bandwidth = k, t_s3tilde = t_s3tilde, resids = fit$residuals) 
    }
  }
```

```{r dm_code, echo=FALSE}

dm_test_highlevel <- function(lag = NULL, prewhite = TRUE, return_s3tilde = FALSE, df_corr = 1, get_acf = FALSE){
  # Diebold-Mariano test implementation, similar to function t_hac here:
  # https://github.com/FK83/forecastcalibration/blob/main/R/R_procs.R

  dm_dat <- vector(mode = "list", length = 24)

  dm_acf <- vector(mode = "list", length = 24)
  i <- 0

  combs_methods <- data.table::CJ(hr = c(0, 0.5, 1, 1.5),
                                  tgt = c("pcpi_pch", "ngdp_rpch"),
                                  model1 = c("IMF"),
                                  model2 = c("ar", "bvar_const", "bvar_const-direct"))

  for(i in 1:nrow(combs_methods)){
    curr_comb <- combs_methods[i,]
    curr_hr <- curr_comb[,"hr"] |> unname() |> unlist()
    curr_tgt <- curr_comb[,"tgt"] |> unname() |> unlist()
    curr_mod1 <-  curr_comb[,"model1"] |> unname() |> unlist()
    curr_mod2 <-  curr_comb[,"model2"] |> unname() |> unlist()

    ####SCORE EINLESEN ÄNDERN
    #loss_mod1 <- fread(here("scores", "extcis_crps_values_ho_byyr.csv")) |>
    loss_mod1 <- fread(here("scores", "ci_scores_byyr_ho.csv")) |>
      .d(horizon == curr_hr) |>
      .d(target == curr_tgt) |>
      .d(model == curr_mod1) |>
      .d(, "interval_score") |>
      #.d(, "score") |>
      unname() |> unlist()

    #loss_mod2 <- fread(here("scores", "extcis_crps_values_ho_byyr.csv"))## |>
    if(curr_mod2 == "bvar_const-direct"){
      filename <- "bvar_ci_scores_byyr_ho.csv"
      curr_mod2 <- "bvar_const" #type of model (direct / not direct) is governed by file name
      curr_mod2_new <- "bvar_const-direct"
    } else {
      filename <- "ci_scores_byyr_ho.csv"
      curr_mod2_new <- "bvar_const"
    }

    loss_mod2 <- fread(here("scores", filename)) |>
      .d(horizon == curr_hr) |>
      .d(target == curr_tgt) |>
      .d(model == curr_mod2)|>
      .d(, "interval_score") |>
      #.d(, "score") |>
      unname() |> unlist()

    if(curr_mod2_new == "bvar_const-direct"){
      curr_mod2 <- curr_mod2_new
    }

    dm_res <- dm_test(loss1 = loss_mod1, loss2 = loss_mod2, 
                      lag = lag, prewhite = prewhite,
                      return_s3tilde = return_s3tilde, df_corr = df_corr)

    dm_dat[[i]] <- data.table(model1 = curr_mod1,
                              model2 = curr_mod2,
                              horizon = curr_hr,
                              target = curr_tgt,
                              tstat = dm_res$t_stat,
                              p_val = dm_res$p_val,
                              bandwidth = dm_res$bandwidth,
                              t_s3tilde = dm_res$t_s3tilde)

    if(get_acf){
      dm_acf[[i]] <- vector(mode = "list", length = 2)
      dm_acf[[i]][[1]] <- acf(dm_res$resids, plot = FALSE)
      plottgt <- ifelse(curr_tgt == "pcpi_pch", "Inf.", "GDP")
      dm_acf[[i]][[2]] <- paste0(plottgt,", ", curr_mod2, ", hor. ", curr_hr) 
    }

  }

  dm_dat <- rbindlist(dm_dat)

  if(get_acf){
    return(dm_acf)
  } else {
    return(dm_dat)
  }
}
```

## Automatic lag choice and prewhitening 
This is the default option implemented in the NeweyWest-function, and the setting we have so far been using. It is obtained by running

```{r, eval = FALSE}
NeweyWest(fit)
```

We thereby get the following results

```{r, echo = FALSE}
dm_dat <- dm_test_highlevel()
datatable(
  dm_dat,
  options = list(
    pageLength = 20
    #columnDefs = list(list(width = '100px', targets = "_all")) # force fixed widths
  )
) |>
  formatRound(columns = c("tstat", "p_val", "bandwidth"), digits = 5)
```

With `r nrow(dm_dat |> .d(p_val < 0.05))` significant results, as before (since it's the same code that we've run so far).

```{r, echo = FALSE}
datatable(
  dm_dat |> .d(p_val < 0.05),
  options = list(
    pageLength = 20
  )
) |>
  formatRound(columns = c("tstat", "p_val", "bandwidth"), digits = 5)
```

## Automactic lag choice and no prewhitening

Here, we calculate the variance based on the raw residuals by running
```{r, eval = FALSE}
NeweyWest(fit, prewhite = FALSE)
```

```{r, echo = FALSE}
dm_dat <- dm_test_highlevel(prewhite = FALSE)
datatable(
  dm_dat,
  options = list(
    pageLength = 20
  )
) |>
  formatRound(columns = c("tstat", "p_val", "bandwidth"), digits = 5)
```

With `r nrow(dm_dat |> .d(p_val < 0.05))` significant results. Note the warnings above, which stem from the bandwidth parameters, which are in some cases very large.

```{r, echo = FALSE}
datatable(
  dm_dat |> .d(p_val < 0.05),
  options = list(
    pageLength = 20
  )
) |>
  formatRound(columns = c("tstat", "p_val", "bandwidth"), digits = 5)
```

## S3-Tilde
Compare to results obtained by calculating the variance only using lag = 0, based on the raw residuals, with significance determined by the t-distribution:
```{r, echo = FALSE}
dm_dat <- dm_test_highlevel(return_s3tilde = TRUE, df_corr = 1)
datatable(
  dm_dat |> .d(, .SD, .SDcols = c("model1", "model2", "horizon", "target", "tstat", "t_s3tilde")),
  options = list(
    pageLength = 20
  )
) |>
  formatRound(columns = c("tstat", "t_s3tilde"), digits = 5)
```

```{r, echo = FALSE}
tsig <- dm_dat |> 
  .d(t_s3tilde > qt(0.975, 10) | t_s3tilde < -qt(0.975, 10))
```
Based on the above, we get `r nrow(tsig)` significant results:
```{r, echo = FALSE}
datatable(
  tsig,
  options = list(
    pageLength = 20
  )
) |>
  formatRound(columns = c("tstat", "t_s3tilde"), digits = 5)
```

## Sanity Check: Lag choice = 0 and no prewhitening 
Side note (more of a sanity check). If we don't do prewhitening and set lag = 0 for $S^3$  *and* we don't do the degrees of freedom correction for $\tilde{S}^3$  (i.e. divide by T and not by T-1), the two test statistics do coincide: 
```{r, eval = FALSE}
NeweyWest(fit, lag = 0, prewhite = FALSE)
```

```{r, echo = FALSE}
dm_dat <- dm_test_highlevel(lag = 0, prewhite = FALSE, return_s3tilde = TRUE, df_corr = 0)
datatable(
  dm_dat |> .d(, .SD, .SDcols = c("model1", "model2", "horizon", "target", "tstat", "t_s3tilde")),
  options = list(
    pageLength = 20
  )
) |>
  formatRound(columns = c("tstat", "t_s3tilde"), digits = 5)
```

## Additional Info: ACF curves
Here, we show the autocorrelation of the demeaned loss differentials. The header displays the respective competing model and the forecast horizon.

```{r, echo = FALSE}
dm_acf <- dm_test_highlevel(get_acf = TRUE)
#par(mfrow = c(4, 6), cex.main = 0.85)

# Plot each acf object
#for (acf_obj in dm_acf) {
#  plot(acf_obj[[1]], main = acf_obj[[2]])
#}
```

### GDP

```{r, echo = FALSE}
par(mfrow = c(3, 4), cex.main = 0.85)
for (k in c(1:3, 7:9, 13:15, 19:21)) {
  plot(dm_acf[[k]][[1]], main = dm_acf[[k]][[2]])
}
```

### Inflation

```{r, echo = FALSE}
par(mfrow = c(3, 4), cex.main = 0.85)
for (k in c(4:6, 10:12, 16:18, 22:24)) {
  plot(dm_acf[[k]][[1]], main = dm_acf[[k]][[2]])
}
```

### 2025-10-15 miscellaneous/presentation/make_figures/mainplots_presentationversion/exctry_cvgplots.R

@@ -1,0 +1,176 @@
+library(data.table)
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(MetBrewer)
+library(patchwork)
+library(here)
+devtools::load_all()
+
+prefix <- "extcntry_"
+
+
+ciscores <- fread(here("scores", paste0(prefix, "ci_scores_ho.csv")))|>
+  .d(, c("model", "target", "country", "horizon", "coverage_50", "coverage_80"))
+
+
+ciscores2 <- fread(here("scores", paste0(prefix, "bvar_ci_scores_ho.csv"))) |>
+  .d(, c("model", "target", "country", "horizon", "coverage_50", "coverage_80")) |>
+  .d(, model := ifelse(model=="ar_annual", "Direct: AR-Annual", model))|>
+  .d(, model := ifelse(model=="arx_annual", "Direct: ARX-Annual", model)) |>
+  .d(, model := factor(model, levels = c("IMF", "Direct: AR-Annual", "Direct: ARX-Annual")))
+ciscores <- rbind(ciscores, ciscores2)|>
+  .d(, error_method := "absolute") |>
+  .d(, method := "rolling window")
+
+ciscores_avg <- fread(here("scores", paste0(prefix, "cvg_pooled_ho.csv"))) |>
+  .d(, c("model", "target", "coverage_50", "coverage_80"))
+ciscores_avg2 <- fread(here("scores", paste0(prefix, "bvar_cvg_pooled_ho.csv"))) |>
+  .d(, c("model", "target", "coverage_50", "coverage_80")) |>
+  .d(, model := ifelse(model=="ar_annual", "Direct: AR-Annual", model))|>
+  .d(, model := ifelse(model=="arx_annual", "Direct: ARX-Annual", model))|>
+  .d(, model := factor(model, levels = c("IMF", "Direct: AR-Annual", "Direct: ARX-Annual")))
+ciscores_avg <- rbind(ciscores_avg, ciscores_avg2) |>
+  .d(, error_method := "absolute") |>
+  .d(, method := "rolling window")
+
+
+scores_cvgshort <- fread(here("scores", paste0(prefix, "ci_scores_avgcnt_ho.csv"))) |>
+  .d(model %in% c("IMF")) ##|>
+#setnames("model", "source", skip_absent = TRUE)
+
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/mainplots_presentationversion/extcis_qucvgplot.R

@@ -1,0 +1,261 @@
+library(data.table)
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(MetBrewer)
+library(patchwork)
+devtools::load_all()
+
+prefix <- "extcis_"
+
+ciscores <- fread(here("scores", paste0(prefix, "cvg_pooled_ho.csv"))) |>
+  .d(model != "bvar") |> #filter out SV BVAR model (not used anymore)
+  .d(, c("model", "target", paste0("qucoverage_", c(seq(5,45, by = 5), seq(55,95, by = 5))))) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP Growth", "Inflation")) |>
+  .d(, model := gsub("_", "", model)) |>
+  melt(id.vars = c("model", "target"), variable.name = "lvl", value.name = "cvg") |>
+  .d(,lvl := as.numeric(substr(lvl, 12, 20)))
+
+ciscores2 <- fread(here("scores", paste0(prefix, "bvar_cvg_pooled_ho.csv"))) |>
+  .d(model != "bvar_qu") |> #filter out SV BVAR model (not used anymore)
+  .d(, c("model", "target", paste0("qucoverage_", c(seq(5,45, by = 5), seq(55,95, by = 5))))) |>
+  .d(, target := ifelse(target == "ngdp_rpch", "GDP Growth", "Inflation")) |>
+  .d(, model := gsub("_", "", model)) |>
+  .d(, model := paste0(model, "-direct")) |>
+  melt(id.vars = c("model", "target"), variable.name = "lvl", value.name = "cvg") |>
+  .d(,lvl := as.numeric(substr(lvl, 12, 20)))
+
+ciscores_perfect <- data.table(model = rep("nominal", 18),
+                               target = rep("GDP Growth", 18),
+                               lvl = c(seq(5,45, by = 5), seq(55,95, by = 5)),
+                               cvg = c(seq(5,45, by = 5), seq(55,95, by = 5))/100)
+
+ciscores_perfect <- rbind(ciscores_perfect,
+                          ciscores_perfect |>
+                            copy() |>
+                            .d(,target := "Inflation"))
+
+ciscores1 <- rbind(ciscores, ciscores_perfect) |>
+  .d(, lvl := lvl/100) |>
+  .d(, dev :=  cvg-lvl) |>
+  .d(, model := fifelse(model == "ar-direct", "Direct: AR",
+                        fifelse(model == "arannual-direct", "Direct: AR-annual",
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/mainplots_presentationversion/plot_ci_lengths.R

@@ -1,0 +1,118 @@
+library(here)
+library(data.table)
+library(ggplot2)
+library(MetBrewer)
+devtools::load_all()
+
+source(here("specs", "specs.R"))
+
+.d <- `[`
+
+global_file_prefix <- ""
+
+
+imf_fc <- fread(here("quantile_forecasts", paste0("quantile_forecasts_ho", ".csv"))) |>
+  .d(source == "IMF") |>
+  .d(error_method == "absolute") |>
+  .d(method == "rolling window") |>
+  .d(quantile %in% c(0.1, 0.25, 0.75, 0.9)) |>
+  .d(, quantile := paste0("q", quantile)) |>
+  .d(, .(country, target, target_year, horizon, quantile, prediction)) |>
+  dcast(country + target + target_year + horizon ~ quantile) |>
+  .d(, cil5 := q0.75-q0.25) |>
+  .d(, cil9 := q0.9 - q0.1) |>
+  .d(, meancil5 := round(mean(cil5),10), by = c("horizon", "target")) |>
+  .d(, meancil9 := round(mean(cil9),10), by = c("horizon", "target")) |>
+  .d(, .(target, horizon, meancil5, meancil9)) |>
+  unique() |>
+  #.d(, target := factor(ifelse(target == "pcpi_pch", "Inflation", "GDP Growth")),)
+  .d(, target := factor(target,
+                        levels = c("pcpi_pch", "ngdp_rpch"),
+                        labels = c("I: Inflation", "G: GDP Growth"),
+                        ordered = "TRUE") )
+
+baseval <- 0
+
+imf_fc <- imf_fc |>
+  .d(, q0.1 := baseval -meancil9/2) |>
+  .d(, q0.25 := baseval -meancil5/2) |>
+  .d(, q0.75 := baseval + meancil5/2) |>
+  .d(, q0.9 := baseval + meancil9/2) |>
+  .d(, .(target, horizon, q0.1, q0.25, q0.75, q0.9)) #|>
+  #melt(id.vars = c("target", "horizon"), value.name = "prediction", variable.name = "quantile")
+
+imf_fc$target_year <- factor(rep(1:4, 2),
+                             levels = 1:4,
+                             labels = c("Fall, Current", "Spring, Current",
+                             "Fall, Next", "Spring, Next"),
+                            ordered = TRUE)
+
+#imf_fc$target_year <- rep(1:4, times = 2)
+
+
+
+qu_lvlss <- function(lvls){
+
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/mainplots_presentationversion/visualize_quantileextraction.R

@@ -1,0 +1,156 @@
+library(ggplot2)
+library(MetBrewer)
+library(data.table)
+library(gghighlight)
+library(here)
+devtools::load_all()
+
+.d <- `[`
+
+set.seed(2922)
+w <- 11
+labelvec <- c("raw error\nvalues, from\n previous 11 years", "error values,\nabsolute transformed", "6th and 9th largest\nvalue highlighted", "predictive distribution,\nconstructed around\n a point forecast of zero")
+
+errors <- rnorm(w) |> sort()
+errors <- errors * (-1)
+errors[1] <- 2.49
+abs_errors <- errors |> abs() ##|> sort()
+
+##make data
+errordat <- data.frame(
+  type = rep(1, w),
+  value = errors,
+  col = 1:11
+)
+errordat_abs_before <- data.frame(
+  type = rep(2, w),
+  value = abs_errors,
+  col = 1:11
+)
+errordat_abs <- data.frame(
+  type = rep(3, w),
+  value = abs_errors,
+  col = 1:11
+)
+errordat_extra <- data.frame(
+  type = rep(4, w),
+  value = NA,
+  col = 1:11
+)
+
+
+
+errordat <- rbind(errordat, errordat_abs) |>
+  rbind(errordat_abs_before) |>
+  rbind(errordat_extra) |>
+  setDT() |>
+  .d(, value := ifelse(type == 3, value, value + 1e-09))
+
+val80 <- quantile(abs_errors, 0.8)
+val50 <- quantile(abs_errors, 0.5)
+
+linerangedat <- data.frame(
+  type = rep(c(1, 2, 4), each = 1),
+  upper80 = c(0, 0, val80),
+  lower80 = c(0, 0, -val80),
+  upper50 = c(0, 0, val50),
+  lower50 = c(0, 0, -val50)
+) |>
+  setDT()
+
+pointdat <- data.frame(
+  type = rep(c(1, 2,4), each = 1),
+  pointval = c(NA, NA, 0))|>
+  setDT()
+
+
+#Define segment function
+geom_segment_hor <- function(x, y, xend, yend = y,
+                    lineend = "butt", linejoin = "round",
+                    color = "grey80", alpha = 0.8,
+                    linetype = "dashed", size = 0.25,
+                    arrow = NULL) {
+  geom_segment(
+    aes(x = x, y = y, xend = xend, yend = yend),
+    lineend = lineend, linejoin = linejoin,
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/mainplots_presentationversion/wis_plots.R

@@ -1,0 +1,66 @@
+source(here("R", "plot.R"))
+
+wis_plot_paper <- function(dataset_suffix,
+                           chosen_target,
+                           prefix,
+                           cscale = "Hokusai3"){
+
+
+  ######## WIS Data
+  #scores <- fread(here("scores", "ci_scores_pava.csv"))
+
+  if(nchar(dataset_suffix) > 0){
+
+    dataset_suffix <- paste0("_", dataset_suffix)
+  }
+
+  if (dataset_suffix == "_directional"){
+
+    bvar_dataset_suffix <- ""
+  } else {
+
+    bvar_dataset_suffix <- dataset_suffix
+  }
+
+  wis_scores <- fread(here("scores", paste0(global_file_prefix, "ci_scores_avgcnt", dataset_suffix, ".csv"))) |>
+    data.table::copy() |>
+    .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+    setnames("model", "source") |>
+    .d(source %in% c("IMF", "bvar_mix", "mean_ensemble"))
+
+
+  bvar_wis_scores <- fread(here("scores", paste0(global_file_prefix, "bvar_ci_scores_avgcnt", bvar_dataset_suffix, ".csv"))) |>
+    data.table::copy() |>
+    .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
+    .d(model %in% c("ar", "bvar_mix", "arx_annual")) |>
+    .d(, model := paste0(model, "-direct")) |>
+    setnames("model", "source") |>
+    .d(,error_method := unique(wis_scores$error_method)) |>
+    .d(,method := unique(wis_scores$method))
+
+
+  wis_scores <- rbind(wis_scores, bvar_wis_scores) |>
+    .d(, source := factor(source, levels = c("IMF", "bvar_mix", "bvar_mix-direct", "ar-direct", "arx_annual-direct", "mean_ensemble"),
+                          label = c("IMF", "BVAR-Mix", "BVAR-Mix - direct", "AR - direct", "AR-X", "Ensemble")))
+
+  colors_manual <- met.brewer(cscale, 4)[1]
+  colors_manual2 <- met.brewer("Hokusai2", 5)
+  colors_manual <- c(colors_manual, colors_manual2)
+  names(colors_manual) <- unique(wis_scores$source)
+
+
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/master_makeplots_presentation.R

@@ -1,0 +1,47 @@
+library(data.table)
+library(here)
+library(ggplot2)
+library(patchwork)
+library(MetBrewer)
+library(tidyverse)
+devtools::load_all()
+.d <- `[`
+
+#load plot files
+source(here("manuscript_plots", "wis_plots.R"))
+source(here("manuscript_plots", "presentation_coverage_plots.R"))
+
+#oecd truth version or "normal" (imf) truth
+#global_file_prefix <- "oecd_"
+global_file_prefix <- ""
+
+
+splits <- c("ho")
+chosen_targets <- c("ngdp_rpch", "pcpi_pch")
+
+all_plotcombs <- expand.grid(
+  dataset_suffix = splits,
+  chosen_target = chosen_targets
+)
+
+for(m in 1:nrow(all_plotcombs)){
+
+  current_comb <- all_plotcombs[m,]
+
+  dataset_suffix <- as.character(current_comb$dataset_suffix)
+  chosen_target <- as.character(current_comb$chosen_target)
+
+  wis_plot <- wis_plot_paper(dataset_suffix = dataset_suffix,
+                             chosen_target = chosen_target)
+  cvg_plot <- coverage_plot_paper(dataset_suffix = dataset_suffix,
+                                  chosen_target = chosen_target)
+
+  dataset_suffix <- ifelse(nchar(dataset_suffix) > 0, paste0("_", dataset_suffix), dataset_suffix)
+  ggplot2::ggsave(here(paste0(global_file_prefix, "ext_wis_", chosen_target, dataset_suffix, ".pdf")),
+                  wis_plot, width = 11, height = 7)
+  ggplot2::ggsave(here(paste0(global_file_prefix, "coverage_", chosen_target,dataset_suffix,".pdf")),
+                  cvg_plot, width = 5.2, height = 4)
+
+  #source(here("manuscript-plots", "coverage_plots.R"))
+}
+

### 2025-10-15 miscellaneous/presentation/make_figures/presentation_coverage_plots.R

@@ -1,0 +1,95 @@
+coverage_plot_paper <- function(dataset_suffix,
+                                chosen_target,
+                                cscale = "Hokusai3"){
+
+  if(nchar(dataset_suffix) > 0){
+
+    dataset_suffix <- paste0("_", dataset_suffix)
+  }
+
+  if (dataset_suffix == "_directional"){
+
+    bvar_dataset_suffix <- ""
+  } else {
+
+    bvar_dataset_suffix <- dataset_suffix
+  }
+
+  ####Read and filter coverage data
+  #Scores by average country
+  scores_cvgshort <- fread(here("scores", paste0(global_file_prefix, "ci_scores_avgcnt", dataset_suffix, ".csv"))) |>
+    .d(model %in% c("IMF", "ar", "bvar_const")) ##|>
+  #setnames("model", "source", skip_absent = TRUE)
+
+  bvar_scores_cvgshort <- fread(here("scores", paste0(global_file_prefix, "bvar_ci_scores_avgcnt", bvar_dataset_suffix, ".csv"))) |>
+    #setnames("model", "source", skip_absent = TRUE) |>
+    .d(model == "bvar_const") |>
+    .d(, model := "bvar_const-direct") |>
+    .d(,error_method := unique(scores_cvgshort$error_method)) |>
+    .d(,method := unique(scores_cvgshort$method))
+
+  scores_cvgshort <- rbind(scores_cvgshort, bvar_scores_cvgshort) |>
+    #setnames("model", "source", skip_absent = TRUE) |>
+    .d(target == chosen_target) |>
+    .d(, model := factor(model, levels = c("IMF", "bvar_const", "bvar_const-direct", "ar"),
+                         label = c("IMF", "BVAR", "BVAR - direct", "AR"),
+                         ordered = TRUE))
+
+
+
+  scores_cvgaggregate <- fread(here("scores", paste0(global_file_prefix, "cvg_pooled", dataset_suffix, ".csv"))) |>
+    .d(model %in% c("IMF", "ar", "bvar_const")) |>
+    rbind(fread(here("scores", paste0(global_file_prefix, "bvar_cvg_pooled", bvar_dataset_suffix, ".csv"))) |>
+            .d(,error_method := unique(scores_cvgshort$error_method)) |>
+            .d(,method := unique(scores_cvgshort$method)) |>
+            .d(model == "bvar_const") |>
+            .d(, model := "bvar_const-direct")) |>
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/progressionplots_quantileextraction/quantileextraction0.R

@@ -1,0 +1,9 @@
+library(ggplot2)
+
+# Create a blank plot
+p <- ggplot() + theme_void()
+
+# Save to PDF with desired size (in inches)
+ggsave(here("miscellaneous", "presentation", "make_figures", "progressionplots_quantileextraction", "illustration_pava_0.pdf"), plot = p,width = 10, height = 5)
+
+#ggsave("illustration_quantileextraction_0.pdf", plot = p,width = 8, height = 3.75)

### 2025-10-15 miscellaneous/presentation/make_figures/progressionplots_quantileextraction/quantileextraction1.R

@@ -1,0 +1,131 @@
+library(ggplot2)
+library(MetBrewer)
+library(data.table)
+library(gghighlight)
+library(here)
+devtools::load_all()
+
+.d <- `[`
+
+set.seed(2922)
+w <- 11
+labelvec <- c("error values,\nprevious 11 years")
+
+errors <- rnorm(w) |> sort()
+errors <- errors * (-1)
+errors[1] <- 2.49
+abs_errors <- errors |> abs() ##|> sort()
+
+##make data
+errordat <- data.frame(
+  type = rep(1, w),
+  value = errors,
+  col = 1:11
+)
+errordat_abs_before <- data.frame(
+  type = rep(2, w),
+  value = NA,
+  col = 1:11
+)
+errordat_abs <- data.frame(
+  type = rep(3, w),
+  value = NA,
+  col = 1:11
+)
+errordat_extra <- data.frame(
+  type = rep(4, w),
+  value = NA,
+  col = 1:11
+)
+
+q50 <- quantile(abs_errors, 0.5)
+q80 <- quantile(abs_errors, 0.8)
+
+lrcols <- met.brewer("Hokusai2", 2)
+
+errordat <- rbind(errordat, errordat_abs) |>
+  rbind(errordat_abs_before) |>
+  rbind(errordat_extra) |>
+  setDT() |>
+  .d(, color := ifelse(type == 3 & value == q50, lrcols[1],
+                       ifelse(type == 3 & value == q80, lrcols[2], "grey70")))
+  #.d(, value := ifelse(type == 3, value, value + 1e-09))
+
+val80 <- quantile(abs_errors, 0.8)
+val50 <- quantile(abs_errors, 0.5)
+
+linerangedat <- data.frame(
+  type = rep(c(1, 2, 4), each = 1),
+  upper80 = c(0, 0, val80),
+  lower80 = c(0, 0, -val80),
+  upper50 = c(0, 0, val50),
+  lower50 = c(0, 0, -val50)
+) |>
+  setDT()
+
+pointdat <- data.frame(
+  type = rep(c(1, 2,4), each = 1),
+  pointval = c(NA, NA, 0))|>
+  setDT()
+
+
+#Define segment function
+geom_segment_hor <- function(x, y, xend, yend = y,
+                             lineend = "butt", linejoin = "round",
+                             color = "grey80", alpha = 0.8,
+                             linetype = "dashed", size = 0.25,
+                             arrow = NULL) {
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/progressionplots_quantileextraction/quantileextraction2.R

@@ -1,0 +1,132 @@
+library(ggplot2)
+library(MetBrewer)
+library(data.table)
+library(gghighlight)
+library(here)
+devtools::load_all()
+
+.d <- `[`
+
+set.seed(2922)
+w <- 11
+labelvec <- c("error values,\nprevious 11 years", "absolute transformed\nerror values")
+
+errors <- rnorm(w) |> sort()
+errors <- errors * (-1)
+errors[1] <- 2.49
+abs_errors <- errors |> abs() ##|> sort()
+
+##make data
+errordat <- data.frame(
+  type = rep(1, w),
+  value = errors,
+  col = 1:11
+)
+errordat_abs_before <- data.frame(
+  type = rep(2, w),
+  value = abs_errors,
+  col = 1:11
+)
+errordat_abs <- data.frame(
+  type = rep(3, w),
+  value = NA,
+  col = 1:11
+)
+errordat_extra <- data.frame(
+  type = rep(4, w),
+  value = NA,
+  col = 1:11
+)
+
+q50 <- quantile(abs_errors, 0.5)
+q80 <- quantile(abs_errors, 0.8)
+
+lrcols <- met.brewer("Hokusai2", 2)
+
+errordat <- rbind(errordat, errordat_abs) |>
+  rbind(errordat_abs_before) |>
+  rbind(errordat_extra) |>
+  setDT() |>
+  .d(, color := ifelse(type == 3 & value == q50, lrcols[1],
+                       ifelse(type == 3 & value == q80, lrcols[2], "grey70")))
+#.d(, value := ifelse(type == 3, value, value + 1e-09))
+
+val80 <- quantile(abs_errors, 0.8)
+val50 <- quantile(abs_errors, 0.5)
+
+linerangedat <- data.frame(
+  type = rep(c(1, 2, 4), each = 1),
+  upper80 = c(0, 0, val80),
+  lower80 = c(0, 0, -val80),
+  upper50 = c(0, 0, val50),
+  lower50 = c(0, 0, -val50)
+) |>
+  setDT()
+
+pointdat <- data.frame(
+  type = rep(c(1, 2,4), each = 1),
+  pointval = c(NA, NA, 0))|>
+  setDT()
+
+
+#Define segment function
+geom_segment_hor <- function(x, y, xend, yend = y,
+                             lineend = "butt", linejoin = "round",
+                             color = "grey80", alpha = 0.8,
+                             linetype = "dashed", size = 0.25,
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/progressionplots_quantileextraction/quantileextraction3.R

@@ -1,0 +1,134 @@
+library(ggplot2)
+library(MetBrewer)
+library(data.table)
+library(gghighlight)
+library(here)
+devtools::load_all()
+
+.d <- `[`
+
+set.seed(2922)
+w <- 11
+labelvec <- c("error values,\nprevious 11 years", "absolute transformed\nerror values", "6th and 9th\nlargest value")
+
+errors <- rnorm(w) |> sort()
+errors <- errors * (-1)
+errors[1] <- 2.49
+abs_errors <- errors |> abs() ##|> sort()
+
+##make data
+errordat <- data.frame(
+  type = rep(1, w),
+  value = errors,
+  col = 1:11
+)
+errordat_abs_before <- data.frame(
+  type = rep(2, w),
+  value = abs_errors,
+  col = 1:11
+)
+errordat_abs <- data.frame(
+  type = rep(3, w),
+  value = abs_errors,
+  col = 1:11
+)
+errordat_extra <- data.frame(
+  type = rep(4, w),
+  value = NA,
+  col = 1:11
+)
+
+q50 <- quantile(abs_errors, 0.5)
+q80 <- quantile(abs_errors, 0.8)
+
+lrcols <- met.brewer("Hokusai2", 2)
+
+errordat <- rbind(errordat, errordat_abs) |>
+  rbind(errordat_abs_before) |>
+  rbind(errordat_extra) |>
+  setDT() |>
+  .d(, color := ifelse(type == 3 & value == q50, lrcols[1],
+                       ifelse(type == 3 & value == q80, lrcols[2], "grey70")))
+#.d(, value := ifelse(type == 3, value, value + 1e-09))
+
+val80 <- quantile(abs_errors, 0.8)
+val50 <- quantile(abs_errors, 0.5)
+
+linerangedat <- data.frame(
+  type = rep(c(1, 2, 4), each = 1),
+  upper80 = c(0, 0, val80),
+  lower80 = c(0, 0, -val80),
+  upper50 = c(0, 0, val50),
+  lower50 = c(0, 0, -val50)
+) |>
+  setDT()
+
+pointdat <- data.frame(
+  type = rep(c(1, 2,4), each = 1),
+  pointval = c(NA, NA, 0))|>
+  setDT()
+
+
+#Define segment function
+geom_segment_hor <- function(x, y, xend, yend = y,
+                             lineend = "butt", linejoin = "round",
+                             color = "grey80", alpha = 0.8,
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/progressionplots_quantileextraction/quantileextraction4.R

@@ -1,0 +1,161 @@
+library(ggplot2)
+library(MetBrewer)
+library(data.table)
+library(gghighlight)
+library(here)
+devtools::load_all()
+
+.d <- `[`
+
+set.seed(2922)
+w <- 11
+labelvec <- c("error values,\nprevious 11 years", "absolute transformed\nerror values", "6th and 9th\nlargest value", "predictive\ndistribution")
+
+errors <- rnorm(w) |> sort()
+errors <- errors * (-1)
+errors[1] <- 2.49
+abs_errors <- errors |> abs() ##|> sort()
+
+##make data
+errordat <- data.frame(
+  type = rep(1, w),
+  value = errors,
+  col = 1:11
+)
+errordat_abs_before <- data.frame(
+  type = rep(2, w),
+  value = abs_errors,
+  col = 1:11
+)
+errordat_abs <- data.frame(
+  type = rep(3, w),
+  value = abs_errors,
+  col = 1:11
+)
+errordat_extra <- data.frame(
+  type = rep(4, w),
+  value = NA,
+  col = 1:11
+)
+
+q50 <- quantile(abs_errors, 0.5)
+q80 <- quantile(abs_errors, 0.8)
+
+lrcols <- met.brewer("Hokusai2", 2)
+
+errordat <- rbind(errordat, errordat_abs) |>
+  rbind(errordat_abs_before) |>
+  rbind(errordat_extra) |>
+  setDT() |>
+  .d(, color := ifelse(type == 3 & value == q50, lrcols[2],
+                       ifelse(type == 3 & value == q80, lrcols[1], "grey70")))
+#.d(, value := ifelse(type == 3, value, value + 1e-09))
+
+val80 <- quantile(abs_errors, 0.8)
+val50 <- quantile(abs_errors, 0.5)
+
+linerangedat <- data.frame(
+  type = rep(c(1, 2, 4), each = 1),
+  upper80 = c(0, 0, val80),
+  lower80 = c(0, 0, -val80),
+  upper50 = c(0, 0, val50),
+  lower50 = c(0, 0, -val50)
+) |>
+  setDT()
+
+pointdat <- data.frame(
+  type = rep(c(1, 2,4), each = 1),
+  pointval = c(NA, NA, 0))|>
+  setDT()
+
+
+#Define segment function
+geom_segment_hor <- function(x, y, xend, yend = y,
+                             lineend = "butt", linejoin = "round",
+                             color = "grey80", alpha = 0.8,
[…]

### 2025-10-15 miscellaneous/presentation/make_figures/plot_ci_lengths_germany2023.R
update to new file naming

@@ -1,5 +1,6 @@
 library(here)
 library(data.table)
+library(MetBrewer)
 devtools::load_all()
 
 source(here("specs", "specs.R"))
@@ -12,7 +13,7 @@ score_min_year <- specs$score_min_year
 tv_release <- specs$tv_release
 window_length <- specs$window_length
 
-imf_fc <- fread(here("quantile_forecasts", "quantile_forecasts_pava.csv")) |>
+imf_fc <- fread(here("quantile_forecasts", "quantile_forecasts_ho.csv")) |>
   .d(target_year == 2023) |>
   .d(source == "IMF") |>
   .d(target == "ngdp_rpch") |>
@@ -107,7 +108,8 @@ if(FALSE){
 }
 
 
-pdf(file = here("presentation", "figures", "horizon_uncc_germany2023_current.pdf"), width = 5, height = 3.35)
+#pdf(file = here("presentation", "figures", "horizon_uncc_germany2023_current.pdf"), width = 5, height = 3.35)
+pdf(file = here("horizon_uncc_germany2023_current.pdf"), width = 5, height = 3.35)
 ggplot(aes(x = target_year, group = target, color = target), data = imf_fc) +
   geom_linerange(
     aes(x = target_year,
